### 2013-10-11 docs/paper/paper.tex
paper work

% v2-acmsmall-sample.tex, dated March 6 2012
% This is a sample file for ACM small trim journals
%
% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
% (c) 2010 Association for Computing Machinery (ACM)
%
% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
% Users can also go through the FAQs available on the journal's submission webpage.
%
% Steps to compile: latex, bibtex, latex latex
%
% For tracking purposes => this is v1.3 - March 2012

\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax

% Package to generate and customize Algorithm as per ACM style
\usepackage[ruled]{algorithm2e}
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

% Metadata Information

\def\@acmVolume{0} %the volume
\def\@acmNumber{0} %the number
\def\@acmArticle{0} %article number
\def\@articleSeq{0} %article Sequence
\def\@acmPrice{0} %article price  % Changed to 15 - June 2012 - Gerry
\def\@acmYear{2013} %the last two digits of the year, 
\def\@acmMonth{12}  %the month
\def\@journalName{COMPUTER AND NETWORK SYSTEM ADMINISTRATION} %the name of the ACM journal
\def\@journalNameShort{CNT 5605} %the acronym of the ACM journal 
\def\@journalCode{jn} %the code of the ACM journal 
\def\@permissionCodeOne{0000-0000} %the permission code of the ACM journal
\def\@doi{0000000.0000000} % These 'default' '0' values are over-ridden, during production, with 'correct' numbers entered via source .tex file - Gerry March 2012

% Document starts
\begin{document}

% Page heads
% \markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}

% Title portion
\title{The Incredible Mutating Test Files! Smart Mutation for Binary Fuzzing}
\author{Clark Wood
\affil{Florida State University}
% NOTE! Affiliations placed here should be for the institution where the
%       BULK of the research was done. If the author has gone to a new
%       institution, before publication, the (above) affiliation should NOT be changed.
%       The authors 'current' address may be given in the "Author's addresses:" block (below).
%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
%       currently affiliated with NASA.
}

\category{CNT 5605}{Fall 2013}{Dynamic Taint Analysis, Mutation, Fuzzing}

\acmformat{Clark Wood, Paper CNT 5605}
% At a minimum you need to supply the author names, year and a title.
% IMPORTANT:
% Full first names whenever they are known, surname last, followed by a period.
% In the case of two authors, 'and' is placed between them.
% In the case of three or more authors, the serial comma is used, that is, all author names
% except the last one but including the penultimate author's name are followed by a comma,
% and then 'and' is placed before the final author's name.
% If only first and middle initials are known, then each initial
% is followed by a period and they are separated by a space.
% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.

\maketitle

\section{Fuzzing Overview}

white/black/graybox, mutation/generation, Dynamic Taint Analysis,

As programs grow larger, so do the test suites designed to exercise execution paths within the program. White box approaches have the advantage of source code, allowing developers to write test cases which exercise paths in a higher level language. With black box approaches, however, test cases would typically target assembly block-level code paths [A,...NEEDED].

\subsection{Dynamic Taint Analysis}

Dynamic taint analysis (DTA) is the process of locating sources of taint and following their propagation through a binary to data sinks. Since, for exploitation, bugs must be triggered by user input, DTA usually identifies all user input (files, command line arguments, UI interactions, ...) as tainted, and marks it accordingly.

The granularity of taint marking is variable. Assigning everything from a generic binary value of tainted/not tainted to bit-level marking of which part of user input affected which variable is conceivable, although finer-grained taint analysis is more computationally expensive and difficult to determine [CITE]. Consider the following pseudocode:
\begin{verbatim} 
x = userInput & 1
if x % 2 == 0:
	vuln()				
\end{verbatim}

TODO
Taint can propagate via explicit or implicit flows (Figure 1). Explicit flows involve a tainted variable, x, which is used in an assignment expression to compute a new variable, y. In this situation, x taints y, and if y is involved in any further assignment to a variable z, then x taints z by transitivity. In contrast, implicit data flows ... [D].

Because of subtle implicit flow cases referenced by Clause, J. et all [D], which can be difficult to spot (Page 2, Figure 2b). Implicit data flows are not always considered by dynamic tainting techniques [E].

\begin{verbatim}
# Explicit taint

# Implicit taint
\end{verbatim}

Propagation

\section{Dynamic Binary Instrumentation with Intel PIN}

Pintools

\section{Ways to mutate test cases}

Machine learning in lieu of symbolic execution?

\section{Implementation}

	\subsection{Pintools for Finding Vulnerable Conditions}

	\subsection{Mutation Algorithm}

Fuzzing optimization techniques are evolving to deal with the path explosion problem [CITES] in various ways, focusing on ...

Researchers at VUPEN Security mention the value of discovering test case sets of equivalent coverage, but smaller size, via test suite reduction algorithms [A].

\section{Future Work}

\section{References}

[A] Bekrar, Sofia, et al. "A taint based approach for smart fuzzing." Software Testing, Verification and Validation (ICST), 2012 IEEE Fifth International Conference on. IEEE, 2012.
[B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with
Evolutionary Fuzzing", BlackHat and Defcon 2007.
[C] Schwartz, E.J., Avgerinos, T., Brumley, D. "All You Ever Wanted to Know About Dynamic Taint Analysis and Forward Symbolic Execution (but might have been afraid to ask)." 2010 IEEE Symposium on Security and Privacy.
[D] Clause, J. Li, W., Orso, A. "Dytan: a generic dynamic taint analysis framework". 2007 Int'l symposium on Software testing and analysis. ACM, 2007.
[E] ... "Beyond Instruction Level Taint Propagation".

\end{document}

% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM

### 2013-10-14 docs/paper/paper.tex
added paper and paragraph

@@
 
+\section{Machine Learning}
+While research has applied machine learning techniques to successfully extrapolate vulnerability patterns, previous efforts have required source code and training examples containing known vulnerabilities to drive learning [F].
+In contrast, we implement ...
+
 \section{Dynamic Binary Instrumentation with Intel PIN}
@@
 [E] ... "Beyond Instruction Level Taint Propagation".
+[F] Yamaguchi, Fabian, Felix Lindner, and Konrad Rieck.
+"Vulnerability extrapolation: assisted discovery of vulnerabilities using machine learning." Proceedings of the 5th USENIX conference on Offensive technologies.
+USENIX Association, 2011.
 

### 2013-10-19 docs/paper/paper.tex

@@
 TODO
-Taint can propagate via explicit or implicit flows (Figure 1).
+Taint can propagate via explicit or implicit flows (Figure 1), sometimes also called data and control dependencies respectively [G].
 Explicit flows involve a tainted variable, x, which is used in an assignment expression to compute a new variable, y.
 In this situation, x taints y, and if y is involved in any further assignment to a variable z, then x taints z by transitivity.
-In contrast, implicit data flows ...
-[D].
+In contrast, implicit data flows involve a tainted variable used to affect control flow within a program which subsequently sets the value of another variable, for instance at a branch [D].
 
@@
 Implicit data flows are not always considered by dynamic tainting techniques [E].
+
+This is a problem BECAUSE TODO
 
@@
 USENIX Association, 2011.
+[G] Bao, Tao, et al. "Strict control dependence and its effect on dynamic information flow analyses." Proceedings of the 19th international symposium on Software testing and analysis. ACM, 2010.
 

### 2013-10-19 MyPinTool/FollowExecution.h
follows control paths

@@ -1,4 +1,5 @@
 // FollowExecution.h
+
 /* ===================================================================== */
 /* Control Flow following functions, currently at bbl level */
 /* ===================================================================== */
@@ -25,6 +26,11 @@ typedef struct
 
 ControlFlowStruct ControlFlow;
 
+// Returns starting address for given trace.
+ADDRINT GetTraceStart(TRACE trace)
+{
+    return TRACE_Address(trace);
+}
 
 // Follow each instruction in each bbl of each trace.
 // basic block is single entrace, single exit block of sequential instructions.
@@ -35,7 +41,9 @@ VOID FollowTraces(TRACE trace, VOID *v)
         return;
     }
 
-    ControlFlowFile << "START: " << TRACE_Address(trace) << endl;
+    ControlFlowFile << GetTraceStart(trace) << endl;
+
+    /*
     // For each basic block, track each instruction
     for (BBL bbl = TRACE_BblHead(trace); BBL_Valid(bbl); bbl = BBL_Next(bbl)) {
         for (INS ins = BBL_InsHead(bbl); INS_Valid(ins); ins = INS_Next(ins) ) {
@@ -51,4 +59,9 @@ VOID FollowTraces(TRACE trace, VOID *v)
 
         }
     }
+    */
+
 } // End FollowTraces
+
+// End FollowExecution.h
+

### 2013-10-19 MyPinTool/MyPinTool.cpp

@@ -31,10 +31,11 @@ END_LEGAL */
 
 #include "pin.H"
 #include <asm/unistd.h>
-#include <iostream>
 #include <fstream>
-#include <string>
+#include <functional> // for hashes
+#include <iostream>
 #include <list>
+#include <string>
 #include <unordered_map>
 using namespace std;
 
@@ -171,6 +172,7 @@ VOID Fini(INT32 code, VOID *v)
 {
     TraceFile.close();
     TaintFile.close();
+    FiniFollowExecution();
 }
 
 /* ===================================================================== */
@@ -198,6 +200,8 @@ int main(int argc, char *argv[])
     }
     
     // Write to a file since cout and cerr maybe closed by the application
+    InitFollowExecution();
+
     TraceFile.open(KnobOutputFile.Value().c_str());
     TraceFile << hex;
     TraceFile.setf(ios::showbase);
@@ -212,6 +216,7 @@ int main(int argc, char *argv[])
     IMG_AddInstrumentFunction(WatchMain, 0);
 
     // Follow execution at BBL or Trace level
+    //TRACE_AddInstrumentFunction(FollowTraces, 0);
     TRACE_AddInstrumentFunction(FollowTraces, 0);
 
     // Instrument read syscall to get taint sources

### 2013-10-19 vulnerable_programs/trivial/controlPath.c

@@ -10,7 +10,7 @@ void main(int argc, char* argv)
 
     // Assign value to x based on input
     int x;
-    if (choice == 'X') {
+    if (choice == '1') {
         x = 111;
     } else {
         x = 222;

### 2013-10-20 MyPinTool/MyPinTool.cpp
little cleanup, shamelessly use salwan's awesome stuff for demo and progress

@@ -44,18 +44,17 @@ using namespace std;
 /* ===================================================================== */
 
 bool IN_MAIN = false;
-//std::ofstream TraceFile;
 
 #if defined(TARGET_MAC)
 #define MALLOC "_malloc"
-#define FREE "_free"
+//#define FREE "_free"
 #define MAIN "_main"
 #define LIBCSTART "__libc_start_main"
 #define GETCHAR "_getchar"
 #define STRCPY "_strcpy"
 #else
 #define MALLOC "malloc"
-#define FREE "free"
+//#define FREE "free"
 #define MAIN "main"
 #define LIBCSTART "__libc_start_main"
 #define GETCHAR "getchar"
@@ -65,9 +64,10 @@ bool IN_MAIN = false;
 /* ===================================================================== */
 /* User Libraries */
 /* ===================================================================== */
-#include "FollowExecution.h"
+//#include "FollowExecution.h"
 //#include "DTA.h"
-#include "taint_example_3.h"
+//#include "taint_example_3.h"
+#include "FindUseAfterFree.h"
 //#include "FindVulnerability.h"
 
 
@@ -91,8 +91,6 @@ KNOB<string> KnobOutputFile(KNOB_MODE_WRITEONCE, "pintool",
 VOID ToggleLogging(bool status)
 {
     IN_MAIN = status; 
-    //TraceFile << "HERE" << endl;
-    ControlFlowFile << "HERE" << endl;
     // Global, can be turned off to speed up execution
     //EnableInstrumentation = status;
 
@@ -122,60 +120,13 @@ VOID WatchMain(IMG img, VOID *v)
 
 }
    
-VOID WatchMemoryAllocation(IMG img, VOID *v)
-{
-    // Instrument the malloc() and free() functions.  Print the input argument
-    // of each malloc() or free(), and the return value of malloc().
-    //
-    //  Find the malloc() function.
-    RTN mallocRtn = RTN_FindByName(img, MALLOC);
-    if (RTN_Valid(mallocRtn))
-    {
-        RTN_Open(mallocRtn);
-
-        /*
-        // Instrument malloc() to print the input argument value and the return value.
-        RTN_InsertCall(mallocRtn, IPOINT_AFTER, (AFUNPTR)MallocInfo,
-                       IARG_ADDRINT, MALLOC,
[…]

### 2013-10-20 MyPinTool/backup.cpp

@@ -1,110 +1,0 @@
-//
-//  Jonathan Salwan - Copyright (C) 2013-08
-// 
-//  http://shell-storm.org
-//  http://twitter.com/JonathanSalwan
-//
-//  Note: Example 1 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
-//        Simple taint memory area from read syscall. 
-//
-
-#include "pin.H"
-#include <asm/unistd.h>
-#include <fstream>
-#include <iostream>
-#include <list>
-
-/* bytes range tainted */
-struct range
-{
-  UINT64 start;
-  UINT64 end;
-};
-
-std::list<struct range> bytesTainted;
-
-INT32 Usage()
-{
-    cerr << "Ex 1" << endl;
-    return -1;
-}
-
-VOID ReadMem(UINT64 insAddr, std::string insDis, UINT64 memOp)
-{
-  list<struct range>::iterator i;
-  UINT64 addr = memOp;
-  
-  for(i = bytesTainted.begin(); i != bytesTainted.end(); ++i){
-      if (addr >= i->start && addr < i->end){
-        std::cout << std::hex << "[READ in " << addr << "]\t" << insAddr << ": " << insDis<< std::endl;
-      }
-  } 
-}
-
-VOID WriteMem(UINT64 insAddr, std::string insDis, UINT64 memOp)
-{
-  list<struct range>::iterator i;
-  UINT64 addr = memOp;
-
-  for(i = bytesTainted.begin(); i != bytesTainted.end(); ++i){
-      if (addr >= i->start && addr < i->end){
-        std::cout << std::hex << "[WRITE in " << addr << "]\t" << insAddr << ": " << insDis << std::endl;
-      }
-  } 
-}
-
-VOID Instruction(INS ins, VOID *v)
-{
-  if (INS_MemoryOperandIsRead(ins, 0) && INS_OperandIsReg(ins, 0)){
-    INS_InsertCall(
-        ins, IPOINT_BEFORE, (AFUNPTR)ReadMem,
-        IARG_ADDRINT, INS_Address(ins),
-        IARG_PTR, new string(INS_Disassemble(ins)),
-        IARG_MEMORYOP_EA, 0,
-        IARG_END);
-  }
-  else if (INS_MemoryOperandIsWritten(ins, 0)){
-    INS_InsertCall(
-        ins, IPOINT_BEFORE, (AFUNPTR)WriteMem,
[…]

### 2013-10-20 MyPinTool/examples/salwanUseAfterFree.cpp

@@ -1,0 +1,389 @@
+//
+//  Jonathan Salwan - Copyright (C) 2013-08
+// 
+//  http://shell-storm.org
+//  http://twitter.com/JonathanSalwan
+//
+//  Note: Example 5 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
+//        Detect the classical use after free vulnerability 
+//
+
+#include "pin.H"
+#include <asm/unistd.h>
+#include <fstream>
+#include <iostream>
+#include <list>
+
+#define LOCKED    1
+#define UNLOCKED  !LOCKED
+
+#define ALLOCATE  1
+#define FREE      !ALLOCATE
+
+static size_t         lastSize;
+
+struct mallocArea
+{
+  UINT32  base;
+  UINT32  size;
+  BOOL    status;
+};
+
+UINT32 lockTaint = LOCKED;
+
+std::list<UINT32>               addressTainted;
+std::list<REG>                  regsTainted;
+std::list<struct mallocArea>    mallocAreaList;
+
+INT32 Usage()
+{
+    std::cerr << "Ex 5" << std::endl;
+    return -1;
+}
+
+BOOL checkAlreadyRegTainted(REG reg)
+{
+  list<REG>::iterator i;
+
+  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
+    if (*i == reg){
+      return true;
+    }
+  }
+  return false;
+}
+
+VOID removeMemTainted(UINT32 addr)
+{
+  addressTainted.remove(addr);
+  std::cout << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
+}
+
+VOID addMemTainted(UINT32 addr)
+{
+  addressTainted.push_back(addr);
+  std::cout << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
+}
+
+BOOL taintReg(REG reg)
+{
+  if (checkAlreadyRegTainted(reg) == true){
+    std::cout << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
+    return false;
+  }
+
+  switch(reg){
+
+    case REG_EAX:  regsTainted.push_front(REG_EAX); 
+    case REG_AX:   regsTainted.push_front(REG_AX); 
+    case REG_AH:   regsTainted.push_front(REG_AH); 
+    case REG_AL:   regsTainted.push_front(REG_AL); 
[…]

### 2013-10-20 MyPinTool/taint_example_3.h

@@ -1,256 +1,0 @@
-unordered_map<ADDRINT, BOOL> AddressTaintMap;
-unordered_map<ADDRINT, BOOL> RegisterTaintMap;
-std::ofstream TaintFile;
-
-bool checkAlreadyRegTainted(REG reg)
-{
-    if (RegisterTaintMap.count(reg) > 0) {
-      return true;
-    }
-  return false;
-}
-
-VOID removeMemTainted(UINT32 addr)
-{
-    AddressTaintMap.erase(addr);
-  TaintFile << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
-}
-
-VOID addMemTainted(UINT32 addr)
-{
-    AddressTaintMap[addr] = false;
-  TaintFile << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
-}
-
-bool taintReg(REG reg)
-{
-  if (checkAlreadyRegTainted(reg) == true){
-    TaintFile << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
-    return false;
-  }
-
-  switch(reg){
-
-    case REG_EAX:  RegisterTaintMap.insert(REG_EAX); 
-    case REG_AX:   RegisterTaintMap.insert(REG_AX); 
-    case REG_AH:   RegisterTaintMap.insert(REG_AH); 
-    case REG_AL:   RegisterTaintMap.insert(REG_AL); 
-         break;
-
-    case REG_EBX:  RegisterTaintMap.insert(REG_EBX);
-    case REG_BX:   RegisterTaintMap.insert(REG_BX);
-    case REG_BH:   RegisterTaintMap.insert(REG_BH);
-    case REG_BL:   RegisterTaintMap.insert(REG_BL);
-         break;
-
-    case REG_ECX:  RegisterTaintMap.insert(REG_ECX);
-    case REG_CX:   RegisterTaintMap.insert(REG_CX);
-    case REG_CH:   RegisterTaintMap.insert(REG_CH);
-    case REG_CL:   RegisterTaintMap.insert(REG_CL);
-         break;
-
-    case REG_EDX:  RegisterTaintMap.insert(REG_EDX); 
-    case REG_DX:   RegisterTaintMap.insert(REG_DX); 
-    case REG_DH:   RegisterTaintMap.insert(REG_DH); 
-    case REG_DL:   RegisterTaintMap.insert(REG_DL); 
-         break;
-
[…]

### 2013-10-20 vulnerable_programs/trivial/salwanExample.c

@@ -1,0 +1,19 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+#include <unistd.h>
+
+int main(int ac, char **av)
+{
+    char *buf;
+    char c;
+
+    if (!(buf = malloc(32)))
+        return -1;
+
+    c = buf[0];           /* UAF not match */
+    free(buf);  
+    c = buf[0];           /* UAF match     */
+    buf = malloc(32);
+    c = buf[0];           /* UAF not match */
+}

### 2013-10-20 vulnerable_programs/trivial/useAfterFree.c

@@ -3,21 +3,25 @@
 #include <string.h>
 #include <unistd.h>
 
-int main(int argc, char **argv) {
-	char *buf;
-	// Allocate memory
-	buf = (char *) malloc(512);
+int main(int argc, char **argv)
+{
+    char *buf = malloc(32);
+    char c;
 
-	// Free memory
-	free(buf);
+    // User input
+    char *userInput = malloc(32);
+    gets(userInput);
 
-	// Get used input, taint source
-	char string[32];
-	printf("%s", "Enter string: ");
-  	gets(string);	
-
-	// Use memory after freed
-	strcpy(buf, string);
+    c = buf[0];             /* UAF not match */
+    if (userInput[0] == 'A') {
+        printf("Running UAF branch\n");
+        free(buf);  
+        c = buf[0];         /* UAF match     */
+        buf = malloc(32);
+        c = buf[0];         /* UAF not match */
+    }
+    if (userInput[0] != 'A') {
+        printf("NOT running UAF branch\n");
+    }
 
 }
-

### 2013-10-20 docs/paper/paper.tex

@@
 
+	\subsection{Dynamic Taint Analysis}
+We implemented dynamic taint analysis for multiple input sources.
+When performing certain actions, like reading a file, which makes use of the read() syscall in Linux, it was possible to watch for all reads after an specific opens which suggested user involvement, and follow the buffers read in.
+For user input directed to STDIN or through command line arguments however, it was necessary to hook into c library functions which allowed user input, like strcpy.
+
 	\subsection{Pintools for Finding Vulnerable Conditions}

### 2013-10-20 check.c
some work on proj3. can't test cuz openmp breaking and no internet

@@ -1,0 +1,52 @@
+int main() {
+
+	for (int i = 0; i < numPipes; i++) {
+		pipe(fds[i]);
+	}
+
+	//Last pipe always the same
+	if (fork()== 0) {
+		printf("end pipe: %d\n", numPipes - 1);
+		close(0); dup(fds[numPipes - 1][0]); /* redirect standard input to fds[1] */
+		close(fds[numPipes - 1][1]);
+		for (int i = 0; i < numPipes; i++) {
+			close(fds[i][0]);
+			close(fds[i][1]);
+		}
+		execv(argvs[numPipes][0], argvs[numPipes]);
+		exit(0);
+	}
+
+	for (int i = numPipes - 1; i > 0; i--) {
+		if (fork()== 0) {
+			printf("middle pipe out: %d\n", i);
+			close(1); dup(fds[i][1]);
+			printf("middle pipe in: %d\n", i - 1);
+			close(0); dup(fds[i - 1][0]); 
+			for (int i = 0; i < numPipes; i++) {
+				close(fds[i][0]);
+				close(fds[i][1]);
+			}
+			//having this makes it stop?
+			execv(argvs[i][0], argvs[i]);
+			exit(0);
+		}
+	}
+
+
+	if (fork() == 0) {
+		close(1); dup(fds[0][1]);  /* redirect standard output to fds[0] */
+		for (int i = 0; i < numPipes; i++) {
+			close(fds[i][0]);
+			close(fds[i][1]);
+		}
+		execv(argvs[0][0], argvs[0]);
+		exit(0);
+
+	}
+
+	for (int i = 0; i < numPipes; i++) {
+		close(fds[i][0]);
+		close(fds[i][1]);
+	}
+}

### 2013-10-20 examples/lect2/example1.c

@@ -1,0 +1,19 @@
+#include <stdio.h>
+#include <string.h>
+
+char *str;
+
+char aa[1000];
+int main()
+{
+  int ii;
+
+  str = aa;
+
+  printf("Hello, world. ii = %d\n", ii);
+  strcpy(str, "Hello, world.");
+  printf("%s\n", str);
+  return 0;
+}
+
+  

### 2013-10-20 examples/lect2/example4.c

@@ -1,0 +1,9 @@
+#include <stdio.h>
+
+int main(int argc, char *argv[])
+{
+  int i;
+  for (i=0; i<argc; i++) 
+    printf("argv[%d] = %s\n", i, argv[i]);
+  return 0;
+}

### 2013-10-20 examples/lect2/example5.c

@@ -1,0 +1,39 @@
+/* example for sprintf and sscanf */
+
+#include <stdio.h>
+#include <stdlib.h>
+#include <string.h>
+
+int main(int argc, char * argv[])
+{
+  char command[100];
+  char cmd[100];
+  char buf[100];
+  FILE *fd;
+
+  int pid;
+  char tty[20];
+  int hr, min, sec;
+  int n;
+  char cmdd[20];
+  strcpy(command, "ps");
+
+  sprintf(cmd, "%s > tmp000", command);
+  printf("executing %s\n", cmd);
+  system(cmd);
+
+  fd = fopen("tmp000", "r");
+  fgets(buf, 100, fd);  /* skip the first line */
+
+  fgets(buf, 100, fd);
+  while(!feof(fd)) {
+    sscanf(buf, "%d %[^/]/%d %d:%d:%d %s", &pid, tty, &n, &hr, &min, &sec, cmdd);
+    printf("pid = %d, tty = %s, n = %d, min=%d, sec = %d, hr = %d, cmd = %s\n", pid, tty, n, min, sec, hr, cmdd);
+    fgets(buf, 100, fd);
+  }
+  return 0;
+}
+
+  
+  
+  

### 2013-10-20 examples/lect3/example1.c

@@ -1,0 +1,14 @@
+#include <stdio.h>
+#include <unistd.h>
+
+int main() 
+{
+
+  printf("I am here 1.\n");
+  getchar();
+  fork();
+  printf("I am here 2\n");
+  getchar();
+  printf("I am here 3\n");
+}
+  

### 2013-10-20 examples/lect3/example3c.c

@@ -1,0 +1,27 @@
+#include <stdio.h>
+#include <stdlib.h>
+#include <unistd.h>
+
+int main(int argc, char* argv[])
+{
+  int i, pid;
+  char *my[2];
+
+  if (argc < 2) {
+    printf("Usage: a.out command\n");
+    exit(0);
+  }
+  
+  for (i = 1; i< argc; i++) {
+    my[0] = argv[i];
+    my[1] = NULL;
+
+    if (fork() == 0) {
+      if(execv(argv[i], &my[0]) == -1) {
+	printf("Command execution failed.\n");
+      }
+    }
+    wait(&pid);
+  }
+}
+

### 2013-10-20 examples/lect3/example6.c

@@ -1,0 +1,26 @@
+#include <stdio.h>
+#include <unistd.h>
+#include <stdlib.h>
+#include <string.h>
+
+int main() 
+{
+  char * p;
+  int pid;
+  int status;
+
+  p = malloc(10);
+
+  strcpy(p, "abcd");
+
+  if ((pid=fork()) == 0) {
+    strcpy(p, "kkkkk");
+    printf("child process, pid = %d, p = %lld, content(p) = %s\n", getpid(),
+           (long long int)p, p);
+    exit(0);
+  } 
+  wait(&status);
+  getchar();
+  printf("pid = %d, p = %lld, content(p) = %s\n", getpid(), (long long int)p, p);
+}
+  

### 2013-10-20 examples/lect4/practice.c

@@ -1,0 +1,54 @@
+/* implementing  "/usr/bin/ps -ef | /usr/bin/more" */
+#include <stdio.h>
+#include <unistd.h>
+#include <stdlib.h>
+
+int main()
+{
+  int fds[2];
+  int fds2[2];
+  int child[2];
+  char *argv[3];
+  pipe(fds);
+
+  if (fork()== 0) {
+    close(0); dup(fds2[0]); // redirect standard input to fds[1]
+  //  close(fds2[1]);close(fds2[0]);
+    argv[0] = "/bin/more";
+    argv[1] = NULL;           // check how the argv array is set 
+    execv(argv[0], argv);
+    exit(0);
+  }
+
+  // middle
+  if (fork()== 0) {
+    close(1); dup(fds2[1]); 
+    close(0); dup(fds[0]); 
+    //close(fds2[1]); bad descriptor
+    close(fds[1]);
+    argv[0] = "/usr/bin/wc";
+    argv[1] = NULL;           /* check how the argv array is set */
+    execv(argv[0], argv);
+    exit(0);
+
+
+  }
+  if (fork() == 0) {
+    close(1); dup(fds[1]);  
+ //   close(fds[1]);close(fds[0]);
+//    close(fds2[1]);close(fds2[0]);
+    argv[0] = "/bin/ps";
+    argv[1] = "-e"; argv[2] = NULL;
+    execv(argv[0], argv);
+    exit(0);
+
+  }
+
+  close(fds[0]);
+  close(fds2[0]);
+  close(fds[1]);
+  close(fds2[1]);
+  wait(&child[0]);
+  wait(&child[0]);  
+  wait(&child[0]);
+} 

### 2013-10-20 examples/lect7/mymore.c

@@ -1,0 +1,23 @@
+#include <stdio.h>
+#include<sys/types.h>
+#include <unistd.h>
+#include <errno.h>
+
+main()
+{
+
+	int i;
+
+	if( tcgetpgrp(STDIN_FILENO) < 0) {
+		printf("errno = %d", errno);
+		perror("tcgetpgrp");
+	}
+
+	printf("pgrp=%d pid=%d term=%d\n", getpgrp(), getpid(), tcgetpgrp(STDIN_FILENO));
+
+	for( i=0; i<10; i++) {
+		printf("line %d\n", i);
+		getchar();
+	}
+}
+

### 2013-10-20 examples/lect9/example1.c

@@ -1,0 +1,48 @@
+#include <pthread.h>
+#include <unistd.h>
+#include <stdio.h>
+
+void *produce(void *);
+void *consume(void *);
+
+
+int main(int argc, char* argv[]){
+
+     pthread_t thread1;
+     pthread_t thread2;
+     int i;
+     if ((i=pthread_create(&thread1, NULL, produce, (void*)NULL)) != 0) {
+       printf("thread creation failed. %d\n", i);
+     }
+
+     if ((i=pthread_create(&thread2, NULL, consume, (void*)NULL)) != 0) {
+       printf("thread creation failed. %d\n", i);
+     }
+
+     pthread_join(thread1, NULL);
+     pthread_join(thread2, NULL);
+
+     printf("Exiting main\n");
+     return 0;
+
+}
+
+void *produce(void *arg){
+  int i;
+  for(i=0;i<10;i++){
+    printf("I produce\n");
+    sleep(1);
+  }
+  return NULL;
+}
+
+void *consume(void *arg){
+  int i;
+  for(i=0;i<10;i++){
+    printf("I consume\n");
+    sleep(1);
+  }
+  return NULL;
+}
+
+

### 2013-10-20 proj3/jacobi.c

@@ -1,0 +1,104 @@
+#include <unistd.h>
+#include <stdlib.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+#include <stdio.h>
+
+#define N 4096
+
+float x[N+2][N+2][2];
+
+#define myabs(a) (((a) > 0) ? (a):(-(a)))
+
+int main(void) 
+{
+  int NN;
+  float a1, a2, a3, a4, a5, a6;
+  float MAXDIFF;
+  int i, j;
+  int t, t1, t2;
+  float  maxdiff1;
+  int iteration;
+
+  
+  scanf("%d %f %f %f %f %f %f %f", &NN, &a1, &a2, &a3, &a4, &a5, &a6, &MAXDIFF);
+  
+
+  printf("%d %f %f %f %f %f %f %f\n", NN, a1, a2, a3, a4, a5, a6, MAXDIFF);   
+  /*  a1 = a2 = a3 = a4 = 0.25; a6 = 0; a5 = 0.1;
+
+  MAXDIFF = 0.0001;
+  */
+
+  printf("maxdiff = %13.12f\n", MAXDIFF);
+
+  for (i=1; i<=NN+1; i++) {
+    x[i][0][0] = a5*i;
+    x[i][0][1] = a5*i;
+
+    x[i][NN+1][0] = a6*i;
+    x[i][NN+1][1] = a6*i;
+
+    x[0][i][0] = 0.0;
+    x[0][i][1] = 0.0;
+
+    x[NN+1][i][0] = 0.0;
+    x[NN+1][i][1] = 0.0; 
+  }
+
+
+  for (i=1; i<=NN; i++) 
+    for (j=1; j<=NN; j++) {
+      x[i][j][0] = 0.0;
+      x[i][j][1] = 0.0;
+    }
+
+  printf("maxdiff=%13.12f\n", MAXDIFF);
+
+  t = 0; t1 = 1;
+  maxdiff1 = 100000.0;
+  iteration = 0;
+
+  while (maxdiff1 > MAXDIFF) {
+    maxdiff1 = -1.0;
+    for (i=1; i <= NN; i++) 
+      for (j=1; j <=NN; j++) {
+        x[i][j][t] = a1*x[i-1][j][t1] + a3 * x[i+1][j][t1] +
+	             a2*x[i][j-1][t1] + a4 * x[i][j+1][t1];
+	if (myabs(x[i][j][t] - x[i][j][t1]) > maxdiff1)
[…]

### 2013-10-23 MyPinTool/MyPinTool.cpp
from here, come up with features for mutation and get it to work well on trivial uaf

@@ -66,9 +66,7 @@ bool IN_MAIN = false;
 /* ===================================================================== */
 //#include "FollowExecution.h"
 //#include "DTA.h"
-//#include "taint_example_3.h"
 #include "FindUseAfterFree.h"
-//#include "FindVulnerability.h"
 
 
 /* ===================================================================== */

### 2013-10-23 vulnerable_programs/trivial/dta.cpp

@@ -1,34 +1,0 @@
-#include<iostream>
-#include<cstdio>
-#include<cstdlib>
-#include<unistd.h>
-#include<fcntl.h>
-
-int foo2(char a, char b, char c)
-{
-    a = 1;
-    b = 2;
-    c = 3;
-    return 0;
-}
-
-int foo(char *buf)
-{
-    char c, b, a;
-
-    c = buf[0];
-    b = c;
-    a = buf[8];
-    foo2(a, b, c);
-    return true;
-}
-
-int main(int ac, char **av)
-{
-    int fd;
-    char *buf;
-
-    fd = open("./file.txt", O_RDONLY);
-    read(fd, buf, 32), close(fd);
-    foo(buf);
-}

### 2013-10-23 docs/paper/paper.tex
some more to paper, abstract

@@
 \maketitle
+
+\section{Abstract}
+
+Finding exploitable bugs in binaries is a difficult and lucrative endeavour.
+Fuzzing, or the feeding of random input into processes to try and detect vulnerable conditions [CITE], is one technique used by researchers and analysts.
+Applications tested for vulnerability discovery are often black boxes because source code is unavailable.
+This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce [CITES].
+Among these issues are efficient and thorough dynamic taint analysis [CITE], the path explosion problem [CITE], and what we call the path exploration problem [CITE?].
+Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
+The path explosion problem arises from the nature of assembly languages.
+Jump instructions, which may make up as much as X\% of machine instructions in programs [CITE], each multiply the total number of existing paths in a binary by two.
+Considering the size of binaries, this quickly leads to an un-tenably large set of possible paths to explore via conventional techniques like symbolic execution.
+And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way.
+Such automated exploit generation is the subject of much research [CITES].
+
+Our works aims to reduce the severity of the latter two problems while being wary of the first during implementation.
+Instead of trying to eke out slightly more reasonable performance by using symbolic execution less or more wisely [CITE], we focus instead of using machine learning techniques to mutation previous input test cases in efficient ways, so that more paths are explored "naturely" by the test suite, and vulnerable conditions are more likely to be found.
+
+In the hope of developing as scalable and re-usable a product as possible, we assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary.
 

### 2013-10-23 docs/paper/paper.tex
working on following control flow, get a good way to record changes, then work in dta, then ML

@@
 This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce [CITES].
-Among these issues are efficient and thorough dynamic taint analysis [CITE], the path explosion problem [CITE], and what we call the path exploration problem [CITE?].
+Among these issues are efficient and thorough dynamic taint analysis [CITE], the path explosion problem [CITE], and the code coverage problem [CITE?].
 Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
@@
 Our works aims to reduce the severity of the latter two problems while being wary of the first during implementation.
-Instead of trying to eke out slightly more reasonable performance by using symbolic execution less or more wisely [CITE], we focus instead of using machine learning techniques to mutation previous input test cases in efficient ways, so that more paths are explored "naturely" by the test suite, and vulnerable conditions are more likely to be found.
+Instead of trying to eke out slightly more reasonable performance by using symbolic execution less or more wisely [CITE], we focus instead of using machine learning techniques to mutation previous input test cases in efficient ways, so that more paths are explored "naturally" by the test suite, and vulnerable conditions are more likely to be found.
 

### 2013-10-23 MyPinTool/FollowExecution.h

@@ -1,7 +1,7 @@
 // FollowExecution.h
 
 /* ===================================================================== */
-/* Control Flow following functions, currently at bbl level */
+/* Control Flow following jumps                                          */
 /* ===================================================================== */
 std::ofstream ControlFlowFile;
 
@@ -15,42 +15,24 @@ typedef struct
 
 ControlFlowStruct ControlFlow;
 
-// Returns starting address for given trace.
-ADDRINT GetTraceStart(TRACE trace)
-{
-    return TRACE_Address(trace);
-}
 
-// Follow each instruction in each bbl of each trace.
-// basic block is single entrace, single exit block of sequential instructions.
-// trace is single entrace, multiple exits, and generated at entrace during runtime.
-VOID FollowTraces(TRACE trace, VOID *v)
+// Record every taken jump
+// TODO find a better way to ONLY look at instructions inside main
+VOID FollowBranches(INS ins, VOID *v)
 {
     if (!IN_MAIN) {
         return;
     }
 
-    ControlFlowFile << GetTraceStart(trace) << endl;
-
-    /*
-    // For each basic block, track each instruction
-    for (BBL bbl = TRACE_BblHead(trace); BBL_Valid(bbl); bbl = BBL_Next(bbl)) {
-        for (INS ins = BBL_InsHead(bbl); INS_Valid(ins); ins = INS_Next(ins) ) {
-		    ControlFlowFile << INS_Disassemble(ins) << "\t" << INS_Address(ins);
-
-            // Get routine name if it's a call instruction
-            if (INS_IsDirectCall(ins) && INS_IsDirectBranchOrCall(ins) ) {
-                ADDRINT addrint = INS_DirectBranchOrCallTargetAddress(ins);
-                ControlFlowFile << RTN_FindNameByAddress(addrint);
-            }
-
-            ControlFlowFile << endl;
-
-        }
+    if (INS_IsBranch(ins)) {
+        //ControlFlowFile << INS_Disassemble(ins) << endl;
+        // TODO instead of addresses, which will change, get the instruction and (jmpAddr - currentAddr), maybe that'll work better
+        //ControlFlowFile << StringFromAddrint(INS_NextAddress(ins)) << endl;
+        ControlFlowFile << CATEGORY_StringShort(INS_Category(ins)) << ":" 
[…]

### 2013-10-23 MyPinTool/MyPinTool.cpp

@@ -64,7 +64,7 @@ bool IN_MAIN = false;
 /* ===================================================================== */
 /* User Libraries */
 /* ===================================================================== */
-//#include "FollowExecution.h"
+#include "FollowExecution.h"
 //#include "DTA.h"
 #include "FindUseAfterFree.h"
 
@@ -123,7 +123,7 @@ VOID WatchMain(IMG img, VOID *v)
 
 VOID Fini(INT32 code, VOID *v)
 {
-    //FiniFollowExecution();
+    FiniFollowExecution();
     FiniFindUseAfterFree();
     //FiniDTA();
 }
@@ -155,7 +155,7 @@ int main(int argc, char *argv[])
     }
     
     // Init functions for modules
-    //InitFollowExecution();
+    InitFollowExecution();
     InitFindUseAfterFree();
     //InitDTA();
 
@@ -164,7 +164,7 @@ int main(int argc, char *argv[])
 //TaintFile.setf(ios::showbase);
 
     // Watch main function
-    //IMG_AddInstrumentFunction(WatchMain, 0);
+    IMG_AddInstrumentFunction(WatchMain, 0);
     INS_AddInstrumentFunction(Instruction, 0);
 
     PIN_AddFiniFunction(Fini, 0);

### 2013-11-01 docs/paper/paperUpdate.tex
paper for network security

--- 2013-10-23 docs/paper/paper.tex
@@
 
-\documentclass[prodmode,acmtecs]{acmsmall} % Aptara syntax
+\documentclass[10pt, twocolumn, times, nocopyrightspace, preprint]{sigplanconf} % Aptara syntax
 
@@
 \def\@acmMonth{12}  %the month
-\def\@journalName{COMPUTER AND NETWORK SYSTEM ADMINISTRATION} %the name of the ACM journal
+\def\@journalName{Network Security} %the name of the ACM journal
 \def\@journalNameShort{CNT 5605} %the acronym of the ACM journal 
@@
 % Title portion
-\title{The Incredible Mutating Test Files! Smart Mutation for Binary Fuzzing}
+\title{Approximating Symbolic Execution with Dynamic Taint Analysis}
 \author{Clark Wood
@@
 
-\category{CNT 5605}{Fall 2013}{Dynamic Taint Analysis, Mutation, Fuzzing}
+\category{CNT 5605}{Fall 2013}{Dynamic Taint Analysis, Symbolic Execution, Mutation, Fuzzing}
 
-\acmformat{Clark Wood, Paper CNT 5605}
+\acmformat{Clark Wood, Project CNT 5412}
 % At a minimum you need to supply the author names, year and a title.
@@
 
-\section{Abstract}
+\section{Introduction}
 
@@
 Fuzzing, or the feeding of random input into processes to try and detect vulnerable conditions [CITE], is one technique used by researchers and analysts.
-Applications tested for vulnerability discovery are often black boxes because source code is unavailable.
+Applications tested for vulnerabilities are often black boxes because source code is unavailable.
 This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce [CITES].
-Among these issues are efficient and thorough dynamic taint analysis [CITE], the path explosion problem [CITE], and the code coverage problem [CITE?].
+Among these issues are i) efficient and thorough dynamic taint analysis [CITE], ii) the path explosion problem [CITE], and iii) the code coverage problem [CITE?].
 Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
@@
 And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way.
-Such automated exploit generation is the subject of much research [CITES].
+Such automated exploit generation is the subject of much research [H, I, CITES].
 
-Our works aims to reduce the severity of the latter two problems while being wary of the first during implementation.
-Instead of trying to eke out slightly more reasonable performance by using symbolic execution less or more wisely [CITE], we focus instead of using machine learning techniques to mutation previous input test cases in efficient ways, so that more paths are explored "naturally" by the test suite, and vulnerable conditions are more likely to be found.
+This work aims to reduce the severity of the latter two problems while being wary of the first during implementation.
+Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
+This is possible by tracking taint at the instruction level, then backsolving from every jump to the source of taint to come up with smarter ways to mutate user input and create new test cases.
+For instance, in the below example:
 
-In the hope of developing as scalable and re-usable a product as possible, we assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary.
+\begin{verbatim}
+mv eax, userInput1
+mv ebx, userInput2
+cmp eax, ebx
+jge 0xDEADBEEF
+\end{verbatim}
 
-\section{Fuzzing Overview}
+If we already had a test case where userInput1 equalled 10 and userInput2 equalled 5, this test case would jump to 0xDEADBEEF.
+To generate a test case where we would not jump, we take the complement of the jge instruction's comparison function, which would be "less than".
+We can find the last instruction that modified the Z flag, which is how jge decides to jump or not.
+We see that this compare instruction was tained by the eax and ebx registers, which were in turn tainted by userInputs 1 and 2.
+Since we can impact both values in the comparison, it is easy to modify user input smartly to alter the value of the Z flag and jump during the next execution.
+Perhaps we could switch the values, or auto-increment/decrement one until we satisfy the needed comparison, or mutate values randomly.
 
-white/black/graybox, mutation/generation, Dynamic Taint Analysis,
+There are a finite number of ways to compare data in x86, so I can create cases for all possible ways jumps are decided.
+I only want to prove this is possible however, so I will only implement a subset and instead comment on how to implement the other comparisons.
 
-As programs grow larger, so do the test suites designed to exercise execution paths within the program.
-White box approaches have the advantage of source code, allowing developers to write test cases which exercise paths in a higher level language.
-With black box approaches, however, test cases would typically target assembly block-level code paths [A,...NEEDED].
+\section{Assumptions and Scoping}
 
-\subsection{Dynamic Taint Analysis}
+I assume ASLR is disabled for the binary to be fuzzed.
+This allows the program to easily track and compare execution paths by creating a list of jump locations.
+Since the world is moving more and more toward 64-bit architectures, I plan to implement the technique for x86\_64.
+
+I also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary.
+The program will then attempt to concretely execute each path within the binary by backsolving, hopefully at a greater speed than symbolic execution.
+
+I am hopeful about the results because current selective symbolic execution engines still appear to introduce significant overhead (Between 6 and 78X overhead more than QEMU for S2E.
+Just QEMU is between 4 and 10 times slower on some benchmarks, more like 15 on others) [J, K, L].
+In contrast, basic block counting using Intel Pin, the framework I am leveraging, introduced between 2 and 4X overhead [M].
+However, the pintool needed for my proposed technique will introduce greater levels of overhead, since I will be working at the instruction level instead of the basic block level.
+
+I am leveraging Intel PIN to perform dynamic binary instrumentation.
+I plan to test first on dummy programs with many paths that are easy to backsolve, similar to the example above.
+A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, should create an appropriate binary.
+I then plan to test against S2E and Peach Fuzzer.
+
+\section{Research}
 
@@
 Assigning everything from a generic binary value of tainted/not tainted to bit-level marking of which part of user input affected which variable is conceivable, although finer-grained taint analysis is more computationally expensive and difficult to determine [CITE].
-Consider the following pseudocode:
-\begin{verbatim} 
-x = userInput & 1
-if x % 2 == 0:
-	vuln()				
-\end{verbatim}
 
-TODO
-Taint can propagate via explicit or implicit flows (Figure 1), sometimes also called data and control dependencies respectively [G].
+Taint can propagate via explicit or implicit flows, sometimes also called data and control dependencies respectively [G].
 Explicit flows involve a tainted variable, x, which is used in an assignment expression to compute a new variable, y.
@@
 
-This is a problem BECAUSE TODO
+For my project, implicit data flows are very important, so I need to implement DTA which catches both implicit and explicit flows.
 
-\begin{verbatim}
-# Explicit taint
-
-# Implicit taint
-\end{verbatim}
-
-Propagation
-
-\section{Machine Learning}
-While research has applied machine learning techniques to successfully extrapolate vulnerability patterns, previous efforts have required source code and training examples containing known vulnerabilities to drive learning [F].
-In contrast, we implement ...
-
-\section{Dynamic Binary Instrumentation with Intel PIN}
-
-Pintools
-
-\section{Ways to mutate test cases}
-
-Machine learning in lieu of symbolic execution?
+DTA has been used to implement smart mutation fuzzers [A], but I think my work is unique from and complementary to Bekrar's work.
+In [A], DTA is proposed as a way to intelligently decide which parts of user input should be mutated.
+I plan to add on to this idea by allowing smarter mutations to be selected by backsolving to decide which values are most likely to result in new paths being explored.
 
@@
 
-	\subsection{Dynamic Taint Analysis}
-We implemented dynamic taint analysis for multiple input sources.
-When performing certain actions, like reading a file, which makes use of the read() syscall in Linux, it was possible to watch for all reads after an specific opens which suggested user involvement, and follow the buffers read in.
-For user input directed to STDIN or through command line arguments however, it was necessary to hook into c library functions which allowed user input, like strcpy.
-
-	\subsection{Pintools for Finding Vulnerable Conditions}
-
-	\subsection{Mutation Algorithm}
-
-Fuzzing optimization techniques are evolving to deal with the path explosion problem [CITES] in various ways, focusing on ...
-
-Researchers at VUPEN Security mention the value of discovering test case sets of equivalent coverage, but smaller size, via test suite reduction algorithms [A].
-
-\section{Future Work}
+	I plan to implement dynamic taint analysis for files as input sources.
+I am basing my DTA heavily on Jonathan Salwan's work [N].
+I've been in contact with him and received permission to use his sample code.
+I can watch for all reads after a file is opened, then tag user input and follow it as it moves throughout the binary.
+	I will need to implement a system which keeps track of how taint propagates at the instruction level. A directed graph structure, with initial nodes representing the bytes of user input which are
 
 \section{References}
-
-[A] Bekrar, Sofia, et al. "A taint based approach for smart fuzzing." Software Testing, Verification and Validation (ICST), 2012 IEEE Fifth International Conference on. IEEE, 2012.
-[B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with
+\begin{itemize}
+	\item [A] Bekrar, Sofia, et al. "A taint based approach for smart fuzzing." Software Testing, Verification and Validation (ICST), 2012 IEEE Fifth International Conference on. IEEE, 2012.
+	\item [B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with
 Evolutionary Fuzzing", BlackHat and Defcon 2007.
-[C] Schwartz, E.J., Avgerinos, T., Brumley, D.
+	\item [C] Schwartz, E.J., Avgerinos, T., Brumley, D.
 "All You Ever Wanted to Know About Dynamic Taint Analysis and Forward Symbolic Execution (but might have been afraid to ask)." 2010 IEEE Symposium on Security and Privacy.
-[D] Clause, J. Li, W., Orso, A. "Dytan: a generic dynamic taint analysis framework". 2007 Int'l symposium on Software testing and analysis. ACM, 2007.
-[E] ... "Beyond Instruction Level Taint Propagation".
-[F] Yamaguchi, Fabian, Felix Lindner, and Konrad Rieck.
+	\item [D] Clause, J. Li, W., Orso, A. "Dytan: a generic dynamic taint analysis framework". 2007 Int'l symposium on Software testing and analysis. ACM, 2007.
+	\item [E] ... "Beyond Instruction Level Taint Propagation".
+	\item [F] Yamaguchi, Fabian, Felix Lindner, and Konrad Rieck.
 "Vulnerability extrapolation: assisted discovery of vulnerabilities using machine learning." Proceedings of the 5th USENIX conference on Offensive technologies.
 USENIX Association, 2011.
-[G] Bao, Tao, et al. "Strict control dependence and its effect on dynamic information flow analyses." Proceedings of the 19th international symposium on Software testing and analysis. ACM, 2010.
+	\item [G] Bao, Tao, et al.
+"Strict control dependence and its effect on dynamic information flow analyses." Proceedings of the 19th international symposium on Software testing and analysis.
+ACM, 2010.
+	\item [H] Cha, Sang Kil, et al. "Unleashing mayhem on binary code." Security and Privacy (SP), 2012 IEEE Symposium on. IEEE, 2012.
+	\item [I] Avgerinos, Thanassis, et al. "AEG: Automatic Exploit Generation." NDSS. Vol. 11. 2011.
+	\item [J] Chipounov, Vitaly, Volodymyr Kuznetsov, and George Candea.
+"S2E: A platform for in-vivo multi-path analysis of software systems." ACM SIGARCH Computer Architecture News 39.1 (2011): 265-278.
+	\item [K] Bellard, Fabrice. "QEMU, a Fast and Portable Dynamic Translator." USENIX Annual Technical Conference, FREENIX Track. 2005.
+	\item [L] Guillon, Christophe. "Program Instrumentation with QEMU." 1st International QEMU Users’ Forum. 2011.
+	\item [M] Luk, Chi-Keung, et al. "Pin: building customized program analysis tools with dynamic instrumentation." Acm Sigplan Notices. Vol. 40. No. 6. ACM, 2005.
+	\item [N] Salwan, Jonathan. \url{http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/}
+
+\end{itemize}
 

### 2013-11-01 docs/paper/sigplanconf-template.tex
paper for network security

--- 2013-11-01 docs/paper/paperUpdate.tex
@@
-% v2-acmsmall-sample.tex, dated March 6 2012
-% This is a sample file for ACM small trim journals
+%-----------------------------------------------------------------------------
 %
-% Compilation using 'acmsmall.cls' - version 1.3 (March 2012), Aptara Inc.
-% (c) 2010 Association for Computing Machinery (ACM)
+%               Template for sigplanconf LaTeX Class
 %
-% Questions/Suggestions/Feedback should be addressed to => "acmtexsupport@aptaracorp.com".
-% Users can also go through the FAQs available on the journal's submission webpage.
+% Name:         sigplanconf-template.tex
 %
-% Steps to compile: latex, bibtex, latex latex
+% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
+%               file for SIGPLAN conference proceedings.
 %
-% For tracking purposes => this is v1.3 - March 2012
+% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
+%               sigplanconf-guide.pdf
+%
+% Author:       Paul C. Anagnostopoulos
+%               Windfall Software
+%               978 371-2316
+%               paul@windfall.com
+%
+% Created:      15 February 2005
+%
+%-----------------------------------------------------------------------------
 
-\documentclass[10pt, twocolumn, times, nocopyrightspace, preprint]{sigplanconf} % Aptara syntax
+\documentclass[10pt, twocolumn, times, nocopyrightspace, preprint]{sigplanconf}
 
-% Package to generate and customize Algorithm as per ACM style
-\usepackage[ruled]{algorithm2e}
-\renewcommand{\algorithmcfname}{ALGORITHM}
-\SetAlFnt{\small}
-\SetAlCapFnt{\small}
-\SetAlCapNameFnt{\small}
-\SetAlCapHSkip{0pt}
-\IncMargin{-\parindent}
+% The following \documentclass options may be useful:
 
-% Metadata Information
+% preprint      Remove this option only once the paper is in final form.
+% 10pt          To set in 10-point type instead of 9-point.
+% 11pt          To set in 11-point type instead of 9-point.
+% authoryear    To obtain author/year citation style instead of numeric.
 
-\def\@acmVolume{0} %the volume
-\def\@acmNumber{0} %the number
-\def\@acmArticle{0} %article number
-\def\@articleSeq{0} %article Sequence
-\def\@acmPrice{0} %article price  % Changed to 15 - June 2012 - Gerry
-\def\@acmYear{2013} %the last two digits of the year, 
-\def\@acmMonth{12}  %the month
-\def\@journalName{Network Security} %the name of the ACM journal
-\def\@journalNameShort{CNT 5605} %the acronym of the ACM journal 
-\def\@journalCode{jn} %the code of the ACM journal 
-\def\@permissionCodeOne{0000-0000} %the permission code of the ACM journal
-\def\@doi{0000000.0000000} % These 'default' '0' values are over-ridden, during production, with 'correct' numbers entered via source .tex file - Gerry March 2012
+\usepackage{amsmath}
 
-% Document starts
 \begin{document}
 
-% Page heads
-% \markboth{G. Zhou et al.}{A Multifrequency MAC Specially Designed for WSN Applications}
+\special{papersize=8.5in,11in}
+\setlength{\pdfpageheight}{\paperheight}
+\setlength{\pdfpagewidth}{\paperwidth}
 
-% Title portion
-\title{Approximating Symbolic Execution with Dynamic Taint Analysis}
-\author{Clark Wood
-\affil{Florida State University}
-% NOTE! Affiliations placed here should be for the institution where the
-%       BULK of the research was done. If the author has gone to a new
-%       institution, before publication, the (above) affiliation should NOT be changed.
-%       The authors 'current' address may be given in the "Author's addresses:" block (below).
-%       So for example, Mr. Abdelzaher, the bulk of the research was done at UIUC, and he is
-%       currently affiliated with NASA.
-}
+\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
+\copyrightyear{20yy} 
+\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
+\doi{nnnnnnn.nnnnnnn}
 
-\category{CNT 5605}{Fall 2013}{Dynamic Taint Analysis, Symbolic Execution, Mutation, Fuzzing}
+% Uncomment one of the following two, if you are not going for the 
+% traditional copyright transfer agreement.
 
-\acmformat{Clark Wood, Project CNT 5412}
-% At a minimum you need to supply the author names, year and a title.
-% IMPORTANT:
-% Full first names whenever they are known, surname last, followed by a period.
-% In the case of two authors, 'and' is placed between them.
-% In the case of three or more authors, the serial comma is used, that is, all author names
-% except the last one but including the penultimate author's name are followed by a comma,
-% and then 'and' is placed before the final author's name.
-% If only first and middle initials are known, then each initial
-% is followed by a period and they are separated by a space.
-% The remaining information (journal title, volume, article number, date, etc.) is 'auto-generated'.
+%\exclusivelicense                % ACM gets exclusive license to publish, 
+                                  % you retain copyright
+
+%\permissiontopublish             % ACM gets nonexclusive license to publish
+                                  % (paid open-access papers, 
+                                  % short abstracts)
+
+\titlebanner{banner above paper title}        % These are ignored unless
+\preprintfooter{short description of paper}   % 'preprint' option specified.
+
+\title{Approximating Symbolic Execution Using Dynamic Taint Analysis}
+\subtitle{Subtitle Text, if any}
+
+\authorinfo{Clark Wood}
+           {Florida State University}
+           {clark.w.wood@gmail.com}
+%\authorinfo{Name2\and Name3}
+%           {Affiliation2/3}
+%           {Email2/3}
 
 \maketitle
+
+\begin{abstract}
+This is the text of the abstract.
+\end{abstract}
+
+\category{CR-number}{subcategory}{third-level}
+
+% general terms are not compulsory anymore, 
+% you may leave them out
+%\terms
+%term1, term2
+
+%\keywords
+%keyword1, keyword2
 
@@
 	I plan to implement dynamic taint analysis for files as input sources.
-I am basing my DTA heavily on Jonathan Salwan's work [N].
+I am basing my DTA heavily on Jonathan Salwan\'s work [N].
 I've been in contact with him and received permission to use his sample code.
 I can watch for all reads after a file is opened, then tag user input and follow it as it moves throughout the binary.
-	I will need to implement a system which keeps track of how taint propagates at the instruction level. A directed graph structure, with initial nodes representing the bytes of user input which are
+	I will need to implement a system which keeps track of how taint propagates at the instruction level.
+A directed graph structure, with initial nodes representing the bytes of user input and edges pointing to subsequent instructions which propagate taint, along with some metadata to make backsolving easier, seems like a reasonable data structure.
 
@@
 	\item [M] Luk, Chi-Keung, et al. "Pin: building customized program analysis tools with dynamic instrumentation." Acm Sigplan Notices. Vol. 40. No. 6. ACM, 2005.
-	\item [N] Salwan, Jonathan. \url{http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/}
+	\item [N] Salwan, Jonathan. Shell-storm.org %\url{http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/}
 
@@
 
+%\appendix
+%\section{Appendix Title}
+
+%This is the text of the appendix, if you need one.
+
+%\acks
+
+%Acknowledgments, if needed.
+
+% We recommend abbrvnat bibliography style.
+
+\bibliographystyle{abbrvnat}
+
+% The bibliography should be embedded for final submission.
+
+%\begin{thebibliography}{}
+%\softraggedright
+
+%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
+%P. Q. Smith, and X. Y. Jones. ...reference text...
+
+%\end{thebibliography}
+
 \end{document}
 
-% End of v2-acmsmall-sample.tex (March 2012) - Gerry Murray, ACM
+%                       Revision History
+%                       -------- -------
+%  Date         Person  Ver.    Change
+%  ----         ------  ----    ------
+
+%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2013-11-01 docs/paper/sigplanconf-template.tex
project proposal for network security. a little short

@@
 
+\subsection{Dynamic Taint Analysis}
+
 Dynamic taint analysis (DTA) is the process of locating sources of taint and following their propagation through a binary to data sinks.
@@
 
+\subsection{Symbolic Execution}
+
+Symbolic execution supplies symbolic instead of concrete values for input [O].
+This technique has been used to effectively detect bugs in software [Q], although historically it has required access to source code, which makes traditional symbolic execution infeasible in many vulnerability research situations where source code is unavailable.
+In addition, symbolic execution often uses instruction translators like QEMU [K] and satisfiability modulo theorem solvers like Z3 [P], which introduce significant overhead.
+This makes it difficult for symbolic execution to scale past the order of tens of thousands of lines of code.
+
+Current research focuses on carefully deciding when to use symbolic execution [J, CITE].
+Such so-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research [CITE].
+
+Without utilizing symbolic execution, however, it is difficult to automatically guarantee that all possible paths in a binary have been explored.
+Where most current research focuses on improving speed by using symbolic execution less, I propose to achieve similar code coverage to symbolic execution by implementing something similar to symbolic execution, but without using the SMT solvers and instruction emulation which tend to make symbolic execution slow.
+
 \section{Implementation}
@@
 
+\section{Setbacks}
+
+Dynamic taint analysis and fuzzing are hot topics of research, and so the area moves quickly.
+I have been trying to come up with ideas which are both novel and implementable within my graduation timeframe, but this has proved difficult.
+
+I have made progress using the Pin instrumentation framework, and feel comfortable developing code using the API.
+I have also read quite a few papers which have progressed my knowledge of the area, so in the worst case I have still learned a lot about a subject that interests me and written some code.
+I think, at the least, this can be a project option for my graduation, but I still think a thesis is possible.
+
+I need to:
+\begin{itemize}
+	\item Read more papers to make sure what I am proposing is novel and will not step on any toes.
+	\item Begin writing a prototype and prove that a subset of I am proposing is feasible.
+	\item Benchmark my prototype against modern applications like S2E and Peach Fuzzer to decide whether or not it makes sense to continue.
+\end{itemize}
+
 \section{References}
+
 \begin{itemize}
@@
 	\item [N] Salwan, Jonathan. Shell-storm.org %\url{http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/}
+	\item [O] King, James C. "Symbolic execution and program testing." Communications of the ACM 19.7 (1976): 385-394.
+	\item [P] De Moura, Leonardo, and Nikolaj Bjørner. "Z3: An efficient SMT solver." Tools and Algorithms for the Construction and Analysis of Systems. Springer Berlin Heidelberg, 2008. 337-340.
+	\item [Q] Godefroid, Patrice, Michael Y. Levin, and David Molnar. "Sage: Whitebox fuzzing for security testing." Queue 10.1 (2012): 20.
 

### 2013-11-01 docs/paper/sigplanconf-template.tex
progress on paper for project proposal

@@
 
-\title{Approximating Symbolic Execution Using Dynamic Taint Analysis}
-\subtitle{Subtitle Text, if any}
+\title{Pseudo-Symbolic Execution (Or Minimialistic Constraint Solving) Using Dynamic Taint Analysis and Backsolving}
+%\subtitle{Subtitle Text, if any}
 
@@
 
-\begin{abstract}
-This is the text of the abstract.
-\end{abstract}
+%\begin{abstract}
+%This is the text of the abstract.
+%\end{abstract}
 
@@
 This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce [CITES].
-Among these issues are i) efficient and thorough dynamic taint analysis [CITE], ii) the path explosion problem [CITE], and iii) the code coverage problem [CITE?].
+Among these issues are i) efficient and thorough dynamic taint analysis [CITE], ii) the path explosion problem [U], and iii) the code coverage problem [CITE?].
 Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
@@
 Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
-This is possible by tracking taint at the instruction level, then backsolving from every jump to the source of taint to come up with smarter ways to mutate user input and create new test cases.
+This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to come up with smarter ways to mutate user input and create new test cases.
 For instance, in the below example:
@@
 
+This works similarly to a constraint solver, but constraint solving appears to be a traditional bottleneck, requiring generating symbolic input, usually in a different language like LLVM intermediate representation [V] and passing execution to the constraint solver.
+
+I propose to avoid using a constraint solver entirely, and instead backsolve completely in memory.
+This is easier to implement than many of the clever optimizations used by S2E and could result in speedup over symbolic execution.
+
 There are a finite number of ways to compare data in x86, so I can create cases for all possible ways jumps are decided.
@@
 I am hopeful about the results because current selective symbolic execution engines still appear to introduce significant overhead (Between 6 and 78X overhead more than QEMU for S2E.
-Just QEMU is between 4 and 10 times slower on some benchmarks, more like 15 on others) [J, K, L].
+Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others) [J, K, L].
 In contrast, basic block counting using Intel Pin, the framework I am leveraging, introduced between 2 and 4X overhead [M].
@@
 I then plan to test against S2E and Peach Fuzzer.
+I already have this program written and have verified using IDA Pro that there are a many, many paths to try and find.
 
@@
 
-DTA has been used to implement smart mutation fuzzers [A], but I think my work is unique from and complementary to Bekrar's work.
+DTA has been used to implement smart mutation fuzzers [A, T, MORE], but I think my work is unique from and complementary to Bekrar's work.
 In [A], DTA is proposed as a way to intelligently decide which parts of user input should be mutated.
-I plan to add on to this idea by allowing smarter mutations to be selected by backsolving to decide which values are most likely to result in new paths being explored.
+In [T], dynamic taint analysis identified hot bytes, which were then modified randomly or with boundary values.
+
+I plan to add on to these ideas by allowing smarter mutations to be selected by backsolving to decide which values are most likely to result in new paths being explored.
+This has been done with symbolic execution before, but traditional symbolic execution is much more heavy-weight, both in time required to setup the environment and in overhead introduced to run the program, than my proposed approach.
 
@@
 
-Current research focuses on carefully deciding when to use symbolic execution [J, CITE].
-Such so-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research [CITE].
-
 Without utilizing symbolic execution, however, it is difficult to automatically guarantee that all possible paths in a binary have been explored.
 Where most current research focuses on improving speed by using symbolic execution less, I propose to achieve similar code coverage to symbolic execution by implementing something similar to symbolic execution, but without using the SMT solvers and instruction emulation which tend to make symbolic execution slow.
+
+Call-chain-backward symbolic execution has been proposed by [R], although this technique achieved a backward symbolic execution by iteratively applying a forward execution from successively farther away points in the program and the reducing the set of possible symbolic inputs.
+In contrast, I propose to avoid symbolic execution, forward or backward, by backsolving concretely and then applying heuristics to generate concrete input which is highly likely to result in exploring a new path.
+Symbolic execution never occurs, although I believe in many situations an equal degree of precision in determining new paths can be attained.
+
+\subsection{Concolic Execution}
+
+Current research focuses on carefully deciding when to use symbolic execution [J, T, CITE].
+So-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research [CITE].
 
@@
 I can watch for all reads after a file is opened, then tag user input and follow it as it moves throughout the binary.
+
 	I will need to implement a system which keeps track of how taint propagates at the instruction level.
 A directed graph structure, with initial nodes representing the bytes of user input and edges pointing to subsequent instructions which propagate taint, along with some metadata to make backsolving easier, seems like a reasonable data structure.
+
+Testing can begin on
 
@@
 	\item [Q] Godefroid, Patrice, Michael Y. Levin, and David Molnar. "Sage: Whitebox fuzzing for security testing." Queue 10.1 (2012): 20.
+	\item [R] Ma, Kin-Keung, et al. "Directed symbolic execution." Static Analysis. Springer Berlin Heidelberg, 2011. 95-111.
+	\item [S] Boyer, Robert S., Bernard Elspas, and Karl N. Levitt. "SELECT—a formal system for testing and debugging programs by symbolic execution." ACM SigPlan Notices. Vol. 10. No. 6. ACM, 1975.
+	\item [T] Wang, Tielei, et al. "Checksum-aware fuzzing combined with dynamic taint analysis and symbolic execution." ACM Transactions on Information and System Security (TISSEC) 14.2 (2011): 15.
+	\item [U] Cadar, Cristian, and Koushik Sen. "Symbolic execution for software testing: three decades later." Communications of the ACM 56.2 (2013): 82-90.
+	\item [V] Cadar, Cristian, Daniel Dunbar, and Dawson R. Engler. "KLEE: Unassisted and Automatic Generation of High-Coverage Tests for Complex Systems Programs." OSDI. Vol. 8. 2008.
 

### 2013-11-02 docs/paper/sigplanconf-template.tex
small additions to paper for project proposal

@@
 
+There are allowable situations in programs which are outside the scope of this program.
+For instance, programs can loop forever [X].
+These can be dealt with using reasonable heuristics and could be the subject of future research.
+
 \section{Research}
@@
 
-Current research focuses on carefully deciding when to use symbolic execution [J, T, CITE].
+Current research focuses on carefully deciding when and how to use symbolic execution [J, T, W, CITE].
 So-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research [CITE].
+
+Concolic testing has been shown to improve runtime while still allowing both wide and deep inspection of a program's execution tree, although it often still requires source code to be instrumented [X, Y].
 
@@
 
-Testing can begin on
+Testing can begin on dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
+If results appear promising I can try to make the fuzzer as complete as possible and begin running it on real-world applications.
+Achieving a noticeable speedup over modern symbolic execution would be the goal.
 
@@
 	\item [V] Cadar, Cristian, Daniel Dunbar, and Dawson R. Engler. "KLEE: Unassisted and Automatic Generation of High-Coverage Tests for Complex Systems Programs." OSDI. Vol. 8. 2008.
+	\item [W] McCamant, Stephen, et al. Transformation-aware symbolic execution for system test generation. Tech. Rep. UCB/EECS-2013-125, University of California, Berkeley (Jun 2013), 2013.
+	\item [X] Majumdar, Rupak, and Koushik Sen. "Hybrid concolic testing." Software Engineering, 2007. ICSE 2007. 29th International Conference on. IEEE, 2007.
+	\item [Y] Sen, Koushik, Darko Marinov, and Gul Agha. CUTE: a concolic unit testing engine for C. Vol. 30. No. 5. ACM, 2005.
 

### 2013-11-07 proj4/user.cpp
finishing user

@@ -13,17 +13,25 @@
 using namespace std;
 
 // Globals
+// TODO every 5 minutes, write this to a file
 vector<user> users;
 
-user::user(string n, string pw)
+// TODO
+// parseInput() for commands, receives string from main.cpp user input
+//                      returns string for main.cpp to handle
+// 
+
+user::user(string n, 
+           string pw,
+           string info,
+           unsigned int wins,
+           unsigned int losses)
 {
     name = n;
     password = pw;
     wins = 0;
     losses = 0;
-    isOnline = false;
 }
-
 
 
 /*
@@ -31,11 +39,8 @@ user::user(string n, string pw)
  *  Only the guest user may register new users.
  *  Usernames should be unique. 
  */
-void user::registerUser(string n, string pw)
+void registerUser(string n, string pw)
 {
-    if (this->getName() != "guest") {
-        return;
-    }
 
     for (vector<user>::iterator it = users.begin(); it != users.end(); ++it) {
 
@@ -44,11 +49,67 @@ void user::registerUser(string n, string pw)
         } 
     }
 
-    user newUser(n, pw);    
+    // Create new user with no wins, losses, or info.
+    user newUser(n, pw, "", 0, 0);    
     users.push_back(newUser);    
     return;
 
 }
+
+/*
+ *  Print a user's stats
+ *  TODO check tesla when it's back up so we can see how sample works
+ *
+ */ 
+string user::stats()
+{
+    string res = "";
+    res += "User: " + this->getName() + "\n";
+    res += "Info: " + this->getInfo() + "\n";
+    res += "Rating: " + "0.000" + "\n";
+    //res += "Wins: " + itoa(this->getWins()) + ", Losses: " + itoa(this->getLosses()) + "\n";;
+    //Info: <none>
+
+    //cwood is currently online.
+    return info;
+}
+
+
+// Mutator methods
+bool user::setName(string n)
+{
+    if (n == "") {
+        return false;
+    }
+
+    name = n;
+    return true;
+}
+
+bool user::setPassword(string pw)
+{
+    if (pw == "") {
+        return false;
+    }
+
+    password = pw;
+    return true;
+
+}
+
+bool user::setInfo(string i)   // Used for info command
+{
+    if (i == "") {
+        return false;
+    }
+
+    info = i;
+    return true;
+
+}
+
+
+
 
 #endif
 

### 2013-11-07 proj4/user.h

@@ -1,42 +1,57 @@
 #ifndef __USER_H__
 #define __USER_H__
 #include<string>
+#include<cstdlib>
 
 using namespace std;
+
+// TODO
+// error checking for NULL strings for user data get/set
+// 
+
+// General purpose function
+void registerUser(string n, string pw);
+
 
 class user {
 
     public:
-        user(string n, string pw);
-        ~user();
+        user(string n, 
+             string pw,
+             string info,
+             unsigned int wins,
+             unsigned int losses);
 
         // Accessor methods
-        string getName() {return name;};
-        string getPassword() {return password;};
-        unsigned int getWins() {return wins;};
-        unsigned int getLosses() {return losses;};
+        string getName()                        {return name;};
+        string getPassword()                    {return password;};
+        string getInfo()                        {return info;};
+        unsigned int getWins()                  {return wins;};
+        unsigned int getLosses()                {return losses;};
         // getMessages; 
-        bool getIsOnline() {return isOnline;};
 
         // Mutator methods
-        void setName(string n);
-        void setPassword(string pw);
-        void setWins(unsigned int i);
-        void setLosses(unsigned int i);
-        // getMessages;
-        void setIsOnline(bool b);
+        bool setName(string n);
+        bool setPassword(string pw);            // Used for passwd command
+        bool setInfo(string info);              // Used for info command
+        bool setWins(unsigned int i);
+        bool setLosses(unsigned int i);
+        // setMessages;
 
         // Other functions
-        void registerUser(string n, string pw);
+        void wonGame()                          {wins++;};
+        void LostGame()                         {losses++;};
+        string stats();
+        void observe(unsigned int gameNumber);
+        void unobserve();
 
     private:
-        //const static string guest = "guest";
         string name;
         string password;
+        string info;
         unsigned int wins;
         unsigned int losses;
         // messages;
-        bool isOnline;
 
 };
 

### 2013-11-07 proj4/main.cpp
user class ready

@@ -1,0 +1,18 @@
+#include "user.cpp"
+#include <iostream>
+using namespace std;
+
+int main() 
+{
+    user u("user", "pw");
+    //user u("user", "pw", "info", 12, 20);
+
+    cout << u.stats() << endl;
+
+
+    cout << registerUser("clark", "blah") << endl;
+    cout << registerUser("clark", "blah") << endl;
+
+
+
+}

### 2013-11-07 proj4/user.cpp

@@ -16,62 +16,73 @@ using namespace std;
 // TODO every 5 minutes, write this to a file
 vector<user> users;
 
-// TODO
-// parseInput() for commands, receives string from main.cpp user input
-//                      returns string for main.cpp to handle
-// 
 
+/*
+ *  User Constructor
+ */
 user::user(string n, 
            string pw,
-           string info,
-           unsigned int wins,
-           unsigned int losses)
+           string i = "<none>",
+           int w = 0,
+           int l = 0)
 {
     name = n;
     password = pw;
-    wins = 0;
-    losses = 0;
+    info = i;
+    wins = w;
+    losses = l;
 }
 
 
 /*
  *  Register a new user.
+ *  Returns string informing success/failure.
  *  Only the guest user may register new users.
  *  Usernames should be unique. 
  */
-void registerUser(string n, string pw)
+string registerUser(string n, string pw)
 {
 
     for (vector<user>::iterator it = users.begin(); it != users.end(); ++it) {
 
         if (it->getName() == n) {
-            return;    
+            return it->getName() + " registered already.";    
         } 
     }
 
     // Create new user with no wins, losses, or info.
-    user newUser(n, pw, "", 0, 0);    
+    user newUser(n, pw);    
     users.push_back(newUser);    
-    return;
+    return "User created.";
 
 }
 
 /*
- *  Print a user's stats
- *  TODO check tesla when it's back up so we can see how sample works
- *
+ *  Print a user's stats.
+ *  Returns string.
  */ 
 string user::stats()
 {
     string res = "";
     res += "User: " + this->getName() + "\n";
     res += "Info: " + this->getInfo() + "\n";
-    res += "Rating: " + "0.000" + "\n";
-    //res += "Wins: " + itoa(this->getWins()) + ", Losses: " + itoa(this->getLosses()) + "\n";;
-    //Info: <none>
+    res += "Rating: ";
+    res += "0.000";
+    res += "\n";
+    res += "Wins: ";
+    res += static_cast<ostringstream*>( &(ostringstream() << this->getWins() ) )->str();
+    res += ", Losses: ";
+    res += static_cast<ostringstream*>( &(ostringstream() << this->getLosses() ) )->str();
+    res += "\n";
 
-    //cwood is currently online.
-    return info;
+    /* TODO use this when we have a way to determine if user is online or not.
+    res += "\n";
+    res += this->getName();
+    res += " ";
[…]

### 2013-11-07 proj4/user.h

@@ -1,16 +1,14 @@
 #ifndef __USER_H__
 #define __USER_H__
 #include<string>
-#include<cstdlib>
+#include<iostream>
+#include<sstream>
 
 using namespace std;
 
-// TODO
-// error checking for NULL strings for user data get/set
-// 
 
-// General purpose function
-void registerUser(string n, string pw);
+// General purpose functions
+string registerUser(string n, string pw);
 
 
 class user {
@@ -19,38 +17,38 @@ class user {
         user(string n, 
              string pw,
              string info,
-             unsigned int wins,
-             unsigned int losses);
+              int wins,
+              int losses);
 
         // Accessor methods
         string getName()                        {return name;};
         string getPassword()                    {return password;};
         string getInfo()                        {return info;};
-        unsigned int getWins()                  {return wins;};
-        unsigned int getLosses()                {return losses;};
+        int getWins()                  {return wins;};
+        int getLosses()                {return losses;};
         // getMessages; 
 
         // Mutator methods
         bool setName(string n);
         bool setPassword(string pw);            // Used for passwd command
         bool setInfo(string info);              // Used for info command
-        bool setWins(unsigned int i);
-        bool setLosses(unsigned int i);
+        bool setWins( int i);
+        bool setLosses( int i);
         // setMessages;
 
         // Other functions
         void wonGame()                          {wins++;};
         void LostGame()                         {losses++;};
         string stats();
-        void observe(unsigned int gameNumber);
+        void observe( int gameNumber);
         void unobserve();
 
     private:
         string name;
         string password;
         string info;
-        unsigned int wins;
-        unsigned int losses;
+        int wins;
+        int losses;
         // messages;
 
 };

### 2013-11-07 docs/paper/sigplanconf-template.tex

@@
 Concolic testing has been shown to improve runtime while still allowing both wide and deep inspection of a program's execution tree, although it often still requires source code to be instrumented [X, Y].
+What I propose is akin to concolic testing, in that I am augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
+However, the lack of a heavyweight constraint solver and the ability to work on binaries without instrumenting or using source code in any way have, to the best of my knowledge, not yet been proposed.
 
@@
 I've been in contact with him and received permission to use his sample code.
-I can watch for all reads after a file is opened, then tag user input and follow it as it moves throughout the binary.
+I can watch for all reads after a file is opened, then tag user input at the byte level and follow it as it moves throughout the binary.
 
@@
 
-Dynamic taint analysis and fuzzing are hot topics of research, and so the area moves quickly.
+Dynamic taint analysis, symbolic execution and fuzzing are hot topics of research, and so the area moves quickly.
 I have been trying to come up with ideas which are both novel and implementable within my graduation timeframe, but this has proved difficult.
@@
 I have also read quite a few papers which have progressed my knowledge of the area, so in the worst case I have still learned a lot about a subject that interests me and written some code.
-I think, at the least, this can be a project option for my graduation, but I still think a thesis is possible.
+In addition, using the Pin API to instrument binaries, and debugging my pintools using tools like strace, has taught me more about assembly language, which is valuable for reverse engineering, a branch of information security I want to pursue a career in.
+
+I think, at the least, this can be a project option for my graduation, but I still believe a thesis is possible at this point.
 
@@
 	\item Benchmark my prototype against modern applications like S2E and Peach Fuzzer to decide whether or not it makes sense to continue.
+\end{itemize}
+
+Possible complications are:
+
+\begin{itemize}
+	\item Difficulty achieving completeness.
+Since there are many different ways that user input can be modified and compared, there will be many cases to account for.
+I think I can at least implement a subset of them in order to demonstrate speedup under a specific set of circumstances
+	\item This work is not novel.
+Until very recently I was looking at DTA more than symbolic execution, so it is hard to say whether my proposal is actually new.
+I'm doing my best to read all the relevant papers, and so far it appears that the use of a separate constraint solver or other satisfiability prover is a prerequisite of symbolic execution.
+	\item No noticeable speedup.
+Pin introduces noticeable overhead, and my ideas may simply not be faster than current approaches, even when test cases are reasonably tailored to work in my favor.
+In this case I simply go the project route unless something else strikes me.
+Although research with negative results is theoretically publishable, I don't see very much of it, so I assume it's a faux pas in computer science.
 \end{itemize}

### 2013-12-03 docs/paper/fsuthesis/sample/citations.tex
docs/paper/fsuthesis/thesis-template/paper.tex has my paper

%%% For this chapter, I need a few extra definitions.  First, I create a
%%% new macro so that I can easily type the BibTeX logo.

\def\BibTeX{{\rmfamily B\kern-.05em%
   \textsc{i\kern-.025em b}\kern-.08em\TeX}}

%%% Next I create a new environment called 'narrowref' simulating the
%%% appearance of the 'references' environment.  The margins are
%%% narrowed to set off the material a little better.  I also invoke
%%% the 'singlespaced' environment to demonstrate the look of the
%%% actual output of the references in case I'm processing this
%%% document using 'expanded' mode.  If you'd like to create your own
%%% environments for special purposes, refer to the references for the
%%% details.  For aspiring LaTeX experts, note that I reset
%%% the \parskip parameter *after* beginning the first paragraph
%%% with \leavevmode.  This is because I only want to use the new
%%% paragraph spacing between paragraphs contained *within* this
%%% environment, and the default paragraph spacing outside the
%%% environment.  (The \parskip glue is added before the start of a
%%% new paragraph, not at the end of the old paragraph.)

\newenvironment{narrowref}{
  \begin{singlespaced}
  \frenchspacing
  \setlength{\leftskip}{4em}
  \setlength{\rightskip}{3em}
  \setlength{\parindent}{-2em}
  \addvspace{0.5\baselineskip}
  \leavevmode
  \setlength{\parskip}{0.6\baselineskip}\ignorespaces}
 {\end{singlespaced}\addvspace{.5\baselineskip}}

%%% Now let the chapter begin.

\chapter{Citations and References}
In this chapter I demonstrate how to use features of \LaTeX{} and
the \pkg{fsuthesis} class to help me create a list of references or
bibliography.  There are two options: (1)~use the \lit{references}
environment and enter bibliographic entries with styling 
that I create myself, or (2)~use the \LaTeX\ \verb|\cite| macro
and \BibTeX{} to order and style the bibliographic entries according
to a pre-defined style sheet.

\section{Using the \texttt{references} Environment}
Let's start simply.  Assuming we don't have many citations, we'll
create a references section manually using the
\verb|\begin{references}| environment provided by the
\textsf{fsuthesis} class.  If your discipline has a style
guide for presenting references, you should use that information to
create your own entries.  Here are some example entries with
explicit formatting specified:
\begin{verbatim}
\begin{references}
Picaut, J., F. Masia, and Y. du Penhoat, 1997: An advective-reflective
conceptual model for the oscillatory nature of the ENSO.
\textit{Science}, \textbf{277}, 663--666.

Yasunari, T., 1990: Impact of Indian monsoon on the coupled
atmosphere/ocean system in the tropical Pacific.
\textit{Meteor. Atmos. Phys.}, \textbf{44}, 19--41.
\end{references}
\end{verbatim}

Note that I had to specify italics and bold-facing myself, according
to the style guide that I'm using.  (If you don't have a
discipline-specific style guide, see \cite{Anonymous:1993:CMS}
or \cite{Anonymous:2009:PMA} for lots of bibliographic examples.)
The \lit{references} environment provides exdented entries, spacing,
and a heading, but the rest of the formatting is up to you.  Likewise,
citations of these references within your document must be formatted
manually.  Once processed, the reference entries above look like the
following:
\begin{narrowref}
Picaut, J., F. Masia, and Y. du Penhoat, 1997: An advective-reflective
conceptual model for the oscillatory nature of the ENSO.
\textit{Science}, \textbf{277}, 663--666.

Yasunari, T., 1990: Impact of Indian monsoon on the coupled
atmosphere/ocean system in the tropical Pacific.
\textit{Meteor. Atmos. Phys.}, \textbf{44}, 19--41.
\end{narrowref}

%%% My \BibTeX macro fails me in this section title, because there are
%%% no smallcaps bold-faced fonts provided by default with my LaTeX
%%% installation.  For this one place, I do something slightly different.

\section{Citations and B{\small IB}\TeX}
If your thesis or dissertation does not have many citations or
references, then the \lit{references} environment may be all you
need. However, if you have more than a handful of citations, you owe
it to yourself to invest a little more energy into learning about the
powerful, time-saving features of \BibTeX.  To use \BibTeX,
bibliographic entries are added to an external file with attributes
identifying elements of the entry, such as authors, titles, journals,
etc.  You may then cite a reference in your document using its unique
key.  Many disciplines have developed large \BibTeX{} databases
already, so if you're lucky, you only need download a pre-built file
ready to go.  You can always add a few more references if those
entries don't already exist in the file you download.

For this sample document, I have created a small \BibTeX{}
bibliography database in a file called \lit{myrefs.bib} which is
excerpted from a larger collection of pre-generated \TeX-related
entries I downloaded from the web.  If your discipline does not
already distribute \BibTeX{} databases publicly, it's just a bit
more typing to create your own \BibTeX{} file.  As an example, here's
what a \BibTeX{} entry might look like:
\begin{verbatim}
@Article{Picaut:1997,                  
  author = "J. Picaut and F. Masia and Y. du Penhoat",
  title = "An advective-reflective conceptual model for
    the oscillatory nature of the ENSO",
  volume = "277",
  year = "1997",
  journal = "Science",
  pages = "663--666"
}
\end{verbatim}

Another advantage of the \BibTeX{} approach is that you can continue
to add to this database throughout your professional career, creating
entries as you read books and journal articles you may want to
reference in the future.  I encourage you to refer to the
standard \LaTeX{} references (e.g., \cite{Lamport:1994:LDP}
and \cite{Kopka:2004:GLT}) or to search the web for further
information on creating your own \BibTeX{} database.

Once you've created or downloaded a \BibTeX{} database, you may cite a
document using its unique \textit{key} as an argument to
the \LaTeX{} \verb|\cite| macro.  For example, in the previous
paragraph, I used the commands \verb|\cite{Lamport:1994:LDP}| and
\verb|\cite{Kopka:2004:GLT}|, where \lit{Lamport:1994:LDP} and
\lit{Kopka:2004:GLT} are the keys for their respective documents.
(The keys are defined in the \BibTeX\ database file.)  By making these
citations, the bibliographic entries for these documents will be
pulled from my \BibTeX{} database and added to the bibliography
automatically.

I can also add entries to the bibliography without having citations in
my text by using the \verb|\nocite{key}| command with the
desired \textit{key}.  If I want every entry in my \BibTeX{} file
inserted into my bibliography, then I can issue the
command \verb|\nocite{*}| as a shortcut.  (You don't have to worry
about citations being redundant: bibliographic entries will be
included only once no matter how many times they may be \verb|\cite|d
or \verb|\nocite|d in your document.)

\section{Alternative Citation and Bibliography Formats}
The pre-formatted version of this document uses the default citation
and bibliography formatting supplied by \LaTeX\ and \BibTeX.  There
are a few options to alter the appearance of citations and the
bibliography.  (See one of the references for your choices.)  However,
many disciplines and journals have created their own
advanced \BibTeX{} formatting styles, and you may want to use one of
these in your document.

\subsection{The \pkg{natbib} Package}
The \pkg{natbib} package, activated by
including \verb|\usepackage{natbib}| in the document preamble,
provides a common alternative to the default \LaTeX\ bibliography and
citation styles.  Among other things, this package will allow you to
make author--year citations in your document automatically (e.g.,
``Fargunkle et al., (2001)'') without any changes to the \BibTeX{}
database file.  In addition to the default \LaTeX\ \verb|\cite| macro,
the package provides several new macros for creating citations in
different contexts.

This document's driver file (\lit{thesis.tex}) has options for trying
out the \pkg{natbib} package.  Look for the \verb|\usepackage{natbib}|
line near the top of the file, and then scroll down to the
bibliography section for additional style selections you must specify
for the bibliography itself.  For a bibliography formatted according
to the style of the Association for Computing Machinery, for example,
you would issue the command \verb|\bibliographystyle{acm}| before
the \verb|\bibliography| command.  See \cite{Kopka:2004:GLT} (or
search the web) for more information on \pkg{natbib}.

\subsection{The \pkg{apacite} Package}
The APA (American Psychological Association) created another
commonly-used style guide for citations and bibliographic formatting.
The \LaTeX\ package \pkg{apacite} was designed to follow the APA
guidelines.  The package provides its own set of macros for specifying
citations in the document text, but it also has a mode for
compatibility with the popular \pkg{natbib} package.  With this
compatibility mode enabled, you may use \pkg{natbib}-style citation
commands in your document to generate the APA-style citations and
bibliography.  In addition, using this compatibility mode means that
you may switch between these two package alternatives without having
to re-write the citations in your document.

If you use the \pkg{apacite} package, and if you have also enabled
the \pkg{hyperref} package for your document, you \emph{must} enable
\lit{natbibapa} compatibility mode, or citations will give you
cryptic error messages when your document is processed.  Load the
package using the following line:
\begin{verbatim}
\usepackage[natbibapa]{apacite}
\end{verbatim}
The corresponding bibliography style would be set by the following 
command line:
\begin{verbatim}
\bibliographystyle{apacite}
\end{verbatim}

\section{Even More Options}

For those writing documents in the humanities or history disciplines,
there are several other options you may want to consider.  Because
of limitations in the older \BibTeX{} system, there is a move toward a
newer system called \pkg{biblatex}.  Bibliography styles based on this
system use different citation commands and generate bibliographies
in a different way.

For a comparison of the \BibTeX{} and \pkg{biblatex} systems, the
links below provide useful information.  To use the \pkg{biblatex}
package, you will have to customize the \textsf{fsuthesis} class to
accommodate.
\begin{itemize}\small
\item \textsf{http://tex.stackexchange.com/questions/25701/bibtex-vs-biber-and-biblatex-vs-natbib}
\item \textsf{http://tex.stackexchange.com/questions/5091/what-to-do-to-switch-to-biblatex}
\end{itemize}

\subsection{The \pkg{biblatex-chicago} Package}
While the \pkg{natbib} package provides an optional bibliography style
that closely follows the so-called ``Chicago style''
(see \cite{Anonymous:1993:CMS}), the \pkg{biblatex-chicago} package
provides many more features and stricter stylistic adherence over a
wider range of types of references.

This package makes use of a new ``back-end'' processor
called \lit{biber} rather than the \BibTeX{} program.  The
major \TeX{} distributions already include the required programs.
However, you may need to configure your environment to run \lit{biber}
rather than \BibTeX{} to process your document.

\subsection{The \pkg{biblatex-historian} Package}
A \pkg{historian} package is similar to \pkg{biblatex-chicago}, but it
is tuned for documents that require extensive footnote citations in the
Turabian/Chicago styles.  The user manual provides detailed
descriptions of fields, citation commands, and plenty of examples.
This package also requires the \lit{biber} back-end processor.

### 2013-12-03 docs/paper/fsuthesis/sample/figures.tex
docs/paper/fsuthesis/thesis-template/paper.tex has my paper

%%% There's not a lot of extra documentation in this file, other than
%%% the text itself.  On the other hand, you may be looking for
%%% a few examples of how to insert figures, so go ahead and peruse.

\chapter{Working with Graphics}

In this chapter, we'll be dealing with the inclusion and placement of
figures and other graphics in your thesis.  Usually a figure will be a
graphic of some type (e.g., a photograph, line drawing, chart) that
resides in a separate file external to your document.  You will need
to decide on a format for these figures.  If you are generating your
own graphics using other programs, you may have the option to choose
the output format.  Otherwise, you may need to use other software to
convert the graphic into a compatible format for inclusion in your
\LaTeX{} document.

\section{Raster and Vector Graphics}
Graphics for print media are generally in one of two classes: raster
images or vector drawings.  A \acro{JPEG} photograph is an example of
a raster format, where a matrix of pixels has a defined value.  Raster
images may be scaled up or down in size, but within limits. Scale such
an image too large and it will become ``pixelated'' or blocky.
Reduce the image too much, and finer details will be blurred or lost.
If you use raster images in your thesis, they should be generated with
a sufficiently high resolution that scaling artifacts will be
minimized.  For print media, a resolution of 300 to 600\,dpi (dots per
inch) might be typical.  For viewing on screen, a minimum resolution
of 100\,dpi may be adequate.  \acro{PNG}, \acro{JPEG} and \acro{GIF}
images are common examples of a raster type.  PhotoShop, The Gimp, and
other paint-type or photo-manipulation programs typically generate
raster images.  Scanning documents or other graphics will also
generate a raster image of some kind, usually in one of \acro{JPEG},
\acro{TIFF}, or \acro{PDF} formats.

In contrast, vector images will scale better.  Vector images are
usually line-drawings, text, and many kinds of graphs.  Vector images
can be scaled better because the pixel values are not defined until
after the scaling occurs, so the image can be rendered at the full
resolution of the output device, whether it be for print or screen.
Also, vector images are often encoded in a much smaller space than a
comparably-sized raster image.  Adobe Illustrator, CorelDRAW,
Inkscape, and Flash are examples of programs that generate vector
images.  \acro{WMF} and \acro{SVG} are also common vector formats,
though these types of files may not be included in your documents
directly: they must be first converted to another file format.

In generating figures for your document, if you have a choice, choose
a vector format, since it will provide the best scaling flexibility.
(See figure~\ref{ex-complete} for an example of a vector drawing.)
However, if you must include a photograph or scanned document of some
type, then be sure that the raster image has a sufficiently high
resolution for the intended publishing medium. (Figure~\ref{franklin}
is an example of a \acro{JPEG} raster image.)

\section{The \pkg{graphicx} Package}
The \LaTeX{} package \pkg{graphicx} allows you to insert external
PostScript or other files into your document.  There are other
figure-inclusion packages that you can use, but \pkg{graphicx} is
probably the most commonly-used, providing several useful features for
the task.

Using the MiK\TeX or Mac\TeX packages, you are probably using the
\lit{pdflatex} program to create a \acro{PDF} document directly from
the file sources.  If you look back at this document's ``driver'' file
\lit{thesis.tex}, you'll find a line that says
\verb|\usepackage[pdftex]{graphicx}|.  The option \lit{pdftex}
indicates that the \pkg{graphicx} package should employ the
\lit{pdftex} version of the driver to insert figures in a manner
compatible with the pdf\LaTeX{} processor.  Using this driver, all of
your external figures will need to be in \acro{PDF}, \acro{PNG},
\acro{JPEG}, or \acro{GIF} format.  Other types of graphics files will
need to be converted to one of these formats before they may be
included in your document.

An alternative driver to \lit{pdftex} is the option \lit{dvips}, which
will require all your figures to be in Encapsulated PostScript
(\acro{EPS}) format.  Other formats will need to be first converted to
PostScript.  (Both PostScript and \acro{PDF} formats may contain
either raster or vector images, or even both at once.)  This is the
driver you should use if you are using the program \lit{latex} instead
of \lit{pdflatex} to process your document.  The \acro{DVI} output
from the \lit{latex} program is later processed by the \lit{dvips}
program to convert the output to PostScript, which may then be
converted to \acro{PDF}.  If you have lots of figures in PostScript
format already, or if you will be using one of many \LaTeX\ packages
that creates PostScript figures, you may need to use this driver (and
you probably know what you're doing already).

For the purposes of this sample document, the figures are provided in
both \acro{EPS} and \acro{PDF} forms, so you may choose to use either
the $\mbox{\lit{latex}}\rightarrow\mbox{\lit{dvips}}$ command chain,
or \lit{pdflatex} to process this document. In fact, there's some
fancy code in the \lit{thesis.tex} file that chooses the right driver
depending on whether you're running \lit{pdflatex} or \lit{latex} on
these source texts.

\section{PostScript, Encapsulated PostScript, and PDF}
PostScript is a programming language for putting marks on a page.  As
such, PostScript files can usually be edited using plain text editors,
should that ever be necessary.  A file containing Encapsulated
PostScript conforms to additional standards, allowing the graphic to
be manipulated or included in other PostScript programs more readily.

As far as \LaTeX{} is concerned, the most important feature of an
Encapsulated PostScript file is the \lit{\%\%BoundingBox}, which is
defined as the smallest rectangle that completely encloses the figure.
Two sets of $x$- and $y$-coordinates describe the bounding box; the
first $(x,y)$ pair gives the lower left-hand coordinates of box
relative to the bottom left-hand corner of the page, and the second
pair of coordinates identify the upper right-hand corner of the
bounding box.  You normally don't have to worry about this information
at all, but if a PostScript figure does not contain
\lit{\%\%BoundingBox} information, or if the \lit{\%\%BoundingBox} is
incorrect, the \pkg{graphicx} package allows you to specify the
bounding box coordinates yourself when you insert the figure into your
document.

A \acro{PDF} figure will have its dimensions embedded within it
already, so you will not need to make any special preparations to
include it in your document. \acro{PDF} has a lot in common with
PostScript, and the two formats may be converted from one to the
other, usually without any loss in quality.  Depending on your
distribution of \LaTeX, you may have a program already installed which
converts \acro{EPS} files to \acro{PDF}.  One of the simplest
converters is the program \lit{epstopdf}, which can be executed as
follows:
\begin{verbatim}
epstopdf myfig.eps
\end{verbatim}
A Windows version of this program might pop up a user interface for
fine-tuning the figure conversion, while the Unix/Linux version of the
program will simply do the conversion, creating \lit{myfig.pdf}
without any intervention required.

\section{Inserting Figures}
The basic mechanics of including a PostScript graphic (\lit{dvips}
driver) or \acro{PDF} graphic (\lit{pdftex} driver) are relatively
simple:
\begin{verbatim}
\includegraphics{figurefile}
\end{verbatim}
This command will insert the graphic contained in the file
\lit{figurefile} at that particular location in the text.  The file
name may have optional extensions, depending on the driver.  For
example, the \lit{dvips} driver will recognize the \lit{.ps} or
\lit{.eps} file extensions, while the \lit{pdftex} driver will
recognize extensions \lit{.pdf} and \lit{.jpg}.  \LaTeX{} will leave
space for the graphic according to the bounding box information that
the file contains.

For inclusion in your thesis or dissertation, a graphic will normally
be labeled and given a caption.  To do this, you will wrap the
\verb|\includegraphics| command in a \lit{figure} environment.
Figures will usually ``float'' from the location where they were
defined.  By default, \LaTeX{} will try to place figures at the bottom
of the current page (if there's sufficient room), then at the top of
the next available page.  Failing that, \LaTeX{} will place figures
onto their own page.  The \verb|\caption| command will number the
figure automatically.  If you need to refer to the figure in your
text, include a \verb|\label| command following the \verb|\caption|,
and then use the \verb|\ref| and \verb|\pageref| commands to
retrieve the figure number and figure's page number, as required.

As a complete example, refer to Figure~\ref{ex-complete}.  I used the
following commands to include the figure graphic:
\begin{verbatim}
\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{figs/fleur}
\end{center}
\caption{This is a simple figure, ...}
\label{ex-complete}
\end{figure}
\end{verbatim}
In this case, the graphic file is located in the folder \lit{figs},
and the complete file name is either \lit{fleur.eps} or
\lit{fleur.pdf}. If I'm using the \lit{dvips} driver, the \lit{.eps}
extension is added automatically; likewise, the \lit{.pdf} extension
would be added if I am using the \lit{pdftex} driver.  To
center the graphic horizontally, I enclosed the
\verb|\includegraphics| command in a \lit{center} environment. The
\verb|\caption| command handles text like this: a short, one-line
caption will be horizontally centered, and a longer caption will be
broken into multiple lines as required, with narrower margins.

At the beginning of the previous paragraph, I typed
\verb|Figure~\ref{ex-complete}| to retrieve the figure number.  If I
use this mechanism for all of the equations, tables, and figures in my
manuscript, I never have to worry about renumbering anything should I
choose to move blocks of text or figures around.  I can also state that
Figure~\ref{ex-complete} will be found on page~\pageref{ex-complete}
by typing
\begin{verbatim}
Figure~\ref{ex-complete} will be found on page~\pageref{ex-complete}
\end{verbatim}

\begin{figure}
\begin{center}
\includegraphics[scale=0.6]{figs/fleur}
\end{center}
\caption{This is a simple figure, but a complete example. This figure
is a vector drawing, so it may be scaled up or down without loss of
precision.}
\label{ex-complete}
\end{figure}

The \verb|\includegraphics| command has several optional arguments
which will allow you to adjust figure position, bounding box,
rotation, scaling, and other elements, without having to edit the
figure itself.  Figure~\ref{franklin} displays an image in its raw
state, and then a close-up, rotated image of a segment of the same
PostScript graphic.  A complete description of the all the options
available is best left for the \pkg{graphicx} package manual page, but
the transformed image was accomplished with the following
\verb|\includegraphics| line:
\begin{verbatim}
\includegraphics[viewport=.9in 2.1in 1.15in 2.35in,clip,
    scale=10.67,angle=90]{figs/ben}
\end{verbatim}

\begin{figure}
\begin{center}
\includegraphics{figs/ben}
\includegraphics[viewport=.9in 2.1in 1.15in 2.35in,clip,
    scale=10.67,angle=90]{figs/ben}
\end{center}
\caption{Benjamin Franklin, in raw form (left), and close-up and
  rotated (right).  (Notice that the close-up figure displays
  ``pixelation'' effects of a raster image scaled too large.)}
\label{franklin}
\end{figure}

\section{Inserting Forms or Full-Page Figures}
If you need to include a copy of an approval form or certification in
your document, you can take advantage of a few additional options of
the \verb|\includegraphics| command to allow the figure to occupy most
of the page.  If you already have an electronic version of a full-page
form, you can eliminate some of the white space border of the
page before insertion to reduce the amount of scaling required.
As an example, the file \lit{rights} in the \lit{figs} folder is a
full page of text with 1-inch borders on all sides.
I can tell \verb|\includegraphics| to trim this space and fill
the rest of the page with a command like this:
\begin{verbatim}
\includegraphics[trim=1in 1in 1in 1in, clip,
    height=\textheight]{figs/rights}}
\end{verbatim}

The \verb|trim| and \verb|clip| options remove the whitespace border.
The \verb|height=\textheight| command stretches or compresses the
figure to the full text column height, allowing room for the page
number. On the other hand, if the full-page image needs a caption,
you'll need to reduce the scale a bit more to fit it in.  In addition,
I could draw an outline around the figure with an \verb|\fbox| command
to give it a page-within-a-page appearance.  In this case, I might
want to leave a small amount of whitespace around the text of the
inserted page.  Making these modifications and leaving a bit of room
for the caption gives us the commands below.  You can see the results
on page~\pageref{fig:rights}.
\begin{verbatim}
\begin{figure}
\fbox{\includegraphics[trim=.9in .9in .9in .9in,clip,
        height=7.8in]{figs/rights}}
\caption{The Bill of Rights}
\label{fig:rights}
\end{figure}
\end{verbatim}

\begin{figure}\centering
\fbox{\includegraphics[trim=.9in .9in .9in .9in, clip,
           height=7.8in]{figs/rights}}
\caption{The Bill of Rights}
\label{fig:rights}
\end{figure}

\section{Musical Examples}
If your thesis or dissertation requires you to include musical
examples, the \pkg{fsuthesis} class has an environment already set up
for you.  Each musical example should be in its own PostScript
\acro{EPS} file or \acro{PDF} file (depending on the \pkg{graphicx}
driver you are using).  Then, rather than using the \lit{figure}
environment, you would use the \lit{musex} environment as demonstrated
here to create Example~\ref{mus:bass-ode}:
\begin{verbatim}
\begin{musex}
\begin{center}
\includegraphics{figs/freude}
\end{center}
\caption{The bass soloist's opening statement in the 9th Symphony.
  \label{mus:bass-ode}}
\end{musex}
\end{verbatim}

As with figures, the caption follows the graphic.  However, the
caption will be automatically titled with ``Example'' rather than
``Figure''.  If your document contains more than one musical example,
they can be listed in their own table by using the command
\verb|\listofmusex| in the front matter section of your document.

\begin{musex}
\begin{center}
\includegraphics{figs/freude}
\end{center}
\caption{The bass soloist's opening statement in the 9th Symphony.
\label{mus:bass-ode}}
\end{musex}

\section{Further Information}
This chapter intended to provide a brief overview of figure inclusion,
along with a few simple examples.  If your figure-insertion needs have
not yet been addressed, you should look up the document \textit{Using
  Imported Graphics in \LaTeX{} and pdf\LaTeX} by Keith Reckdahl,
which is part of the Comprehensive \TeX{} Archive Network (CTAN).
This document provides a wealth of detail about figure manipulation,
insertion, and placement.

In addition to the inclusion of external figures, \LaTeX{} provides
several environments and packages for creating figures mathematically
(usually technical line-drawings) within a \LaTeX{} document itself.
Investigate the \pkg{picture} package and its extensions \pkg{epic}
and \pkg{eepic}.  Other figures and text manipulations can be carried
out with the \pkg{pstricks} package.  The program \MP\ can generate
precise renderings of mathematical objects and diagrams.  And there
are many more utilities and packages to assist you.

### 2013-12-03 docs/paper/fsuthesis/sample/history.tex
docs/paper/fsuthesis/thesis-template/paper.tex has my paper

\chapter{The World According to Student~Bloopers}

One of the fringe benefits of being an English or History teacher is
receiving the occasional jewel of a student blooper in an essay. I
have pasted together the following ``history'' of the world from
certifiably genuine student bloopers collected by teachers throughout
the United States, from eight grade through college level. Read
carefully, and you will learn a lot.

The inhabitants of Egypt were called mummies. They lived in the Sarah
Dessert and traveled by Camelot. The climate of the Sarah is such that
the inhabitants have to live elsewhere, so certain areas of the
dessert are cultivated by irritation. The Egyptians built the
Pyramids in the shape of a huge triangular cube. The Pramids are a
range of mountains between France and Spain.

The Bible is full of interesting caricatures. In the first book of the
Bible, Guinesses, Adam and Eve were created from an apple tree. One of
their children, Cain, asked ``Am I my brother's son?'' God asked Abraham
to sacrifice Issac on Mount Montezuma. Jacob, son of Issac, stole his
brother's birthmark. Jacob was a partiarch who brought up his twelve
sons to be partiarchs, but they did not take to it. One of Jacob's
sons, Joseph, gave refuse to the Israelites.

Pharaoh forced the Hebrew slaves to make bread without straw. Moses
led them to the Red Sea, where they made unleavened bread, which is
bread made without any ingredients. Afterwards, Moses went up on Mount
Cyanide to get the ten commandments. David was a Hebrew king skilled
at playing the liar. He fougth with the Philatelists, a race of people
who lived in Biblical times. Solomon, one of David's sons, had 500
wives and 500 porcupines.

Without the Greeks, we wouldn't have history. The Greeks invented
three kinds of columns---Corinthian, Doric and Ironic. They also had
myths. A myth is a female moth. One myth says that the mother of
Achilles dipped him in the River Stynx until he became
intolerable. Achilles appears in ``The Illiad'', by Homer. Homer also
wrote the ``Oddity'', in which Penelope was the last hardship that
Ulysses endured on his journey. Actually, Homer was not written by
Homer but by another man of that name.

Socrates was a famous Greek teacher who went around giving people
advice. They killed him. Socrates died from an overdose of wedlock.

In the Olympic Games, Greeks ran races, jumped, hurled the biscuits,
and threw the java. The reward to the victor was a coral wreath. The
government of Athen was democratic because the people took the law
into their own hands. There were no wars in Greece, as the mountains
were so high that they couldn't climb over to see what their neighbors
were doing. When they fought the Parisians, the Greeks were
outnumbered because the Persians had more men.

Eventually, the Ramons conquered the Geeks. History call people Romans
because they never stayed in one place for very long. At Roman
banquets, the guests wore garlic in their hair. Julius Caesar
extinguished himself on the battlefields of Gaul. The Ides of March
killed him because they thought he was going to be made king. Nero was
a cruel tyrany who would torture his poor subjects by playing the
fiddle to them.

Then came the Middle Ages. King Alfred conquered the Dames, King
Arthur lived in the Age of Shivery, King Harlod mustarded his troops
before the Battle of Hastings, Joan of Arc was cannonized by George
Bernard Shaw, and the victims of the Black Death grew boobs on their
necks. Finally, the Magna Carta provided that no free man should be
hanged twice for the same offense.

In midevil times most of the people were alliterate. The greatest
writer of the time was Chaucer, who wrote many poems and verse and
also wrote literature. Another tale tells of William Tell, who shot
an arrow through an apple while standing on his son's head.

The Renaissance was an age in which more individuals felt the value of
their human being. Martin Luther was nailed to the church door at
Wittenberg for selling papal indulgences. He died a horrible death,
being excommunicated by a bull. It was the painter Donatello's
interest in the female nude that made him the father of the
Renaissance. It was an age of great inventions and
discoveries. Gutenberg invented the Bible. Sir Walter Raleigh is a
historical figure because he invented cigarettes. Another important
invention was the circulation of blood. Sir Francis Drake circumcised
the world with a 100-foot clipper.

The government of England was a limited mockery. Henry VIII found
walking difficult because he had an abbess on his knee. Queen
Elizabeth was the ``Virgin Queen.'' As a queen she was a success. When
Elizabeth exposed herself before her troops, they all shouted
``hurrah.'' Then her navy went out and defeated the Spanish Armadillo.

The greatest writer of the Renaissance was William
Shakespear. Shakespear never made much money and is famous only
because of his plays. He lived in Windsor with his merry wives,
writing tragedies, comedies and errors. In one of Shakespear's famous
plays, Hamlet rations out his situation by relieving himself in a long
soliloquy. In another, Lady Macbeth tries to convince Macbeth to
kill the King by attacking his manhood. Romeo and Juliet are an
example of a heroic couplet. Writing at the same time as Shakespear
was Miquel Cervantes. He wrote ``Donkey Hote''. The next great author
was John Milton. Milton wrote ``Paradise Lost.'' Then his wife dies and
he wrote ``Paradise Regained.''

During the Renaissance America began. Christopher Columbus was a great
navigator who discovered America while cursing about the Atlantic. His
ships were called the Nina, the Pinta, and the Santa Fe. Later the
Pilgrims crossed the Ocean, and the was called the Pilgrim's
Progress. When they landed at Plymouth Rock, they were greeted by
Indians, who came down the hill rolling their was hoops before
them. The Indian squabs carried porposies on their back. Many of the
Indian heroes were killed, along with their cabooses, which proved
very fatal to them. The winter of 1620 was a hard one for the
settlers. Many people died and many babies were born. Captain John
Smith was responsible for all this.

One of the causes of the Revolutionary Wars was the English put tacks
in their tea. Also, the colonists would send their pacels through the
post without stamps. During the War, Red Coats and Paul Revere was
throwing balls over stone walls. The dogs were barking and the
peacocks crowing. Finally, the colonists won the War and no longer had
to pay for taxis.

Delegates from the original thirteen states formed the Contented
Congress. Thomas Jefferson, a Virgin, and Benjamin Franklin were two
singers of the Declaration of Independence. Franklin had gone to
Boston carrying all his clothes in his pocket and a loaf of bread
under each arm. He invented electricity by rubbing cats backwards
and declared ``a horse divided against itself cannot stand.'' Franklin
died in 1790 and is still dead.

George Washington married Matha Curtis and in due time became the
Father of Our Country. Them the Constitution of the United States was
adopted to secure domestic hostility. Under the Constitution the
people enjoyed the right to keep bare arms.

Abraham Lincoln became America's greatest Precedent. Lincoln's mother
died in infancy, and he was born in a log cabin which he built with
his own hands. When Lincoln was President, he wore only a tall silk
hat. He said, ``In onion there is strength.'' Abraham Lincoln write
the Gettysburg address while traveling from Washington to Gettysburg
on the back of an envelope. He also signed the Emasculation
Proclamation, and the Fourteenth Amendment gave the ex-Negroes
citizenship. But the Clue Clux Clan would torcher and lynch the
ex-Negroes and other innocent victims. On the night of April 14, 1865,
Lincoln went to the theater and got shot in his seat by one of the
actors in a moving picture show. The believed assinator was John
Wilkes Booth, a supposedly insane actor. This ruined Booth's career.

Meanwhile in Europe, the enlightenment was a reasonable time. Voltare
invented electricity and also wrote a book called ``Candy''. Gravity was
invented by Issac Walton. It is chiefly noticeable in the Autumn, when
the apples are flaling off the trees.

Bach was the most famous composer in the world, and so was
Handel. Handel was half German, half Italian and half English. He was
very large. Bach died from 1750 to the present. Beethoven wrote music
even though he was deaf. He was so deaf he wrote loud music. He took
long walks in the forest even when everyone was calling for
him. Beethoven expired in 1827 and later died for this.

France was in a very serious state. The French Revolution was
accomplished before it happened. The Marseillaise was the theme song
of the French Revolution, and it catapulted into Napoleon. During
the Napoleonic Wars, the crowned heads of Europe were trembling in
their shoes. Then the Spanish gorrilas came down from the hills and
nipped at Napoleon's flanks. Napoleon became ill with bladder problems
and was very tense and unrestrained. He wanted an heir to inheret his
power, but since Josephine was a baroness, she couldn't bear him any
children.

The sun never set on the British Empire because the British Empire is
in the East and the sun sets in the West. Queen Victoria was the
longest queen. She sat on a thorn for 63 years. He reclining years and
finally the end of her life were exemplatory of a great
personality. Her death was the final event which ended her reign.

The nineteenth century was a time of many great inventions and
thoughts. The invention of the steamboat caused a network of rivers to
spring up. Cyrus McCormick invented the McCormick Raper, which did the
work of a hundred men. Samuel Morse invented a code for
telepathy. Louis Pastuer discovered a cure for rabbis. Charles Darwin
was a naturailst who wrote the ``Organ of the Species''. Madman Curie
discovered radium. And Karl Marx became one of the Marx Brothers.

The First World War, cause by the assignation of the Arch-Duck by a
surf, ushered in a new error in the anals of human history.

\begin{flushright}
\textit{--- Richard Lederer, St.~Paul's School}
\end{flushright}

### 2013-12-03 docs/paper/fsuthesis/thesis-template/paper.tex
docs/paper/fsuthesis/thesis-template/paper.tex has my paper

--- 2013-11-07 docs/paper/sigplanconf-template.tex
@@
-%-----------------------------------------------------------------------------
-%
-%               Template for sigplanconf LaTeX Class
-%
-% Name:         sigplanconf-template.tex
-%
-% Purpose:      A template for sigplanconf.cls, which is a LaTeX 2e class
-%               file for SIGPLAN conference proceedings.
-%
-% Guide:        Refer to "Author's Guide to the ACM SIGPLAN Class,"
-%               sigplanconf-guide.pdf
-%
-% Author:       Paul C. Anagnostopoulos
-%               Windfall Software
-%               978 371-2316
-%               paul@windfall.com
-%
-% Created:      15 February 2005
-%
-%-----------------------------------------------------------------------------
+% This is a "bare-bones" thesis template file.  For examples of how to
+% use a few more LaTeX features, look in the 'sample' folder.  Read
+% the User Guide for documentation of the 'fsuthesis' class features.
 
-\documentclass[10pt, twocolumn, times, nocopyrightspace, preprint]{sigplanconf}
+\documentclass[11pt,expanded,copyright]{fsuthesis}
 
-% The following \documentclass options may be useful:
+% Additional packages may be loaded here.
 
-% preprint      Remove this option only once the paper is in final form.
-% 10pt          To set in 10-point type instead of 9-point.
-% 11pt          To set in 11-point type instead of 9-point.
-% authoryear    To obtain author/year citation style instead of numeric.
+\title{A Backsolving Technique Using Dynamic Taint Analysis}
+\author{Clark Wood}
+\college{College of Arty Science}
+\department{Department of Computer Science} % Delete if no department
+\manuscripttype{Thesis}              % [Thesis, Dissertation, Treatise]
+\degree{Masters of Science}                 
+\semester{Spring}                            % [Spring, Summer, Fall]
+\degreeyear{2014}
+\defensedate{Spring 2014}
 
-\usepackage{amsmath}
+%\subject{My Topic}
+%\keywords{keyterm1; keyterm2; keyterm3; ...}
+
+%\committeeperson{Faux Causson Yorverk}{Professor Directing Thesis}
+%\committeeperson{Verda Boizaar}{University Representative}
+%\committeeperson{Beauxeau D'Claune}{Committee Member}
+%\committeeperson{Arlip Zarseeld}{Committee Member}
+
+\clubpenalty=9999
+\widowpenalty=9999
 
@@
 
-\special{papersize=8.5in,11in}
-\setlength{\pdfpageheight}{\paperheight}
-\setlength{\pdfpagewidth}{\paperwidth}
+\frontmatter
+\maketitle
+\makecommitteepage
 
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
+%\begin{dedication}
+%\end{dedication}
 
-% Uncomment one of the following two, if you are not going for the 
-% traditional copyright transfer agreement.
+%\begin{acknowledgments}
+%\end{acknowledgments}
 
-%\exclusivelicense                % ACM gets exclusive license to publish, 
-                                  % you retain copyright
+\tableofcontents
+%\listoftables
+%\listoffigures
+%\listofmusex
 
-%\permissiontopublish             % ACM gets nonexclusive license to publish
-                                  % (paid open-access papers, 
-                                  % short abstracts)
+%\begin{listofsymbols}
+%\end{listofsymbols}
 
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
-
-\title{Pseudo-Symbolic Execution (Or Minimialistic Constraint Solving) Using Dynamic Taint Analysis and Backsolving}
-%\subtitle{Subtitle Text, if any}
-
-\authorinfo{Clark Wood}
-           {Florida State University}
-           {clark.w.wood@gmail.com}
-%\authorinfo{Name2\and Name3}
-%           {Affiliation2/3}
-%           {Email2/3}
-
-\maketitle
+%\begin{listofabbrevs}
+%\end{listofabbrevs}
 
 %\begin{abstract}
-%This is the text of the abstract.
+%This is my abstract.
 %\end{abstract}
 
-\category{CR-number}{subcategory}{third-level}
+\mainmatter
 
-% general terms are not compulsory anymore, 
-% you may leave them out
-%\terms
-%term1, term2
-
-%\keywords
-%keyword1, keyword2
+%\input chapter1
 
@@
 Finding exploitable bugs in binaries is a difficult and lucrative endeavour.
-Fuzzing, or the feeding of random input into processes to try and detect vulnerable conditions [CITE], is one technique used by researchers and analysts.
+Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions [CITE], is one technique used by researchers and analysts.
 Applications tested for vulnerabilities are often black boxes because source code is unavailable.
@@
 This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to come up with smarter ways to mutate user input and create new test cases.
-For instance, in the below example:
+For instance, in the figure 1 example:
 
 \begin{verbatim}
-mv eax, userInput1
-mv ebx, userInput2
-cmp eax, ebx
-jge 0xDEADBEEF
+figure 1:
+call read
+mov eax, [ebp - val]
+inc eax
+mul eax, 5
+cmp eax, 42
+jnz 0x8BADMEAT
 \end{verbatim}
 
-If we already had a test case where userInput1 equalled 10 and userInput2 equalled 5, this test case would jump to 0xDEADBEEF.
-To generate a test case where we would not jump, we take the complement of the jge instruction's comparison function, which would be "less than".
-We can find the last instruction that modified the Z flag, which is how jge decides to jump or not.
-We see that this compare instruction was tained by the eax and ebx registers, which were in turn tainted by userInputs 1 and 2.
-Since we can impact both values in the comparison, it is easy to modify user input smartly to alter the value of the Z flag and jump during the next execution.
-Perhaps we could switch the values, or auto-increment/decrement one until we satisfy the needed comparison, or mutate values randomly.
+If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADMEAT.
+With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted).
+After some number of transformations, perhaps zero, to the value in the eax register, we see a compare instruction, which checks eax's value against an immediate value.
+Then we can keep track of specific taint sources, and can record any movements or transformations, we have all the necessary information to "solve" the branch.
+Once we reach the tainted branch, we know that user input can affect whether we jump or not, and consequently we can backsolve to find out how to affect the branch instruction.
+In particular, we know the conditional jump instruction jnz depends on the Z flag in the EFLAGS register.
+We record whatever instruction last modified each flag in the Z flags register, so we handle the compare instruction next.
+Because we have kept track of taint propagation, we know we can affect the value of eax, but not 42, since it is an immediate value, so we know we need to make the value in eax equal 42.
+We follow the instructions that have modified the value of eax and use any appropriate operands involved with the inverse operation of the one originally performed on the value to reverse the transformations to eax's value.
+Finally, we notice eax originally received taint when a value was moved from memory, which was read into memory using the read syscall.
 
@@
 
-There are a finite number of ways to compare data in x86, so I can create cases for all possible ways jumps are decided.
+Because there are a finite number of conditional jumps, all of which depend on different flags or combinations of flags in the EFLAGS register, and a finite number of instructions that modify the EFLAGS register in x86, I can create cases for all possible ways jumps are decided.
 I only want to prove this is possible however, so I will only implement a subset and instead comment on how to implement the other comparisons.
+
+\section{Related Work}
+
+The major impetus for this work is outlined in "A Taint Based Approach for Smart Fuzzing".
+This paper proposes a fuzzing tool architecture, involving vulnerability detection, followed by taint analysis based upon found vulnerabilities, which drives the generation of intelligent tests.
+As tests are run they are checked to ensure they provide adequate code coverage, and results are carefully monitored for interesting situations like crashes [A].
+The paper also serves as an excellent explanation of the current state and future of fuzzing.
+In particular, they suggest combining taint analysis with backward slicing.
+The technique discussed in the paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
 
@@
 This allows the program to easily track and compare execution paths by creating a list of jump locations.
-Since the world is moving more and more toward 64-bit architectures, I plan to implement the technique for x86\_64.
+Since the world is moving more and more toward 64-bit architectures, I plan to implement the technique for 32-bit x86 assembly.
+This is because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both 32 vs.
+64-bit and the flavor of architecture (ARM, x86, PowerPC), since compilers try to adhere to the C standard.
 
@@
 A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, should create an appropriate binary.
-I then plan to test against S2E and Peach Fuzzer.
+I then plan to test against S2E and Peach Fuzzer [Z].
 I already have this program written and have verified using IDA Pro that there are a many, many paths to try and find.
@@
 
-\section{Research}
+\section{Techniques}
+
+Several valuable techniques to improve fuzzers' code coverage have evolved over the years.
+Two, in particular, inspire this work directly: Dynamic Taint Analysis and Concolic Execution.
+Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing.
+Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims to ameliorate the path explosion problem.
+These each come with their own drawbacks, a primary one of which is the lack of automated instrumentation.
+Historically, symbolic execution required a programmer to directly instrument source code, but much research is now focused on automating as much as possible.
 
@@
 
-Dynamic taint analysis (DTA) is the process of locating sources of taint and following their propagation through a binary to data sinks.
+DTA is the process of locating sources of taint and following their propagation through a binary to data sinks.
 Since, for exploitation, bugs must be triggered by user input, DTA usually identifies all user input (files, command line arguments, UI interactions, ...) as tainted, and marks it accordingly.
@@
 
-I plan to implement dynamic taint analysis for files as input sources.
+I implement dynamic taint analysis for files as input sources.
 I am basing my DTA heavily on Jonathan Salwan\'s work [N].
-I've been in contact with him and received permission to use his sample code.
-I can watch for all reads after a file is opened, then tag user input at the byte level and follow it as it moves throughout the binary.
+Currently I instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
+I instrument binaries at the assembly instruction level using Intel Pin.
+Each instruction is handled differently based upon the following criteria:
 
-I will need to implement a system which keeps track of how taint propagates at the instruction level.
-A directed graph structure, with initial nodes representing the bytes of user input and edges pointing to subsequent instructions which propagate taint, along with some metadata to make backsolving easier, seems like a reasonable data structure.
+\begin{itemize}
+	\item Is the instruction a conditional jump?
+	\item Is the first operand a memory location or a register?
+	\item Is the first operand read or written?
+	\item Is the first (second if applicable) operand tainted?
+\end{itemize}
+
+Operations involving an untainted first operand and a tainted second operand generally spread taint, while operations with a tainted first operand and an untainted second operand remove taint.
+Tainted branches trigger the backsolving technique.
+Various precautions, such as removing taint for an instruction like "xor eax, eax", must be taken.
+Lossy operations, like shifts, must be handled carefully to be backsolve-able.
+
+\subsection{Testing Harness}
+
+Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing.
+Currently, I record input, output, and taint for each test executed, using an auto-incrementing id and separating results at the directory level.
+I also keep track of the mutations which have already been explored.
+Users can grep for interesting conditions like segfaults or unexpected output, then cross reference the test number with the observed taint flow and the particular mutation tested.
+
+Professional fuzzing products, like Peach Fuzzer
+
+\subsection{Methodology}
 
@@
 
-\section{Setbacks}
+\subsection{Evaluation}
+
+%
+%Currently have results for crackmes, give idea of my fuzzer vs. %peach fuzz, and where i plan to go.
+
+\section{Future Work}
+
+% Was setbacks, modify and remove heavily
 
@@
 	\item [Y] Sen, Koushik, Darko Marinov, and Gul Agha. CUTE: a concolic unit testing engine for C. Vol. 30. No. 5. ACM, 2005.
+	\item [Z] Peach Fuzzer. url{http://peachfuzzer.com/}
+	\item [AA] Zhang, Xiangyu, Rajiv Gupta, and Youtao Zhang. "Precise dynamic slicing algorithms." Software Engineering, 2003. Proceedings. 25th International Conference on. IEEE, 2003.
 
@@
 
+%\input chapter2
+%\input chapter3
+
 %\appendix
-%\section{Appendix Title}
+%\input appendix1
 
-%This is the text of the appendix, if you need one.
+% You have your choice of bibliography sections, either
+% hand-crafted or BibTeX.
 
-%\acks
+% This is the "hand-crafted" bibliography/references section:
+%\begin{references}
+%Mybib, Sample. \textit{An Example of a Bibliographic Entry
+% Created Manually}. Tallahassee, Florida: Fornish and Frak, 2010.
 
-%Acknowledgments, if needed.
+%Smith, Marigold. \textit{Lots and Lots of Bibliographic Entries
+% and How to Display Them}. Tallahassee, Florida: Gibson and %Goulash, 2010.
+%\end{references}
 
-% We recommend abbrvnat bibliography style.
+% Or use the BibTeX bibliography/references section below.  View the
+% file 'myrefs.bib' to get a feel for what these entries may look
+% like.  See the document in the 'sample' folder for more citation and
+% BibTeX examples.
 
-\bibliographystyle{abbrvnat}
+% \bibliographystyle{plain}
+% \bibliography{myrefs}
 
-% The bibliography should be embedded for final submission.
-
-%\begin{thebibliography}{}
-%\softraggedright
-
-%\bibitem[Smith et~al.(2009)Smith, Jones]{smith02}
-%P. Q. Smith, and X. Y. Jones. ...reference text...
-
-%\end{thebibliography}
+\begin{biosketch}
+This is my biography.
+\end{biosketch}
 
 \end{document}
-
-%                       Revision History
-%                       -------- -------
-%  Date         Person  Ver.    Change
-%  ----         ------  ----    ------
-
-%  2013.06.29   TU      0.1--4  comments on permission/copyright notices

### 2013-12-03 docs/paper/fsuthesis/user-guide.tex
docs/paper/fsuthesis/thesis-template/paper.tex has my paper

%\documentclass[11pt,letterpaper]{article}
\documentclass[11pt,letterpaper]{ltxdockit}[2011/03/25]
\usepackage[american]{babel}
\usepackage{shortvrb}
\usepackage{pifont}
\usepackage{libertine}
\usepackage[scaled=0.8]{beramono}
\usepackage{microtype}
\usepackage{makeidx}

\lstset{basicstyle=\ttfamily,keepspaces=true}
\KOMAoptions{numbers=noenddot}
\definecolor{spot}{rgb}{0.5,0.1,0.1}
\definecolor{boxfill}{rgb}{0.99,0.98,0.95}

\addtokomafont{paragraph}{\spotcolor}
\addtokomafont{section}{\spotcolor}
\addtokomafont{subsection}{\spotcolor}
\addtokomafont{subsubsection}{\spotcolor}
\addtokomafont{descriptionlabel}{\spotcolor}

\setlength{\paperwidth}{8.5in}
\setlength{\paperheight}{11in}
\setlength{\pdfpagewidth}{\paperwidth}
\setlength{\pdfpageheight}{\paperheight}

\newcommand*{\acro}[1]{{\small\textsc{#1}}}
\newcommand*{\booktitle}[1]{\textit{#1}}
\newcommand*{\complit}[1]{\texttt{#1}}
\newcommand*{\pkg}[1]{\textsf{#1}}
\newcommand*{\comm}[1]{\texttt{\textbackslash#1}}

\newcommand*{\fsuth}{\pkg{fsuthesis}}

\renewcommand{\-}{\discretionary{}{}{}}

% Logos:
\def\BibTeX{{\rmfamily B\kern-.05em%
   \textsc{i\kern-.025em b}\kern-.08em\TeX}}
\def\MiKTeX{MiK\TeX}
\def\MacTeX{\textsf{Mac}\TeX}
\def\TeXLive{\TeX\,Live}

\newenvironment*{macrolist}
  {\list{}{%
      \setlength{\labelwidth}{1.5in}
      \setlength{\labelsep}{10pt}
      \setlength{\leftmargin}{0pt}
      \setlength{\parsep}{0pt}
      \setlength{\listparindent}{\parindent}
      \renewcommand*{\makelabel}[1]{{\setbox0=\hbox{\parbox[t]{1.5in}{\raggedleft\leavevmode\marglistfont##1}}\dp0=0pt\box0}}}}
  {\endlist}

\newenvironment*{narrowref}%
 {\par\frenchspacing
  \setlength{\leftskip}{4em}
  \setlength{\rightskip}{3em}
  \setlength{\parindent}{-2em}
  \setlength{\parskip}{0.6\baselineskip}\ignorespaces}
 {\par\addvspace{.5\baselineskip}}

\DeclareListParser*{\listofitems}{,}

\def\cmditem#1{\cmd{#1}\\}
\def\plainitem#1{#1\\}

\def\macroitems#1{\item[\listofitems{\cmditem}{#1}]}
\def\envitems#1{\item[\listofitems{\plainitem}{Environment\rlap{:},#1}]}
\def\optionitems#1{\item[\listofitems{\plainitem}{#1}]}

\setlength{\marginparsep}{10pt}
\setlength{\marginparwidth}{1.5in}

\def\margcmds#1{\leavevmode\marginpar{\raggedleft\leavevmode\marglistfont\listofitems{\cmditem}{#1}}\ignorespaces}
\reversemarginpar
\def\margenvs#1{\leavevmode\marginpar{\raggedleft\leavevmode\marglistfont\listofitems{\plainitem}{Environment\rlap{:},#1}}\ignorespaces}
\reversemarginpar
\def\margplain#1{\leavevmode\marginpar{\raggedleft\leavevmode\marglistfont\listofitems{\plainitem}{#1}}\ignorespaces}

\setcounter{tocdepth}{2}
\raggedbottom

\title{The \textsf{fsuthesis} \LaTeX{} Class:\\
  A User's Guide}
\author{Bret D. Whissel\\Department of Computer Science\\Florida State University}
\date{October 4, 2013}

\makeindex

\begin{document}

\maketitle

\tableofcontents

\section{Introduction to \LaTeX}
\label{sec:intro}

If you are already a \TeX/\LaTeX{} convert, you may skip over this
introductory material and jump ahead to the description of the
\fsuth{} class macros in section~\ref{sec:class}.  If you're new to
\LaTeX, you may want to learn a little bit more about what you may be
getting yourself into~first.

If you have grown up only learning to use the word-processing tools
that are installed on a typical PC, \LaTeX{} may feel awkward
initially.  However, \LaTeX's ability to generate cross-references,
lists of tables and figures, and a table of
contents---automatically---is already worth the small amount of effort
required to get started with this very powerful typesetting system.
Further, if your document contains mathematics, you'll be hard-pressed
to find better software for making your equations look good in~type.

Historically, \LaTeX{} is not a \acro{WYSIWYG}\footnote{pronounced
  ``wizzywig'': What You See Is What You Get}\index{WYSIWYG} system.  Instead,
documents are created using any available plain text editor.  Your
document will contain ``markup'' commands that identify things like
chapter titles, section headings, citations, quotations, enumerated
lists, etc.  When ready, the document is run through \LaTeX{} to
produce viewable or printable output.  This two-step process may be
different from what you're used to, but one advantage is that it
allows authors to focus more on the content of their documents, and to
focus less on the formatting (or at least to defer the attention to
formatting until the final stages of document preparation).

\section{Installation}%
\index{latex@\LaTeX!installation}%
\label{sec:install}

\subsection{The Basic \LaTeX{} System}

The \LaTeX{} system (and the \TeX{} engine upon which it is built)
will take just a little effort and download time to get installed and
running.  It is completely free software with a large and committed
group of users, and there are lots of resources for helping you to get
started.  These are much more comprehensive than this
\booktitle{User's Guide} can~be.

If you are working in a Microsoft Windows environment, take a look at
the \MiKTeX\ project\index{latex@\LaTeX!distributions!\MiKTeX} (see
\url{http://miktex.org}).  Mac users will find the
\MacTeX\index{latex@\LaTeX!distributions!\MacTeX} resources useful (see
\url{http://www.tug.org/mactex}).  Linux/\acro{UNIX} users should
investigate the \TeXLive\index{latex@\LaTeX!distributions!\TeXLive}, if
\TeX{} is not already a part of your installation (see
\url{http://www.tug.org/texlive}).

\subsection{Editors and IDEs}

In addition to the \TeX/\LaTeX{} system, you will need a plain text
editor.  Both of the recommended packages for Windows and Mac provide
an editor suitable for editing your document. Linux/\acro{UNIX}
enthusiasts will probably already have access to and familiarity with
\complit{emacs} or \complit{vim} (both of which have also been ported
to Windows and Mac environments).

There are more advanced document editors for \LaTeX\ which include
document previews or \acro{WYSIWYG} functionality. One such option for
Windows users is \textsf{\TeX nicCenter}\index{latex@\LaTeX!editors!\TeX
  nicCenter}, available from \url{http://texniccenter.org/}.  This
application provides a complete editing and previewing environment for
creating \LaTeX\ documents, including drop-down menus for common
\LaTeX\ commands.  The application
\textsf{Texmaker}\index{latex@\LaTeX!editors!Texmaker} (see
\url{http://www.xm1math.net/texmaker}) provides an integrated
development environment for all three major operating system
platforms.

Another popular option is the
\textsf{LyX}\index{latex@\LaTeX!editors!LyX} document processor (see
\url{http://www.lyx.org}).  However, in order to use the features
provided by the \fsuth\ class, you will need to create a custom layout
for \textsf{LyX} that corresponds to \fsuth.  Unfortunately, this is
not trivial.  If you wish to use \textsf{LyX}, you could try creating
your document using the standard \LaTeX\ \pkg{report} class layout
within \textsf{LyX}, export the document to \LaTeX, and then do the
final editing using the standard tools.

\subsection{Installing the \fsuth{} Class File}

The \fsuth\ class\index{fsuthesis@\pkg{fsuthesis}!package!contents} is
packaged and distributed as a zip file.  When the zip file is
unpacked, a folder called \complit{fsuthesis} is created.  In that
folder will be found this \booktitle{User's Guide}, in both its
\acro{PDF} and \LaTeX{} source form, as well as a few other files, the
\complit{thesis-template} folder, and a \complit{sample} folder.

The \fsuth{} class file is called \complit{fsuthesis.cls}.  Using
the directory \complit{thesis-template} as a starting point, the
\complit{fsuthesis.cls} file is already unpacked there and ready to
go.  You can copy the \complit{thesis-template} directory to a new
location and generate your document within that folder as a
self-contained entity.  No further installation is necessary.

If you are already a \LaTeX\ enthusiast, you may make customizations
to the \fsuth\ class yourself.  To do this, you will probably want to
take a look at the documented version of the \fsuth\ class definitions
found in the \complit{fsuthesis.dtx}
source\index{fsuthesis@\pkg{fsuthesis}!source code} file in the main
directory.  Processing this file with \LaTeX, you'll create a
nicely-formatted and indexed version to read:
\begin{verbatim}
pdflatex fsuthesis.dtx 
makeindex -s gglo.ist -o fsuthesis.gls fsuthesis.glo
makeindex -s gind.ist -o fsuthesis.ind fsuthesis.idx
pdflatex fsuthesis.dtx 
\end{verbatim}
Be sure to document your changes, and only edit the
\complit{fsuthesis.dtx} file. If you make changes to the
\complit{fsuthesis.cls} file, they may be overwritten later if the
class file is re-extracted.

To extract a new class file from the altered source, run the
following command:
\begin{verbatim}
latex fsuthesis.ins
\end{verbatim}
To make the class available
system-wide\index{fsuthesis@\pkg{fsuthesis}!installation}, copy the
\complit{fsuthesis.cls} file into the \LaTeX{} file search tree.  (The
proper location is operating system and installation-dependent.  For
\acro{UNIX}/Linux systems, this location might be something like
\complit{/usr/\-share/\-texmf-site/\-tex/\-latex/\-fsuthesis/}.)
Otherwise, for local use only, copy the new \complit{fsuthesis.cls}
file to the folder where your thesis or dissertation document resides.

\section{Helpful \LaTeX\ References}
\label{sec:references}

For simple texts, you might not need more from
\LaTeX\index{latex@\LaTeX!references} than what's described in this
\booktitle{User's Guide}.  For more complicated texts, however, or for
documents containing several tables, figures, or mathematics, you will
certainly want to supplement your \LaTeX{} references.  You will find
a wealth of information on-line using your favorite web search engine,
as well as several bound and printed reference materials.  I have
found the texts cited below to be of particular value.
\begin{itemize}
\item
For first-timers,
\href{http://www.ctan.org/tex-archive/info/lshort/english/lshort-letter.pdf}%
{\booktitle{The Not So Short Introduction to \LaTeXe}}
by Tobias Oetiker, Hubert Partl, Irene Hyna, and Elisabeth Schlegl
promises to have you off and running in a few hours' time.  It's a
document you may find readily on-line in \acro{PDF} form.

\item
The standard reference is the book \booktitle{\LaTeX: A Document
  Preparation System}, 2nd~Ed., by Leslie Lamport, the original author
of \LaTeX{}.  This text covers all the basics clearly and succinctly.

\item
A larger starting reference book is \booktitle{Guide to \LaTeX},
4th~Ed., by Helmut Kopka and Patrick W.~Daly.  At twice the length of
the Lamport book, \booktitle{Guide} covers all the basics, and it also
touches on a few of the more common add-on packages.  The book
comes with a CD-ROM with the \TeXLive\ distribution included, which
can save you a lot of downloading time.

\item
Once your working knowledge of \LaTeX{} is secure, \booktitle{The
  \LaTeX{} Companion}, 2nd~Ed., by Frank Mittelbach and Michel
Goossens covers a broad range of topics and \LaTeX{} add-on packages.
This text goes far beyond the basics, but it's an indispensable
reference if you're interested in customizing the appearance of
\LaTeX{} documents.
\end{itemize}

\section{Working with \LaTeX}

Files you create for processing by \LaTeX{} should have file
extensions of \complit{.tex}, for example, \complit{mythesis.tex}.
For your own convenience, you may split the document into pieces
(perhaps one file per chapter), which may make the editing process a
little easier by keeping manageable the amount of text you must scroll
through at any one time.

While you're typing your document, you will insert macro commands that
mark up elements of your document, indicating chapter and section
headings, equations, tables, figures, etc.  Markup languages attempt
to separate the content of the document from its appearance.  As an
author, you need not be quite as concerned about how everything looks,
just what it says.  By marking up your document appropriately, you can
let \LaTeX{} worry about how everything looks.

\subsection{Paragraphs and Space}
Typing your manuscript for processing by \LaTeX\ is not hard, but
there are a few rules you should know. To end a
paragraph\index{paragraph} and begin a new one, simply leave a
blank\index{blank line} line between them.  No matter how many blank
lines you leave between paragraphs, it's the same as typing a single
blank line: all the extra space is ignored.  Likewise, a 100~taps of
the space\index{space} bar has the same result as a single space.

Don't worry about where the end-of-line occurs as you're typing:
\LaTeX\ will reformat the paragraph for you.  \LaTeX\ will also insert
paragraph indentations, so there's no need to type tabs or spaces (and
they'll be ignored anyway).

The \fsuth\ class has defined most of the document spacing for you, so
you generally don't need to worry about it.  If you have particular
spacing needs, look into the references in
section~\ref{sec:references} for more information.  Here's an example
of how \LaTeX\ processes what you type into paragraphs:

\medskip\noindent\hskip3em
\begin{minipage}[t]{2.1in}\rightskip=0pt plus1.5in
\noindent\textit{Typed as \ldots}\\[5pt]
\noindent\small\texttt{I am typing a silly\\
paragraph to see how it
will turn out.\\
\\
And here is the
next paragraph.}\par
\end{minipage}
\hfill
\begin{minipage}[t]{2.4in}
\parindent=1em\rightskip=3em
\noindent\textit{Displayed as \ldots}\\[5pt]
\indent I am typing a silly paragraph to
see how it will turn out.

And here is the next paragraph.
\end{minipage}

\subsection{Special Characters}
\label{sec:special}
Certain keyboard characters have special significance to \LaTeX, and
you must be aware of how they are used as you're preparing your
document.\index{special characters}  The ten special characters~are:
\begin{verbatim}
# $ % & _ { } ^ ~ \
\end{verbatim}
If you need these characters in your text, you cannot enter them in
your manuscript as is: they need extra attention.  The first seven may
be simply prefixed with the backslash character, and the last three
require a small bit of additional syntax.  Here's how you would type
the characters in your document to have them printed:
\begin{verbatim}
\# \$ \% \& \_ \{ \} \^{} \~{} \textbackslash
\end{verbatim}
which, after processing, results in: \# \$ \% \& \_ \{ \} \^{} \~{} \textbackslash

\subsection{Dashes and Quotes}
Since \LaTeX\ is a high-quality typesetting system, we are given
additional choices in preparing our document for output.  For example,
there are four distinct dash-type\index{dash-type characters}
characters available to us, and we
should choose the correct dash for the circumstance:
\begin{center}
\begin{tabular}{c l l}
\textit{Dash Type}&\textit{Typed as \ldots}&\textit{Displayed as \ldots}\\[3pt]
hyphen & \verb|anti-theoretical| & anti-theoretical \\
N-dash & \verb|pages 23--45| & pages 23--45 \\
M-dash & \verb|Wait---I'm thinking| & Wait---I'm thinking \\
minus & \verb|$x-y=z$| & $x-y=z$ \\
\end{tabular}
\end{center}

You should also be aware of single- and double-quote characters: in
well-printed documents, the lefthand-side quotes\index{quote
  characters} are shaped differently than righthand-side quotes.  The
\LaTeX-aware editors that come with the distributions usually handle
this for you automatically when you type the double-quote character
(\texttt{"}) on your keyboard, translating it into the appropriate
pair of characters.

Single quotes don't usually get the same automatic treatment, and you
should type the individual characters yourself.  The left-side
``backward'' single quote character is usually found beneath the tilde
(``squiggle'') on your keyboard.  The right-side single quote
character (apostrophe) is usually found underneath the double-quote
character.  Sometimes it may be necessary to add a small amount of
space between sets of quotes using the \verb|\,| command (as in the
last example below), but this is a more subtle typographic nicety.
\begin{center}
\begin{tabular}{l l}
\textit{Typed as \ldots}&\textit{Displayed as \ldots}\\[3pt]
\verb|This `word' is single-quoted| & This `word' is single-quoted \\
\verb|``These words'' are double-quoted| & ``These words'' are double-quoted \\
\verb|``\,`I' am, I think''| & ``\,`I' am, I think''\\
\end{tabular}
\end{center}

\subsection{Macros, Comments, and Ties}
\label{sec:comments}
\LaTeX{} macros begin with a `\verb+\+' (backslash) special character,
followed by the command name.  Depending on the command,
macros\index{macros}\index{commands|see{macros}} will often require
one or more arguments, and some will accept additional optional
arguments.  The template for such \LaTeX\ commands~is:
\begin{verbatim}
\commandname[option1,option2]{Required Argument}
\end{verbatim}
The optional arguments are included in square brackets (e.g.,
\verb+[+\textit{option}\verb+]+) immediately following the macro
invocation.  Required arguments follow the optional arguments (if any)
between curly braces (e.g., \verb+{+\textit{This is a required
  argument}\verb+}+).  The letter case of the macro is important:
you must spell commands exactly as they are presented, or \LaTeX\ will
complain about unrecognized commands when your document is processed.

The function of the percent sign (\verb|%|) special character is to
introduce a document comment\index{comments}, which runs to the end of
the line of the input file.  Commented text is ignored by \LaTeX{}
entirely, and will not be typeset.  Recall that we may avoid this
special behavior by prefixing a backslash character:
\begin{center}
\begin{tabular}{l l}
\textit{Typed as \ldots}&\textit{Displayed as \ldots}\\[3pt]
\verb|total is 23\% of adjusted gross|&
total is 23\% of adjusted gross\\
\end{tabular}
\end{center}
(Refer to section~\ref{sec:special} for the complete list of special
characters and how to type them.)

\LaTeX\ attempts to fill up each line of a paragraph optimally, and
sometimes we need to provide some advice for where \emph{not} to
create a line break.  The function of the tilde (\verb|~|) special
character is to tie adjoining words together with an ``unbreakable
space''\index{space!unbreakable}\index{unbreakable space} so that they
are not split between lines.  This is often useful to ensure that
honorific titles don't get separated from their name (e.g.,
``\verb|Frau.~Blucher|'', ``\verb|Dr.~Frankenstein|''), or after
certain abbreviations (e.g., ``\verb|a vs.~b|'',
``\verb|cf.~Fig.~5|''), or where numbered entities are referenced,
(e.g., ``\verb|page~23|'').

\subsection{Document Divisions} 
A \LaTeX\ document begins with a division called the
``preamble''\index{preamble}.  In this section, you specify the
document type, set up the document-wide processing settings (like page
margins, or selecting the font size, for example), set the document's
title, author, and other such parameters, and perhaps load additional
packages which provide new features for processing your document.

The rest of the document is called the document ``body''.  It begins
with the \LaTeX\ command
\verb|\begin{document}|\index{environment!document@\verb+document+},
and anything that comes before this command is considered part of the
preamble. Some \LaTeX\ commands are only allowed in the preamble,
while others are allowed only in the document body.

\section{The \fsuth{} Class}
\label{sec:class}

A standard \LaTeX{} installation comes with several pre-defined
document types (called classes), such as \pkg{article},
\pkg{book}, and \pkg{report}.  The \fsuth{} class is an
extension of the \LaTeX{} \pkg{report} class.  In essence, the
\fsuth{} class provides all the features of \pkg{report}, along
with customizations to meet the standards of FSU's
\booktitle{Guidelines \& Requirements for Electronic Theses, Treatises
  and Dissertations}, revised August~2013.  The rest of this
document describes how to use the features of the \fsuth{} class, and
introduces a few other functions provided by \LaTeX.

\subsection{Files in the Package}

Packaged along with this \booktitle{User's Guide} and the \fsuth{}
class file, you will find a folder called
\complit{thesis-template}\index{fsuthesis@\pkg{fsuthesis}!package!contents}.
Within the folder is a small collection of files, a skeleton upon
which you may build your own document.  I suggest that you copy and
rename this folder in a new location, giving your \emph{magnum opus}
its own workspace.

For now, we'll assume that you have renamed the folder
\complit{thesis}.  Inside the folder, you'll find a file called
\complit{mythesis.tex}.  This will be your document's principal file.
We will assume that you will create additional files in this folder to
add to your document, assuming at least one file per chapter.  You are
free to rename any of these files as you like, as long as they end
with the \complit{.tex} extension.

The document skeleton constitutes a complete document as it stands,
and you may run \LaTeX\ on \complit{mythesis.tex} immediately if you
need to test your installation.  (How you invoke \LaTeX\ is
platform-dependent, so you may need to refer to
section~\ref{sec:install} on \textsc{Installation} above for
references specific to your environment.  In the environments provided
by \MiKTeX\ and \MacTeX, processing your document is usually
accomplished by a single button click.)

Besides the \complit{thesis-template} folder, there is a
\complit{sample} folder which contains a more robust sample document,
demonstrating features of \LaTeX\ and the \fsuth\ class, as well as a
few optional features which you may enable if you find them helpful.

\subsection{The Document Preamble}

If you look at the file \complit{mythesis.tex}, you will see that it
consists primarily of \LaTeX{} macros and ``commented out'' lines
containing more \LaTeX{} macros.  (Recall section~\ref{sec:comments}.)
As you add text and flesh out your document, you may ``uncomment''
additional lines in this primary file by removing the leading percent
sign, thereby making the line active.

The document setup may look intimidating at first, but don't let this
deter you.  The template document and the sample document provide you
with some boiler-plate information: you can just fill in the blanks
with your own data to get started quickly.  You don't have to know or
understand all this stuff at first.  I encourage you to look at the
example files and review the output documents to see how they are
correlated.

\subsubsection{Document Options}
\label{sec:docoptions}
The first line of every \LaTeX{} document declares the type of
document to be processed, along with a few processing options.  After
some initial comments, the first line of the document skeleton file
\complit{mythesis.tex} contains the
following:\index{documentclass@\verb=\documentclass=}
\begin{ltxexample}
\documentclass[11pt,expanded]{fsuthesis}
\end{ltxexample}
This line declares the document type to be \fsuth, and that the text
will be set in 11-point type using \verb|expanded| spacing. (Note the
optional arguments supplied in square brackets, and required argument
provided in curly braces.)

Class \fsuth{} is derived from the \pkg{report} class, so all
the standard document options supported by \pkg{report} will be
supported by \fsuth.  (See one of the \LaTeX{} references in
section~\ref{sec:references} for complete lists of document options.)
The \fsuth{} class provides four additional document options\index{documentclass@\verb=\documentclass=!options}:
\complit{hardcopy}, \complit{chapterleaders}, \complit{expanded}, and
\complit{copyright}.

\begin{macrolist}
\item[10pt, 11pt, 12pt] These options select the font point size for
  the document.  Without any\index{font size}\index{point size}
  specifications, \complit{10pt} is the default.  (The standard
  \LaTeX\ \pkg{report} class supplies these options.)

\optionitems{chapterleaders}
This option adds leader dots on chapter headings in the \textsl{Table
  of Contents}.
\index{chapterleaders@\verb+chapterleaders+}%
\index{contents, table of!leaders}%
Normally, chapter headings are displayed in bold type with a page
number and \emph{without} leader dots, while by default, sections and
subsections are displayed with leader dots connecting their page
numbers.  If you write a thesis without sections or subsections, or if
you suppress their display in the \textsl{Table of Contents}, then you
might want to specify the \complit{chapterleaders} option.

\optionitems{copyright}
This option adds a copyright\index{copyright@\verb+copyright+}
statement at the bottom of the title page.  Though your thesis or
dissertation is protected by copyright law already, you may wish to
state the copyright ownership explicitly using this option.

\optionitems{expanded}
This option expands line
spacing\index{expanded@\verb+expanded+}\index{line spacing, expanded} by 50\%.
Some colleges, schools, or departments will prefer expanded spacing to
allow committee members to pencil in comments.  In addition, ETD
requires that the document \emph{not} be single-spaced.

\optionitems{hardcopy}
This option adds extra space along the binding edge of a page.  This
may be useful for printing hard copies\index{hardcopy@\verb+hardcopy+}
for review by your thesis committee, or if you want to have a
professionally bound copy of your thesis or dissertation.  If you also
include the standard \pkg{report} option
\complit{twoside}\index{twoside@\verb+twoside+}, then in addition to
the binding-edge offset, all the chapters of your document will be
forced to start on odd-numbered (right-hand) pages.

\end{macrolist}

\subsubsection{Thesis/Dissertation Description Macros}
The next section in \complit{mythesis.tex} contains several macros
that customize the title page and committee page of your document.  As
a general rule, these macros require text arguments that should be
given in mixed case using title capitalization\index{capitalization}
rules (i.e., each word capitalized, except for articles, prepositions,
and conjunctions; refer to your discipline's preferred style guide if
in doubt).  All proper names should be capitalized normally.  If the
FSU \booktitle{Guidelines} require elements to be displayed
differently (all-caps, for example), the \fsuth{} class will make the
adjustments required for you.  These macros all belong in the
preamble.

\begin{macrolist}
\macroitems{title}
This macro declares the title\index{title@\verb+\title+} of your
thesis or dissertation.  If the title is long, it will be broken over
several lines on the title page.  You can control how the title
is broken into lines\index{title!line breaks} two ways:
using the \LaTeX\ line-separator operator (`\verb+\\+') to force
a line break, or using the word tie (`\verb+~+') between words
to prevent a line break.  (The line-separator command is what the
\LaTeX{} manual calls ``fragile'', and so you must say
`\verb+\protect\\+' when it is used in the argument of the
\verb|\title| command. See the example in the box below.)

\macroitems{author}
This macro stores your name\index{author@\verb+\author+}.  Your name
should be given as specified in the FSU \booktitle{Guidelines}.

\macroitems{college}
This macro should contain the official name of your
school\index{college@\verb+\college+} or college.

\macroitems{department}
If your degree comes from a school or college with separate academic
departments\index{department@\verb+\department+} which issue degrees,
the \verb|\department| macro should declare this name.  Otherwise, you
should comment-out or delete the \verb|\department| line from your
document file.

\macroitems{manuscripttype}
This should be set to one of the following words, as
appropriate:\index{manuscripttype@\verb+\manuscripttype+}
\complit{Thesis}, \complit{Treatise}, or \complit{Dissertation}.

\macroitems{degree}
The title of your degree\index{degree@\verb+\degree+} (e.g., ``Master
of Arts'' or ``Doctor of Philosophy'') is given by the \verb|\degree|
macro.

\macroitems{semester}
This should be set to one of\index{semester@\verb+\semester+}
\complit{Fall}, \complit{Spring}, or \complit{Summer}, according to
the semester in which your degree was awarded.

\macroitems{degreeyear}
The year your degree\index{degreeyear@\verb+\degreeyear+} is awarded
should be set here.  This should be a full 4-digit year.

\macroitems{defensedate}
The date\index{defensedate@\verb+\defensedate+} of your thesis,
treatise, or dissertation defense should be provided by the
\verb|\defensedate| macro.  Refer to the FSU \booktitle{Guidelines}
for the appropriate format.

\end{macrolist}

\noindent 
In your own document up to this point, you could have something like the
following (after the initial \verb|\documentclass| command):
\begin{ltxexample}
\title{This Is My Title:\protect\\ And This Is Its Second Line}
\author{Viktor Spoyles}
\college{College of Arts and Sciences}
\department{Department of Physics}
\manuscripttype{Dissertation}
\degree{Doctor of Philosophy}
\semester{Fall}
\degreeyear{2012}
\defensedate{October 31, 2012}
\end{ltxexample}

If you are generating a \acro{PDF} file, you can add a subject and
search keywords to the document's ``metadata''.\index{metadata} This
information is not printed in your document at all, but it becomes
part of the electronic version of the document's internal
description. The title and author's name will already be included in
the metadata by default.  Since the document metadata are searchable,
adding keywords and a subject may assist those performing a more
targeted search.
\begin{macrolist}
\macroitems{subject}
A terse description\index{subject@\verb+\subject+} of the manuscript
topic.

\macroitems{keywords}
A comma- or semi-colon-separated list of germane
keywords\index{keywords@\verb+\keywords+}.

\begin{ltxexample}
\subject{FTL Propulsion Theory}
\keywords{warp drive; wormhole travel; subspace geometry}
\end{ltxexample}

\end{macrolist}

\subsubsection{Committee Macros}

\margcmds{committeeperson}
The \fsuth{} class provides macros for generating your committee
information page.  The
\verb|\committeeperson|\index{committeeperson@\verb+\committeeperson+}
macro takes two arguments.  The first argument is the name of the
committee member, given without titles.  The second argument is the
committee membership status, e.g., ``Professor Directing
Dissertation'' or ``Committee Member''.  (See the FSU
\booktitle{Guidelines} about the appropriate options.)  You should
provide one \verb|\committeeperson| line for each person, in the order
in which they should appear on the committee page.
\begin{ltxexample}
\committeeperson{Arthur Vandelay}{Professor Directing Thesis}
\committeeperson{Whoopsie Daisy}{Committee Member}
\committeeperson{Garnet G. Adirolf}{Committee Member}
\end{ltxexample}

\subsection{The Document Body}

\margenvs{document}
With the document setup complete, you start the document body with the
\LaTeX{} command
\verb|\begin{document}|.\index{environment!document@\verb+document+}
You will notice that whenever you
\verb|\begin{|\textit{something}\verb|}|, you should always supply a
corresponding \verb|\end{|\textit{something}\verb|}| or \LaTeX{} will
complain.  So at the end of \complit{mythesis.tex}, you will find the
\verb|\end{document}| command.  Anything beyond this point in the file
is ignored by \LaTeX{}.  In \LaTeX\ parlance, anything enclosed within
a
\verb|\begin{|\textit{something}\verb|}|\,\ldots\verb|\end{|\textit{something}\verb|}|
pair is called an ``environment''.\index{environment} We'll encounter
several environments along the way.

\subsubsection{Front Matter}

\begin{macrolist}
\macroitems{frontmatter}
The first element after \verb|\begin{document}| should be the macro
command \verb|\frontmatter|,\index{frontmatter@\verb+\frontmatter+}
which sets up roman numeral\index{roman numerals} page numbering for
the document elements that precede the first chapter of your thesis or
dissertation.  The document skeleton in \complit{mythesis.tex}
contains place-holders in the proper order for all the optional
elements of the front matter.  Uncomment those elements that you will
use, or you may leave commented or delete those elements that you
don't use.

\macroitems{maketitle,makecommitteepage}
Once \verb|\frontmatter| has set the stage, the macro command
\verb|\maketitle|\index{maketitle@\verb+\maketitle+} will generate the
document title page.  Likewise, the
\verb|\makecommitteepage|\index{makecommitteepage@\verb+\makecommitteepage+}
macro will create the committee page.  Information for these pages is
gathered from the data you have already set in macro calls in the
preamble.
\begin{ltxexample}
\begin{document}
\frontmatter
\maketitle
\makecommitteepage
\end{ltxexample}

\envitems{dedication}
If you wish to include an optional dedication in your thesis or
dissertation, uncomment the
\verb|\begin{dedication}|
\index{environment!dedication@\verb+dedication+}%
\index{dedication@\verb+dedication+}%
and \verb|\end{dedication}|
lines, and type your dedication between them.  The text that you
insert will appear about 1/3rd of the distance from the top of the
page.  The rest of the formatting is up to you.
\begin{ltxexample}
\begin{dedication}
  \begin{center}
    To my parents
  \end{center}
\end{dedication}
\end{ltxexample}

\envitems{acknowledgments}
Likewise, if you wish to include acknowledgments in your document,
uncomment the
\verb|\begin{acknowledgments}|
\index{acknowledgments@\verb+acknowledgments+}%
\index{environment!acknowledgments@\verb+acknowledgments+}%
and \verb|\end{acknowledgments}| lines, and insert the acknowledgment text
between these lines.  The resulting page will have the centered
heading \textbf{ACKNOWLEDGMENTS}, followed by your text.
\begin{ltxexample}
\begin{acknowledgments}
Thanks to my committee, especially my major professor.
\end{acknowledgments}
\end{ltxexample}

\macroitems{tableofcontents}
The next item in the front matter is the \textsl{Table of Contents},
which is generated for you automatically by the macro
\verb|\tableofcontents|.
\index{tableofcontents@\verb+\tableofcontents+}%
\index{contents, table of}%
By default, the \textsl{Contents} page(s)
will contain entries for the remaining front matter material, and
entries for chapter headings, section headings, and subsection
headings.  If you find your \textsl{Table of Contents} has too much
detail, you may adjust the level of headings included.  (See
section~\ref{sec:tocdetail}.)

\macroitems{listoftables,listoffigures,listofmusex}
The FSU \booktitle{Guidelines} state that if you have more than one
figure
\index{listoftables@\verb+\listoftables+}%
\index{listoffigures@\verb+\listoffigures+}%
\index{listofmusex@\verb+\listofmusex+}%
or table in your document, the figures and/or tables should be
contained in their own lists.  Turn each of these options on by
uncommenting the \verb|\listoftables| and/or \verb|\listoffigures|
lines in \complit{mythesis.tex}.  These tables will be generated for
you automatically when your document is processed.  For those
documents which contain multiple musical examples, a list of these may
also be generated by uncommenting \verb|\listofmusex|.
\begin{ltxexample}
\tableofcontents
\listoftables
\listoffigures
\listofmusex
\end{ltxexample}

\envitems{listofsymbols,listofabbrevs} If a \textsl{List of Symbols}
or \textsl{List of Abbreviations} might be helpful to your readers,
\index{environment!listofsymbols@\verb+listofsymbols+}%
\index{environment!listofabbrevs@\verb+listofabbrevs+}%
\index{listofabbrevs@\verb+listofabbrevs+}%
\index{listofsymbols@\verb+listofsymbols+}%
\fsuth{} provides these environments.  If you wish to include such
document elements, uncomment the appropriate
\verb|\begin|~\ldots\verb|\end| pair, and add any text you may
require.

These entities would likely consist of tabular material, so you'll
want to dig into \LaTeX{} table-making using any of the basic
references mentioned in section~\ref{sec:references}.  Below is a
simple example of how you might use these environments to create
tables with some useful information if needed.
\begin{ltxexample}
\begin{listofsymbols}
  \begin{center}\begin{tabular}{r l}
    $E$   & Energy--Mass equivalence: $mc^2$ \\
    $R_e$ & Mean Radius of the Earth, ${}\approx 6367.65\,\textup{km}$\\
    $\pi$ & $3.1415926\ldots$\\
  \end{tabular}\end{center}
\end{listofsymbols}
\end{ltxexample}
\begin{ltxexample}
\begin{listofabbrevs}
  \begin{center}\begin{tabular}{l l}
    i.e. & \textit{id est}, ``that is''\\
    e.g. & \textit{exempli gratia}, ``for example''\\
  \end{tabular}\end{center}
\end{listofabbrevs}
\end{ltxexample}

\envitems{abstract}
The last element of the front matter is a document abstract.
\index{environment!abstract@\verb+abstract+}%
\index{abstract@\verb+abstract+}%
Insert your text between the abstract \verb|\begin|~\ldots\verb|\end| pair.
The proper heading is included for you automatically.
\begin{ltxexample}
\begin{abstract}
This abstract is a concrete example.
\end{abstract}
\end{ltxexample}

\end{macrolist}

\subsection{The Main Text}

\margcmds{mainmatter}
At last, with the preliminaries out of the way, you may now get to the
meat of your document.  Following the abstract, the command
\verb|\mainmatter|\index{mainmatter@\verb+\mainmatter+} restarts page
numbering at ``1'' in arabic numerals\index{arabic numerals}, ready
for your first chapter.

The skeleton file \complit{mythesis.tex} has been set up to include
the first chapter from an external file.  Note the
command \verb+\input+:\index{input@\verb+\input+}
\begin{verbatim}
\input chapter1
\end{verbatim}
This tells \LaTeX{} to insert the text of the file
\complit{chapter1.tex} at this position and continue processing. (The
file extension is appended automatically.)  There is nothing special
about the file names\index{file names}, except that they should end
with the extension \complit{.tex}.  Otherwise, you may call the
external files whatever you like.  (However, avoid using filenames
with spaces or special symbols, as these may be difficult for either
\LaTeX{} or your operating system to handle properly.)  You can break
up large chapters into even smaller pieces if you like, and then
change \complit{mythesis.tex} accordingly, e.g.,
\begin{verbatim}
\input chapter1a
\input chapter1b
\end{verbatim}
Or you could just continue adding text to \complit{mythesis.tex}
directly, avoiding having to deal with any other external files
entirely.  This is all up to you.

\subsubsection{Chapter and Section Headings}

\margcmds{chapter,section,subsection,subsubsection,paragraph,subparagraph}
Several levels of headings
are provided by the \fsuth{} class in the
heading styles defined by FSU's \booktitle{Guidelines}.
\index{chapter@\verb+\chapter+}%
\index{section@\verb+\section+}%
\index{subsection@\verb+\subsection+}%
\index{subsubsection@\verb+\subsubsection+}%
\index{paragraph@\verb+\paragraph+}%
\index{subparagraph@\verb+\subparagraph+}%
\index{headings}%
By default,
entries down to the subsection level are listed in the \textsl{Table
  of Contents}.  (See section~\ref{sec:tocdetail} for information on
changing this default.) Listed from the highest level downward, these
sectioning commands are:
\par\medskip
\begin{itemize}\addtolength{\parskip}{-7pt}
\item \verb|\chapter{My Chapter Title}|
\item \verb|\section{A Main Section Heading}|
\item \verb|\subsection{The Subsection Heading}|
\item \verb|\subsubsection{A Subsubsection Title}|
\item \verb|\paragraph{Do You Need This Many Levels?}|
\item \verb|\subparagraph{Come On, You're Kidding!}|
\end{itemize}
Each of these macros takes a single argument, the text of the heading.
All headings should be capitalized\index{capitalization} as titles,
i.e., mixed case text, each word capitalized except articles,
prepositions, and conjunctions.  Chapter headings will force the start
of a new page.  The file \complit{chapter1.tex} in the
\complit{thesis} folder has some example text to get you started.  (If
any of your headings include math symbols, you may want to activate
the \pkg{textcase} package. See section~\ref{sec:packages} for more
information.)

By default, section and subsection headings are prefixed by section
and subsection numbers. Sub-subsections produce an unnumbered in-line
heading in bold-face type as the opening of a paragraph.  Paragraph and
sub-paragraph headings also produce in-line headings and start new
paragraphs, but with progressively subtler font selections.
If you like, you may change the level at which headings are numbered.
See section~\ref{sec:headnum} for more information.

\subsection{Back Matter}

\margcmds{appendix}
Following the major chapters of your manuscript, you may have
additional material for one appendix\index{appendix@\verb+\appendix+}
or more.  To shift from chapter headings to appendix headings, insert
the macro \verb+\appendix+ at the end of your last chapter, before the
first appendix.  Then use the \verb+\chapter+ macro just as you have
for each of your chapters.  (Appendices will be lettered rather than
numbered.)
\begin{ltxexample}
\appendix
\input appendix1
\input appendix2
\end{ltxexample}

\subsubsection{References/Bibliography}

\margenvs{references}
The \fsuth{} class provides two options to produce a bibliography or
references section.  The first (and simplest) option is to use the
\complit{references}
environment.
\index{environment!references@\verb+references+}%
\index{references@\verb+references+}%
Begin this section with
\verb|\begin{references}|.  Then add each bibliographic entry with a
blank line between each reference.  Follow the last entry with
\verb+\end{references}+.  With this option, you will have to format
each entry according to the style guide you have chosen to follow.
\begin{ltxexample}
\begin{references}
Picaut, J., F. Masia, and Y. du Penhoat, 1997: An advective--reflective
conceptual model for the oscillatory nature of the ENSO.
\textit{Science}, \textbf{277}, 663--666.

Yasunari, T., 1990: Impact of Indian monsoon on the coupled
atmosphere/ocean system in the tropical Pacific.
\textit{Meteor. Atmos. Phys.}, \textbf{44}, 19--41.
\end{references}
\end{ltxexample}
This example provides two bibliography entries.  I had to specify the
style-guide preferences myself (such as presenting journal names in italic
type, volume numbers in bold-face, etc.).  Once these are processed,
they'll look like the following:
\begin{narrowref}
Picaut, J., F. Masia, and Y. du Penhoat, 1997: An advective--reflective
conceptual model for the oscillatory nature of the ENSO.
\textit{Science}, \textbf{277}, 663--666.

Yasunari, T., 1990: Impact of Indian monsoon on the coupled
atmosphere/ocean system in the tropical Pacific.
\textit{Meteor. Atmos. Phys.}, \textbf{44}, 19--41.
\end{narrowref}

\margcmds{cite,bibliographystyle,bibliography}
The second option is to set up a \BibTeX{}\index{bibtex@\BibTeX}
database.
\index{cite@\verb+\cite+}%
\index{bibliographystyle@\verb+\bibliographystyle+}%
\index{bibliography@\verb+\bibliography+}%
To use \BibTeX, you create
or download a separate file of reference materials in a particular
format.  Then you may cite any of these references within your
manuscript using the \verb|\cite| macro.  By running \LaTeX{} in
combination with \BibTeX, citations are resolved, and a list of the
cited references are pulled into your document automatically.  To use
this feature, you first select the bibliographic style, and then
specify the \BibTeX{} database file:
\begin{ltxexample}
\bibliographystyle{plain}
\bibliography{myrefs}
\end{ltxexample}
This selects the \complit{plain} bibliography style, and the
\BibTeX{} database is said to reside in \complit{myrefs.bib}.
Processing your document now requires a few extra steps as well:
\par\medskip
\noindent\begin{minipage}[t]{2.5in}
\begin{itemize}\addtolength{\parskip}{-7pt}
\item Run \LaTeX{}
\item Run \BibTeX{}\par\nobreak
\item Run \LaTeX{} \emph{twice more}
\end{itemize}
\end{minipage}

If you have a relatively small number of bibliographic entries or
citations, then choosing the \complit{references} environment is
probably the easiest solution.  However, if you are trying to manage a
large number of citations or work in a discipline that has already
established a large \BibTeX{} database, then it may save you
considerable effort to learn how to use \BibTeX, in which case you
will certainly need to use one of the \LaTeX{} references mentioned
earlier.

Depending on your discipline, you may need more substantial citation
and bibliography-formatting capabilities.  Many disciplines and
journals have created their own \BibTeX\ styles, and you may want to
take advantage of these efforts.  First, you'll need to install the
correct option package (see section~\ref{sec:packages} to get
started).  You should also check out the document in the
\complit{sample} directory for some more concrete examples.

\subsubsection{Biographical Sketch}

\margenvs{biosketch}
At last, you've reached the final page of your \booktitle{magnum
  opus}.  It will contain your biographical sketch, starting with
\verb+\begin{biosketch}+,
\index{environment!biosketch@\verb+biosketch+}%
\index{biosketch@\verb+\biosketch+}%
and ending with \verb+\end{biosketch}+ as usual.  Insert what
biographical material you wish to include here, but remember not to
include any personal contact information.

Once the biographical sketch is done, we wrap things up with the
\verb|\end{document}| command (matching the \verb|\begin{document}|
earlier in the file).  Anything that follows \verb|\end{document}|
will be ignored by \LaTeX.
\begin{ltxexample}
\begin{biosketch}
The author was born, educated, and re-educated
until this document was finally completed.
\end{biosketch}

\end{document}
\end{ltxexample}

\section{More \LaTeX\ Features}

\subsection{List Environments}

\margenvs{itemize,enumerate,description}
Standard \LaTeX\ provides a means of generating lists of things.
\index{lists}%
\index{environment!itemize@\verb+itemize+}%
\index{environment!enumerate@\verb+enumerate+}%
\index{environment!description@\verb+description+}%
\index{itemize@\verb+itemize+}%
\index{enumerate@\verb+enumerate+}%
\index{description@\verb+description+}%
A simple bulleted list can be created this way:

\medskip
\noindent\hskip2em
\index{lists!bulleted}\begin{minipage}[t]{2.1in}
\textit{Typed as \ldots}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}
\textit{Displayed as \ldots}
\end{minipage}
\par\nobreak\vskip3pt\nobreak
\noindent\hskip2em
\begin{minipage}[t]{2.1in}%
\small\begin{verbatim}
\begin{itemize}
\item Granny Smith Apples
\item Hominy Grits
\item Gruy\`ere Cheese
\end{itemize}
\end{verbatim}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}\small\sloppy
\begin{itemize}
\item Granny Smith Apples
\item Hominy Grits
\item Gruy\`ere Cheese
\end{itemize}
\end{minipage}
\bigskip

Similarly, an enumerated list is constructed this way:

\medskip
\noindent\hskip2em
\index{lists!enumerated}\begin{minipage}[t]{2.1in}
\textit{Typed as \ldots}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}
\textit{Displayed as \ldots}
\end{minipage}
\par\nobreak\vskip3pt\nobreak
\noindent\hskip2em
\begin{minipage}[t]{2.1in}%
\small\begin{verbatim}
\begin{enumerate}
\item Beat eggs until frothy.
\item Stir in milk.
\item Whisk in flour.
\end{enumerate}
\end{verbatim}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}\small\vskip-5pt
\begin{enumerate}
\item Beat eggs until frothy.
\item Stir in milk.
\item Whisk in flour.
\end{enumerate}
\end{minipage}
\bigskip

Yet another list style is provided by the \complit{description}
environment.  This looks like the following:

\medskip
\noindent\hskip2em
\index{lists!description}\begin{minipage}[t]{2.1in}
\textit{Typed as \ldots}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}
\textit{Displayed as \ldots}
\end{minipage}
\par\nobreak\vskip3pt\nobreak
\noindent\hskip2em
\begin{minipage}[t]{2.1in}%
\small\begin{verbatim}
\begin{description}
\item[Green eggs] A delicacy.
\item[Ham] Cured pork.
\item[Sam I Am] Hawker of food.
\end{description}
\end{verbatim}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}\small
\begin{description}
\item[\defaultcolor Green eggs] A delicacy.
\item[\defaultcolor Ham] Cured pork.
\item[\defaultcolor Sam I Am] Hawker of food.
\end{description}
\end{minipage}
\bigskip

You may also create lists inside of lists, mixing and matching
\complit{itemize}, \complit{enumerate}, and \complit{description}
styles as necessary.  Lists may also be customized in many ways, so if
you need something fancier, you should read through one of the references.

\subsection{Quotation Environments}

\margenvs{quote,quotation}
\LaTeX\ provides for another common construction in documents:
quotations.\index{quotations} Quotations are set off from the rest of
the text with narrower margins (and smaller line-spacing if the
\complit{expanded} option has been turned on).  There are two
varieties of quotation environments.  For shorter quotations, use the
\complit{quote} environment.  Each paragraph in the \complit{quote}
\index{environment!quote@\verb+quote+}%
\index{quote@\verb+quote+}%
environment is not indented (though the
margins are narrower), and there's just a small space added between
them.  This is appropriate for one or two-line quotes, or for a series
of short quotations.

\medskip
\noindent\hskip2em
\begin{minipage}[t]{2.1in}
\textit{Typed as \ldots}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}
\textit{Displayed as \ldots}
\end{minipage}
\par\nobreak\vskip3pt\nobreak
\noindent\hskip2em
\begin{minipage}[t]{2.1in}%
\small\begin{verbatim}
\begin{quote}
Ars Longa, Vita Brevis.

Wow, that's a short quotation.
\end{quote}
\end{verbatim}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}\small
\begin{quote}
Ars Longa, Vita Brevis.

Wow, that's a short quotation.
\end{quote}
\end{minipage}
\bigskip

For longer quoted passages (one or more paragraphs), use the
\complit{quotation}
\index{environment!quotation@\verb+quotation+}%
\index{quotation@\verb+quotation+}%
environment.  Each paragraph in the \complit{quotation} environment is
indented.

\medskip
\noindent\hskip2em
\begin{minipage}[t]{2.1in}
\textit{Typed as \ldots}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}
\textit{Displayed as \ldots}
\end{minipage}
\par\nobreak\vskip3pt\nobreak
\noindent\hskip2em
\begin{minipage}[t]{2.1in}%
\small\begin{verbatim}
\begin{quotation}
This quotation is a bit
longer, just as a test.

And here's a second
paragraph now.
\end{quotation}
\end{verbatim}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}\small
\begin{quotation}
This quotation is a bit
longer, just as a test.

And here's a second
paragraph now.
\end{quotation}
\end{minipage}
\bigskip

\subsection{Single-Spacing Environment}

\margenvs{singlespaced}
If our document is being typeset in \complit{expanded} spacing mode,
\index{singlespaced@\verb+singlespaced+}%
\index{environment!singlespaced@\verb+singlespaced+}%
\index{line spacing, single}%
there may be times when we prefer to typeset something in
single-spaced mode.  For this purpose, the \pkg{fsuthesis} class
provides the \complit{singlespaced} environment.
\begin{ltxexample}
\begin{singlespaced}
This paragraph will be typeset
in single-space mode, even when I've
asked for expanded spacing.
\end{singlespaced}
\end{ltxexample}
You should not need this environment too often:  lists and quotations
already reduce their spacing for you.  Also, if you are typing
algorithms or computer code in \LaTeX's \complit{verbatim} environment, 
spacing has already been reset to single-space mode.  If you have not
set the \complit{expanded} spacing document option, then this
environment formats its contents as a regular paragraph.

\subsection{Insertions: Figures, Tables, Musical Examples}

\margenvs{figure,table,musex}
Standard \LaTeX\ provides environments for \complit{figure}s and
\complit{table}s.
\index{insertions}%
\index{environment!figure@\verb+figure+}%
\index{environment!table@\verb+table+}%
\index{environment!musex@\verb+musex+}%
\index{figure@\verb+figure+}%
\index{table@\verb+table+}%
\index{musex@\verb+musex+}%
The \pkg{fsuthesis} class provides an additional
environment called \complit{musex} for those authors who need to
provide musical examples.  The \complit{musex} environment behaves
similarly to the \complit{figure} environment, except that captions
include the heading ``Example'' instead of ``Figure'', and all the
musical examples can be listed in the front matter in the \textsl{List
  of Musical Examples}.

By setting material off in a \complit{figure}, \complit{table}, or
\complit{musex} environment, the material will be allowed to drift
from its position in the text to the closest available location as
follows: if there is space for the material at the bottom of the
current page, it will be placed there; otherwise, it will be placed at
the top of the next page, or perhaps on a page by itself.  (You have
some control over the placement of floating elements.  For more
detail, you'll need to consult one of the \LaTeX{} references in
section~\ref{sec:references}.)

\margcmds{caption}
Each \complit{figure}, \complit{table}, or \complit{musex} should
contain a \LaTeX{} \verb+\caption+
command\index{caption@\verb+\caption+} whose single argument contains
the text of the caption.  For figures and musical examples, the
caption should be placed below the figure or musical example.  For
tables, the caption should be located above the tabular material.
Examples of the use of each of these environments can be found in the
in the \complit{sample} directory.

\LaTeX{} keeps track of the number of tables, figures, and musical
examples, and your caption will be labeled and numbered automatically.
The caption text will also be inserted into the appropriate
\mbox{\textsl{List of \ldots}} if you requested the list in the
front matter of your document.

\LaTeX{} has many features to assist you in producing tabular material
of arbitrary complexity.  Also, simple diagrams may be created using
the \LaTeX{} \complit{picture} environment.
\index{picture@\verb+picture+}\index{environment!picture@\verb+picture+}%
If you want to include graphics generated by external
software, then you'll need to learn to use the features of the
\pkg{graphicx} package\index{graphicx@\verb+graphicx+}, and you should
add the appropriate \verb+\usepackage+ command in
\complit{mythesis.tex} preamble (see section~\ref{sec:packages}).  You
are strongly advised to refer to the \LaTeX{} references to learn more
about figures and tables if you intend to use them in your manuscript.

\subsection{Cross References}
\label{sec:labels}
One of the advantages of working with \LaTeX{} is the ability to
cross-reference\index{cross references} equations, figures, tables,
musical examples, and section headings.  In writing and revising your
manuscript, it is likely that references to elements may shift as text
is added or moved around.  \LaTeX{} addresses this problem by allowing
you to assign a \textit{label key} to each element.  Then you make a
reference to an element's label key in your text to retrieve its
number or page location.  When your document is processed, \LaTeX{}
replaces all the label key references with their numerical values.

As an example, let's take a look at how this might work if we wish to
refer to an equation in our text.  The left column is the source text
we've typed (unimportant text omitted for brevity), and the result is
in the right column.

\medskip
\noindent\hskip2em
\index{label@\verb+\label+}\begin{minipage}[t]{2.0in}
\textit{Typed as \ldots}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}
\textit{Displayed as \ldots}
\end{minipage}
\par\nobreak\vskip3pt\nobreak
\noindent\hskip2em
\begin{minipage}[t]{2.0in}%
\small\begin{verbatim}
Leonhard Euler was a prolific
...
Equation~\ref{eq:euler-id} on
page~\pageref{eq:euler-id} is
...
\begin{equation}
e^{i\pi} + 1 = 0
\label{eq:euler-id}
\end{equation}
\end{verbatim}
\end{minipage}
\hskip3em
\begin{minipage}[t]{2.5in}%
  \small\sloppy
  Leonhard Euler was a prolific mathematician whose
  pioneering work in power series helped to develop the field
  of mathematical analysis.  Equation~\ref{eq:euler-id} on
  page~\pageref{eq:euler-id} is known as
  \textit{Euler's Identity}, what physicist Richard Feynman called
  ``the most remarkable formula in mathematics''.
  \begin{equation}
    e^{i\pi} + 1 = 0
    \label{eq:euler-id}
  \end{equation}
\end{minipage}
\bigskip

\margcmds{label,ref,pageref}
The \complit{equation} environment
\index{label@\verb+\label+}%
\index{ref@\verb+\ref+}%
\index{pageref@\verb+\pageref+}%
\index{equation@\verb+equation+}%
\index{environment!equation@\verb+equation+}%
automatically numbers equations for us.  The command
\verb|\label{eq:euler-id}| creates the label key
``\complit{eq:euler-id}'', tied to the automatically-numbered
equation.  To access the equation number, we use the
\verb|\ref{eq:euler-id}| macro, while the macro
\verb|\pageref{eq:euler-id}| retrieves the page number.  For figures,
tables, or musical examples, the \verb|\label| command should
immediately follow the \verb|\caption| macro.  In the example, you
might also note the use of the tie special character between the
\verb|\ref| and \verb|\pageref| commands and the text that precedes
them (see section~\ref{sec:comments}).

Since your text may \verb|\ref| label keys before the corresponding
\verb|\label| has been encountered, you will need to run your document
through the \LaTeX{} processor \emph{at least twice}.  The first pass
will write all the label keys and page numbers out to an auxiliary
file, and the second pass will then be able to resolve all the
references properly.  (\LaTeX{} will complain about unresolved or
changed references, reminding you to run the processor a second time.)

As you're writing your document, you might want to keep a list of the
label keys you've created so that you don't have to surf through other
files to recall what a particular label key was.  Keep in mind that
figures, tables, musical examples, and equations all use the same
label system, and all label keys must be unique.  You may develop your
own label key standards (like using \complit{eq:} when referencing an
equation, \complit{fig:} to label a figure, etc., to avoid label
``collision'').  If you expect to have lots of figures, tables, etc.,
you may find it helpful to use descriptive label keys rather than
generic ones, as they may be easier to remember.  E.g.,
\complit{fig:map-Europe-pre1914} is probably more mnemonic than
\complit{fig:MapOne}.

\section{Changing Default Settings}

You may change document default settings in the document preamble.
For example, should you want to change the width of the text column or
the page margins, the document preamble is where you would do it.
(Note that you must still adhere to FSU's \booktitle{Guidelines}, so
be sure you know what you're doing.)

\subsection{Changing \textsl{Table of Contents} Detail}
\label{sec:tocdetail}
If listing section or subsection headings provides too
much detail
\index{contents, table of!detail}%
\index{tocdepth@\verb+tocdepth+}%
for your taste, you may remove these entries by resetting
the \LaTeX{} counter \complit{tocdepth}.  \LaTeX{} considers chapter
headings to be Level~0, section headings to be Level~1, and so on.
The default setting of \complit{tocdepth} is~2 (so subsection
headings are included).  To include only chapter and section headings
in the \textsl{Contents}, for example, you could reset
\complit{tocdepth} in the document preamble with the following line:
\begin{ltxexample}
\setcounter{tocdepth}{1}
\end{ltxexample}
If you set \complit{tocdepth} to zero, then only chapter titles will
be listed in the table of contents.  In this case, you may want to
enable the \complit{chapterleaders} document option. (See
section~\ref{sec:docoptions}).

\subsection{Changing the Level of Heading Numbering}
\label{sec:headnum}
You may change the level at which the heading macros produce numbered
entries by setting \complit{secnumdepth}.
\index{headings!numbered}%
\index{secnumdepth@\verb+secnumdepth+}%
The default setting is
level~two, which means that headings up to subsections will be
numbered automatically.  To stop numbering at the \complit{section}
level (for example), reduce the value of \complit{secnumdepth} to one
by issuing the following command in the document preamble:
\begin{ltxexample}
\setcounter{secnumdepth}{1}
\end{ltxexample}
By setting \complit{secnumdepth} to zero, you may disable all heading
numbering except at the chapter level.  Or you may increase the value
up to five to generate heading numbers all the way down to the
sub-paragraph heading level.

\subsection{Avoiding Club and Widow Lines}
\LaTeX\ makes some typographic decisions (for example, where to place
a page break) based on a system of penalties that are calculated while
the document is processed.
\index{club lines}%
\index{widow lines}%
\index{widowpenalty@\verb+\widowpenalty+}%
\index{clubpenalty@\verb+\clubpenalty+}%
The \complit{sample} document sets
the penalties for ``widow'' and ``club'' lines\footnote{The last line
  of a paragraph which occurs at the top of a page is called a
  ``widow''; the first line of a paragraph which occurs at the bottom
  of a page is called a club.  These are relatively ugly,
  typographically speaking.} as follows:
\begin{ltxexample}
\widowpenalty=9999
\clubpenalty=9999
\end{ltxexample}
To \LaTeX, the value 10,000 is the maximum penalty.  By setting these
values to almost the maximum, \LaTeX\ will avoid generating widow or
club lines in all but the most extreme cases.

\subsection{Adjustments to Titles}
Any of the headings in your document may be re-labeled, should you
need to do so.\index{headings!default}
The following is a table of heading variables and
the default setting in the \pkg{fsuthesis} class.
\begin{center}\small
\begin{tabular}{l l l l}
\textit{Variable Name}&\textit{Default Text}&
  \textit{Variable Name}&\textit{Default Text}\\[3pt]
\verb|\abstractname| & Abstract\index{abstractname@\verb+\abstractname+} &
   \verb|\listabbrevname| & List of Abbreviations\index{listabbrevname@\verb+\listabbrevname+} \\
\verb|\acknowledgename| & Acknowledgments\index{acknowledgename@\verb+\acknowledgename+} &
  \verb|\listfigurename| & List of Figures\index{listfigurename@\verb+\listfigurename+} \\
\verb|\appendixtocname| & Appendix\index{appendixtocname@\verb+\appendixtocname+} &
  \verb|\listtablename| & List of Tables\index{listtablename@\verb+\listtablename+} \\
\verb|\bibname| & Bibliography\index{bibname@\verb+\bibname+}  &
  \verb|\listmusexname| & List of Musical Examples\index{listmusexname@\verb+\listmusexname+} \\
\verb|\biosketchname| & Biographical Sketch\index{biosketchname@\verb+\biosketchname+} &
  \verb|\listsymname| & List of Symbols\index{listsymname@\verb+\listsymname+} \\
\verb|\contentsname| & Table of Contents\index{contentsname@\verb+\contentsname+} &
  \verb|\musexname| & Example\index{musexname@\verb+\musexname+} \\
\end{tabular}
\end{center}

Should you wish to change any of these defaults~--- for example, you need
to change ``Bibliography'' to ``References''~--- you would add the
following to the document preamble:
\begin{ltxexample}
\renewcommand*{\bibname}{References}
\end{ltxexample}
Similarly, if you have more than one appendix, you may want to change
\verb|\appendixtocname| so that the entry in the table of contents is
correct. 
\begin{ltxexample}
\renewcommand*{\appendixtocname}{Appendices}
\end{ltxexample}

There's another way that this mechanism could be useful.  Let's say
that your document has a lot of maps associated with it, and you'd
like to keep the lists of maps and figures separate.  Further, you'd
like to have a ``List of Maps'' included in the front matter of your
document.  You can do this by renaming some other environment that
you're not using, say the List of Musical Examples.
\begin{ltxexample}
\renewcommand*{\musexname}{Map}
\renewcommand*{\listmusexname}{List of Maps}
\end{ltxexample}
Having done this, whenever you invoke the \complit{musex} environment,
the caption will be labeled with ``Map'' rather than
``Example''.  If you include the \verb|\listofmusex| in the front
matter of your document, then ``List of Maps'' will be the heading of
that page instead of ``List of Musical Examples''.

\subsection{Extra Packages}
\label{sec:packages}
\LaTeX{} has many document feature add-ons.
\index{packages}%
If you wish to load additional packages, these options should follow
the document class selection.  Be warned that some packages may not be
compatible with the \fsuth{} class.  Many optional packages may
already come installed with your \TeX/\LaTeX{} distribution, or you
can download and install them from the \acro{CTAN} website
(\url{http://www.ctan.org}).  The skeleton document does not enable
any additional packages.  However, the \complit{sample} folder
provides several examples of external packages you may wish to use.

You enable features by adding a \verb+\usepackage+
command\index{usepackage@\verb+\usepackage+} to the document preamble.
Some packages provide sets of features or configuration options which
can be enabled via the command line.  Here are some~examples:
\begin{ltxexample}
\usepackage{amsmath}
\usepackage[round]{natbib}
\end{ltxexample}
This loads the \pkg{amsmath} package with its default settings and
options, and it loads the \pkg{natbib} package with the
\complit{round} option (which sets citations off in parentheses rather
than square brackets).  Read the package documentation! Packages may
rely on other packages and options, and some combinations of packages
may be incompatible.

The following list is by no means exhaustive.  There are hundreds of
packages available, but a few may be generally useful (or harmful) to
a wide number of users, and so I highlight them here.
\begin{description}
\item[\pkg{geometry}, \pkg{spacing}] \emph{Do not use these packages
  with \fsuth!} (unless you really know what you're doing).  These
  packages will change page layouts and spacing, undoing a lot of
  the hard work that \fsuth{} has done for you.  In many cases,
  interactions between settings in \pkg{geometry} or \pkg{spacing}
  and \fsuth{} will cause ugly or non-compliant spacing. You have
  been warned!

\item[\pkg{amsmath}] The American Mathematical Society has
  developed a large set of symbols and macros to assist you in
  producing high-quality mathematics.

\item[\pkg{textcase}] If you have title, chapter, or section
  headings which include mathematic symbols, you may want to
  install the \pkg{textcase} package, as this will prevent the
  titling macros from upper-casing the math symbols inappropriately.

\item[\pkg{graphicx}] If you will be inserting figures into
  your document electronically, you should investigate the
  \pkg{graphicx} package.  You can find some simple examples of
  figure inclusion in the \complit{sample} directory, but for the
  highest quality output, you owe it to yourself to learn more about
  this topic.  Searching the web for ``latex figure inclusion'' or
  other similar terms will turn up some useful links.

\item[\pkg{natbib}, \pkg{apacite}, \pkg{historian}] These packages
  provide alternatives for formatting citations and bibliographic
  reference lists.  The document in the \complit{sample} folder
  provides more citation examples, and provides links to other
  information regarding bibliography creation.

\item[\pkg{hyperref}] If you are generating an electronic version of
  your document for which you'd like to have hyperlinks automatically
  connecting cross-references and entries in the \textsl{Table of
    Contents}, you should activate the \pkg{hyperref} package.  The
  \pkg{hyperref} package has lots of configuration options, and you
  should refer to its documentation for helpful information.  The use
  of external hyperlinks within your document is discouraged. If
    you enable this package, be sure to turn color links \emph{off},
  as the \booktitle{Guidelines} prohibit multi-colored text in your
  document.
\end{description}

\section{Keeping Things in Order}

If you have lots of figures or musical example files in your document,
you may want to keep these files in the sub-folder already created for
you.  This helps to keep your thesis folder a little less cluttered.
Then if you have a chart called \complit{pie.eps} stored in the
\complit{figures} folder, you just need to include the folder name
when issuing the \verb|\includegraphics|
command\index{includegraphics@\verb+\includegraphics+}, e.g.,
\begin{ltxexample}
\includegraphics{figures/pie.eps}
\end{ltxexample}
You can create any number of folders and sub-folders to help keep
your files organized.

\section{More Examples}
The files in the \complit{thesis-template} directory are only a
bare-bones template to help you get started on your own manuscript.
You will find a more complete example of a thesis manuscript in the
\complit{sample} directory.\index{examples}
The \LaTeX{} source
files in this directory contain explanatory comments and many more
examples of useful code.  The file \complit{thesis.pdf} in the
\complit{sample} directory is the result of processing the source
files, so you can easily compare the source files to the output to see
how everything works.  You'll find some simple examples of equations,
figures, tables, and bibliographic citations to help you create your
own document.  You can find much more help from the web should you
need more sophisticated examples.

\section{Bugs, Corrections, Improvements}

Should you discover what you think is a bug in the way that \fsuth{}
formats your document, you may e-mail me at \texttt{bwhissel@fsu.edu}.
It would be helpful to send the portion of your document which you
believe is misbehaving.  Likewise, if you think that the appearance
of theses or dissertations may be improved in some way, or if you have
some macro definitions that you think may be generally useful and
could be added to \fsuth, I am happy to hear your ideas.

Also, if you think that any of this documentation is misleading or
unclear, \emph{please} let me know.  I wish to make this
\booktitle{User's Guide} and the \fsuth{} class as helpful as
possible.

Please note that I cannot help you to learn features of \LaTeX: there
are many resources and tutorials that are freely available, and I am
unable to support individual requests for help with anything that does
not pertain directly to the \fsuth{} class.

\bigskip
\noindent
Best wishes, and good luck!

\clearpage

\addcontentsline{toc}{section}{Index}
\printindex

\end{document}

### 2013-12-03 docs/paper/sigplanconf-template.tex
docs/paper/fsuthesis/thesis-template/paper.tex has my paper

@@
 
-\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
-\copyrightyear{20yy} 
-\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
-\doi{nnnnnnn.nnnnnnn}
+%\conferenceinfo{CONF 'yy}{Month d--d, 20yy, City, ST, Country} 
+%\copyrightyear{20yy} 
+%\copyrightdata{978-1-nnnn-nnnn-n/yy/mm} 
+%\doi{nnnnnnn.nnnnnnn}
 
@@
 
-\titlebanner{banner above paper title}        % These are ignored unless
-\preprintfooter{short description of paper}   % 'preprint' option specified.
+%\titlebanner{banner above paper title}        % These are ignored unless
+%\preprintfooter{short description of paper}   % 'preprint' option specified.
 
-\title{Pseudo-Symbolic Execution (Or Minimialistic Constraint Solving) Using Dynamic Taint Analysis and Backsolving}
+\title{A Backsolving Technique Using Dynamic Taint Analysis}
 %\subtitle{Subtitle Text, if any}
@@
 
+\section{Abstract}
+
 \section{Introduction}
@@
 This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to come up with smarter ways to mutate user input and create new test cases.
-For instance, in the below example:
+For instance, in the figure 1 example:
+\\
+\\
 
 \begin{verbatim}
-mv eax, userInput1
-mv ebx, userInput2
-cmp eax, ebx
-jge 0xDEADBEEF
+figure 1:
+call read
+mov eax, [ebp - val]
+inc eax
+mul eax, 5
+cmp eax, 42
+jnz 0x8BADMEAT
 \end{verbatim}
 
-If we already had a test case where userInput1 equalled 10 and userInput2 equalled 5, this test case would jump to 0xDEADBEEF.
-To generate a test case where we would not jump, we take the complement of the jge instruction's comparison function, which would be "less than".
-We can find the last instruction that modified the Z flag, which is how jge decides to jump or not.
-We see that this compare instruction was tained by the eax and ebx registers, which were in turn tainted by userInputs 1 and 2.
-Since we can impact both values in the comparison, it is easy to modify user input smartly to alter the value of the Z flag and jump during the next execution.
-Perhaps we could switch the values, or auto-increment/decrement one until we satisfy the needed comparison, or mutate values randomly.
+If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADMEAT.
+With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted).
+After some number of transformations, perhaps zero, to the value in the eax register, we see a compare instruction, which checks eax's value against an immediate value.
+Then we can keep track of specific taint sources, and can record any movements or transformations, we have all the necessary information to "solve" the branch.
+Once we reach the tainted branch, we know that user input can affect whether we jump or not, and consequently we can backsolve to find out how to affect the branch instruction.
+In particular, we know the conditional jump instruction jnz depends on the Z flag in the EFLAGS register.
+We record whatever instruction last modified each flag in the Z flags register, so we handle the compare instruction next.
+Because we have kept track of taint propagation, we know we can affect the value of eax, but not 42, since it is an immediate value, so we know we need to make the value in eax equal 42.
+We follow the instructions that have modified the value of eax and use any appropriate operands involved with the inverse operation of the one originally performed on the value to reverse the transformations to eax's value.
+Finally, we notice eax originally received taint when a value was moved from memory, which was read into memory using the read syscall.
 

### 2013-12-03 MyPinTool/FollowExecution.h

@@ -18,6 +18,8 @@ UINT32 lastCmpImmediate;
 UINT32 lastEaxTaintValue; // HACK to get 300 for buf[300]
 UINT32 taintPosition;
 BOOL taintedCmp = false;
+//REG eipValue;
+UINT32 eipValue;
 
 /* ===================================================================== */
 /* Control Flow following jumps                                          */
@@ -84,6 +86,9 @@ bool taintReg(REG reg)
     }
 
     switch (reg) {
+        //case REG_EIP:  regsTainted.push_front(REG_EIP); 
+        //               TaintFile << "TAINT REACHED EIP" << endl;
+        //               break;
 
         case REG_EAX:  regsTainted.push_front(REG_EAX); 
         case REG_AX:   regsTainted.push_front(REG_AX); 
@@ -390,13 +395,20 @@ VOID Branches(INS ins, VOID *v)
  *  Instrument read syscall
  */
 VOID Syscall_entry(THREADID thread_id, CONTEXT *ctx, SYSCALL_STANDARD std, VOID *v)
-//VOID Syscall_exit(THREADID thread_id, CONTEXT *ctx, SYSCALL_STANDARD std, VOID *v)
 {
     unsigned int i;
     UINT32 start, size;
     //UINT32 read;
+    if (PIN_GetSyscallNumber(ctx, std) == __NR_open) {
+        //TaintFile << "BLAH " << PIN_GetSyscallArgument(ctx, std, 1);
+        TaintFile << "OPEN " << PIN_GetSyscallArgument(ctx, std, 0) << " "
+                             << PIN_GetSyscallArgument(ctx, std, 1) << endl;
+    }
 
     if (PIN_GetSyscallNumber(ctx, std) == __NR_read) {
+
+        eipValue = PIN_GetContextReg(ctx, REG_EIP);
+        TaintFile << "EIP value\t" << std::hex << eipValue << endl;
 
         //UINT32 fd = static_cast<UINT32>((PIN_GetSyscallArgument(ctx, std, 0)));
         start = static_cast<UINT32>((PIN_GetSyscallArgument(ctx, std, 1)));
@@ -404,13 +416,15 @@ VOID Syscall_entry(THREADID thread_id, CONTEXT *ctx, SYSCALL_STANDARD std, VOID 
         //read  = static_cast<UINT32>((PIN_GetSyscallReturn(ctx, std)));
 
         // Cheap trick for demo, will need to remove later?
-         if (size != 500) {
[…]

### 2013-12-03 MyPinTool/MyPinTool.cpp

@@ -48,6 +48,7 @@ bool IN_MAIN = false;
 /* User Libraries */
 /* ===================================================================== */
 #include "FollowExecution.h"
+//#include "buffer_linux.h"
 //#include "DTA.h"
 //#include "FindUseAfterFree.h"
 
@@ -78,6 +79,7 @@ VOID Fini(INT32 code, VOID *v)
     FiniFollowExecution();
     //FiniFindUseAfterFree();
     //FiniDTA();
+    //FiniBufferLinux();
 }
 
 /* ===================================================================== */
@@ -113,6 +115,7 @@ int main(int argc, char *argv[])
     InitFollowExecution();
     //InitFindUseAfterFree();
     //InitDTA();
+    //InitBufferLinux();
 
     // Watch main function
     //IMG_AddInstrumentFunction(WatchMain, 0);

### 2013-12-03 MyPinTool/buffer_linux.h

@@ -1,0 +1,258 @@
+/*BEGIN_LEGAL 
+Intel Open Source License 
+
+Copyright (c) 2002-2013 Intel Corporation. All rights reserved.
+ 
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are
+met:
+
+Redistributions of source code must retain the above copyright notice,
+this list of conditions and the following disclaimer.  Redistributions
+in binary form must reproduce the above copyright notice, this list of
+conditions and the following disclaimer in the documentation and/or
+other materials provided with the distribution.  Neither the name of
+the Intel Corporation nor the names of its contributors may be used to
+endorse or promote products derived from this software without
+specific prior written permission.
+ 
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE INTEL OR
+ITS CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+END_LEGAL */
+/*
+ * Sample buffering tool
+ * 
+ * This tool collects an address trace of instructions that access memory
+ * by filling a buffer.  When the buffer overflows,the callback writes all
+ * of the collected records to a file.
+ *
+ */
+
+#include <iostream>
+#include <fstream>
+#include <stdlib.h>
[…]

### 2013-12-03 MyPinTool/clean.sh

@@ -1,5 +1,6 @@
 #!/bin/bash -x
 rm -f input/input.* output/output.* taint/taint.* mutations/mutation.*
-rm -f results.out
-rm -f taint.out
+rm -f results.out file.out taint.out
+rm -f buffer.out.*
 echo > taint/explored.0
+

### 2013-12-03 MyPinTool/driver.py

@@ -18,7 +18,10 @@ def test(inputFile, taintFile, seed = ('0', '0', '0') ):
         '../pin/pin', 
         '-t', 'obj-ia32/MyPinTool.so', 
         #'--', '../vulnerable_programs/trivial/a.out', inputFile
-        '--', './a.out', inputFile
+        #'--', './a.out', inputFile
+        '--', './simpleCrackme', inputFile
+        #'--', './strcpy', inputFile
+        #'--', 'ls'
     ]
 
     # Which test are we running? 
@@ -61,7 +64,11 @@ def mutate(inputFile, seed):
 
     # Change input value to equal non-tainted immediate
     if (int(seed[1]) < 256):
-        f[int(seed[0])] = chr(int(seed[2]))
+        try:
+            f[int(seed[0])] = chr(int(seed[2]))
+        except OverflowError as e:
+            print 'Value too large for C type long'
+            return
 
     out = ''.join(f)
 

### 2013-12-03 vulnerable_programs/trivial/removeTaint.c

@@ -1,0 +1,38 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+
+    // remove taint
+    int i;
+    for (i = 0; i < 500; i++) {
+        buf[i] = '\0';
+    }
+
+    int win = 0;
+    if (buf[300] == 'X') {
+        win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2013-12-03 vulnerable_programs/trivial/simpleCrackme2.c

@@ -1,0 +1,31 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'X' && buf[301] == 'Y' && buf[302] == 'Q' && buf[303] == 'R') {
+        win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2013-12-03 vulnerable_programs/trivial/strcpy.c

@@ -1,11 +1,35 @@
 /* strcpy example */
 #include <stdio.h>
+#include <unistd.h>
+#include <stdlib.h>
 #include <string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
 
 int main (int argc, char *argv[])
 {
-    char str1[40];
-    strcpy(str1,argv[1]);
-    printf("str1: %s\n",str1);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[20];
+    char str1[20];
+    int res = read(fd, buf, 20);
+
+
+    // Vuln. condition
+    if (buf[10] == 'A') {
+        while (read(fd, buf, 50) > 0) {
+            strcat(str1, buf);
+            printf("%s\n",str1);
+
+        }
+        //strcpy(str1, buf);
+    }
+    else {
+        strcpy(str1, "Didn't work");
+    }
+
+    printf("%s\n",str1);
+    close(fd);
     return 0;
 }
+

### 2013-12-03 vulnerable_programs/trivial/stringCmp.c

@@ -1,0 +1,34 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    char str[100];
+    int res = read(fd, buf, 500);
+    close(fd);
+    strcpy(str, buf);
+
+    printf("%s\n", buf);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (strncmp(str, "thepassword", strlen("thepassword") ) == 0) {
+        win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2013-12-06 docs/paper/fsuthesis/thesis-template/paper.tex
paper for jeff and nabil

@@
 
-\title{A Backsolving Technique Using Dynamic Taint Analysis}
+\title{Rough Draft: A Backsolving Technique Using Dynamic Taint Analysis}
 \author{Clark Wood}
-\college{College of Arty Science}
+\college{College of Arts and Science}
 \department{Department of Computer Science} % Delete if no department
@@
 
-\section{Introduction}
+\chapter{Introduction}
 
-Finding exploitable bugs in binaries is a difficult and lucrative endeavour.
-Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions [CITE], is one technique used by researchers and analysts.
+Finding exploitable bugs in binaries is a difficult but valuable endeavour.
+Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions, is one technique used by researchers and analysts.
 Applications tested for vulnerabilities are often black boxes because source code is unavailable.
-This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce [CITES].
-Among these issues are i) efficient and thorough dynamic taint analysis [CITE], ii) the path explosion problem [U], and iii) the code coverage problem [CITE?].
-Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
+This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce.
+Among these issues are i) efficient and thorough dynamic taint analysis, ii) the path explosion problem [U], and iii) the code coverage problem.
+Dynamic taint analysis is also difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
 The path explosion problem arises from the nature of assembly languages.
-Jump instructions, which may make up as much as X\% of machine instructions in programs [CITE], each multiply the total number of existing paths in a binary by two.
+Jump instructions, which may make up a decent percentage of machine instructions in programs, each multiply the total number of existing paths in a binary by two.
 Considering the size of binaries, this quickly leads to an un-tenably large set of possible paths to explore via conventional techniques like symbolic execution.
 And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way.
-Such automated exploit generation is the subject of much research [H, I, CITES].
+Such automated exploit generation is the subject of much research [H, I].
 
@@
 Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
-This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to come up with smarter ways to mutate user input and create new test cases.
+This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to determine smarter ways to mutate user input and create new test cases.
 For instance, in the figure 1 example:
+\\
+\\
+\\
 
@@
 In particular, we know the conditional jump instruction jnz depends on the Z flag in the EFLAGS register.
-We record whatever instruction last modified each flag in the Z flags register, so we handle the compare instruction next.
+We record whatever instruction last modified each flag in EFLAGS, so we handle the compare instruction next.
 Because we have kept track of taint propagation, we know we can affect the value of eax, but not 42, since it is an immediate value, so we know we need to make the value in eax equal 42.
@@
 
-\section{Related Work}
+\chapter{Related Work}
 
@@
 In particular, they suggest combining taint analysis with backward slicing.
-The technique discussed in the paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
+The technique discussed in this paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
 
-\section{Assumptions and Scoping}
+\chapter{Assumptions and Scoping}
 
 I assume ASLR is disabled for the binary to be fuzzed.
-This allows the program to easily track and compare execution paths by creating a list of jump locations.
-Since the world is moving more and more toward 64-bit architectures, I plan to implement the technique for 32-bit x86 assembly.
-This is because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both 32 vs.
-64-bit and the flavor of architecture (ARM, x86, PowerPC), since compilers try to adhere to the C standard.
+This allows the program to easily track and compare execution paths.
+I plan to implement the technique for 32-bit x86 assembly, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both the size and flavor of architecture (32 vs.
+64-bit, ARM vs.
+x86 vs.
+PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
 
@@
 
-I am hopeful about the results because current selective symbolic execution engines still appear to introduce significant overhead (Between 6 and 78X overhead more than QEMU for S2E.
+Because current selective symbolic execution engines still appear to introduce significant overhead (Between 6 and 78X overhead more than QEMU for S2E.
 Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others) [J, K, L].
 In contrast, basic block counting using Intel Pin, the framework I am leveraging, introduced between 2 and 4X overhead [M].
-However, the pintool needed for my proposed technique will introduce greater levels of overhead, since I will be working at the instruction level instead of the basic block level.
+However, the pintool needed for my proposed technique will introduce greater levels of overhead, since I will be working at the instruction level instead of the basic block level, requiring more instrumentations for a given binary.
 
 I am leveraging Intel PIN to perform dynamic binary instrumentation.
-I plan to test first on dummy programs with many paths that are easy to backsolve, similar to the example above.
-A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, should create an appropriate binary.
+I am first testing dummy programs with many paths that are easy to backsolve, similar to the example above.
+A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
 I then plan to test against S2E and Peach Fuzzer [Z].
-I already have this program written and have verified using IDA Pro that there are a many, many paths to try and find.
 
-There are allowable situations in programs which are outside the scope of this program.
+In addition, there are allowable situations in programs which are outside the scope of this program.
 For instance, programs can loop forever [X].
@@
 
-\section{Techniques}
+\chapter{Techniques}
 
@@
 Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing.
-Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims to ameliorate the path explosion problem.
+Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims to ameliorate the path explosion problem while maintaining good code coverage.
 These each come with their own drawbacks, a primary one of which is the lack of automated instrumentation.
@@
 
-\subsection{Dynamic Taint Analysis}
+\section{Dynamic Taint Analysis}
 
@@
 The granularity of taint marking is variable.
-Assigning everything from a generic binary value of tainted/not tainted to bit-level marking of which part of user input affected which variable is conceivable, although finer-grained taint analysis is more computationally expensive and difficult to determine [CITE].
+Assigning everything from a generic binary value of tainted/not tainted to bit-level marking of which part of user input affected which variable is conceivable, although finer-grained taint analysis is more computationally expensive and difficult to determine.
 
@@
 
-Because of subtle implicit flow cases referenced by Clause, J.
-et all [D], which can be difficult to spot (Page 2, Figure 2b).
-Implicit data flows are not always considered by dynamic tainting techniques [E].
-
-For my project, implicit data flows are very important, so I need to implement DTA which catches both implicit and explicit flows.
+Handling taint correctly is of great important because of the existence of subtle implicit flow cases referenced by Clause, J.
+et al [D].
+Implicit data flows are not always considered by dynamic tainting techniques [E], but for my project, implicit data flows are very important, so I need to implement DTA which catches both implicit and explicit flows.
 
@@
 
-\subsection{Symbolic Execution}
+\section{Symbolic Execution}
 
@@
 Without utilizing symbolic execution, however, it is difficult to automatically guarantee that all possible paths in a binary have been explored.
-Where most current research focuses on improving speed by using symbolic execution less, I propose to achieve similar code coverage to symbolic execution by implementing something similar to symbolic execution, but without using the SMT solvers and instruction emulation which tend to make symbolic execution slow.
+Where most current research focuses on improving speed by using symbolic execution less, I propose to achieve similar code coverage to symbolic execution by implementing something akin to symbolic execution, but without using the SMT solvers and instruction emulation which tend to make symbolic execution slow.
 
@@
 
-\subsection{Concolic Execution}
+\section{Concolic Execution}
 
-Current research focuses on carefully deciding when and how to use symbolic execution [J, T, W, CITE].
-So-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research [CITE].
+Current research focuses on carefully deciding when and how to use symbolic execution [J, T, W].
+So-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research.
 
 Concolic testing has been shown to improve runtime while still allowing both wide and deep inspection of a program's execution tree, although it often still requires source code to be instrumented [X, Y].
-What I propose is akin to concolic testing, in that I am augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
+What I propose is similar to concolic testing, in that I am augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
 However, the lack of a heavyweight constraint solver and the ability to work on binaries without instrumenting or using source code in any way have, to the best of my knowledge, not yet been proposed.
 
-\section{Implementation}
+\chapter{Implementation}
 
@@
 
-Operations involving an untainted first operand and a tainted second operand generally spread taint, while operations with a tainted first operand and an untainted second operand remove taint.
+For example, move operations involving an untainted first operand and a tainted second operand generally spread taint, while those with a tainted first operand and an untainted second operand remove taint.
 Tainted branches trigger the backsolving technique.
@@
 
-\subsection{Testing Harness}
+\section{Testing Harness}
 
@@
 
-Professional fuzzing products, like Peach Fuzzer
+%Professional fuzzing products, like Peach Fuzzer
 
-\subsection{Methodology}
+\section{Methodology}
 
-Testing can begin on dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
+I am currently instrumenting dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
 If results appear promising I can try to make the fuzzer as complete as possible and begin running it on real-world applications.
@@
 
-\subsection{Evaluation}
+As of this writing I am moving towards fuzzing Linux utilities.
+Results for toy binaries are promising, with "crackme" type programs which ask for a secret being solved in approximately 2*n runs, where n is the length of the secret.
+There is, however, still some overtainting which must be accounted for.
+%\section{Evaluation}
 
@@
 
-\section{Future Work}
-
 % Was setbacks, modify and remove heavily
 
-Dynamic taint analysis, symbolic execution and fuzzing are hot topics of research, and so the area moves quickly.
-I have been trying to come up with ideas which are both novel and implementable within my graduation timeframe, but this has proved difficult.
-
-I have made progress using the Pin instrumentation framework, and feel comfortable developing code using the API.
-I have also read quite a few papers which have progressed my knowledge of the area, so in the worst case I have still learned a lot about a subject that interests me and written some code.
-In addition, using the Pin API to instrument binaries, and debugging my pintools using tools like strace, has taught me more about assembly language, which is valuable for reverse engineering, a branch of information security I want to pursue a career in.
-
-I think, at the least, this can be a project option for my graduation, but I still believe a thesis is possible at this point.
-
-I need to:
-\begin{itemize}
-	\item Read more papers to make sure what I am proposing is novel and will not step on any toes.
-	\item Begin writing a prototype and prove that a subset of I am proposing is feasible.
-	\item Benchmark my prototype against modern applications like S2E and Peach Fuzzer to decide whether or not it makes sense to continue.
-\end{itemize}
-
-Possible complications are:
-
-\begin{itemize}
-	\item Difficulty achieving completeness.
-Since there are many different ways that user input can be modified and compared, there will be many cases to account for.
-I think I can at least implement a subset of them in order to demonstrate speedup under a specific set of circumstances
-	\item This work is not novel.
-Until very recently I was looking at DTA more than symbolic execution, so it is hard to say whether my proposal is actually new.
-I'm doing my best to read all the relevant papers, and so far it appears that the use of a separate constraint solver or other satisfiability prover is a prerequisite of symbolic execution.
-	\item No noticeable speedup.
-Pin introduces noticeable overhead, and my ideas may simply not be faster than current approaches, even when test cases are reasonably tailored to work in my favor.
-In this case I simply go the project route unless something else strikes me.
-Although research with negative results is theoretically publishable, I don't see very much of it, so I assume it's a faux pas in computer science.
-\end{itemize}
-
-\section{References}
+\chapter{References}
 

### 2013-12-06 MyPinTool/driver.py

@@ -34,7 +34,7 @@ def test(inputFile, taintFile, seed = ('0', '0', '0') ):
     p1.wait()
 
     # Find which taint are new
-    # input  -> input/ and mutated
+    # input -> input/ and mutated
     # taint -> taint/
     explored        =   open('./taint/explored.0', 'r').read().split()
     exploredFile    =   open('./taint/explored.0', 'a')

### 2013-12-06 MyPinToolMultiProcess/DTA.h

@@ -1,0 +1,309 @@
+//
+//  Jonathan Salwan - Copyright (C) 2013-08
+// 
+//  http://shell-storm.org
+//  http://twitter.com/JonathanSalwan
+//
+//  Note: Example 4 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
+//        Detect a use after free vulnerability via a old stack frame
+//
+
+#include "pin.H"
+#include <asm/unistd.h>
+#include <fstream>
+#include <iostream>
+#include <list>
+
+std::ofstream TaintFile;
+std::list<UINT32> addressTainted;
+std::list<REG> regsTainted;
+
+
+bool checkAlreadyRegTainted(REG reg)
+{
+  list<REG>::iterator i;
+
+  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
+    if (*i == reg){
+      return true;
+    }
+  }
+  return false;
+}
+
+VOID removeMemTainted(UINT32 addr)
+{
+  addressTainted.remove(addr);
+  TaintFile << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
+}
+
+VOID addMemTainted(UINT32 addr)
+{
+  addressTainted.push_back(addr);
+  TaintFile << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
+}
+
+bool taintReg(REG reg)
+{
+  if (checkAlreadyRegTainted(reg) == true){
+    TaintFile << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
+    return false;
+  }
+
+  switch(reg){
+
+    case REG_EAX:  regsTainted.push_front(REG_EAX); 
+    case REG_AX:   regsTainted.push_front(REG_AX); 
+    case REG_AH:   regsTainted.push_front(REG_AH); 
+    case REG_AL:   regsTainted.push_front(REG_AL); 
+         break;
+
+    case REG_EBX:  regsTainted.push_front(REG_EBX);
+    case REG_BX:   regsTainted.push_front(REG_BX);
+    case REG_BH:   regsTainted.push_front(REG_BH);
+    case REG_BL:   regsTainted.push_front(REG_BL);
+         break;
+
+    case REG_ECX:  regsTainted.push_front(REG_ECX);
+    case REG_CX:   regsTainted.push_front(REG_CX);
[…]

### 2013-12-06 MyPinToolMultiProcess/FindUseAfterFree.h

@@ -1,0 +1,378 @@
+// Based heavily on Jonathan Salwan's code, all credit to him. Thanks!
+
+//  Jonathan Salwan - Copyright (C) 2013-08
+// 
+//  http://shell-storm.org
+//  http://twitter.com/JonathanSalwan
+//
+//  Note: Example 5 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
+//        Detect the classical use after free vulnerability 
+//
+
+#include <asm/unistd.h>
+#include <fstream>
+#include <iostream>
+#include <list>
+
+#define LOCKED    1
+#define UNLOCKED  !LOCKED
+
+#define ALLOCATE  1
+#define FREE      !ALLOCATE
+
+static size_t         lastSize;
+
+struct mallocArea
+{
+  UINT32  base;
+  UINT32  size;
+  BOOL    status;
+};
+
+UINT32 lockTaint = LOCKED;
+
+std::list<UINT32>               addressTainted;
+std::list<REG>                  regsTainted;
+std::list<struct mallocArea>    mallocAreaList;
+
+BOOL checkAlreadyRegTainted(REG reg)
+{
+  list<REG>::iterator i;
+
+  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
+    if (*i == reg){
+      return true;
+    }
+  }
+  return false;
+}
+
+VOID removeMemTainted(UINT32 addr)
+{
+  addressTainted.remove(addr);
+  std::cout << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
+}
+
+VOID addMemTainted(UINT32 addr)
+{
+  addressTainted.push_back(addr);
+  std::cout << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
+}
+
+BOOL taintReg(REG reg)
+{
+  if (checkAlreadyRegTainted(reg) == true){
+    std::cout << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
+    return false;
+  }
+
+  switch(reg){
+
+    case REG_EAX:  regsTainted.push_front(REG_EAX); 
+    case REG_AX:   regsTainted.push_front(REG_AX); 
+    case REG_AH:   regsTainted.push_front(REG_AH); 
+    case REG_AL:   regsTainted.push_front(REG_AL); 
+         break;
+
[…]

### 2013-12-06 MyPinToolMultiProcess/MyPinTool.cpp

@@ -1,0 +1,135 @@
+/*BEGIN_LEGAL 
+Intel Open Source License 
+
+Copyright (c) 2002-2013 Intel Corporation. All rights reserved.
+ 
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are
+met:
+
+Redistributions of source code must retain the above copyright notice,
+this list of conditions and the following disclaimer.  Redistributions
+in binary form must reproduce the above copyright notice, this list of
+conditions and the following disclaimer in the documentation and/or
+other materials provided with the distribution.  Neither the name of
+the Intel Corporation nor the names of its contributors may be used to
+endorse or promote products derived from this software without
+specific prior written permission.
+ 
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE INTEL OR
+ITS CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+END_LEGAL */
+
+#include "pin.H"
+#include <asm/unistd.h>
+#include <fstream>
+#include <iostream>
+#include <list>
+#include <string>
+#include <unordered_map>
+using namespace std;
+
+/* ===================================================================== */
+/* Global Variables */
+/* ===================================================================== */
+
+bool IN_MAIN = false;
+
+/* ===================================================================== */
+/* User Libraries */
[…]

### 2013-12-06 MyPinToolMultiProcess/clean.sh

@@ -1,0 +1,6 @@
+#!/bin/bash -x
+rm -f input/input.* output/output.* taint/taint.* mutations/mutation.*
+rm -f results.out file.out taint.out
+rm -f buffer.out.*
+echo > taint/explored.0
+

### 2013-12-06 MyPinToolMultiProcess/driver.py

@@ -1,0 +1,130 @@
+# Driver to decide how to mutate
+
+import os, shutil
+import subprocess
+from operator import itemgetter
+
+
+def test(inputFile, taintFile, seed = ('0', '0', '0') ):
+
+    # First time, don't mutate
+    if seed != ('0', '0', '0'):
+        mutate(inputFile, seed)
+    else:
+        print('Initial run')
+    
+    # command for subprocess, pintool
+    cmd =   [   
+        '../pin/pin', 
+        '-t', 'obj-ia32/MyPinTool.so', 
+        #'--', '../vulnerable_programs/trivial/a.out', inputFile
+        #'--', './a.out', inputFile
+        '--', './simpleCrackme', inputFile
+        #'--', './strcpy', inputFile
+        #'--', 'ls'
+    ]
+
+    # Which test are we running? 
+    testNumber = getTestNumber('./taint/')
+    print 'Running test #' + str(testNumber), 'based on mutation seed', seed, '...' 
+
+    # One iteration of pintool, generates new (input.txt, taint.out) pair
+    outputFile = open('./file.out', 'w')
+    p1 = subprocess.Popen(cmd, stdout=outputFile)
+    p1.wait()
+
+    # Find which taint are new
+    # input -> input/ and mutated
+    # taint -> taint/
+    explored        =   open('./taint/explored.0', 'r').read().split()
+    exploredFile    =   open('./taint/explored.0', 'a')
+    taint           =   open(taintFile, 'r').read().split()
+
+    newTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in taint}
+    exploredTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in explored}
+
+    # Set difference
+    newTaint = {x: newTaintDict[x] for x in newTaintDict if x not in exploredTaintDict.keys()} 
+
+    # Copy taint and append latest taint to explored
+    recordResults(inputFile, outputFile, newTaint, seed, testNumber) 
+    exploredFile.write(':'.join(seed) + "\n")
+
+    # file in format pos:op:arg1:arg2
+    toExplore = [(r, newTaint[r][0], newTaint[r][1]) for r in newTaint]
+
+    toExplore = sorted(toExplore, key=itemgetter(0))
+    return toExplore
+
+# End test
+
+# TODO will need to handle non-character cases for seed[1]
+def mutate(inputFile, seed):
+    f = list(open(inputFile, 'r').read())
+
[…]

### 2013-12-06 MyPinToolMultiProcess/examples/countJumps.cpp

@@ -1,0 +1,116 @@
+/*BEGIN_LEGAL 
+Intel Open Source License 
+
+Copyright (c) 2002-2013 Intel Corporation. All rights reserved.
+ 
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are
+met:
+
+Redistributions of source code must retain the above copyright notice,
+this list of conditions and the following disclaimer.  Redistributions
+in binary form must reproduce the above copyright notice, this list of
+conditions and the following disclaimer in the documentation and/or
+other materials provided with the distribution.  Neither the name of
+the Intel Corporation nor the names of its contributors may be used to
+endorse or promote products derived from this software without
+specific prior written permission.
+ 
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE INTEL OR
+ITS CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+END_LEGAL */
+#include <iostream>
+#include <fstream>
+#include "pin.H"
+
+ofstream OutFile;
+
+// Used to print every instruction in main 
+    
+VOID FindBranchOrJump(INS ins, VOID *v)
+{
+    // Categories are higher-level semantic descriptions than opcodes.
+    // The constant matches all conditional branches
[…]

### 2013-12-07 MyPinToolMultiProcess/mp.c
working on multiproc version

@@ -1,0 +1,33 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+
+int main(int argc, char* argv[])
+{
+    // argv1 is number of processes to run
+    // subsequent argvs are file for each process to fuzz
+
+    char* args[10];
+    int st;
+
+    int i;
+    for (i = 0; i < atoi(argv[1]); i++) {
+
+        if (fork() == 0) {
+            args[0] = "../pin/pin";
+            args[1] = "-t";
+            args[2] = "obj-ia32/MyPinTool.so"; 
+            args[3] = "--";
+            args[4] = "./simpleCrackme";
+            args[5] = argv[2];      // input file, generated by python driver
+            args[6] = NULL;
+
+            execv(args[0], args);
+
+        }
+
+    }
+    wait(&st);
+
+
+}

### 2013-12-13 docs/paper/fsuthesis/thesis-template/paper.tex
working on sigplan for netsec final report

@@
 
+\section{Parallelization}
+
+I have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
+Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel.
+For this project I have tested my program on a personally created binary, simpleCrackme.
+This binary takes a file containing a password in argv1.
+If the password matches its secret, then it prints "You win", otherwise, it prints "You lose".
+
+After running my program, one can grep for the win string in the output/ directory.
+This is similar to concept to running a fuzzer, and grepping around the output recorded for more interesting conditions, like segfaults.
+Results show a noticeable speedup.
+
+Sequential:
+After several runs, I've seen performance ranging from ~33 seconds to 19 seconds.
+26.12user 7.15system 0:33.42elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+0inputs+1496outputs (0major+1168365minor)pagefaults 0swaps
+
+14.66user 4.67system 0:19.44elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+0inputs+1496outputs (0major+1168305minor)pagefaults 0swaps
+
+Parallel:
+The parallel implementation seems to decrease time by somewhere around half, which makes sense considering the problem is not embarassingly parellel, and Intel Pin may try and use multiple cores during startup.
+30.64user 9.71system 0:10.83elapsed 372\%CPU (0avgtext+0avgdata 12952maxresident)k
+0inputs+816outputs (0major+1368622minor)pagefaults 0swaps
+
+However, I have seen runs as high as ~13 seconds elapsed.
+Since my testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
+I also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
+
 %

### 2013-12-13 docs/paper/sigplanconf-template.tex
working on sigplan for netsec final report

@@
 
-Finding exploitable bugs in binaries is a difficult and lucrative endeavour.
-Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions [CITE], is one technique used by researchers and analysts.
+Finding exploitable bugs in binaries is a difficult but valuable endeavour.
+Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions, is one technique used by researchers and analysts.
 Applications tested for vulnerabilities are often black boxes because source code is unavailable.
-This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce [CITES].
-Among these issues are i) efficient and thorough dynamic taint analysis [CITE], ii) the path explosion problem [U], and iii) the code coverage problem [CITE?].
-Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
+This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce.
+Among these issues are i) efficient and thorough dynamic taint analysis, ii) the path explosion problem [U], and iii) the code coverage problem.
+Dynamic taint analysis is also difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
 The path explosion problem arises from the nature of assembly languages.
-Jump instructions, which may make up as much as X\% of machine instructions in programs [CITE], each multiply the total number of existing paths in a binary by two.
+Jump instructions, which may make up a decent percentage of machine instructions in programs, each multiply the total number of existing paths in a binary by two.
 Considering the size of binaries, this quickly leads to an un-tenably large set of possible paths to explore via conventional techniques like symbolic execution.
 And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way.
-Such automated exploit generation is the subject of much research [H, I, CITES].
+Such automated exploit generation is the subject of much research [H, I].
 
@@
 Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
-This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to come up with smarter ways to mutate user input and create new test cases.
+This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to determine smarter ways to mutate user input and create new test cases.
 For instance, in the figure 1 example:
+\\
 \\
@@
 In particular, they suggest combining taint analysis with backward slicing.
-The technique discussed in the paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
+The technique discussed in this paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
+This data is put to use by solving for the input state necessary to explore new blocks in the binary by taking the opposite path for a particular branch in the previous run.
+
+Often, research leveraging taint analysis requires access to source code or even programming optimization.
+However, minimizing programmer workload is more in spirit with fuzzing.
+Fuzzers should be fire and forget, allowing expensive programmers to work on something else while testing runs in the background.
+Work such as [E] has kept the spirit of this, although they focus at a different granularity of taint collection and propagation.
+The authors argue for following taint at the function level instead of at the instruction level, primarily to improve performance.
+The paper proposes several performance-saving heuristics, such as statically  constructing a finite state machine, which is executed with information gleaned during dynamic analysis, to help follow taint propagation within loops.
+However, perhaps because of the reliance on QEMU, or the initial translation of code to an intermediate representation without side-effects, significant overhead is introduced.
 
@@
 I assume ASLR is disabled for the binary to be fuzzed.
-This allows the program to easily track and compare execution paths by creating a list of jump locations.
-Since the world is moving more and more toward 64-bit architectures, I plan to implement the technique for 32-bit x86 assembly.
-This is because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both 32 vs.
-64-bit and the flavor of architecture (ARM, x86, PowerPC), since compilers try to adhere to the C standard.
+This allows the program to easily track and compare execution paths.
+I plan to implement the technique for 32-bit x86 assembly, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both the size and flavor of architecture (32 vs.
+64-bit, ARM vs.
+x86 vs.
+PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
 
@@
 
-Current research focuses on carefully deciding when and how to use symbolic execution [J, T, W, CITE].
-So-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research [CITE].
+Current research focuses on carefully deciding when and how to use symbolic execution [J, T, W].
+So-called concolic execution mixes concrete and symbolic input, and various heuristics to determine when to resort to symbolic execution are in research.
 
 Concolic testing has been shown to improve runtime while still allowing both wide and deep inspection of a program's execution tree, although it often still requires source code to be instrumented [X, Y].
-What I propose is akin to concolic testing, in that I am augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
+What I propose is similar to concolic testing, in that I am augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
 However, the lack of a heavyweight constraint solver and the ability to work on binaries without instrumenting or using source code in any way have, to the best of my knowledge, not yet been proposed.
@@
 
-Professional fuzzing products, like Peach Fuzzer
+%Professional fuzzing products, like Peach Fuzzer
 
@@
 
-Testing can begin on dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
+I am currently instrumenting dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
 If results appear promising I can try to make the fuzzer as complete as possible and begin running it on real-world applications.
@@
 
-\subsection{Evaluation}
+As of this writing I am moving towards fuzzing Linux utilities.
+Results for toy binaries are promising, with "crackme" type programs which ask for a secret being solved in approximately 2*n runs, where n is the length of the secret.
+There is, however, still some overtainting which must be accounted for.
+%\section{Evaluation}
+
+\subsection{Parallelization}
+
+I have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
+Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel.
+For this project I have tested my program on a personally created binary, simpleCrackme.
+This binary takes a file containing a password in argv1.
+If the password matches its secret, then it prints "You win", otherwise, it prints "You lose".
+
+After running my program, one can grep for the win string in the output/ directory.
+This is similar to concept to running a fuzzer, and grepping around the output recorded for more interesting conditions, like segfaults.
+Results show a noticeable speedup.
+
+Sequential:
+After several runs, I've seen performance ranging from ~33 seconds to 19 seconds.
+26.12user 7.15system 0:33.42elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+0inputs+1496outputs (0major+1168365minor)pagefaults 0swaps
+
+14.66user 4.67system 0:19.44elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+0inputs+1496outputs (0major+1168305minor)pagefaults 0swaps
+
+Parallel:
+The parallel implementation seems to decrease time by somewhere around half, which makes sense considering the problem is not embarassingly parellel, and Intel Pin may try and use multiple cores during startup.
+30.64user 9.71system 0:10.83elapsed 372\%CPU (0avgtext+0avgdata 12952maxresident)k
+0inputs+816outputs (0major+1368622minor)pagefaults 0swaps
+
+However, I have seen runs as high as ~13 seconds elapsed.
+Since my testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
+I also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
 

### 2013-12-13 MyPinToolMultiProcess/DTA.h

@@ -1,309 +1,0 @@
-//
-//  Jonathan Salwan - Copyright (C) 2013-08
-// 
-//  http://shell-storm.org
-//  http://twitter.com/JonathanSalwan
-//
-//  Note: Example 4 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
-//        Detect a use after free vulnerability via a old stack frame
-//
-
-#include "pin.H"
-#include <asm/unistd.h>
-#include <fstream>
-#include <iostream>
-#include <list>
-
-std::ofstream TaintFile;
-std::list<UINT32> addressTainted;
-std::list<REG> regsTainted;
-
-
-bool checkAlreadyRegTainted(REG reg)
-{
-  list<REG>::iterator i;
-
-  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
-    if (*i == reg){
-      return true;
-    }
-  }
-  return false;
-}
-
-VOID removeMemTainted(UINT32 addr)
-{
-  addressTainted.remove(addr);
-  TaintFile << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
-}
-
-VOID addMemTainted(UINT32 addr)
-{
-  addressTainted.push_back(addr);
-  TaintFile << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
-}
-
-bool taintReg(REG reg)
-{
-  if (checkAlreadyRegTainted(reg) == true){
-    TaintFile << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
-    return false;
-  }
-
-  switch(reg){
-
-    case REG_EAX:  regsTainted.push_front(REG_EAX); 
-    case REG_AX:   regsTainted.push_front(REG_AX); 
-    case REG_AH:   regsTainted.push_front(REG_AH); 
-    case REG_AL:   regsTainted.push_front(REG_AL); 
-         break;
-
-    case REG_EBX:  regsTainted.push_front(REG_EBX);
-    case REG_BX:   regsTainted.push_front(REG_BX);
-    case REG_BH:   regsTainted.push_front(REG_BH);
-    case REG_BL:   regsTainted.push_front(REG_BL);
-         break;
-
-    case REG_ECX:  regsTainted.push_front(REG_ECX);
-    case REG_CX:   regsTainted.push_front(REG_CX);
[…]

### 2013-12-13 MyPinToolMultiProcess/FindUseAfterFree.h

@@ -1,378 +1,0 @@
-// Based heavily on Jonathan Salwan's code, all credit to him. Thanks!
-
-//  Jonathan Salwan - Copyright (C) 2013-08
-// 
-//  http://shell-storm.org
-//  http://twitter.com/JonathanSalwan
-//
-//  Note: Example 5 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
-//        Detect the classical use after free vulnerability 
-//
-
-#include <asm/unistd.h>
-#include <fstream>
-#include <iostream>
-#include <list>
-
-#define LOCKED    1
-#define UNLOCKED  !LOCKED
-
-#define ALLOCATE  1
-#define FREE      !ALLOCATE
-
-static size_t         lastSize;
-
-struct mallocArea
-{
-  UINT32  base;
-  UINT32  size;
-  BOOL    status;
-};
-
-UINT32 lockTaint = LOCKED;
-
-std::list<UINT32>               addressTainted;
-std::list<REG>                  regsTainted;
-std::list<struct mallocArea>    mallocAreaList;
-
-BOOL checkAlreadyRegTainted(REG reg)
-{
-  list<REG>::iterator i;
-
-  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
-    if (*i == reg){
-      return true;
-    }
-  }
-  return false;
-}
-
-VOID removeMemTainted(UINT32 addr)
-{
-  addressTainted.remove(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
-}
-
-VOID addMemTainted(UINT32 addr)
-{
-  addressTainted.push_back(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
-}
-
-BOOL taintReg(REG reg)
-{
-  if (checkAlreadyRegTainted(reg) == true){
-    std::cout << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
-    return false;
-  }
-
-  switch(reg){
-
-    case REG_EAX:  regsTainted.push_front(REG_EAX); 
-    case REG_AX:   regsTainted.push_front(REG_AX); 
-    case REG_AH:   regsTainted.push_front(REG_AH); 
-    case REG_AL:   regsTainted.push_front(REG_AL); 
-         break;
-
[…]

### 2013-12-13 MyPinToolMultiProcess/buffer_linux.h

@@ -1,258 +1,0 @@
-/*BEGIN_LEGAL 
-Intel Open Source License 
-
-Copyright (c) 2002-2013 Intel Corporation. All rights reserved.
- 
-Redistribution and use in source and binary forms, with or without
-modification, are permitted provided that the following conditions are
-met:
-
-Redistributions of source code must retain the above copyright notice,
-this list of conditions and the following disclaimer.  Redistributions
-in binary form must reproduce the above copyright notice, this list of
-conditions and the following disclaimer in the documentation and/or
-other materials provided with the distribution.  Neither the name of
-the Intel Corporation nor the names of its contributors may be used to
-endorse or promote products derived from this software without
-specific prior written permission.
- 
-THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
-``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
-LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
-A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE INTEL OR
-ITS CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
-SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
-LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
-DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
-THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
-(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
-OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
-END_LEGAL */
-/*
- * Sample buffering tool
- * 
- * This tool collects an address trace of instructions that access memory
- * by filling a buffer.  When the buffer overflows,the callback writes all
- * of the collected records to a file.
- *
- */
-
-#include <iostream>
-#include <fstream>
-#include <stdlib.h>
[…]

### 2013-12-13 MyPinToolMultiProcess/examples/countJumps.cpp

@@ -1,116 +1,0 @@
-/*BEGIN_LEGAL 
-Intel Open Source License 
-
-Copyright (c) 2002-2013 Intel Corporation. All rights reserved.
- 
-Redistribution and use in source and binary forms, with or without
-modification, are permitted provided that the following conditions are
-met:
-
-Redistributions of source code must retain the above copyright notice,
-this list of conditions and the following disclaimer.  Redistributions
-in binary form must reproduce the above copyright notice, this list of
-conditions and the following disclaimer in the documentation and/or
-other materials provided with the distribution.  Neither the name of
-the Intel Corporation nor the names of its contributors may be used to
-endorse or promote products derived from this software without
-specific prior written permission.
- 
-THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
-``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
-LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
-A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE INTEL OR
-ITS CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
-SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
-LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
-DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
-THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
-(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
-OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
-END_LEGAL */
-#include <iostream>
-#include <fstream>
-#include "pin.H"
-
-ofstream OutFile;
-
-// Used to print every instruction in main 
-    
-VOID FindBranchOrJump(INS ins, VOID *v)
-{
-    // Categories are higher-level semantic descriptions than opcodes.
-    // The constant matches all conditional branches
[…]

### 2013-12-13 MyPinToolMultiProcess/examples/dta.cpp

@@ -1,310 +1,0 @@
-//
-//  Jonathan Salwan - Copyright (C) 2013-08
-// 
-//  http://shell-storm.org
-//  http://twitter.com/JonathanSalwan
-//
-//  Note: Example 3 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
-//        Spread the taint in memory/registers and follow your data.
-//
-
-#include "pin.H"
-#include <asm/unistd.h>
-#include <fstream>
-#include <iostream>
-#include <list>
-
-std::list<UINT64> addressTainted;
-std::list<REG> regsTainted;
-
-INT32 Usage()
-{
-    cerr << "Ex 3" << endl;
-    return -1;
-}
-
-bool checkAlreadyRegTainted(REG reg)
-{
-  list<REG>::iterator i;
-
-  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
-    if (*i == reg){
-      return true;
-    }
-  }
-  return false;
-}
-
-VOID removeMemTainted(UINT64 addr)
-{
-  addressTainted.remove(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
-}
-
-VOID addMemTainted(UINT64 addr)
-{
-  addressTainted.push_back(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
-}
-
-bool taintReg(REG reg)
-{
-  if (checkAlreadyRegTainted(reg) == true){
-    std::cout << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
-    return false;
-  }
-
-  switch(reg){
-
-    case REG_RAX:  regsTainted.push_front(REG_RAX);
-    case REG_EAX:  regsTainted.push_front(REG_EAX); 
-    case REG_AX:   regsTainted.push_front(REG_AX); 
-    case REG_AH:   regsTainted.push_front(REG_AH); 
-    case REG_AL:   regsTainted.push_front(REG_AL); 
-         break;
-
-    case REG_RBX:  regsTainted.push_front(REG_RBX);
-    case REG_EBX:  regsTainted.push_front(REG_EBX);
-    case REG_BX:   regsTainted.push_front(REG_BX);
-    case REG_BH:   regsTainted.push_front(REG_BH);
-    case REG_BL:   regsTainted.push_front(REG_BL);
[…]

### 2013-12-13 MyPinToolMultiProcess/examples/salwanUseAfterFree.cpp

@@ -1,389 +1,0 @@
-//
-//  Jonathan Salwan - Copyright (C) 2013-08
-// 
-//  http://shell-storm.org
-//  http://twitter.com/JonathanSalwan
-//
-//  Note: Example 5 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
-//        Detect the classical use after free vulnerability 
-//
-
-#include "pin.H"
-#include <asm/unistd.h>
-#include <fstream>
-#include <iostream>
-#include <list>
-
-#define LOCKED    1
-#define UNLOCKED  !LOCKED
-
-#define ALLOCATE  1
-#define FREE      !ALLOCATE
-
-static size_t         lastSize;
-
-struct mallocArea
-{
-  UINT32  base;
-  UINT32  size;
-  BOOL    status;
-};
-
-UINT32 lockTaint = LOCKED;
-
-std::list<UINT32>               addressTainted;
-std::list<REG>                  regsTainted;
-std::list<struct mallocArea>    mallocAreaList;
-
-INT32 Usage()
-{
-    std::cerr << "Ex 5" << std::endl;
-    return -1;
-}
-
-BOOL checkAlreadyRegTainted(REG reg)
-{
-  list<REG>::iterator i;
-
-  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
-    if (*i == reg){
-      return true;
-    }
-  }
-  return false;
-}
-
-VOID removeMemTainted(UINT32 addr)
-{
-  addressTainted.remove(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
-}
-
-VOID addMemTainted(UINT32 addr)
-{
-  addressTainted.push_back(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
-}
-
-BOOL taintReg(REG reg)
-{
-  if (checkAlreadyRegTainted(reg) == true){
-    std::cout << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
-    return false;
-  }
-
-  switch(reg){
-
-    case REG_EAX:  regsTainted.push_front(REG_EAX); 
-    case REG_AX:   regsTainted.push_front(REG_AX); 
-    case REG_AH:   regsTainted.push_front(REG_AH); 
-    case REG_AL:   regsTainted.push_front(REG_AL); 
[…]

### 2013-12-13 MyPinToolMultiProcess/examples/use_after_free.cpp

@@ -1,405 +1,0 @@
-//
-//  Jonathan Salwan - Copyright (C) 2013-08
-// 
-//  http://shell-storm.org
-//  http://twitter.com/JonathanSalwan
-//
-//  Note: Example 5 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
-//        Detect the classical use after free vulnerability 
-//
-
-#include "pin.H"
-#include <asm/unistd.h>
-#include <fstream>
-#include <iostream>
-#include <list>
-
-#define LOCKED    1
-#define UNLOCKED  !LOCKED
-
-#define ALLOCATE  1
-#define FREE      !ALLOCATE
-
-static size_t         lastSize;
-
-struct mallocArea
-{
-  UINT64  base;
-  UINT64  size;
-  BOOL    status;
-};
-
-UINT32 lockTaint = LOCKED;
-
-std::list<UINT64>               addressTainted;
-std::list<REG>                  regsTainted;
-std::list<struct mallocArea>    mallocAreaList;
-
-INT32 Usage()
-{
-    std::cerr << "Ex 5" << std::endl;
-    return -1;
-}
-
-BOOL checkAlreadyRegTainted(REG reg)
-{
-  list<REG>::iterator i;
-
-  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
-    if (*i == reg){
-      return true;
-    }
-  }
-  return false;
-}
-
-VOID removeMemTainted(UINT64 addr)
-{
-  addressTainted.remove(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
-}
-
-VOID addMemTainted(UINT64 addr)
-{
-  addressTainted.push_back(addr);
-  std::cout << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
-}
-
-BOOL taintReg(REG reg)
-{
-  if (checkAlreadyRegTainted(reg) == true){
-    std::cout << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
-    return false;
-  }
-
-  switch(reg){
-
-    case REG_RAX:  regsTainted.push_front(REG_RAX);
-    case REG_EAX:  regsTainted.push_front(REG_EAX); 
-    case REG_AX:   regsTainted.push_front(REG_AX); 
[…]

### 2013-12-13 MyPinToolMultiProcess/simpleCrackme.c

@@ -1,0 +1,31 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'X') {
+        win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-15 docs/paper/fsuthesis/thesis-template/paper.tex
added SAGE deets to paper

@@
 
-\title{Rough Draft: A Backsolving Technique Using Dynamic Taint Analysis}
+\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
 \author{Clark Wood}
@@
 
-%\committeeperson{Faux Causson Yorverk}{Professor Directing Thesis}
+\committeeperson{Zhi Wang}{Professor Directing Thesis}
 %\committeeperson{Verda Boizaar}{University Representative}
@@
 Applications tested for vulnerabilities are often black boxes because source code is unavailable.
-This piles difficulties onto an already complex problem, of which much of current research attempts to solve or reduce.
-Among these issues are i) efficient and thorough dynamic taint analysis, ii) the path explosion problem [U], and iii) the code coverage problem.
+This piles difficulties onto an already complex problem, which current research attempts to solve or reduce.
+Among these issues are:
+	\begin{itemize}
+		\item efficient and thorough dynamic taint analysis
+		\item the path explosion problem [U], and
+		\item the code coverage problem. 
+	\end{itemize}
+
  Dynamic taint analysis is also difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
@@
 \\
-\\
-\\
 
@@
 cmp eax, 42
-jnz 0x8BADMEAT
+jnz 0x8BADC0DE
 \end{verbatim}
 
-If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADMEAT.
+If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADC0DE.
 With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted).
@@
 
+\chapter{Preliminaries}
+
+\section{TODO White vs. Gray vs. Black box}
+
+Explain white vs. black box. How gray could bleed into black because of DBI. Talk about SAGE.
+
+SAGE - architecture, then underlying ideas
+
+Microsoft's Scalable Automatic Guided Execution, or SAGE, is an example of a white box fuzzer.
+Researchers at Microsoft developed SAGE to deal with large, complex programs which needed to be automatically tested for deep bugs.
+Microsoft considers SAGE, and whitebox fuzzing in general, so important that it requires the practice in its Security Development Lifecycle.
+The basic SAGE execution begins when a program to be fuzzed is first run concretely with known good input.
+During this run, the program is instrumented with Microsoft's AppVerifier to watch for bugs.
+Afterwards, SAGE receives a copy of the x86 instructions executed during this run, and symbolically executes the instructions, gathering constraints to be solved later by an SMT such as Z3.
+Once it has a set of these constraints, SAGE will negate each constraint in the set one by one and feed this new set to Z3.
+Sets that pass are ranked in descending order by the number of new instructions they reveal, and return into the start of the loop, to be executed concretely again [Q].
+
+Because SAGE is propietary, the lack of detail about certain procedures raises questions.
+For instance, how does SAGE know when an instruction is new?
+There are a limited number of x86 instructions, which can be combined in an unlimited number of ways, which means it can be difficult to tell when a truly new instruction is executed, unless one keeps a directed cyclical graph of all explored instructions, and follows a run's progress down this graph during execution.
+In addition, problems integral to this work, such as code coverage and path explosion, must be addressed [Q].
+
+SAGE uses symbolic execution, and prunes paths taken with a propietary "generational search" algorithm.
+This algorithm prioritizes generating new test cases (TODO does it draw on the test case reduction and expansion algorithms discussed in that one paper???).
+It takes a set of all constraints and tries negating each constraint independently to generate a new test case.
+SAGE then symbolically re-executes the constraint set using TruScan [TODO CITE] [Q].
+Similarly, s2e uses QEMU for instruction set emulation, and then appears to be a strong trend in white-box fuzzing.
+TODO ADV/DIS?
+
+In practice, because program termination is indeterminable, white box fuzzing could run forever.
+And since programs at Microsoft can easily exceed one million lines of code, with complex control flow structures, pointer manipulation, and other difficult to account for code constructs, SAGE employes several performance enhancing techniques to keep fuzzing practical and economical.
+Symbolically executed instructions and local constraints are cached, and unrelated constraint elimination rids the execution of contraints not related to the constraint under test.
+How this is determined is anyone's guess, since it is impossible to know which constraints are independent until one has explored all the code in a program.
+SAGE also employs a flip count limit, allowing only so many negations of a particular constraint [Q].
+
+This is helpful for dealing with loops, which might evaluate or modify the same constraint many times.
+This technique is an example of a typical tradeoff for fuzzers.
+A lot of program execution time is spent in loops, but deep bugs can lurk in rarely exercised parts of a loop, so fuzzers must pick some heuristic for terminating the exploration of a loop, trading code coverage for running time.
+
+\section{TODO Mutation vs. Generation?}
+
+\section{TODO Local vs. Network}
+
+Do you have access to the program you are fuzzing?
+
+\section{TODO Difficulties}
+
+Path explosion. Code coverage. Complex file formats which mean you create shallow errors over and over again.
+
 \chapter{Related Work}
+
+\section{Taint-based Fuzzing}
 
@@
 The technique discussed in this paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
+
+\section{TODO Mayhem}
+
+Talk about CMU Mayhem.
+
+\section{TODO Argos: 0-Day Emulator}
+
+http://www.few.vu.nl/argos/?page=3
 

### 2014-02-16 docs/paper/fsuthesis/thesis-template/paper.tex
Small edits to paper
added Mayhem deets to paper

@@
 \degreeyear{2014}
-\defensedate{Spring 2014}
+\defensedate{XXXXXXX}
 
@@
 \committeeperson{Zhi Wang}{Professor Directing Thesis}
-%\committeeperson{Verda Boizaar}{University Representative}
 %\committeeperson{Beauxeau D'Claune}{Committee Member}
@@
 \chapter{Introduction}
+
+TODO focus on fact that this stands separate from and complementary to symb. exec? Perhaps performance analysis vs. s2e on binaries to show the potential?
 
@@
 
-SAGE - architecture, then underlying ideas
+\subsection{Microsoft SAGE}
 
@@
 
+Peach Fuzzer
+
 \section{TODO Local vs. Network}
@@
 
-\section{TODO Mayhem}
+\section{TODO Mayhem, AEG, Exploitable Bugs}
 
-Talk about CMU Mayhem.
+Talk about CMU Mayhem. [H]
+AEG [I]
+
+While finding bugs of any sort enhances software by providing developers the opportunity to fix problems with their programs, finding bugs that lead to exploitable conditions are of special interest.
+A bug is exploitable if it allows adveraries to undermine confidentiality, integrity, or availability [CITE] via avenues such as information disclosure, denial of service, or remote execution of code.
+Because these bugs stand alone as a separate, particularly worrying class, efforts have been made to automate the process of proving whether an identified bug is also a vulnerability which can be exploited.
+
+Mayhem, an exploitable bug-finding system, is an attempt to address this issue by exploring state space as efficiently as possible.
+The authors designed Mayhem to handle path explosion by monitoring system resources and balancing the need for concurrent exploration with the resources consumed by forking and running many processes.
+Mayhem accomplishes through hybrid symbolic execution, a technique which heuristically combines offline and online symbolic execution.
+Offline symbolic execution first runs a program concretely, instrumenting the process to gather information which will then be used by a separate symbolic execution engine.
+Online symbolic execution, instead, tries to explore the entire program symbolically by forking new processes at branches.
+[H]
+
+Mayhem improves fuzzing time performance by weaving between these two modes.
+It is implemented as a client-server architecture, with the client running code concretely and passing specific blocks to the server for symbolic execution.
+Only the server outputs results or further test cases to explore concretely.
+The client uses block-level dynamic taint analysis, passing control to the symbolic execution server when tainted branches or jumps are discovered.
+Mayhem modifies its behavior based on system memory constraints, beginning in online mode and switching to offline mode when a threshhold for memory resources is reached.
+Upon switching, Mayhem also saves checkpoints to save its work in an attempt to reduce exploring the same code twice.
+[H]
+
+TODO Mayhem techniques
+
+AEG required source code, where Mayhem needs access only a binary to execute.
+Mayhem is, however, limited to a subset of all system calls for the operating system it executes on.
+This is deliberate on the part of the authors, who reason that OS-wide symbolic execution introduces too much overhead.
+Of significance as an area of future research, Mayhem, and most other fuzzing technology explored, cannot reason about taint propagated through threading mechanisms [H].
+
+TODO similar to Automatic
+patch-based exploit generation is possible: Techniques and
+implications, but mine doesn't require a patch?
 
@@
 
+\section{results}
+
+TODO
+
 % Was setbacks, modify and remove heavily

### 2014-02-18 docs/paper/fsuthesis/thesis-template/paper.tex
some of TaintScope to paper

@@
 
-Peach Fuzzer
+TODO Peach Fuzzer
 
@@
 
-\section{TODO Difficulties}
+\section{TODO Difficulties and Limitations}
 
-Path explosion. Code coverage. Complex file formats which mean you create shallow errors over and over again.
+TODO Path explosion. Code coverage. Complex file formats which mean you create shallow errors over and over again.
+
+TODO Limitations - one-way functions like bitwise shifts and checksums, cryptographic hashes. encryption.
 
@@
 http://www.few.vu.nl/argos/?page=3
+
+\section{Checksum-Aware Fuzzing}
+
+Much of smart fuzzing involves reasoning about constraints gathered during the execution of instrumented code.
+TaintScope [AB] was developed as the result of the following observation: generation-based fuzzing improves as the quality (and consequently effort) of the model to fuzz improves.
+This means better fuzzing is accomplished by devoting more programmer time and effort, instead of allocating more computational resources.
+Since a programmer's time and mental resources are valuable, so fuzzers should do for them by yielding fewer test cases that result in more interesting crashes [T].
+
+TaintScope focuses on checksums, one where area where traditional symbolic execution-based fuzzers tend to perform poorly.
+Other areas, which could be interesting areas of further study, are essentially any other functions that are, in one set of assumptions or another, considered one-way.
+For instance, bitwise shifts, being lossy, are hard to execute symbolically, as are encryption and decryption or hashing without a precomputed table.
+The impetus for TaintScope's design was the desire to find deeper bugs in work like network protocols, which very early on compute checksums for integrity.
+Before TaintScope, fuzzing said protocols often lead to lots of worthless test cases, because they all lead to similar, shallow crashes involving failing the checksum test.
+Since there are far more ways to fail a checksum than to pass it, fuzzers that couldn't reason about the checksum or threw random bytes in the checksum field wasted a lot of work.
+Instead, TaintScope identifies likely checksum integrity checks and instruments programs to let them keep going to try and find deeper, more meaningful bugs [T].
+
+The general method is to:
+
+\begin{enumerate}
+	\item Perform dynamic taint analysis during concrete execution
+	\item Identify what could be checksum validations
+	\item Run the instrumented program again, modifying ZF in EFLAGS to always "pass" the  checksum
+	\item If a crash results, execute again with the checksum bytes marked symbolic
+\end{enumerate}
+
+In order to identify possible checksum validations, TaintScope assumes certain x86 branches exist to validate the results of computing checksums.
+With correct input, the checks leading up to these branches are always either true or false, and with incorrect input they are always the opposite.
+During execution TaintScope watches for these conditions, and once these conditions, and the bytes involved in them, are identified, it treats the bytes and symbolic, collecting constraints during execution.
+After this, TaintScope can alter the previous test case to pass the checksum.
+However to save work, it only spends time solving these bytes when the normal test case results in a crash.
+To get past shallow crashes where checksums fail it will merely hot-patch the ZF before identified "checksum-based jumps".
+Note this approach won't work with hashes, since one-way functions can't be easily solved with constraint solvers [T].
+
+TODO [T] TaintScope [AB]
 
@@
 	\item [AA] Zhang, Xiangyu, Rajiv Gupta, and Youtao Zhang. "Precise dynamic slicing algorithms." Software Engineering, 2003. Proceedings. 25th International Conference on. IEEE, 2003.
+	\item [AB] Wang, Tielei, et al. "TaintScope: A checksum-aware directed fuzzing tool for automatic software vulnerability detection." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
 

### 2014-02-18 docs/paper/fsuthesis/thesis-template/paper.tex
finished TaintScope paper

@@
 
-TODO [T] TaintScope [AB]
+This general scheme is accomplished with fine-grained dynamic taint analysis, that is, taint analysis at the byte level, as opposed to a more general boolean level of taint, where perhaps user input is tainted and all non-user input is untainted.
+As fuzzers evolve they appear to favor more and more finely-grained taint analysis.
+
+TaintScope implements DTA using PIN to instrument syscalls in binaries.
+PIN\_AddSyscallEntryFunction and PIN\_AddSyscallExitFunction are used to monitor syscalls which are known to introduce taint to a system, such as open, which might open a user-specified file, or read, which might read user-defined bytes into memory.
+Taint is followed as it propogates throughout data via move instructions and arithmetic instructions.
+TaintScope's tainting policy however, transfers taint by unioning taint values whenver they both appear in an instruction.
+Thus, if the policy is enforced strictly, and eax and ebx were both tainted, mov eax, ebx would regard eax as now tainted with both eax and ebx, when in reality the value of ebx has been moved into eax, removing the original taint from eax.
+This is one example of overtainting, which should be taken into account to achieve acceptable performance.
+Note also that, as of the paper, TaintScope does not take into account control-flow dependencies when tracking taint [T].
+
+DTA is used to identify the so-called "hot bytes", which are then used as symbolic values later on, should test cases warrant further attention because of a crash or other interesting behavior.
+This strategy has netted TaintScope 27 new vulnerabilities across several different pieces of software, most of which operate on complicated file format specifications like PNG or PCAP files [T].
 

### 2014-02-18 docs/paper/fsuthesis/thesis-template/paper.tex
small changes/additions to paper

@@
 
+\subsection{Grey-box Evolutionary Fuzzing}
+
 \section{TODO Mutation vs. Generation?}
 
-TODO Peach Fuzzer
+TODO Peach Fuzzer does both, overview with pictures?
 
@@
 
+Koushik Sen defines concolic testing as combining "random tesing and symbolic execution to partly remove the limitations of random testing and symbolic execution based testing" [AB].
+This differs from hybrid symbolic execution engines like Mayhem [H], which switch between different types of symbolic execution.
+Hybrid symbolic execution does not itself supplement fuzzing by adding concrete random values.
+Both imply a tradeoff between two types of analysis, however, and thus both, when implemented by different people, will differ in where they assign the tradeoff.
+Some concolic testing, for instance, will start with concrete values which are random, or NULLs for pointer values.
+After an execution, one of the symbolic constraints will be negated, to allow a new path to be explored, and the program will be run again with new random input [AB].
+Various research aims to either use symbolic execution less [Q, R, X], pick better than random values [A], or pick better input bytes to give random values [A, E, T, AB].
+
 \chapter{Implementation}
@@
 	\item [A] Bekrar, Sofia, et al. "A taint based approach for smart fuzzing." Software Testing, Verification and Validation (ICST), 2012 IEEE Fifth International Conference on. IEEE, 2012.
-	\item [B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with
-Evolutionary Fuzzing", BlackHat and Defcon 2007.
+	\item [B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with Evolutionary Fuzzing", BlackHat and Defcon 2007.
 	\item [C] Schwartz, E.J., Avgerinos, T., Brumley, D.
@@
 	\item [D] Clause, J. Li, W., Orso, A. "Dytan: a generic dynamic taint analysis framework". 2007 Int'l symposium on Software testing and analysis. ACM, 2007.
-	\item [E] ... "Beyond Instruction Level Taint Propagation".
+	\item [E] Ajit, Beng Heng Ng Earlence Fernandes, Aluri Atul Prakash, and David Rodriguez Velazquez Zijiang Yang. "Beyond Instruction Level Taint Propagation." (2013).
 	\item [F] Yamaguchi, Fabian, Felix Lindner, and Konrad Rieck.
@@
 	\item [AB] Wang, Tielei, et al. "TaintScope: A checksum-aware directed fuzzing tool for automatic software vulnerability detection." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
+	\item [AC] Sen, Koushik. "Concolic testing." Proceedings of the twenty-second IEEE/ACM international conference on Automated software engineering. ACM, 2007.
 

### 2014-02-21 docs/paper/fsuthesis/thesis-template/paper.tex
added some of javascript fuzzer paper

@@
 % Additional packages may be loaded here.
+\usepackage{graphicx}
+\usepackage{listings}
+\usepackage{color}
+\usepackage{hyperref}
+
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstset{frame=tb,
+  language=C,
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true
+  tabsize=3
+}
+
+% Taken from Lena Herrmann at 
+% http://lenaherrmann.net/2010/05/20/javascript-syntax-highlighting-in-the-latex-listings-package
+
+\definecolor{lightgray}{rgb}{.9,.9,.9}
+\definecolor{darkgray}{rgb}{.4,.4,.4}
+\definecolor{purple}{rgb}{0.65, 0.12, 0.82}
+
+\lstdefinelanguage{JavaScript}{
+  keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
+  keywordstyle=\color{blue}\bfseries,
+  ndkeywords={class, export, boolean, throw, implements, import, this},
+  ndkeywordstyle=\color{darkgray}\bfseries,
+  identifierstyle=\color{black},
+  sensitive=false,
+  comment=[l]{//},
+  morecomment=[s]{/*}{*/},
+  commentstyle=\color{purple}\ttfamily,
+  stringstyle=\color{red}\ttfamily,
+  morestring=[b]',
+  morestring=[b]"
+}
+
+\lstset{
+   language=JavaScript,
+   backgroundcolor=\color{lightgray},
+   extendedchars=true,
+   basicstyle=\footnotesize\ttfamily,
+   showstringspaces=false,
+   showspaces=false,
+   numbers=left,
+   numberstyle=\footnotesize,
+   numbersep=9pt,
+   tabsize=2,
+   breaklines=true,
+   showtabs=false,
+   captionpos=b
+}
 
@@
 \chapter{Introduction}
+
+\section{Motivation}
+TODO US gov't interest via money
+
+%\begin{lstlisting}
+%// Hello.c
+%#include<stdio.h>
+%int main() {
+%	int x = 3;
+%	printf("%d\n", x);
+%}
+%\end{lstlisting}
+
+%\begin{figure}[htb]
+%  	\center{\includegraphics[width=\textwidth]
+%   	{figures/archer.png}}
+%	\caption{\label{fig:my-label} My figure.  An example of a cool figure}
+%\end{figure}
+
+\section{Theoretical Difficulties}
+TODO programming language theory, i.e. what makes fuzzing hard
 
@@
 \subsection{Grey-box Evolutionary Fuzzing}
+
+\section{TODO Fuzzing Web Applications}
+
+Fuzzing is a reliable and inexpensive way to find vulnerabilities not only in compiled C/C++ programs, but also in higher level scripting languages.
+JavaScript, as an example, is a higher-level scripting language becoming more and more prevalent as we continue to connect ever more devices to the internet and grow individual people's connectedness.
+Web browsers, as a portal through which to interact with millions of users, are a common target for malware and other exploitation, and JavaScript, as the de facto client-side scripting language, offers many targets.
+
+Web exploits such as cross site scripting (XSS) are possible because of language functionality like the eval method, which takes an arbitrary string as an input parameter and evaluates that string as if it were JavaScript source code [AE].
+The authors of "A Symbolic Execution Framework for JavaScript" wrote Kudzu because of a perceived lack of sophisticated tools for fuzzing client-side Javascript.
+In particular, constraint solvers at the time seemed unable to reason about JavaScript string objects, which are used in various parts of the web to represent myriad types of data, and are then parsed by custom, open-source, and propietary libraries in order to cast from a string to another data type.
+As an example, consider the following snippet involving eval:
+
+\begin{lstlisting}[caption=Figure BLAH]
+// Let userInput = "2 + 2"
+var str = eval(userInput);
+
+if (str === 4) {
+	everythingDies();
+	throw new Error;
+}
+\end{lstlisting}
+
+In this contrived example, catastrophe occurs when user input, when executed as JavaScript, returns the value 4.
+Without even considering the strange casting and equality rules which JavaScript operates under, there are multiple ways for user input to throw an error, making constraint solving particularly difficult.
+The case where userInput = "4" is straightforward, but other cases which do not look like the String "4" or the Number 4, but evaluate to it, can also trigger the error.
+According to the authors, before Kudzu, string solvers were unable to reason about regular expressions, string equality, or multiple variables [AD].
+
+While JavaScript strings, and their ubiquitous usage in client-side web programming, presented one obstacle, the sheer complexity of modern web browsers presented another.
+Typical browsers can open and display PDFs, play media files, and execute multiple markup and programming languages like HTML, CSS, and JavaScript to present a web page to a user.
+Because of this complexity, the authors decided to divide possible user interaction into two, disparate spaces: an event space and a value space.
+The event space contains HTML elements and their state as defined by user behavior.
+This would include HTML elements like radio buttons or text boxes, along with their current state, such as which radio button is currently selected, along with the state transitions for the current page, such as a user clicking one radio button, then deselecting to check boxes in order.
+As a rule of thumb, GUI elements which users can interact with reside in the event space.
+The notable exception to this is any GUI element a user types into, such as a text box.
+Value space contains the values for these GUI elements, along with any other text which is used as input which users or other web pages have control over [AD].
+
+Kudzu aims to discover vulnerabilities, particularly client-side code injections, by using dynamic symbolic execution to identify constraints placed upon particular input and then solve them to generate new test cases.
+Dynamic symbolic execution, which mixes concrete values with choice symbolic values to optimize for speed and code coverage, is basically concolic execution.
+Kudzu was developed for the WebKit browser and consists of two major parts:
+\begin{enumerate}
+	\item GUI explorer
+	\item Dynamic symbolic execution engine, which includes:
+	\begin{enumerate}
+		\item a constraint extractor
+		\item a constraint solver
+	\end{enumerate}
+\end{enumerate}
+
+The GUI explorer handles the event space by exploring all possible sequences of user-defined events at random.
+In order to discover event handlers, the GUI explorer relies on information from Kudzu, which instruments WebKit functions.
+When an HTML element which can generate an event is found, or when one of these elements in removed, Kudzu's hooks notice this and inform the GUI explorer accordingly.
+
+[AD]
+new things contributed
+challenges - js strings, GUI elements
+arch. use WebKit browser, 
+js example of challenge
+shortcomings - don't support all string ops, nor all JavaScript regex functionality, tradeoff
+results - lots of found vulns involve strings,
 
@@
 	\item [Y] Sen, Koushik, Darko Marinov, and Gul Agha. CUTE: a concolic unit testing engine for C. Vol. 30. No. 5. ACM, 2005.
-	\item [Z] Peach Fuzzer. url{http://peachfuzzer.com/}
+	\item [Z] Peach Fuzzer. \url{<http://peachfuzzer.com/>}
 	\item [AA] Zhang, Xiangyu, Rajiv Gupta, and Youtao Zhang. "Precise dynamic slicing algorithms." Software Engineering, 2003. Proceedings. 25th International Conference on. IEEE, 2003.
@@
 	\item [AC] Sen, Koushik. "Concolic testing." Proceedings of the twenty-second IEEE/ACM international conference on Automated software engineering. ACM, 2007.
+	\item [AD] Saxena, Prateek, et al. "A symbolic execution framework for javascript." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
+	\item [AE] Mozilla Developer Network. \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global\_Objects/eval}
+	\item [AF] The WebKit Open Source Project. \url{http://www.webkit.org/}
 

### 2014-02-21 docs/paper/fsuthesis/thesis-template/paper.tex
finished javascript fuzzer paper

@@
 When an HTML element which can generate an event is found, or when one of these elements in removed, Kudzu's hooks notice this and inform the GUI explorer accordingly.
+Symbolic execution is broken down into a custom constraint extractor, which acts upon an execution trace from a concrete execution of the program, looking for control-flow statements and whether they were taken given the appropriate values compared, and a custom constraint solver, purposefully designed to handle JavaScript objects, which receives symbolic constraints from the extractor.
+After the solver has reasoned about the constraints on some piece of input, a new input test case is generated and fed back into the system.
+Since symbolic execution is costly, Kudzu identifies when user input appears to flow to one of finitely many vulnerability sinks, such as eval or document.write.
+Only this user input is considered symbolically.
+As Kudzu runs, it takes new test cases and executes the program with a mix of symbolic and concrete variables, and checks to see whether input that flows to vulnerable sinks can result in an exploit, for instance by inserting JavaScript alerts and checking to see whether they execute [AD].
 
-[AD]
-new things contributed
-challenges - js strings, GUI elements
-arch. use WebKit browser, 
-js example of challenge
-shortcomings - don't support all string ops, nor all JavaScript regex functionality, tradeoff
-results - lots of found vulns involve strings,
+Like TODO Owen's thing, Kudzu tries to circumvent the issue of solving complicated constraints by first converting JavaScript into an intermediate language called JASIL.
+Strings, in particular, are parsed and partitioned into several sub types which are more uniform.
+For instance, one type handles strings which are semantically regular expressions, another handles strings which are the concatenation of two other strings.
+Although not as featureful as JavaScript strings, this IL captures a large enough number of String features to allow Kudzu to find previous unknown exploits in programs.
+Shortcomings include an incomplete support of String operations and JavaScript regular expressions, notably backreferences, which match a previously matched string in the regex.
+Although representation of strings is incomplete, Kudzu reasons well enough to find two new vulnerabilities, as well as 9 previous vulnerabilities [AD].
 
@@
 
+TODO talk about how this is called many different things, and is a rather amorphous term.
+
 Current research focuses on carefully deciding when and how to use symbolic execution [J, T, W].
@@
 Various research aims to either use symbolic execution less [Q, R, X], pick better than random values [A], or pick better input bytes to give random values [A, E, T, AB].
+
+\section{TODO Conversion to an Intermediate Representation}
+
+Used in javascript fuzzer [AD]
+Used in Owen's slides.
 

### 2014-02-23 docs/paper/fsuthesis/thesis-template/paper.tex
starting to add brumley dta and symbexec paper

@@
 Several valuable techniques to improve fuzzers' code coverage have evolved over the years.
-Two, in particular, inspire this work directly: Dynamic Taint Analysis and Concolic Execution.
+Two, in particular, inspire this work directly: Dynamic Taint Analysis and Symbolic Execution.
 Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing.
-Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims to ameliorate the path explosion problem while maintaining good code coverage.
+Symbolic execution improves code coverage by first running a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of SMT solver [CITE] to solve for what value the element should have under certain conditions.
+Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims for reasonable runtimes while maintaining good code coverage.
 These each come with their own drawbacks, a primary one of which is the lack of automated instrumentation.
-Historically, symbolic execution required a programmer to directly instrument source code, but much research is now focused on automating as much as possible.
+Historically, any amount of symbolic execution required a programmer to directly instrument source code, leading much current research to focus on automating as much as possible.
 
 \section{Dynamic Taint Analysis}
+
+DTA is a form of dynamic analysis, meaning analysis occurs during execution of a program.
+This can be contrasted with static analysis, where a program's source code is analyzed without executing the code.
+The IDA Pro Disassemble [AH], which takes a compiled C binary as input and statically disassembles it to produce some flavor of assembly code, is an example of a static program analysis tool, whereas a debugger, which instruments and executes a program, allowing users to manipulate and watch the process at runtime, is an example of a dynamic analysis tool.
+
+Developers often have an incentive to obfuscate payloads or manipulate code to make static analysis more costly, such as malware and exploit writers who don't want their products detected and reverse engineered.
+This merely raises the bar for attackers, since software cannot be altered to the point where it doesn't perform its original function merely to escape detection and analysis.
+As an example, a program that begins life encrypted must at some point use or download a secret key to decrypt itself and run.
+This might be incredibly difficult to find using only static analysis, but by running the program and letting it decrypt itself, then snapshotting the program's state, we can circumvent the protection entirely.
+Thus, program obfuscation, reverse engineering and anti-RE are cat-and-mouse games.
+This is why dynamic analysis is so important, and it is an open and actively researched question whether there even exists a way to provably make a program strongly obscure [AI].
+
+TODO BRUMLEY
 
@@
 \section{Symbolic Execution}
+
+TODO Add "All you ever wanted to know..." Stuff
 
@@
 	\item [AF] The WebKit Open Source Project. \url{http://www.webkit.org/}
+	\item [AG] Portokalidis, Georgios, Asia Slowinska, and Herbert Bos.
+"Argos: an emulator for fingerprinting zero-day attacks for advertised honeypots with automatic signature generation." ACM SIGOPS Operating Systems Review.
+Vol.
+40.
+No.
+4.
+ACM, 2006.
+	\item [AH] Rescue, Data. "IDA Pro Disassembler." 2006-10-20). http://www. datarescue. com/idabase.
+	\item [AI] Garg, Sanjam, et al.
+"Candidate indistinguishability obfuscation and functional encryption for all circuits." Foundations of Computer Science (FOCS), 2013 IEEE 54th Annual Symposium on.
+IEEE, 2013.
 

### 2014-02-23 docs/paper/fsuthesis/thesis-template/paper.tex
about 2/3 through with brumleys paper

@@
 
-Like TODO Owen's thing, Kudzu tries to circumvent the issue of solving complicated constraints by first converting JavaScript into an intermediate language called JASIL.
+Similar to SimpIL [C], Kudzu tries to circumvent the issue of solving complicated constraints by first converting JavaScript into an intermediate language called JASIL.
 Strings, in particular, are parsed and partitioned into several sub types which are more uniform.
@@
 
-TODO BRUMLEY
+In [C], the authors summarize dynamic taint analysis and symbolic execution and attempt to formalize each technique.
+A formal definition for DTA requires a formal language upon which to perform taint analysis, so the authors use SimpIL, a Simple Intermediate Language.
+Note that this is distinct from but related to the intermediate representations which some fuzzing research converts sources into.
+When fuzzers first convert to an intermediate language, this is done to simplify future analysis, as when Kudzu [AD] converts JavaScript strings into one of several new data types which are easier to reason about.
+Time is traded up front in order to make future operations easier or possible.
+SimpIL is a complete programming language, lacking in features but used as a base for some of the author's other work.
+It should be noted that the features SimpIL lacks, in particular functions and variable scoping, can be implemented using SimpIL, and SimpIL expressions not having side effects similarly do not hinder it.
+The important implementation issues for DTA spring from one's tainting policy.
+Our tainting policy decides under what circumstances we introduce taint, verify it, and track its propagation throughout the program execution [C].
 
-DTA is the process of locating sources of taint and following their propagation through a binary to data sinks.
-Since, for exploitation, bugs must be triggered by user input, DTA usually identifies all user input (files, command line arguments, UI interactions, ...) as tainted, and marks it accordingly.
+Introduction rules should specify when taint first appears in a program, what type of taint it is, and what parts of the program have become tainted as a result.
+We can record taint at varying levels of granularity, with the tradeoff of finer-grained taint requiring greater system resources and slowing down analysis.
+Different types of taint may be more interesting to different kinds of fuzzers because different input comes from sources of varying trustedness [C].
+For instance, we should probably trust raw, unsanitized user input we have read less than we trust a configuration file that only privileged users can modify.
+Both might be read in as input to a program, but the former is much more likely to contain malicious data like shellcode trying to exploit a vulnerability.
+Fuzzers have continued to drill down into finer and finer levels of granularity, from assigning everything with a generic binary value of tainted/not tainted to byte and even bit-level marking of which part of user input affected which variable.
+[CITE] [C] Note that this also expands taint's data type from a bit to something larger, and each tainted object requires this tag.
 
-The granularity of taint marking is variable.
-Assigning everything from a generic binary value of tainted/not tainted to bit-level marking of which part of user input affected which variable is conceivable, although finer-grained taint analysis is more computationally expensive and difficult to determine.
+Just as with taint introduction, we verify taint based on our overall objective.
+If we are worried about a binary being exploited to execute arbitrary code, we may instrument the EIP register.
+When we verify that taint has reached EIP, we know we stand a strong chance of having found an exploitable condition.
+Likewise, were we monitoring taint not in order to generate test cases for fuzzing, but to study a piece of malware, we might instead watch for when a particular routine, which we think is unpacking the malware, has finished, and the malware is now available in an unobfuscated form.
+
+Taint propagates through a program from its initial source, perhaps making its way to vulnerable sinks.
+The condition we are interested in is when user input finds its way to these vulnerable sinks in a program, and is able to influence them.
+As an example, user input received on STDIN which is able to change the value of the EIP register in x86 assembly is able to hijack control flow in the program.
+This may be as innocuous, though annoying, as forcing EIP to strange areas in the binary, resulting in segfaults, to more sinister remote code execution via pointing EIP to user controlled shellcode.
+
+There are several challenges involved with implementing DTA.
+First of all, accurate taint analysis, as free as possible from both over and under tainting, requires a precisely implemented taint policy.
+Different types of control flows, either direct or indirect, must be handled as well, and one-way or lossy functions also tend to be either difficult or untenable to instrument.
+
+TODO under/over
 
@@
 
-Handling taint correctly is of great important because of the existence of subtle implicit flow cases referenced by Clause, J.
+Handling taint correctly is of great importance because of the existence of subtle implicit flow cases referenced by Clause, J.
 et al [D].
@@
 
-DTA has been used to implement smart mutation fuzzers [A, T, MORE], but I think my work is unique from and complementary to Bekrar's work.
+TODO one-way
+
+DTA has been used to implement smart mutation fuzzers [A, T, MORE], but I believe the technique I explore later is unique from and complementary to Bekrar's work.
 In [A], DTA is proposed as a way to intelligently decide which parts of user input should be mutated.
 In [T], dynamic taint analysis identified hot bytes, which were then modified randomly or with boundary values.
-
 I plan to add on to these ideas by allowing smarter mutations to be selected by backsolving to decide which values are most likely to result in new paths being explored.

### 2014-02-24 docs/paper/fsuthesis/thesis-template/paper.tex
working through symb exec for brumley

@@
 
-\lstset{frame=tb,
+\lstdefinestyle{cstyle} {
   language=C,
@@
 
-% Taken from Lena Herrmann at 
-% http://lenaherrmann.net/2010/05/20/javascript-syntax-highlighting-in-the-latex-listings-package
+\definecolor{dkgreen}{rgb}{0,0.6,0}
+\definecolor{gray}{rgb}{0.5,0.5,0.5}
+\definecolor{mauve}{rgb}{0.58,0,0.82}
+
+\lstdefinestyle{asmstyle} {
+  frame=tb,
+  language={[x86masm]Assembler},
+  aboveskip=3mm,
+  belowskip=3mm,
+  showstringspaces=false,
+  columns=flexible,
+  basicstyle={\small\ttfamily},
+  numbers=none,
+  numberstyle=\tiny\color{gray},
+  keywordstyle=\color{blue},
+  commentstyle=\color{dkgreen},
+  stringstyle=\color{mauve},
+  breaklines=true,
+  breakatwhitespace=true
+  tabsize=3
+}
+
+% Adapted from Lena Herrmann at http://lenaherrmann.net/2010/05/20/javascript-syntax-highlighting-in-the-latex-listings-package
 
@@
 
-\lstdefinelanguage{JavaScript}{
+\lstdefinestyle{jsstyle} {
   keywords={typeof, new, true, false, catch, function, return, null, catch, switch, var, if, in, while, do, else, case, break},
@@
   morestring=[b]"
-}
-
-\lstset{
-   language=JavaScript,
-   backgroundcolor=\color{lightgray},
-   extendedchars=true,
-   basicstyle=\footnotesize\ttfamily,
-   showstringspaces=false,
-   showspaces=false,
-   numbers=left,
-   numberstyle=\footnotesize,
-   numbersep=9pt,
-   tabsize=2,
-   breaklines=true,
-   showtabs=false,
-   captionpos=b
 }
@@
 
-%\begin{lstlisting}
-%// Hello.c
-%#include<stdio.h>
-%int main() {
-%	int x = 3;
-%	printf("%d\n", x);
-%}
-%\end{lstlisting}
-
-%\begin{figure}[htb]
-%  	\center{\includegraphics[width=\textwidth]
-%   	{figures/archer.png}}
-%	\caption{\label{fig:my-label} My figure.  An example of a cool figure}
-%\end{figure}
+\begin{lstlisting}[style=cstyle]
+// hello.c
+#include<stdio.h>
+int main() {
+	int x = 3;
+	printf("%d\n", x);
+}
+\end{lstlisting}
 
@@
 This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to determine smarter ways to mutate user input and create new test cases.
-For instance, in the figure 1 example:
-\\
+For instance, in the below example:
 
-\begin{verbatim}
-figure 1:
-call read
-mov eax, [ebp - val]
-inc eax
-mul eax, 5
-cmp eax, 42
+\begin{lstlisting}[style=asmstyle]
+call read 				;instrument read syscall
+mov eax, [ebp - val]			;taint propagates from val to eax reg
+inc eax					;transform eax
+mul eax, 5				;transform eax
+cmp eax, 42				;cmp and jmp based on tainted reg value
 jnz 0x8BADC0DE
-\end{verbatim}
+\end{lstlisting}
+
+%\begin{verbatim}
+%figure 1:
+%call read
+%mov eax, [ebp - val]
+%inc eax
+%mul eax, 5
+%cmp eax, 42
+%jnz 0x8BADC0DE
+%\end{verbatim}
 
@@
 
-\begin{lstlisting}[caption=Figure BLAH]
+%\begin{lstlisting}[caption=Figure BLAH]
+\begin{lstlisting}[style=jsstyle]
 // Let userInput = "2 + 2"
@@
 Our tainting policy decides under what circumstances we introduce taint, verify it, and track its propagation throughout the program execution [C].
+Introduction rules should specify:
+\begin{itemize}
+	\item when taint first appears in a program,
+	\item what type of taint it is, and 
+	\item what parts of the program have become tainted as a result
+\end{itemize}
 
-Introduction rules should specify when taint first appears in a program, what type of taint it is, and what parts of the program have become tainted as a result.
 We can record taint at varying levels of granularity, with the tradeoff of finer-grained taint requiring greater system resources and slowing down analysis.
@@
 
-TODO under/over
+[C] suggests that taint introduction is an easier problem than taint removal.
+After all, taint is introduced into a system by a limited number of avenues, such as files, user input, and the execution environment.
+Once these are instrumented, they can be considered as always introducing taint to the system.
+However, taint removal depends not only on the instruction execution, but also on the context of the instruction.
+In x86, performing the exclusive or operation with the same register as both operands will zero out the register.
+Thus, even if the eax register were tainted, after xor eax, eax the eax register will be untainted, as its value is always 0.
+Taint policy could, for instance, add a rule that xoring a register with itself will remove taint from the register.
+However, what if eax and ebx are both tainted with the same value and we execute xor eax, ebx?
+Now the check must not just blindly remove taint when the same register is both operands, but instead consider the source of taint found in both operands.
+Failing to account for circumstances like this introduces overtaint, which means we spend time analyzing false positives.
 
+Even worse is undertainting.
+Overtainting creates unnecessary work, but undertainting may lead us to miss taint propagations to vulnerable sinks.
+Undertainting typically occurs when we mishandle or fail to perceive information flows [C].
 Taint can propagate via explicit or implicit flows, sometimes also called data and control dependencies respectively [G].
@@
 
-TODO one-way
+TODO Finish brumley DTA
+TODO undertaint info flow code example
+
+TODO one-way functs
 
@@
 TODO Add "All you ever wanted to know..." Stuff
+TODO more stuff from O
 
@@
 This makes it difficult for symbolic execution to scale past the order of tens of thousands of lines of code.
+
+Symbolic execution is defined under SimpIL as execution under which return values from input sources are symbolic, instead of concrete.
+As the program executes, we pick up various constraints on these symbols from expressions and branches.
+For instance, we may start with a symbol s, which is then multiplied by a scalar 10, and then added to a constant 5 to calculate the offset for an effective address in an array.
+The symbol s is now constrained as s*10+5.
+When we encounter branch instructions, we inherit constraints based on whether or not the branch is taken.
+If we branch in the figure below, we now have the constraints x * 10 + 5 == 25 [C].
+
+\begin{lstlisting}[style=cstyle]
+s = get_input();
+index = s * 10 + 5;
+if A[index] == 25
+	func1();
+else
+	func2();
+\end{lstlisting}
+
+Because symbolic execution can reason about the constraints placed on input, it drastically reduces the amount of testing necessary to explore all possible branches [C].
+With purely random testing in the above example, we would need to provide many different values for s to trigger the if statement and explore func1.
+If fact, only one value, s = 2, leads us down this path, where all other values jump to func2.
+Just for integer based evaluations, we would need to test half of all integer values to stand a reasonable chance at triggering both paths of any if statement.
+Symbolic execution, in contrast, solves for s = 2 and s $\neq$ 2, requiring only two separate executions to explore both paths.
+However, this precision comes at a cost.
+Symbolic execution doubles the number of paths which must be explored each time we encounter a  branch, since we can either take or not take each branch.
+Most optimizations for symbolic execution boil down to using symbolic execution less, parallelzing symbolic execution, or trying to simplify constraint formulas to make them easier to reason about [C].
+Using symbolic execution less or more smartly falls into the realm of concolic and mixed execution.
+Parallelization introduces its own set of challenges, raised in [H], such as efficiently using resources by controlling the number of forked programs executing.
+
+Not only is symbolic execution costly, but certain things are difficult to reason about symbolically.
+Accessing memory, for example, is hard to do when we reference not a memory location but an unevaluated expression.
+Solutions to this are imperfect and tend to rely on a combination of outsourcing the work to an SMT solver and performing static analysis on the binary to try and guess about memory locations.
+Schwartz, Avgerinos and Brumley raise the concern that malware could take advantage of most symbolic execution engines inability to perfectly reason about symbolic memory to frustrate malware analysts [C].
+
+TODO challenges - Memory and jumps, syscalls, disk and other "outside" stuff
 
@@
 
-\section{Concolic Execution}
+\section{Mixed and Concolic Execution}
+
+TODO TODO TODO [C] considers concolic execution to be when we first execute concretely and THEN execute the same thing symbolically.
+Mixed execution is when we execute once with both concrete and symbolic input--make sure other works stand by this distinction.
 

### 2014-02-24 docs/paper/fsuthesis/thesis-template/paper.tex
small chapter refactoring in paper

@@
 
-\chapter{Introduction}
-
-\section{Motivation}
-TODO US gov't interest via money
-
-\begin{lstlisting}[style=cstyle]
-// hello.c
-#include<stdio.h>
-int main() {
-	int x = 3;
-	printf("%d\n", x);
-}
-\end{lstlisting}
-
-\section{Theoretical Difficulties}
-TODO programming language theory, i.e. what makes fuzzing hard
-
-TODO focus on fact that this stands separate from and complementary to symb. exec? Perhaps performance analysis vs. s2e on binaries to show the potential?
+\chapter{Abstract}
 
@@
 Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions, is one technique used by researchers and analysts.
-Applications tested for vulnerabilities are often black boxes because source code is unavailable.
+Because many project's source code is not made unavailable to protect intellectual property, applications tested for vulnerabilities are often considered black boxes.
+Reasoning about the inner working of a complex application when one can only observe the relationship between input and output is hard.
+In fact, for some situations, like properly implemented cryptography, it is provably hard.
 This piles difficulties onto an already complex problem, which current research attempts to solve or reduce.
-Among these issues are:
+Among these issues this paper focuses on:
 	\begin{itemize}
@@
 
- Dynamic taint analysis is also difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
+ Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
 The path explosion problem arises from the nature of assembly languages.
@@
 
-This work aims to reduce the severity of the latter two problems while being wary of the first during implementation.
+This work aims to reduce the severity of the latter two problems while being wary of the first during implementation. Chapter 2 explains ZZZZ, Chapter 3 AAAA etc....
+
 Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
@@
 \end{lstlisting}
-
-%\begin{verbatim}
-%figure 1:
-%call read
-%mov eax, [ebp - val]
-%inc eax
-%mul eax, 5
-%cmp eax, 42
-%jnz 0x8BADC0DE
-%\end{verbatim}
 
@@
 
-\chapter{Preliminaries}
+\chapter{Introduction}
+
+\section{Motivation}
+TODO US gov't interest via money, security issues, etc.
+
+\section{Problem Statement}
+
+TODO Overview of difficulties of fuzzing
+
+\section{State of the Field}
+
+TODO current capabilities and shortcomings of fuzzers
+
+\section{Contributions}
+
+TODO a few paragraphs about what I did, missteps, conclusions, etc.
+
+\section{Theoretical Difficulties}
+TODO programming language theory, i.e. what makes fuzzing hard
+
+\chapter{Fuzzing by Example}
+
+TODO fuzzing is a large field, hope to show "fuzzing" by detailing practical examples. Techniques chapter explains a more theoretical base.
 
@@
 
-Explain white vs. black box. How gray could bleed into black because of DBI. Talk about SAGE.
+TODO Explain white vs. black box. How gray could bleed into black because of DBI. Talk about SAGE.
 
@@
 
-\section{TODO Fuzzing Web Applications}
+TODO
+
+\section{Fuzzing Web Applications}
 
@@
 
-%\begin{lstlisting}[caption=Figure BLAH]
 \begin{lstlisting}[style=jsstyle]
@@
 
+TODO should this section be moved from prelims elsewhere?
+
 \chapter{Related Work}
@@
 
-Talk about CMU Mayhem. [H]
-AEG [I]
+TODO AEG [I]?
 
@@
 
-TODO similar to Automatic
-patch-based exploit generation is possible: Techniques and
+TODO similar to Automatic patch-based exploit generation is possible: Techniques and
 implications, but mine doesn't require a patch?
@@
 This strategy has netted TaintScope 27 new vulnerabilities across several different pieces of software, most of which operate on complicated file format specifications like PNG or PCAP files [T].
-
-\chapter{Assumptions and Scoping}
-
-I assume ASLR is disabled for the binary to be fuzzed.
-This allows the program to easily track and compare execution paths.
-I plan to implement the technique for 32-bit x86 assembly, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both the size and flavor of architecture (32 vs.
-64-bit, ARM vs.
-x86 vs.
-PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
-
-I also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary.
-The program will then attempt to concretely execute each path within the binary by backsolving, hopefully at a greater speed than symbolic execution.
-
-Because current selective symbolic execution engines still appear to introduce significant overhead (Between 6 and 78X overhead more than QEMU for S2E.
-Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others) [J, K, L].
-In contrast, basic block counting using Intel Pin, the framework I am leveraging, introduced between 2 and 4X overhead [M].
-However, the pintool needed for my proposed technique will introduce greater levels of overhead, since I will be working at the instruction level instead of the basic block level, requiring more instrumentations for a given binary.
-
-I am leveraging Intel PIN to perform dynamic binary instrumentation.
-I am first testing dummy programs with many paths that are easy to backsolve, similar to the example above.
-A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
-I then plan to test against S2E and Peach Fuzzer [Z].
-
-In addition, there are allowable situations in programs which are outside the scope of this program.
-For instance, programs can loop forever [X].
-These can be dealt with using reasonable heuristics and could be the subject of future research.
 
@@
 
-\chapter{Implementation}
+\chapter{Contribution}
+
+\section{Assumptions and Scoping}
+
+I assume ASLR is disabled for the binary to be fuzzed.
+This allows the program to easily track and compare execution paths.
+I plan to implement the technique for 32-bit x86 assembly, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both the size and flavor of architecture (32 vs.
+64-bit, ARM vs.
+x86 vs.
+PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
+
+I also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary.
+The program will then attempt to concretely execute each path within the binary by backsolving, hopefully at a greater speed than symbolic execution.
+
+Because current selective symbolic execution engines still appear to introduce significant overhead (Between 6 and 78X overhead more than QEMU for S2E.
+Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others) [J, K, L].
+In contrast, basic block counting using Intel Pin, the framework I am leveraging, introduced between 2 and 4X overhead [M].
+However, the pintool needed for my proposed technique will introduce greater levels of overhead, since I will be working at the instruction level instead of the basic block level, requiring more instrumentations for a given binary.
+
+I am leveraging Intel PIN to perform dynamic binary instrumentation.
+I am first testing dummy programs with many paths that are easy to backsolve, similar to the example above.
+A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
+I then plan to test against S2E and Peach Fuzzer [Z].
+
+In addition, there are allowable situations in programs which are outside the scope of this program.
+For instance, programs can loop forever [X].
+These can be dealt with using reasonable heuristics and could be the subject of future research.
+
+\section{Implementation}
 
@@
 
-\section{results}
+\section{Results}
 
@@
 
-% Was setbacks, modify and remove heavily
+\section{Lessons Learned}
+
+TODO
 

### 2014-02-24 docs/paper/fsuthesis/thesis-template/paper.tex
done with symb. exec. and brumley paper in general

@@
   basicstyle={\small\ttfamily},
-  numbers=none,
+  numbers=left,
   numberstyle=\tiny\color{gray},
@@
   breaklines=true,
-  breakatwhitespace=true
+  breakatwhitespace=true,
   tabsize=3
@@
   sensitive=false,
+  numbers=left,
   comment=[l]{//},
@@
 
-TODO challenges - Memory and jumps, syscalls, disk and other "outside" stuff
+Certain constructs, like switch statements, when translated into assembly, are converted into jump tables, which consist of a sequence of checks and jumps to implement each case.
+During symbolic execution these compares and jumps could also be an expression instead of a concrete value.
+Syscalls and operations involving I/O are also difficult to express in a purely symbolic execution, because they can have side effects.
+For example, the write syscall not only returns an integer value representing success and number of bytes written, but also writes to a file descriptor.
+Implementation can model this effect to an external entity, but because of the unique side effects each syscall have, there will be many one-offs [C].
 
@@
 Used in javascript fuzzer [AD]
-Used in Owen's slides.
+Used in [C].
 
 \chapter{Contribution}
+
+TODO explain.
 

### 2014-02-25 docs/paper/fsuthesis/thesis-template/paper.tex
starting on implementation section for paper

@@
 
+\section{TODO Intel PIN}
+
 \chapter{Techniques}
@@
 This allows the program to easily track and compare execution paths.
-I plan to implement the technique for 32-bit x86 assembly, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist in binaries, regardless of both the size and flavor of architecture (32 vs.
+I have implemented the technique for the x86-32 architecture, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
 64-bit, ARM vs.
@@
 PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
+I also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
+The program concretely executes the binary once with the initial test case, recording taint propagation during execution.
+Stdin, stdout, and stderr are recorded for each run, for later analysis.
+After the initial run, the program automatically starts solving each byte by backsolving to try and find new paths.
 
-I also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary.
-The program will then attempt to concretely execute each path within the binary by backsolving, hopefully at a greater speed than symbolic execution.
+TODO in above make sure can catch stderr segfaults, segfaults go to shell's stderr, also a signal
 
-Because current selective symbolic execution engines still appear to introduce significant overhead (Between 6 and 78X overhead more than QEMU for S2E.
-Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others) [J, K, L].
+Current selective symbolic execution engines still appear to introduce significant overhead, between 6 and 78X overhead more than QEMU for S2E.
+Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others [J, K, L].
 In contrast, basic block counting using Intel Pin, the framework I am leveraging, introduced between 2 and 4X overhead [M].
-However, the pintool needed for my proposed technique will introduce greater levels of overhead, since I will be working at the instruction level instead of the basic block level, requiring more instrumentations for a given binary.
+However, the pintool needed for my proposed technique introduces greater levels of overhead, since I will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.
 
 I am leveraging Intel PIN to perform dynamic binary instrumentation.
-I am first testing dummy programs with many paths that are easy to backsolve, similar to the example above.
+I am testing dummy programs with many paths that are easy to backsolve, similar to the example above.
 A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
-I then plan to test against S2E and Peach Fuzzer [Z].
 
-In addition, there are allowable situations in programs which are outside the scope of this program.
+There are allowable situations in programs which are outside the scope of this program.
 For instance, programs can loop forever [X].
-These can be dealt with using reasonable heuristics and could be the subject of future research.
+These can be dealt with using reasonable heuristics, fuzzers tend to simply count loops and terminate after a set threshold is reached, and could be the subject of future research.
+
+% TODO I then plan to test against S2E and Peach Fuzzer [Z].
 
@@
 I implement dynamic taint analysis for files as input sources.
-I am basing my DTA heavily on Jonathan Salwan\'s work [N].
+I am basing my implementation of DTA on Jonathan Salwan\'s work [N].
 Currently I instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
-I instrument binaries at the assembly instruction level using Intel Pin.
+I instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles .
 Each instruction is handled differently based upon the following criteria:
@@
 Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing.
-Currently, I record input, output, and taint for each test executed, using an auto-incrementing id and separating results at the directory level.
+Currently, I record input, output, and taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
 I also keep track of the mutations which have already been explored.

### 2014-02-25 MyPinTool/driver.py
appears to work with passwords of arbitrary length. nice

@@ -19,7 +19,8 @@ def test(inputFile, taintFile, seed = ('0', '0', '0') ):
         '-t', 'obj-ia32/MyPinTool.so', 
         #'--', '../vulnerable_programs/trivial/a.out', inputFile
         #'--', './a.out', inputFile
-        '--', './simpleCrackme', inputFile
+        #'--', './simpleCrackme', inputFile
+        '--', './simpleCrackme2', inputFile
         #'--', './strcpy', inputFile
         #'--', 'ls'
     ]

### 2014-02-26 docs/paper/fsuthesis/thesis-template/paper.tex
added graph to paper and testing oracle attack

@@
 \usepackage{hyperref}
+\usepackage{pgfplots}
+%\usepackage{filecontents}
+%\usepackage{pgfplotstable}
 
@@
 
-TODO explain.
+I have written a proof of concept fuzzer which uses dynamic taint analysis to record the operations performed on user input, then reverses these operations to solve for new paths to explore.
+The fuzzer currently records implicit and explicit taint flows between memory and registers.
+When the EFLAGS register is modified, it is checked whether a comparison instruction with tainted operands was the modifier, and if so this is also recorded.
+After an execution it publishes input, output, taint, and mutation data to a driver program, which reasons about possible user input locations and values one byte at a time.
+This means when branch decisions are determined by comparisons at the byte level, the fuzzer can guarantee a new path is taken, provided it can accurately backsolve information about the transformations performed on the byte.
 
@@
 Currently I instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
-I instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles .
+I instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles each instruction.
 Each instruction is handled differently based upon the following criteria:
@@
 Various precautions, such as removing taint for an instruction like "xor eax, eax", must be taken.
-Lossy operations, like shifts, must be handled carefully to be backsolve-able.
+Lossy operations, like shifts, must be handled carefully to be backsolve-able, and checksums and cryptographic operations are not supported.
+
+As a demonstration I have run my fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values.
+If all of these checks pass, then AAAAA, otherwise BBBBBB (segfault?
+EIP?
+add vulnerability detection alg?).
+I have observed ....
+(insert graphs with password lengths, etc.)
 
@@
 Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing.
-Currently, I record input, output, and taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
+Currently, I record input, output, taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
 I also keep track of the mutations which have already been explored.
-Users can grep for interesting conditions like segfaults or unexpected output, then cross reference the test number with the observed taint flow and the particular mutation tested.
+A driver program keeps track of the observed taint which has already been explored, and selects a new byte to mutate.
+Users can grep for interesting conditions like segfaults or unexpected output, then cross reference the test number with the observed taint flow, input file, particular mutation tested.
 
@@
 
-\section{Methodology}
+%\section{Methodology}
 
-I am currently instrumenting dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
+%I am currently instrumenting dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
 If results appear promising I can try to make the fuzzer as complete as possible and begin running it on real-world applications.
@@
 
-As of this writing I am moving towards fuzzing Linux utilities.
+%As of this writing I am moving towards fuzzing Linux utilities.
 Results for toy binaries are promising, with "crackme" type programs which ask for a secret being solved in approximately 2*n runs, where n is the length of the secret.
@@
 
-TODO
+%Looking like linear with password + constant of 16 overtaint
+%Pw len:   Tests: 
+%1         17
+%4         20
+%7         26
+%10        28
+
+%\begin{filecontents*}{results.txt}
+%	$x$	$y$       
+%	1	17
+%	4	20
+%    7	26
+%    10	28
+%\end{filecontents*}
+
+%\pgfplotsset{results.txt}
+
+\begin{tikzpicture}
+\begin{axis}[
+    title={Oracle Attack},
+    xlabel={Secret Length},
+    ylabel={Test cases},
+    xmin=0, xmax=15,
+    ymin=10, ymax=30,
+    xtick={0,2,4,6,8,10},
+    ytick={15,20,25,30},
+    ymajorgrids=true,
+    grid style=dashed,
+]
+
+\addplot[
+    color=blue,
+    mark=square,
+    ]
+    coordinates {
+    		(1,17)
+    		(4,20)
+    		(7,26)
+    		(10,28)
+    		(15,38)
+    }; 
+\end{axis}
+\end{tikzpicture}
 
@@
 
-TODO
+TODO overtainting, naive implementations had LOTS of it
 

### 2014-02-26 MyPinTool/clean.sh
finished testing simple crackmes

@@ -2,5 +2,6 @@
 rm -f input/input.* output/output.* taint/taint.* mutations/mutation.*
 rm -f results.out file.out taint.out
 rm -f buffer.out.*
+cp fileLose.txt inputFile.txt
 echo > taint/explored.0
 

### 2014-02-26 MyPinTool/driver.py

@@ -20,7 +20,8 @@ def test(inputFile, taintFile, seed = ('0', '0', '0') ):
         #'--', '../vulnerable_programs/trivial/a.out', inputFile
         #'--', './a.out', inputFile
         #'--', './simpleCrackme', inputFile
-        '--', './simpleCrackme2', inputFile
+        #'--', './simpleCrackme2', inputFile
+        '--', './simpleCrackme50', inputFile
         #'--', './strcpy', inputFile
         #'--', 'ls'
     ]
@@ -104,6 +105,7 @@ def recordResults(inputFile, outputFile, taintSet, mutation, n):
 def getTestNumber(taintDir):
 
     taint = os.listdir(taintDir)
+    taint.remove('.gitignore')
     if len(taint) == 1:
         return 1
 

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme10.c

@@ -1,0 +1,37 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'H') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme15.c

@@ -1,0 +1,46 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == 'Q') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme20.c

@@ -1,0 +1,50 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == '1' && 
+	buf[316] == '2' && 
+	buf[317] == '3' && 
+	buf[318] == '4' && 
+	buf[319] == '5') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme25.c

@@ -1,0 +1,56 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == '1' && 
+	buf[316] == '2' && 
+	buf[317] == '3' && 
+	buf[318] == '4' && 
+	buf[319] == '5' && 
+	buf[320] == '6' && 
+	buf[321] == '7' && 
+	buf[322] == '8' && 
+	buf[323] == '9' && 
+
+	buf[324] == '5') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme30.c

@@ -1,0 +1,61 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == '1' && 
+	buf[316] == '2' && 
+	buf[317] == '3' && 
+	buf[318] == '4' && 
+	buf[319] == '5' && 
+	buf[320] == '6' && 
+	buf[321] == '7' && 
+	buf[322] == '8' && 
+	buf[323] == '9' && 
+	buf[324] == '0' && 
+	buf[325] == 'a' && 
+	buf[326] == 'b' && 
+	buf[327] == 'c' && 
+	buf[328] == 'd' && 
+
+	buf[329] == '5') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme35.c

@@ -1,0 +1,66 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == '1' && 
+	buf[316] == '2' && 
+	buf[317] == '3' && 
+	buf[318] == '4' && 
+	buf[319] == '5' && 
+	buf[320] == '6' && 
+	buf[321] == '7' && 
+	buf[322] == '8' && 
+	buf[323] == '9' && 
+	buf[324] == '0' && 
+	buf[325] == 'a' && 
+	buf[326] == 'b' && 
+	buf[327] == 'c' && 
+	buf[328] == 'd' && 
+	buf[329] == 'e' && 
+	buf[330] == 'f' && 
+	buf[331] == 'g' && 
+	buf[332] == 'h' && 
+	buf[333] == 'i' && 
+
+	buf[334] == '5') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme40.c

@@ -1,0 +1,71 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == '1' && 
+	buf[316] == '2' && 
+	buf[317] == '3' && 
+	buf[318] == '4' && 
+	buf[319] == '5' && 
+	buf[320] == '6' && 
+	buf[321] == '7' && 
+	buf[322] == '8' && 
+	buf[323] == '9' && 
+	buf[324] == '0' && 
+	buf[325] == 'a' && 
+	buf[326] == 'b' && 
+	buf[327] == 'c' && 
+	buf[328] == 'd' && 
+	buf[329] == 'e' && 
+	buf[330] == 'f' && 
+	buf[331] == 'g' && 
+	buf[332] == 'h' && 
+	buf[333] == 'i' && 
+	buf[334] == ',' && 
+	buf[335] == '.' && 
+	buf[336] == '!' && 
+	buf[337] == '@' && 
+	buf[338] == '#' && 
+
+	buf[339] == '5') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme45.c

@@ -1,0 +1,76 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == '1' && 
+	buf[316] == '2' && 
+	buf[317] == '3' && 
+	buf[318] == '4' && 
+	buf[319] == '5' && 
+	buf[320] == '6' && 
+	buf[321] == '7' && 
+	buf[322] == '8' && 
+	buf[323] == '9' && 
+	buf[324] == '0' && 
+	buf[325] == 'a' && 
+	buf[326] == 'b' && 
+	buf[327] == 'c' && 
+	buf[328] == 'd' && 
+	buf[329] == 'e' && 
+	buf[330] == 'f' && 
+	buf[331] == 'g' && 
+	buf[332] == 'h' && 
+	buf[333] == 'i' && 
+	buf[334] == ',' && 
+	buf[335] == '.' && 
+	buf[336] == '!' && 
+	buf[337] == '@' && 
+	buf[338] == '#' && 
+	buf[339] == '^' && 
+	buf[340] == ';' && 
+	buf[341] == '/' && 
+	buf[342] == 'a' && 
+	buf[343] == 'b' && 
+
+	buf[344] == '5') {
+        	win = 1;
+    }
+
+    if (win) {
+        printf("you win!\n");
+    }
+    else {
+        printf("you lose!\n");
+    }
+
+}

### 2014-02-26 vulnerable_programs/trivial/simpleCrackme50.c

@@ -1,0 +1,81 @@
+#include<stdio.h>
+#include<unistd.h>
+#include<stdlib.h>
+#include<string.h>
+#include <sys/types.h>
+#include <sys/stat.h>
+#include <fcntl.h>
+
+int main(int argc, char* argv[])
+{
+    // Open and read user input
+    //int fd = open("file.txt", O_RDONLY);
+    int fd = open(argv[1], O_RDONLY);
+    char buf[500];
+    int res = read(fd, buf, 500);
+    close(fd);
+
+    // You win if 300th character is X
+    int win = 0;
+    if (buf[300] == 'B' && 
+	buf[301] == 'B' && 
+	buf[302] == 'C' && 
+	buf[303] == 'D' && 
+	buf[304] == 'E' && 
+	buf[305] == 'F' && 
+	buf[306] == 'G' && 
+	buf[307] == 'H' && 
+	buf[308] == 'I' && 
+	buf[309] == 'J' && 
+	buf[310] == 'K' && 
+	buf[311] == 'L' && 
+	buf[312] == 'M' && 
+	buf[313] == 'N' && 
+	buf[314] == 'O' && 
+	buf[315] == '1' && 
+	buf[316] == '2' && 
+	buf[317] == '3' && 
+	buf[318] == '4' && 
+	buf[319] == '5' && 
+	buf[320] == '6' && 
+	buf[321] == '7' && 
+	buf[322] == '8' && 
+	buf[323] == '9' && 
+	buf[324] == '0' && 
+	buf[325] == 'a' && 
+	buf[326] == 'b' && 
+	buf[327] == 'c' && 
+	buf[328] == 'd' && 
+	buf[329] == 'e' && 
+	buf[330] == 'f' && 
+	buf[331] == 'g' && 
+	buf[332] == 'h' && 
+	buf[333] == 'i' && 
+	buf[334] == ',' && 
+	buf[335] == '.' && 
+	buf[336] == '!' && 
+	buf[337] == '@' && 
+	buf[338] == '#' && 
+	buf[339] == '^' && 
+	buf[340] == ';' && 
+	buf[341] == '/' && 
+	buf[342] == 'a' && 
+	buf[343] == 'b' && 
+	buf[344] == ' ' && 
+	buf[345] == '4' && 
+	buf[346] == '1' && 
+	buf[347] == '`' && 
+	buf[348] == 'b' && 
+
+	buf[349] == '5') {
+        	win = 1;
+    }
+
+    if (win) {
[…]

### 2014-03-10 docs/paper/fsuthesis/thesis-template/paper.tex
added some stuff TODO and planned last few pages

@@
 TODO US gov't interest via money, security issues, etc.
+Raytheon SI/VUPEN use it.
 
@@
 
-TODO should this section be moved from prelims elsewhere?
+TODO add code examples
+%http://en.wikipedia.org/wiki/User_Datagram_Protocol#IPv4_Pseudo_Header
+IDEA write c program to checksum UDP packets and say whether they pass or not, have fuzzer "correct" packets to pass arbitrary, user decided checksum.
+update: probably will not work without noticeable modification, but could maybe notice the situation and reverse engineer the algorithm, then print it out or start making a lookup table?
 
@@
 TODO one-way functs
+Use: https://www.ida.liu.se/~TDDC90/literature/papers/violating05.pdf
+[AJ]
 
@@
 Used in [C].
+Mitigates dealing with side effects, done by PANDA.
+%http://www.cc.gatech.edu/~brendan/tzb_author.pdf
+%http://iris.lib.neu.edu/cgi/viewcontent.cgi?article=1097&context=elec_comp_theses
 
@@
 As a demonstration I have run my fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values.
-If all of these checks pass, then AAAAA, otherwise BBBBBB (segfault?
-EIP?
-add vulnerability detection alg?).
-I have observed ....
-(insert graphs with password lengths, etc.)
+If all of these checks pass, then the program outputs a "win" string, otherwise it outputs a "lose" string.
+This can be thought of conceptually as an oracle attack, and is similar to reverse engineering "crackme" exercises.
+Given no knowledge of the secret key, and only able to query an oracle, a successful attack must discover the secret within a reasonable number of guess [CITE?].
+
+After compiling with the Tiny C Compiler, which performs minimal optimization and doesn't add security measures, this binary and a default test file are given as input to Stubble, which will begin to dynamically generate run cases which will explore new paths within the binary.
+These test cases are fed back into the system, which continues to backsolve to find new ways to explore at branches, until there are no tainted bytes left for exploration.
+
+% (segfault? EIP? add vulnerability detection alg?). I have observed .... (insert graphs with password lengths, etc.)
+
+\section{Results}
+
+Secrets of length 1 to 50 were tested at various intervals.
+It appears that, aside from some constant overhead, that test cases generated and time required to crack the binary  rise linearly with password length.
+The constant overhead is probably introduced from overtaint.
+
+(TODO time smaller oracle attacks)
+TODO attacks which transform input first to show ability to backsolve
+
+\begin{tikzpicture}
+\begin{axis}[
+    title={Oracle Attack},
+    xlabel={Secret Length},
+    ylabel={Test cases},
+    xmin=0, xmax=55,
+    ymin=10, ymax=100,
+    xtick={0,10,20,30,40,50},
+    ytick={20,30,40,50,60,70,80,90,100},
+    ymajorgrids=true,
+    grid style=dashed,
+]
+
+\addplot[
+    color=blue,
+    mark=square,
+    ]
+    coordinates {
+    		(1,17)
+    		(4,20)
+    		(7,26)
+    		(10,28)
+    		(15,38)
+    		(20, 45)
+    		(25, 53) % 1:41.22elapsed
+    		(30, 60) % 1:51.78elapsed
+    		(35, 67) % 2:09.49elapsed
+    		(40, 74) % 2:19.83elapsed
+    		(45, 82) % 2:36.96elapsed
+    		(50, 90) % 2:51.77elapsed
+    }; 
+\end{axis}
+\end{tikzpicture}
+
+\begin{tikzpicture}
+\begin{axis}[
+    title={Oracle Attack},
+    xlabel={Secret Length},
+    ylabel={Time Elapsed (seconds)},
+    xmin=0, xmax=55,
+    ymin=10, ymax=200,
+    xtick={0,10,20,30,40,50},
+    ytick={0,20,30,40,50,60,80,100,120,140,160,180,200},
+    ymajorgrids=true,
+    grid style=dashed,
+]
+
+\addplot[
+    color=red,
+    mark=square,
+    ]
+    coordinates {
+    		(1,0) % TODO time these first couple
+    		(4,0)
+    		(7,0)
+    		(10,0)
+    		(15,0)
+    		(20, 0)
+    		(25, 101) 
+    		(30, 112)
+    		(35, 129) 
+    		(40, 140)
+    		(45, 157) 
+    		(50, 172) 
+    }; 
+\end{axis}
+\end{tikzpicture}
 
@@
 Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel.
-For this project I have tested my program on a personally created binary, simpleCrackme.
-This binary takes a file containing a password in argv1.
-If the password matches its secret, then it prints "You win", otherwise, it prints "You lose".
-
-After running my program, one can grep for the win string in the output/ directory.
-This is similar to concept to running a fuzzer, and grepping around the output recorded for more interesting conditions, like segfaults.
-Results show a noticeable speedup.
+Results show an expected speedup for an application with decently independent input.
 
@@
 
-\section{Results}
-
-%Looking like linear with password + constant of 16 overtaint
-%Pw len:   Tests: 
-%1         17
-%4         20
-%7         26
-%10        28
-
-%\begin{filecontents*}{results.txt}
-%	$x$	$y$       
-%	1	17
-%	4	20
-%    7	26
-%    10	28
-%\end{filecontents*}
-
-%\pgfplotsset{results.txt}
-
-\begin{tikzpicture}
-\begin{axis}[
-    title={Oracle Attack},
-    xlabel={Secret Length},
-    ylabel={Test cases},
-    xmin=0, xmax=15,
-    ymin=10, ymax=30,
-    xtick={0,2,4,6,8,10},
-    ytick={15,20,25,30},
-    ymajorgrids=true,
-    grid style=dashed,
-]
-
-\addplot[
-    color=blue,
-    mark=square,
-    ]
-    coordinates {
-    		(1,17)
-    		(4,20)
-    		(7,26)
-    		(10,28)
-    		(15,38)
-    }; 
-\end{axis}
-\end{tikzpicture}
-
 \section{Lessons Learned}
 
-TODO overtainting, naive implementations had LOTS of it
+TODO overtainting, naive implementations had lots of it.
+TODO difficulties with implementation
 
@@
 	\item [Y] Sen, Koushik, Darko Marinov, and Gul Agha. CUTE: a concolic unit testing engine for C. Vol. 30. No. 5. ACM, 2005.
-	\item [Z] Peach Fuzzer. \url{<http://peachfuzzer.com/>}
+	\item [Z] Eddington, Michael. "Peach fuzzing platform." Peach Fuzzer (2011).
 	\item [AA] Zhang, Xiangyu, Rajiv Gupta, and Youtao Zhang. "Precise dynamic slicing algorithms." Software Engineering, 2003. Proceedings. 25th International Conference on. IEEE, 2003.
@@
 IEEE, 2013.
+	\item [AJ] Oehlert, Peter. "Violating assumptions with fuzzing." Security \& Privacy, IEEE 3.2 (2005): 58-62.
 

### 2014-03-11 docs/paper/fsuthesis/thesis-template/paper.tex
started on pin

@@
 
-\section{TODO Intel PIN}
+\section{Intel PIN}
+
+Heavyweight analysis techniques, like symbolic execution or dynamic taint analysis, which operate over an entire instruction set, must account for the idiosyncracies and diverse operations supported by the architecture.
+By leveraging a pre-existing framework like Intel Pin [M], new software can abstract away from architecture specific details like x86 variable length instructions and avoid re-inventing the wheel.
+
+Pin, developed by Intel Corporation and the University of Colorado, performs dynamic binary instrumentation on x86, Itanium, and ARM architectures.
+Pin takes an arbitrary binary to be instrumented and an user-developed dynamically linked library, and instruments the binary at runtime by inserted user defined routines or changes into the application's code.
+
+Pin's architecture is two-fold: consisting of a virtual machine for compiling and executing code, and a cache for previously executed
+
+instrumentation is accomplished with Unix ptrace, similar to debuggers
+
+TODO finish pin stuff
 
@@
 
-Several valuable techniques to improve fuzzers' code coverage have evolved over the years.
+Several valuable techniques for improving fuzzers' code coverage have evolved over the years.
 Two, in particular, inspire this work directly: Dynamic Taint Analysis and Symbolic Execution.

### 2014-03-11 docs/paper/fsuthesis/thesis-template/paper.tex
done with pin paper

@@
 Pin, developed by Intel Corporation and the University of Colorado, performs dynamic binary instrumentation on x86, Itanium, and ARM architectures.
-Pin takes an arbitrary binary to be instrumented and an user-developed dynamically linked library, and instruments the binary at runtime by inserted user defined routines or changes into the application's code.
+Pin takes an arbitrary binary to be instrumented and a user-developed dynamically linked library, and instruments the binary at runtime by inserting user defined routines or changes into the application's code.
 
-Pin's architecture is two-fold: consisting of a virtual machine for compiling and executing code, and a cache for previously executed
+Pin's architecture is two-fold: consisting of a virtual machine for compiling and executing code, and a code cache for storing invididual code traces.
+An API for developing Pintools is also provided.
+Pin takes apart the program one trace at a time, compiling the native executable and the instrumentation code together into the same architecture.
+Pin defines a trace as a linear sequence of machine code instructions, terminated by either an unconditional jump or a pre-defined number of conditional jumps.
+Traces, hopefully, correspond to higher level control flow structures, but are also limited in size by a pre-defined maximum number of instructions [M].
 
-instrumentation is accomplished with Unix ptrace, similar to debuggers
+The Pin VM can be broken down into three sub-components: a just-in-time compiler which instruments the binary by hooking the appropriate routines and re-compiles into the original architecture, along with a dispatcher and an emulator.
+The dispatcher passes code to the code cache and executes instructions, but, because Pin resides solely in userland, certain activities which occur at a lower level of the operating system, like syscalls, cannot be captured normally.
+The emulator handles these cases [M].
 
-TODO finish pin stuff
+Pin injects itself into a given binary using Ptrace to modify instructions and then trap running processes to inject code in a similar manner to how debuggers like GDB attach to processes and inject software breakpoints [AK].
+Just like GDB, Pin can attach to a running process or instrument a process from the first instruction.
+This stands in contrast to other dynamic binary instrumentation frameworks like DynamoRIO [AL], which use LD\_PRELOAD to force a new  shared library into the process context.
+This noisily shifts shared libraries' memory addresses to accomodate the new, pre-loaded library, and also cannot instrument the first parts of a program before the library loading code executes [M].
+
+Pin instruments at the trace level, JIT compiling a trace and caching it for re-use.
+A number of Pin optimizations revolve around the compilation phase, because testing shows Pin bottlenecks tend to concentrate around the execution of instrumented code.
+This is perhaps because instrumenting code involves hooking perhaps both the entrance and exit to a function, which adds two jumps.
+In addition, transitions between the VM and code cache require saving application state.
+The eflags register, for instance, must be pushed onto the stack to be read or written so that the program's original eflags is preserved.
+Since this register is used for all jumps, among other things, it is accessed often by both Pin and the instrumented program.
+Thus, Pin analyzes the liveness of each flag in eflags on a per-routine basis, and avoids saving and restoring flags which are not used by the routine as an optimization measure [M].
+
+This research leverages Pin to instrument arbitrary binaries at the instruction and syscall levels.
+Code is inserted to track taint introduced by user input, and recorded separately as it propagates.
+When taint reaches a branch, the recorded state information is used to work backwards through lossless operations to try and reason about the location and value of bytes which affect whether the branch is taken or not.
 
@@
 	\item [AJ] Oehlert, Peter. "Violating assumptions with fuzzing." Security \& Privacy, IEEE 3.2 (2005): 58-62.
+	\item [AK] Gilmore, John, and Sten Shebs. "GDB internals—a guide to the internals of the GNU debugger." Found in the doc directory of gdb distribution version 5.1 (2000).
+	\item [AL] Bruening, Derek, and Qin Zhao. "DynamoRIO."
 

### 2014-03-20 docs/paper/fsuthesis/thesis-template/paper.tex
reworking abstract

@@
 \chapter{Abstract}
+
+Fuzzing, or the feeding of manipulated input to processes to try and detect software bugs and vulnerabilities, is an integral, even required, part of the work conducted by both private-sector companies like Microsoft [Q] and Google [AM] and nation-state powers and contractors.
+In 2014, Pwn2Own paid out 850,000 USD to participants over two days for proof of zero-day exploitable vulnerabilities, for an average of 66,000 USD per exploit [AN].
+Forbes suggests black market prices are considerably higher, peaking at over \$150,000 for modern browser exploits [AO].
+
+The software community knows that programmers write buggy software, even with debugging tools and access to source code for auditing purposes.
+Fuzzing, however, cannot even assume source code access, because interesting programs are not always open source.
+As an example, Internet Explorer, a prime exploitation target, is propietary software.
+Successful testing depends upon the fuzzer's ability to explore the binary and detect bugs without source code.
+In addition, each branch instruction in assembly language introduces two new possible paths, leading to an explosion of explorable paths as binaries grow in size and complexity.
+Following all or most these paths, and doing so in a timely manner, requires complex software and time-memory tradeoffs.
+
+In this paper, we present our analysis of existing techniques for improving fuzzers' code coverage and path exploration abilities, along with our own contributions and conclusions.
+We begin by exploring related work in Chapter 2, which describes current fuzzers architecture and limitations.
+Chapter 3 describes several fundamental techniques incorporated in most modern sophisticated fuzzers.
+In Chapter 4, we describe our contributions, in the form of what is, to the best of our knowledge, a new technique for black box binary fuzzing, a proof of concept fuzzer which implements the technique, and testing results.
+Lastly, we describe possible future work and conclusions from the experience in Chapter 5.
+
+Our technique, dubbed taint-
+
+ADD?
+The major impetus for this work is outlined in "A Taint Based Approach for Smart Fuzzing".
+This paper proposes a fuzzing tool architecture, involving vulnerability detection, followed by taint analysis based upon found vulnerabilities, which drives the generation of intelligent tests.
+As tests are run they are checked to ensure they provide adequate code coverage, and results are carefully monitored for interesting situations like crashes [A].
+The paper also serves as an excellent explanation of the current state and future of fuzzing.
+In particular, they suggest combining taint analysis with backward slicing.
+The technique discussed in this paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
+
+\chapter{Old-Abstract}
 
@@
 	\item [AL] Bruening, Derek, and Qin Zhao. "DynamoRIO."	
+	\item [AM] http://googleonlinesecurity.blogspot.com/2011/08/fuzzing-at-scale.html
+	\item [AN] http://www.pwn2own.com/, http://www.pwn2own.com/2014/03/pwn2own-2014-lineup/
+	\item [AO] http://www.forbes.com/sites/andygreenberg/2012/03/23/shopping-for-zero-days-an-price-list-for-hackers-secret-software-exploits/
 

### 2014-03-20 docs/paper/fsuthesis/thesis-template/paper.tex
removed urls, working on abstract

@@
 
-Our technique, dubbed taint-
+Our technique, dynamic slice backsolving, using dynamic taint analysis to watch user input.
+As user input is introduced, each byte is tracked separately and, when the program transforms or manipulates user input, those transformations are recorded.
+When branches which depend upon user input are reached, the recorded transformations, if possible, are reversed, backsolving for a new value of a particular byte in user input which will lead execution down a different path in the binary.
+After execution finishes, input test cases are mutated to reflect this new information, and a new execution test runs.
 
-ADD?
-The major impetus for this work is outlined in "A Taint Based Approach for Smart Fuzzing".
-This paper proposes a fuzzing tool architecture, involving vulnerability detection, followed by taint analysis based upon found vulnerabilities, which drives the generation of intelligent tests.
-As tests are run they are checked to ensure they provide adequate code coverage, and results are carefully monitored for interesting situations like crashes [A].
-The paper also serves as an excellent explanation of the current state and future of fuzzing.
-In particular, they suggest combining taint analysis with backward slicing.
-The technique discussed in this paper boils down to an attempt to automatically solve slices like those introduced in [AA], which have been derived from taint analysis as much as possible.
+The inspiration for this technique comes mainly from "A Taint Based Approach for Smart Fuzzing", which proposes a fuzzing tool architecture, involving vulnerability detection, followed by taint analysis based upon found vulnerabilities, which drives the generation of intelligent tests.
+Dynamic taint analysis tracks which bytes of user input are important in the binary, and these so-called "hot bytes" are made the focus of fuzzing attempts.
+The paper mentions it is valuable to be able to generate backward slices of program traces.
+This traces can be run and analyzed by programmers.
+In the spirit of automation, our work not only generates backward slices based on taint propagation, but also automatically solves these traces to find new byte values.
+Thus, for a subset of programs, we can determine not only the exact location of user input which determines a branch condition, but also generate precise values for both branch and non-branch cases.
 
@@
 \section{Motivation}
-TODO US gov't interest via money, security issues, etc.
-Raytheon SI/VUPEN use it.
 
@@
 
-\section{State of the Field}
-
-TODO current capabilities and shortcomings of fuzzers
+\section{Methodology}
 
@@
 TODO a few paragraphs about what I did, missteps, conclusions, etc.
-
-\section{Theoretical Difficulties}
-TODO programming language theory, i.e. what makes fuzzing hard
 
@@
 	\item [M] Luk, Chi-Keung, et al. "Pin: building customized program analysis tools with dynamic instrumentation." Acm Sigplan Notices. Vol. 40. No. 6. ACM, 2005.
-	\item [N] Salwan, Jonathan. Shell-storm.org %\url{http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/}
+	\item [N] Salwan, Jonathan. Shell-storm.org http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/
 	\item [O] King, James C. "Symbolic execution and program testing." Communications of the ACM 19.7 (1976): 385-394.
@@
 	\item [AD] Saxena, Prateek, et al. "A symbolic execution framework for javascript." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
-	\item [AE] Mozilla Developer Network. \url{https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global\_Objects/eval}
-	\item [AF] The WebKit Open Source Project. \url{http://www.webkit.org/}
+	\item [AE] Mozilla Developer Network. https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global\_Objects/eval
+	\item [AF] The WebKit Open Source Project. http://www.webkit.org/
 	\item [AG] Portokalidis, Georgios, Asia Slowinska, and Herbert Bos.

### 2014-03-20 docs/paper/fsuthesis/thesis-template/paper.tex
moved abstract to intro, made new abstract, nice and short

@@
 
-\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
+\title{Dynamic Slice Backsolving}
+%\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
 \author{Clark Wood}
@@
 
+Finding bugs in software is a difficult but lucrative endeavour.
+Fuzzing is one technique for finding bugs, particularly exploitable vulnerabilities, employed by both software companies and nation-state actors.
+When no source code is available, fuzzing complex programs can prove difficult, and as techniques become more sophisticated they require more resources and time.
+We present a technique, dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to reason about not only the location of user input bytes which contribute to interesting program behavior like branching, but also the exact byte value necessary to trigger a desire branch condition.
+We have implemented this technique in a fuzzer, which is able to reason about large and complex user input and reliably drive program execution down new code paths to explore new portions of compiled code.
+
+\chapter{Introduction}
+
 Fuzzing, or the feeding of manipulated input to processes to try and detect software bugs and vulnerabilities, is an integral, even required, part of the work conducted by both private-sector companies like Microsoft [Q] and Google [AM] and nation-state powers and contractors.
@@
 Thus, for a subset of programs, we can determine not only the exact location of user input which determines a branch condition, but also generate precise values for both branch and non-branch cases.
+
+We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries.
+Stubble requires no access to source code, unlike many fuzzers utilizing symbolic execution, and automatically generates test files which exercise new paths in the input program.
+Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks.
+When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
+Stubble is able to reason about hundreds of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is length of the secret.
+Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
+We believe dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
 

### 2014-03-20 docs/paper/fsuthesis/thesis-template/paper.tex
change I to we

@@
 %\listoftables
-%\listoffigures
+\listoffigures
 %\listofmusex
@@
 
+\section{Motivation}
+
 Fuzzing, or the feeding of manipulated input to processes to try and detect software bugs and vulnerabilities, is an integral, even required, part of the work conducted by both private-sector companies like Microsoft [Q] and Google [AM] and nation-state powers and contractors.
@@
 Forbes suggests black market prices are considerably higher, peaking at over \$150,000 for modern browser exploits [AO].
+
+\section{Problem Statement}
 
@@
 Following all or most these paths, and doing so in a timely manner, requires complex software and time-memory tradeoffs.
+
+\section{Contributions}
 
@@
 
-Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], I focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
+Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], we focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
 This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to determine smarter ways to mutate user input and create new test cases.
@@
 
-I propose to avoid using a constraint solver entirely, and instead backsolve completely in memory.
+We propose to avoid using a constraint solver entirely, and instead backsolve completely in memory.
 This is easier to implement than many of the clever optimizations used by S2E and could result in speedup over symbolic execution.
 
-Because there are a finite number of conditional jumps, all of which depend on different flags or combinations of flags in the EFLAGS register, and a finite number of instructions that modify the EFLAGS register in x86, I can create cases for all possible ways jumps are decided.
-I only want to prove this is possible however, so I will only implement a subset and instead comment on how to implement the other comparisons.
-
-\chapter{Introduction}
-
-\section{Motivation}
-
-\section{Problem Statement}
-
-TODO Overview of difficulties of fuzzing
-
-\section{Methodology}
-
-\section{Contributions}
-
-TODO a few paragraphs about what I did, missteps, conclusions, etc.
+Because there are a finite number of conditional jumps, all of which depend on different flags or combinations of flags in the EFLAGS register, and a finite number of instructions that modify the EFLAGS register in x86, we can create cases for all possible ways jumps are decided.
+We only want to prove this is possible however, so we only implement a subset and instead comment on how to implement the other comparisons.
 
@@
 et al [D].
-Implicit data flows are not always considered by dynamic tainting techniques [E], but for my project, implicit data flows are very important, so I need to implement DTA which catches both implicit and explicit flows.
+Implicit data flows are not always considered by dynamic tainting techniques [E], but for my project, implicit data flows are very important, so we need to implement DTA which catches both implicit and explicit flows.
 
@@
 
-DTA has been used to implement smart mutation fuzzers [A, T, MORE], but I believe the technique I explore later is unique from and complementary to Bekrar's work.
+DTA has been used to implement smart mutation fuzzers [A, T, MORE], but we believe the technique we explore later is unique from and complementary to Bekrar's work.
 In [A], DTA is proposed as a way to intelligently decide which parts of user input should be mutated.
 In [T], dynamic taint analysis identified hot bytes, which were then modified randomly or with boundary values.
-I plan to add on to these ideas by allowing smarter mutations to be selected by backsolving to decide which values are most likely to result in new paths being explored.
+We plan to add on to these ideas by allowing smarter mutations to be selected by backsolving to decide which values are most likely to result in new paths being explored.
 This has been done with symbolic execution before, but traditional symbolic execution is much more heavy-weight, both in time required to setup the environment and in overhead introduced to run the program, than my proposed approach.
@@
 Without utilizing symbolic execution, however, it is difficult to automatically guarantee that all possible paths in a binary have been explored.
-Where most current research focuses on improving speed by using symbolic execution less, I propose to achieve similar code coverage to symbolic execution by implementing something akin to symbolic execution, but without using the SMT solvers and instruction emulation which tend to make symbolic execution slow.
+Where most current research focuses on improving speed by using symbolic execution less, we propose to achieve similar code coverage to symbolic execution by implementing something akin to symbolic execution, but without using the SMT solvers and instruction emulation which tend to make symbolic execution slow.
 
 Call-chain-backward symbolic execution has been proposed by [R], although this technique achieved a backward symbolic execution by iteratively applying a forward execution from successively farther away points in the program and the reducing the set of possible symbolic inputs.
-In contrast, I propose to avoid symbolic execution, forward or backward, by backsolving concretely and then applying heuristics to generate concrete input which is highly likely to result in exploring a new path.
-Symbolic execution never occurs, although I believe in many situations an equal degree of precision in determining new paths can be attained.
+In contrast, we propose to avoid symbolic execution, forward or backward, by backsolving concretely and then applying heuristics to generate concrete input which is highly likely to result in exploring a new path.
+Symbolic execution never occurs, although we believe in many situations an equal degree of precision in determining new paths can be attained.
 
@@
 Concolic testing has been shown to improve runtime while still allowing both wide and deep inspection of a program's execution tree, although it often still requires source code to be instrumented [X, Y].
-What I propose is similar to concolic testing, in that I am augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
+What We propose is similar to concolic testing, in that we are augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
 However, the lack of a heavyweight constraint solver and the ability to work on binaries without instrumenting or using source code in any way have, to the best of my knowledge, not yet been proposed.
@@
 
-I have written a proof of concept fuzzer which uses dynamic taint analysis to record the operations performed on user input, then reverses these operations to solve for new paths to explore.
+We have implemented a proof of concept fuzzer which uses dynamic taint analysis to record the operations performed on user input, then reverses these operations to solve for new paths to explore.
 The fuzzer currently records implicit and explicit taint flows between memory and registers.
@@
 
-I assume ASLR is disabled for the binary to be fuzzed.
+We assume ASLR is disabled for the binary to be fuzzed.
 This allows the program to easily track and compare execution paths.
-I have implemented the technique for the x86-32 architecture, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
+We have implemented the technique for the x86-32 architecture, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
 64-bit, ARM vs.
@@
 PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
-I also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
+We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
 The program concretely executes the binary once with the initial test case, recording taint propagation during execution.
@@
 Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others [J, K, L].
-In contrast, basic block counting using Intel Pin, the framework I am leveraging, introduced between 2 and 4X overhead [M].
-However, the pintool needed for my proposed technique introduces greater levels of overhead, since I will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.
+In contrast, basic block counting using Intel Pin, the framework we are leveraging, introduced between 2 and 4X overhead [M].
+However, the pintool needed for my proposed technique introduces greater levels of overhead, since we will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.
 
-I am leveraging Intel PIN to perform dynamic binary instrumentation.
-I am testing dummy programs with many paths that are easy to backsolve, similar to the example above.
+We are leveraging Intel PIN to perform dynamic binary instrumentation.
+We are testing dummy programs with many paths that are easy to backsolve, similar to the example above.
 A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
@@
 
-% TODO I then plan to test against S2E and Peach Fuzzer [Z].
+% TODO We then plan to test against S2E and Peach Fuzzer [Z].
 
@@
 
-I implement dynamic taint analysis for files as input sources.
-I am basing my implementation of DTA on Jonathan Salwan\'s work [N].
-Currently I instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
-I instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles each instruction.
+We implement dynamic taint analysis for files as input sources.
+We are basing my implementation of DTA on Jonathan Salwan\'s work [N].
+Currently we instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
+We instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles each instruction.
 Each instruction is handled differently based upon the following criteria:
@@
 
-As a demonstration I have run my fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values.
+As a demonstration we have run our fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values.
 If all of these checks pass, then the program outputs a "win" string, otherwise it outputs a "lose" string.
@@
 
-% (segfault? EIP? add vulnerability detection alg?). I have observed .... (insert graphs with password lengths, etc.)
+% (segfault? EIP? add vulnerability detection alg?). We have observed .... (insert graphs with password lengths, etc.)
 
@@
 
+\begin{figure}
+\caption{Fig. 1}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
+
+\end{figure}
 
@@
 Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing.
-Currently, I record input, output, taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
-I also keep track of the mutations which have already been explored.
+Currently, stubble records input, output, taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
+Stubble also keeps track of the mutations which have already been explored.
 A driver program keeps track of the observed taint which has already been explored, and selects a new byte to mutate.
@@
 
-%I am currently instrumenting dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
-If results appear promising I can try to make the fuzzer as complete as possible and begin running it on real-world applications.
+%We are currently instrumenting dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
+If results appear promising we can try to make the fuzzer as complete as possible and begin running it on real-world applications.
 Achieving a noticeable speedup over modern symbolic execution would be the goal.
 
-%As of this writing I am moving towards fuzzing Linux utilities.
+%As of this writing we are moving towards fuzzing Linux utilities.
 Results for toy binaries are promising, with "crackme" type programs which ask for a secret being solved in approximately 2*n runs, where n is the length of the secret.
@@
 
-I have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
+We have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
 Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel.
@@
 
-However, I have seen runs as high as ~13 seconds elapsed.
+However, we have seen runs as high as ~13 seconds elapsed.
 Since my testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
-I also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
+We also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
 

### 2014-03-20 docs/paper/fsuthesis/thesis-template/paper.tex
changed my to our

@@
 et al [D].
-Implicit data flows are not always considered by dynamic tainting techniques [E], but for my project, implicit data flows are very important, so we need to implement DTA which catches both implicit and explicit flows.
+Implicit data flows are not always considered by dynamic tainting techniques [E], but for our project, implicit data flows are very important, so we need to implement DTA which catches both implicit and explicit flows.
 
@@
 We plan to add on to these ideas by allowing smarter mutations to be selected by backsolving to decide which values are most likely to result in new paths being explored.
-This has been done with symbolic execution before, but traditional symbolic execution is much more heavy-weight, both in time required to setup the environment and in overhead introduced to run the program, than my proposed approach.
+This has been done with symbolic execution before, but traditional symbolic execution is much more heavy-weight, both in time required to setup the environment and in overhead introduced to run the program, than our proposed approach.
 
@@
 What We propose is similar to concolic testing, in that we are augmenting concrete execution with dynamic taint analysis to solve for mutations which will exercise new paths in the code.
-However, the lack of a heavyweight constraint solver and the ability to work on binaries without instrumenting or using source code in any way have, to the best of my knowledge, not yet been proposed.
+However, the lack of a heavyweight constraint solver and the ability to work on binaries without instrumenting or using source code in any way have, to the best of our knowledge, not yet been proposed.
 
@@
 In contrast, basic block counting using Intel Pin, the framework we are leveraging, introduced between 2 and 4X overhead [M].
-However, the pintool needed for my proposed technique introduces greater levels of overhead, since we will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.
+However, the pintool needed for our proposed technique introduces greater levels of overhead, since we will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.
 
@@
 We implement dynamic taint analysis for files as input sources.
-We are basing my implementation of DTA on Jonathan Salwan\'s work [N].
+We are basing our implementation of DTA on Jonathan Salwan\'s work [N].
 Currently we instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
@@
 However, we have seen runs as high as ~13 seconds elapsed.
-Since my testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
+Since our testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
 We also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
@@
 %
-%Currently have results for crackmes, give idea of my fuzzer vs. %peach fuzz, and where i plan to go.
+%Currently have results for crackmes, give idea of our fuzzer vs. %peach fuzz, and where i plan to go.
 

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
added arch figure, maybe a little big

@@
 %\usepackage{pgfplotstable}
+
+%\usepackage[latin1]{inputenc}
+\usetikzlibrary{shapes,arrows}
 
@@
 
-\chapter{Fuzzing by Example}
+\chapter{Background and Related Work}
 
@@
 
-\subsection{Microsoft SAGE}
+\section{Microsoft SAGE}
 
@@
 
-\subsection{Grey-box Evolutionary Fuzzing}
+\section{Grey-box Evolutionary Fuzzing}
 
@@
 
-\chapter{Related Work}
-
 \section{Taint-based Fuzzing}
@@
 
-\chapter{Techniques}
+\section{Techniques}
 
@@
 
-\section{Dynamic Taint Analysis}
+\subsection{Dynamic Taint Analysis}
 
@@
 
-\section{Symbolic Execution}
+\subsection{Symbolic Execution}
 
@@
 
-\section{Mixed and Concolic Execution}
+\subsection{Mixed and Concolic Execution}
 
@@
 
-\section{TODO Conversion to an Intermediate Representation}
+\subsection{TODO Conversion to an Intermediate Representation}
 
@@
 
-\chapter{Contribution}
+\chapter{Contributions}
+
+\section{Dynamic Slice Backsolving}
+
+\section{Design}
+
+Stubble architecture
+
+% Source: http://www.texample.net/tikz/examples/simple-flow-chart/
+
+% Define block styles
+\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
+    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
+    text width=5em, text centered, rounded corners, minimum height=4em]
+\tikzstyle{line} = [draw, -latex']
+\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
+    minimum height=2em]
+
+\begin{tikzpicture}[node distance = 2cm, auto]
+    % Place nodes
+    \node [block] (driver) {driver};
+    \node [cloud, left of=driver, node distance=3cm] (binary) {binary};
+    \node [cloud, right of=driver, node distance=3cm] (test case) {test case};
+    \node [block, below of=driver, node distance=4cm] (Pintool) {Pintool};
+
+    \node [block, left of=Pintool, node distance=4cm] (input) {input/};    
+    \node [block, below of=Pintool, below of=input, node distance=2cm] (output) {output/};
+    \node [block, right of=output, node distance=4cm] (explored) {explored/};
+
+    \node [decision, right of=Pintool, node distance=4cm] (decide) {More taint to explore?};
+    \node [block, right of=decide, node distance=4cm] (mutate) {mutate};
+    \node [block, below of=decide, node distance=4cm] (stop) {stop};
+
+    % Draw edges
+    \path [line] (driver) -- (Pintool);
+    \path [line] (Pintool) -- (input);
+    \path [line] (Pintool) -- (output);
+    \path [line] (Pintool) -- (explored);
+    \path [line] (Pintool) -- (decide);
+    \path [line] (decide) -- node {yes} (mutate);
+    \path [line] (mutate) |- (test case);
+    \path [line] (decide) -- node {no}(stop);
+    \path [line,dashed] (binary) -- (driver);
+    \path [line,dashed] (test case) -- (driver);
+    \path [line, dashed] (explored) -- (decide);
+
+\end{tikzpicture}
+
+\section{Implementation}
+
+Pintool, python specifics. Binarys, RE
+
+\section{Parallelization}
+
+MyPinToolMultiProcess, why process level instead of threads, etc.
+
+\section{Testing}
+
+\section{Results}
+
+\chapter{Old Contributions}
 

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
working on intro and moving stuff around

@@
 
-\title{Dynamic Slice Backsolving}
+\title{Automated Dynamic Slice Backsolving}
 %\title{A Survey of Fuzzing and New Technique for Dynamic Analysis}
@@
 
-Finding bugs in software is a difficult but lucrative endeavour.
+Finding software bugs is a difficult but lucrative endeavour.
 Fuzzing is one technique for finding bugs, particularly exploitable vulnerabilities, employed by both software companies and nation-state actors.
-When no source code is available, fuzzing complex programs can prove difficult, and as techniques become more sophisticated they require more resources and time.
-We present a technique, dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to reason about not only the location of user input bytes which contribute to interesting program behavior like branching, but also the exact byte value necessary to trigger a desire branch condition.
+However, when no source code is available, fuzzing complex programs effectively can prove difficult, and as techniques become more sophisticated they require more resources and time.
+We present a technique, automated dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to reason about not only the location of user input bytes which contribute to interesting program behavior like branching, but also the exact byte value necessary to trigger a desire branch condition.
 We have implemented this technique in a fuzzer, which is able to reason about large and complex user input and reliably drive program execution down new code paths to explore new portions of compiled code.
@@
 
+Because of the high market value of finding bugs, either to patch or exploit, many researchers create their own fuzzers, or use open source products like Peach [Z].
+These fuzzers vary in purpose and sophistication.
+The simplest of fuzzers may have little understanding of the program it intends to fuzz, merely changing random bytes in user input and monitoring for interesting situations which suggest a bug has been found, such as segmentation faults.
+A log is produced, which can be analyzed by a programmer at a later date to try and identify the source of the crash.
+However, fuzzers of this variety, while adept at causing program crashes, tend to find shallow bugs or exit conditions.
+This is because, with no understanding of the inner workings of a program, a fuzzer is likely to fail checks at the start of a program over and over again [T].
+As an example, fuzzing an application which implements HTML by mutating random input bytes will have to reproduce the complex markup tags required to produce valid HTML.
+It will expend valuable time and resources failing to create valid head and body tags, instead of finding deep bugs.
+
+In order to fuzz more smartly, researchers employ several techniques, two of which are significant for this paper.
+Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing.
+DTA is a form of dynamic analysis, which marks user input as tainted at some level of granularity, and follows this taint as it propagates through the binary.
+Certain, task-dependent sinks are identified, and if taint flows to one of these sinks, a trace of program execution allows analysis to follow how taint sources are linked to these sinks.
+Symbolic execution first runs a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of solver which decides what values the element should given the recorded conditions.
+Symbolic execution improves code coverage, helping to guide fuzzers into deeper, more interesting parts of a program.
+DTA and symbolic execution, however, are computationally expensive, which leaves room for refinement of techniques by using the technique more wisely or modifying it.
+Our technique uses DTA to hopefully achieve greater code coverage than random testing, without having to convert code to an intermediate representation or outsource constraints to a solver like symbolic execution.
+
 \section{Problem Statement}
@@
 As an example, Internet Explorer, a prime exploitation target, is propietary software.
-Successful testing depends upon the fuzzer's ability to explore the binary and detect bugs without source code.
+Successful testing depends upon the fuzzer's ability to explore the binary as a black box and detect bugs without source code.
+Reasoning about the inner working of a complex application when one can only observe the relationship between input and output is hard.
 In addition, each branch instruction in assembly language introduces two new possible paths, leading to an explosion of explorable paths as binaries grow in size and complexity.
 Following all or most these paths, and doing so in a timely manner, requires complex software and time-memory tradeoffs.
+These two difficulties are called the code coverage problem and the path explosion problem [U] respectively.
+Many current fuzzers use techniques like dynamic taint analysis and symbolic execution to improve code coverage, and often employ various heuristics to mitigate the path explosion problem.
+
+Our work aims to address the code coverage problem in a similar way to symbolic execution, while sidestepping or avoiding entirely some of the negatives associated with symbolic execution.
+In particular, symbolic execution traditionally:
+
+\begin{itemize}
+	\item Requires source code access
+	\item Requires programmers to instrument code manually
+	\item Must convert code to an intermediate representation
+	\item Must emulate the IR in a virtual machine
+	\item Outsources constraint solving to heavyweight SMT solvers
+\end{itemize}
 
@@
 
-In this paper, we present our analysis of existing techniques for improving fuzzers' code coverage and path exploration abilities, along with our own contributions and conclusions.
-We begin by exploring related work in Chapter 2, which describes current fuzzers architecture and limitations.
-Chapter 3 describes several fundamental techniques incorporated in most modern sophisticated fuzzers.
-In Chapter 4, we describe our contributions, in the form of what is, to the best of our knowledge, a new technique for black box binary fuzzing, a proof of concept fuzzer which implements the technique, and testing results.
+Because of these downsides, much research tries to attain more reasonable performance by using symbolic execution less or more wisely [J].
+We focus instead on approximating symbolic execution's code coverage by using dynamic taint analysis to drive test case mutation.
+As the native program executes, we dynamically instrument the binary and record execution slices.
+Memory accesses, loads and stores, and transformations of tainted bytes are recorded, and then used to backsolved to give exact byte values and locations to explore in future runs.
+Our implementation of this technique requires no source code, no modification to a binary, no conversion to an IR, and no SMT solvers.
+
+In this paper, we present our analysis of existing techniques along with our own contributions and conclusions.
+We begin by exploring related work in Chapter 3, which sets the background and describes current fuzzers' techniques and limitations.
+In chapter 4, we describe our contributions, in the form of what is, to the best of our knowledge, a new technique for black box binary fuzzing, a proof of concept fuzzer which implements the technique, and testing results.
 Lastly, we describe possible future work and conclusions from the experience in Chapter 5.
 
-Our technique, dynamic slice backsolving, using dynamic taint analysis to watch user input.
+Our technique, automated dynamic slice backsolving, uses dynamic taint analysis to watch user input.
 As user input is introduced, each byte is tracked separately and, when the program transforms or manipulates user input, those transformations are recorded.
@@
 The paper mentions it is valuable to be able to generate backward slices of program traces.
-This traces can be run and analyzed by programmers.
+These traces can then be run and analyzed by programmers.
 In the spirit of automation, our work not only generates backward slices based on taint propagation, but also automatically solves these traces to find new byte values.
@@
 We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries.
-Stubble requires no access to source code, unlike many fuzzers utilizing symbolic execution, and automatically generates test files which exercise new paths in the input program.
+Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program.
 Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks.
 When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
-Stubble is able to reason about hundreds of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is length of the secret.
+Stubble is able to reason about large amounts of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is the length of the secret.
 Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
-We believe dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
-
-\chapter{Old-Abstract}
-
-Finding exploitable bugs in binaries is a difficult but valuable endeavour.
-Fuzzing, or the feeding of controlled input into processes to try and detect vulnerable conditions, is one technique used by researchers and analysts.
-Because many project's source code is not made unavailable to protect intellectual property, applications tested for vulnerabilities are often considered black boxes.
-Reasoning about the inner working of a complex application when one can only observe the relationship between input and output is hard.
-In fact, for some situations, like properly implemented cryptography, it is provably hard.
-This piles difficulties onto an already complex problem, which current research attempts to solve or reduce.
-Among these issues this paper focuses on:
-	\begin{itemize}
-		\item efficient and thorough dynamic taint analysis
-		\item the path explosion problem [U], and
-		\item the code coverage problem. 
-	\end{itemize}
-
- Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
+We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
+
+TODO add loop invariants experiments
+
+%\chapter{Old-Abstract}
+
+% Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
 The path explosion problem arises from the nature of assembly languages.
@@
 
-This work aims to reduce the severity of the latter two problems while being wary of the first during implementation. Chapter 2 explains ZZZZ, Chapter 3 AAAA etc....
-
-Instead of trying to attain more reasonable performance by using symbolic execution less or more wisely [J], we focus instead on approximating symbolic execution by using dynamic taint analysis to drive mutation.
-This is possible by tracking taint at the instruction level, then backsolving from the jump to the source of taint to determine smarter ways to mutate user input and create new test cases.
-For instance, in the below example:
-
-\begin{lstlisting}[style=asmstyle]
-call read					;instrument read syscall
-mov eax, [ebp - val]		;taint propagates from val to eax reg
-inc eax						;transform eax
-mul eax, 5					;transform eax
-cmp eax, 42					;cmp and jmp based on tainted reg value
-jnz 0x8BADC0DE
-\end{lstlisting}
-
-If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADC0DE.
+% Example for stubble
+%\begin{lstlisting}[style=asmstyle]
+%call read					;instrument read syscall
+%mov eax, [ebp - val]		;taint propagates from val to eax reg
+%inc eax						;transform eax
+%mul eax, 5					;transform eax
+%cmp eax, 42					;cmp and jmp based on tainted reg value
+%jnz 0x8BADC0DE
+%\end{lstlisting}
+
+%If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADC0DE.
 With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted).
@@
 
-This works similarly to a constraint solver, but constraint solving appears to be a traditional bottleneck, requiring generating symbolic input, usually in a different language like LLVM intermediate representation [V] and passing execution to the constraint solver.
-
-We propose to avoid using a constraint solver entirely, and instead backsolve completely in memory.
+%This works similarly to a constraint solver, but constraint solving appears to be a traditional bottleneck, requiring generating symbolic input, usually in a different language like LLVM intermediate representation [V] and passing execution to the constraint solver.
+
+%We propose to avoid using a constraint solver entirely, and instead backsolve completely in memory.
 This is easier to implement than many of the clever optimizations used by S2E and could result in speedup over symbolic execution.
 
-Because there are a finite number of conditional jumps, all of which depend on different flags or combinations of flags in the EFLAGS register, and a finite number of instructions that modify the EFLAGS register in x86, we can create cases for all possible ways jumps are decided.
+%Because there are a finite number of conditional jumps, all of which depend on different flags or combinations of flags in the EFLAGS register, and a finite number of instructions that modify the EFLAGS register in x86, we can create cases for all possible ways jumps are decided.
 We only want to prove this is possible however, so we only implement a subset and instead comment on how to implement the other comparisons.
@@
 
-TODO fuzzing is a large field, hope to show "fuzzing" by detailing practical examples. Techniques chapter explains a more theoretical base.
-
-\section{TODO White vs. Gray vs. Black box}
-
-TODO Explain white vs. black box. How gray could bleed into black because of DBI. Talk about SAGE.
+%TODO fuzzing is a large field, hope to show "fuzzing" by detailing practical examples. Techniques chapter explains a more theoretical base.
+
+%\section{TODO White vs. Gray vs. Black box}
+
+%TODO Explain white vs. black box. How gray could bleed into black because of DBI. Talk about SAGE.
 
@@
 
-\section{Grey-box Evolutionary Fuzzing}
-
-TODO
+%\section{Grey-box Evolutionary Fuzzing}
+
+%TODO
 
@@
 
-\section{TODO Mutation vs. Generation?}
-
-TODO Peach Fuzzer does both, overview with pictures?
-
-\section{TODO Local vs. Network}
-
-Do you have access to the program you are fuzzing?
-
-\section{TODO Difficulties and Limitations}
-
-TODO Path explosion. Code coverage. Complex file formats which mean you create shallow errors over and over again.
-
-TODO Limitations - one-way functions like bitwise shifts and checksums, cryptographic hashes. encryption.
-
-TODO add code examples
+%\section{TODO Mutation vs. Generation?}
+
+%TODO Peach Fuzzer does both, overview with pictures?
+
+%\section{TODO Local vs. Network}
+
+%Do you have access to the program you are fuzzing?
+
+%\section{TODO Difficulties and Limitations}
+
+%TODO Path explosion. Code coverage. Complex file formats which mean you create shallow errors over and over again.
+
+%TODO Limitations - one-way functions like bitwise shifts and checksums, cryptographic hashes. encryption.
+
+%TODO add code examples
 %http://en.wikipedia.org/wiki/User_Datagram_Protocol#IPv4_Pseudo_Header
-IDEA write c program to checksum UDP packets and say whether they pass or not, have fuzzer "correct" packets to pass arbitrary, user decided checksum.
-update: probably will not work without noticeable modification, but could maybe notice the situation and reverse engineer the algorithm, then print it out or start making a lookup table?
+%IDEA write c program to checksum UDP packets and say whether they pass or not, have fuzzer "correct" packets to pass arbitrary, user decided checksum.
+%update: probably will not work without noticeable modification, but could maybe notice the situation and reverse engineer the algorithm, then print it out or start making a lookup table?
 
@@
 
-TODO AEG [I]?
+%TODO AEG [I]?
 
@@
 
-\section{TODO Argos: 0-Day Emulator}
-
-http://www.few.vu.nl/argos/?page=3
+%\section{TODO Argos: 0-Day Emulator}
+
+%http://www.few.vu.nl/argos/?page=3
 
@@
 
-TODO Finish brumley DTA
-TODO undertaint info flow code example
-
-TODO one-way functs
-Use: https://www.ida.liu.se/~TDDC90/literature/papers/violating05.pdf
-[AJ]
+%TODO Finish brumley DTA
+%TODO undertaint info flow code example
+
+%TODO one-way functs
+%Use: https://www.ida.liu.se/~TDDC90/literature/papers/violating05.pdf
+%[AJ]
 
@@
 
-TODO Add "All you ever wanted to know..." Stuff
-TODO more stuff from O
+%TODO Add "All you ever wanted to know..." Stuff
+%TODO more stuff from O
 
@@
 
-\section{Dynamic Slice Backsolving}
+\section{Automated Dynamic Slice Backsolving}
 

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
corrected latex for abstract, some of contributions

@@
 
-%\begin{acknowledgments}
-%\end{acknowledgments}
+\begin{acknowledgments}
+SFS
+% Dr. Wang
+% Bret Whissel
+\end{acknowledgments}
 
@@
 
-%\begin{abstract}
-%This is my abstract.
-%\end{abstract}
-
 \mainmatter
@@
 
-\chapter{Abstract}
+\begin{abstract}
 
@@
 We have implemented this technique in a fuzzer, which is able to reason about large and complex user input and reliably drive program execution down new code paths to explore new portions of compiled code.
+
+\end{abstract}
 
@@
 In this paper, we present our analysis of existing techniques along with our own contributions and conclusions.
-We begin by exploring related work in Chapter 3, which sets the background and describes current fuzzers' techniques and limitations.
-In chapter 4, we describe our contributions, in the form of what is, to the best of our knowledge, a new technique for black box binary fuzzing, a proof of concept fuzzer which implements the technique, and testing results.
-Lastly, we describe possible future work and conclusions from the experience in Chapter 5.
+We begin by exploring related work in Chapter 2, which sets the background and describes current fuzzers' techniques and limitations.
+In chapter 3, we describe our contributions, in the form of what is, to the best of our knowledge, a new technique for black box binary fuzzing, a proof of concept fuzzer which implements the technique, and testing results.
+Lastly, we describe possible future work and conclusions from the experience in Chapter 4.
 
@@
 Such automated exploit generation is the subject of much research [H, I].
-
-% Example for stubble
-%\begin{lstlisting}[style=asmstyle]
-%call read					;instrument read syscall
-%mov eax, [ebp - val]		;taint propagates from val to eax reg
-%inc eax						;transform eax
-%mul eax, 5					;transform eax
-%cmp eax, 42					;cmp and jmp based on tainted reg value
-%jnz 0x8BADC0DE
-%\end{lstlisting}
-
-%If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADC0DE.
-With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted).
-After some number of transformations, perhaps zero, to the value in the eax register, we see a compare instruction, which checks eax's value against an immediate value.
-Then we can keep track of specific taint sources, and can record any movements or transformations, we have all the necessary information to "solve" the branch.
-Once we reach the tainted branch, we know that user input can affect whether we jump or not, and consequently we can backsolve to find out how to affect the branch instruction.
-In particular, we know the conditional jump instruction jnz depends on the Z flag in the EFLAGS register.
-We record whatever instruction last modified each flag in EFLAGS, so we handle the compare instruction next.
-Because we have kept track of taint propagation, we know we can affect the value of eax, but not 42, since it is an immediate value, so we know we need to make the value in eax equal 42.
-We follow the instructions that have modified the value of eax and use any appropriate operands involved with the inverse operation of the one originally performed on the value to reverse the transformations to eax's value.
-Finally, we notice eax originally received taint when a value was moved from memory, which was read into memory using the read syscall.
 
@@
 
+We have developed a technique which, to the best of our knowledge, provides similar code coverage to symbolic execution by using dynamic taint analysis to record relevant program slices and drive test case mutation.
+As a program runs, the introduction and propagation of taint is recorded.
+Should taint flow to a sink of interest, the recorded slice is backsolved to find new byte values which will hopefully lead future program runs down new paths.
+Taint is generally introduced to the program by user input.
+This can come in the form of user-provided files, command line arguments, or stdin.
+When user input is detected, it is marked as tainted at the byte level.
+This means that if user input is conceptualized as a stream of bytes $b_0,b_1,...,b_n$, then the first byte is considered separate from the separate byte, and each is individually followed throughout program execution.
+This level of granularity introduces significantly more overhead than binary tainting, which marks bytes as either tainted or not tainted, but provides far greater detail into which bytes of user input affect which parts of a program.
+
+Once user input is captured and marked tainted, any memory accesses, loads and stores, and transformations of tainted bytes are recorded as they are encountered.
+This creates a slice of moves and alterations to the bytes, which can be followed like a trail of breadcrumbs back to the original position of the byte.
+This continues as the program executes until a conditional branch is reached.
+When a conditional branch instruction is reached, it is either taken or not taken, based upon the value of some comparison.
+If this branch depends upon tainted values, which have descended in one way or another from user input, then there is a strong possibility that the "road not taken" could be explored if only user input looked appropriate.
+In the case where any transformations to user input are reversible, we can backsolve these transformations and, based upon the comparison, modify the byte value so that it leads to the complement of the previous branch condition.
+Not only this, we can identify which byte $b_0,b_1,...,b_n$ to modify, since we have followed each byte from their introduction.
+Using this information, we can mutate the previous test case to create a new test which will result in very similar program behavior, with the exception of branching where before it did not branch, and vice versa.
+
+INSERT COOL FIGURE
+
+The idea for this technique is raised in [A], which suggests using dynamic taint analysis to identify "hot bytes" of user input, which affect important things in a program, and also to generate backward slices [AA].
+Hot bytes become the target of fuzzing, with backward slices providing valuable context to analysts.
+Our contribution is the realization of this idea for a subset of cases, and the automation of solving these slices.
+Our hope is that by solving these slices automatically, we can identify not only the exact location but also the exact value of hot bytes.
+
+we ignore ....loops, more TODO
+
+Our methodology focuses on following taint specifically up to tainted branches, to direct as much attention as possible to finding new paths to explore within the binary.
+This is of particular importance when source code is not available for analysis, which is common in vulnerability research.
+Compiled code can be disassembled or debugged, but compilation is a lossy process.
+Even industry de-compilers like Hex Rays cannot restore comments, since these are not preserved, and they cannot guarantee to reproduce the exact higher level language semantics, given only assembly language.
+Thus, our implementation relies on Intel Pin to dynamically disassemble compiled binaries.
+
+Consider the following example in Intel x86 assembly:
+
+% x86 example
+\begin{lstlisting}[style=asmstyle]
+call read					;instrument read syscall
+mov eax, [ebp - val]		;taint propagates from val to eax reg
+inc eax						;transform eax
+mul eax, 5					;transform eax
+cmp eax, 42					;cmp and jmp based on tainted reg value
+jnz 0x8BADC0DE
+\end{lstlisting}
+
+If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADC0DE.
+With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted).
+After an arbitrary number of transformations, perhaps zero, to the value in the eax register, comes a compare instruction, which checks eax's value against an immediate value.
+Then we can keep track of specific taint sources, and can record any movements or transformations, we have all the necessary information to "solve" the branch.
+Once we reach the tainted branch, we know that user input can affect whether we jump or not, and consequently we can backsolve to find out how to affect the branch instruction.
+In particular, we know the conditional jump instruction jnz depends on the Z flag in the EFLAGS register.
+We record whatever instruction last modified each flag in EFLAGS, so we handle the compare instruction next.
+Because we have kept track of taint propagation, we know we can affect the value of eax, but not 42, since it is an immediate value, so we know we need to make the value in eax equal 42.
+We follow the instructions that have modified the value of eax and use any appropriate operands involved with the inverse operation of the one originally performed on the value to reverse the transformations to eax's value.
+Finally, we notice eax originally received taint when a value was moved from memory, which was read into memory using the read syscall.
+
+FROM INTRO
+We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries.
+Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program.
+Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks.
+When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
+Stubble is able to reason about large amounts of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is the length of the secret.
+Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
+We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
+END FROM INTRO
+
 \section{Design}
 
-Stubble architecture
+Stubble architecture, describe
+why intel pin and not dynamo rio, valgrind, etc.
 
@@
 
+\section{Limitations}
+
 \section{Parallelization}
@@
 These test cases are fed back into the system, which continues to backsolve to find new ways to explore at branches, until there are no tainted bytes left for exploration.
-
-% (segfault? EIP? add vulnerability detection alg?). We have observed .... (insert graphs with password lengths, etc.)
 
@@
 %\section{Methodology}
-
-%We are currently instrumenting dummy programs which use a subset of all possible comparisons and arithmetic operations on tainted variables.
-If results appear promising we can try to make the fuzzer as complete as possible and begin running it on real-world applications.
-Achieving a noticeable speedup over modern symbolic execution would be the goal.
 

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
working on results

@@
 
-\chapter{Old Contributions}
-
-We have implemented a proof of concept fuzzer which uses dynamic taint analysis to record the operations performed on user input, then reverses these operations to solve for new paths to explore.
-The fuzzer currently records implicit and explicit taint flows between memory and registers.
-When the EFLAGS register is modified, it is checked whether a comparison instruction with tainted operands was the modifier, and if so this is also recorded.
-After an execution it publishes input, output, taint, and mutation data to a driver program, which reasons about possible user input locations and values one byte at a time.
-This means when branch decisions are determined by comparisons at the byte level, the fuzzer can guarantee a new path is taken, provided it can accurately backsolve information about the transformations performed on the byte.
-
-\section{Assumptions and Scoping}
-
-We assume ASLR is disabled for the binary to be fuzzed.
-This allows the program to easily track and compare execution paths.
-We have implemented the technique for the x86-32 architecture, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
-64-bit, ARM vs.
-x86 vs.
-PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
-We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
-The program concretely executes the binary once with the initial test case, recording taint propagation during execution.
-Stdin, stdout, and stderr are recorded for each run, for later analysis.
-After the initial run, the program automatically starts solving each byte by backsolving to try and find new paths.
-
-TODO in above make sure can catch stderr segfaults, segfaults go to shell's stderr, also a signal
-
-Current selective symbolic execution engines still appear to introduce significant overhead, between 6 and 78X overhead more than QEMU for S2E.
-Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others [J, K, L].
-In contrast, basic block counting using Intel Pin, the framework we are leveraging, introduced between 2 and 4X overhead [M].
-However, the pintool needed for our proposed technique introduces greater levels of overhead, since we will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.
-
-We are leveraging Intel PIN to perform dynamic binary instrumentation.
-We are testing dummy programs with many paths that are easy to backsolve, similar to the example above.
-A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
-
-There are allowable situations in programs which are outside the scope of this program.
-For instance, programs can loop forever [X].
-These can be dealt with using reasonable heuristics, fuzzers tend to simply count loops and terminate after a set threshold is reached, and could be the subject of future research.
-
-% TODO We then plan to test against S2E and Peach Fuzzer [Z].
-
-\section{Implementation}
-
-We implement dynamic taint analysis for files as input sources.
-We are basing our implementation of DTA on Jonathan Salwan\'s work [N].
-Currently we instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
-We instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles each instruction.
-Each instruction is handled differently based upon the following criteria:
-
-\begin{itemize}
-	\item Is the instruction a conditional jump?
-	\item Is the first operand a memory location or a register?
-	\item Is the first operand read or written?
-	\item Is the first (second if applicable) operand tainted?
-\end{itemize}
-
-For example, move operations involving an untainted first operand and a tainted second operand generally spread taint, while those with a tainted first operand and an untainted second operand remove taint.
-Tainted branches trigger the backsolving technique.
-Various precautions, such as removing taint for an instruction like "xor eax, eax", must be taken.
-Lossy operations, like shifts, must be handled carefully to be backsolve-able, and checksums and cryptographic operations are not supported.
-
-As a demonstration we have run our fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values.
-If all of these checks pass, then the program outputs a "win" string, otherwise it outputs a "lose" string.
-This can be thought of conceptually as an oracle attack, and is similar to reverse engineering "crackme" exercises.
-Given no knowledge of the secret key, and only able to query an oracle, a successful attack must discover the secret within a reasonable number of guess [CITE?].
-
-After compiling with the Tiny C Compiler, which performs minimal optimization and doesn't add security measures, this binary and a default test file are given as input to Stubble, which will begin to dynamically generate run cases which will explore new paths within the binary.
-These test cases are fed back into the system, which continues to backsolve to find new ways to explore at branches, until there are no tainted bytes left for exploration.
-
-\section{Results}
-
-Secrets of length 1 to 50 were tested at various intervals.
+To test stubble's ability to find new paths to explore in a given binary, programs were written in C, which opened a user-specified file and read several hundred bytes, then compared a subset of these bytes with a secret.
+The binary printed a success condition only if all bytes in user input were observed to be identical to its secret.
+Input to stubble consists of the binary in question and a seed input file.
+Input files were guaranteed to work appropriately (not crash the binary), but did not contain any signficant portion of the secret.
+Since the secret was multi-byte and random, it is possible that the input files contained small subsets of the secret.
+
+Secrets of length 1 to 50 were tested at regular intervals.
 It appears that, aside from some constant overhead, that test cases generated and time required to crack the binary  rise linearly with password length.
@@
 
+TODO explain how brute force fuzzers or regular oracles would solve, add their expected number of attempts to graph.
 (TODO time smaller oracle attacks)
@@
 \end{tikzpicture}
+
+%\chapter{Old Contributions}
+
+%We have implemented a proof of concept fuzzer which uses dynamic taint analysis to record the operations performed on user input, then reverses these operations to solve for new paths to explore.
+The fuzzer currently records implicit and explicit taint flows between memory and registers.
+When the EFLAGS register is modified, it is checked whether a comparison instruction with tainted operands was the modifier, and if so this is also recorded.
+After an execution it publishes input, output, taint, and mutation data to a driver program, which reasons about possible user input locations and values one byte at a time.
+This means when branch decisions are determined by comparisons at the byte level, the fuzzer can guarantee a new path is taken, provided it can accurately backsolve information about the transformations performed on the byte.
+
+%\section{Assumptions and Scoping}
+
+%We assume ASLR is disabled for the binary to be fuzzed.
+This allows the program to easily track and compare execution paths.
+We have implemented the technique for the x86-32 architecture, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
+64-bit, ARM vs.
+x86 vs.
+PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
+We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
+The program concretely executes the binary once with the initial test case, recording taint propagation during execution.
+Stdin, stdout, and stderr are recorded for each run, for later analysis.
+After the initial run, the program automatically starts solving each byte by backsolving to try and find new paths.
+
+%TODO in above make sure can catch stderr segfaults, segfaults go to shell's stderr, also a signal
+
+%Current selective symbolic execution engines still appear to introduce significant overhead, between 6 and 78X overhead more than QEMU for S2E.
+Just QEMU is between 4 and 10 times slower on some benchmarks, closer to 15 on others [J, K, L].
+In contrast, basic block counting using Intel Pin, the framework we are leveraging, introduced between 2 and 4X overhead [M].
+However, the pintool needed for our proposed technique introduces greater levels of overhead, since we will be working at the instruction level instead of the basic block level, requiring more insertions for any given binary.
+
+%We are leveraging Intel PIN to perform dynamic binary instrumentation.
+We are testing dummy programs with many paths that are easy to backsolve, similar to the example above.
+A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
+
+%There are allowable situations in programs which are outside the scope of this program.
+For instance, programs can loop forever [X].
+These can be dealt with using reasonable heuristics, fuzzers tend to simply count loops and terminate after a set threshold is reached, and could be the subject of future research.
+
+% TODO We then plan to test against S2E and Peach Fuzzer [Z].
+
+%\section{Implementation}
+
+%We implement dynamic taint analysis for files as input sources.
+We are basing our implementation of DTA on Jonathan Salwan\'s work [N].
+Currently we instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
+We instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles each instruction.
+Each instruction is handled differently based upon the following criteria:
+
+%\begin{itemize}
+%	\item Is the instruction a conditional jump?
+%	\item Is the first operand a memory location or a register?
+%	\item Is the first operand read or written?
+%	\item Is the first (second if applicable) operand tainted?
+%\end{itemize}
+
+%For example, move operations involving an untainted first operand and a tainted second operand generally spread taint, while those with a tainted first operand and an untainted second operand remove taint.
+Tainted branches trigger the backsolving technique.
+Various precautions, such as removing taint for an instruction like "xor eax, eax", must be taken.
+Lossy operations, like shifts, must be handled carefully to be backsolve-able, and checksums and cryptographic operations are not supported.
+
+%As a demonstration we have run our fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values.
+If all of these checks pass, then the program outputs a "win" string, otherwise it outputs a "lose" string.
+This can be thought of conceptually as an oracle attack, and is similar to reverse engineering "crackme" exercises.
+Given no knowledge of the secret key, and only able to query an oracle, a successful attack must discover the secret within a reasonable number of guess [CITE?].
+
+%After compiling with the Tiny C Compiler, which performs minimal optimization and doesn't add security measures, this binary and a default test file are given as input to Stubble, which will begin to dynamically generate run cases which will explore new paths within the binary.
+These test cases are fed back into the system, which continues to backsolve to find new ways to explore at branches, until there are no tainted bytes left for exploration.
 
@@
 \begin{biosketch}
-This is my biography.
+Clark Wood is a Scholarship for Service recipient studying computer science at Florida State University. His research and interests focus on information security.
 \end{biosketch}

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
working on figures and testing,results

@@
 
+This bears a strong resemblance to the classic oracle attack in cryptography.
+Note, however, that stubble would be unable to reason effectively about cryptographic hashes or encryption because of properties like one-way functions and the avalanche effect.
+
+In a traditional oracle attack, the adversary can derive a secret by testing one character at a time.
+This means an attacker can expect success within $\frac{mn}{2}$ tries on average, where m is the number of character possiblities and n is the length of the secret.
+Dumb fuzzers, which are unable to reason about the execution paths in a binary, do much worse by mutating random bytes and hoping to hit upon the secret by chance.
+This strategy can expect success within $\frac{m^n}{2}$ tries on average, since m-many possibilities must be tested for each byte in the secret independently.
+Stubble performs similarly to an attacker with access to an oracle, although because execution slices are backsolved its time complexity has a smaller constant than $\frac{m}{2}$.
+Expected number of tries is linear with secret length, as with an oracle attack, but stubble requires roughly two tries per byte, instead of having to test for all possible m.
+
 Secrets of length 1 to 50 were tested at regular intervals.
-It appears that, aside from some constant overhead, that test cases generated and time required to crack the binary  rise linearly with password length.
-The constant overhead is probably introduced from overtaint.
+It appears that, aside from some constant overhead, that test cases generated and time required to crack the binary rise linearly with password length as expected.
+The constant overhead is probably introduced from overtaint, which itself likely comes from dynamically linked libraries which are opened and read, and thereby mistakenly introduced as tainted input.
 
@@
 \begin{figure}
-\caption{Fig. 1}
+\caption{Secret Guessing Test Cases}
 \begin{tikzpicture}
@@
 
+\begin{figure}
+\caption{Secret Guessing Time Elapsed}
 \begin{tikzpicture}
@@
 \end{tikzpicture}
+\end{figure}
 

### 2014-03-21 docs/paper/fsuthesis/thesis-template/paper.tex
safety commit
looking at todos, working on contributions like design and implementation

@@
 % Bret Whissel
+% Salwan
 \end{acknowledgments}
@@
 We have implemented this technique in a fuzzer, which is able to reason about large and complex user input and reliably drive program execution down new code paths to explore new portions of compiled code.
+
+%TODO add RE protocol to abstract and intro once implemented
 
@@
 
-\section{Contributions}
+\section{Contribution}
 
@@
 We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
-
-TODO add loop invariants experiments
 
@@
 SAGE uses symbolic execution, and prunes paths taken with a propietary "generational search" algorithm.
-This algorithm prioritizes generating new test cases (TODO does it draw on the test case reduction and expansion algorithms discussed in that one paper???).
+This algorithm prioritizes generating new test cases.
 It takes a set of all constraints and tries negating each constraint independently to generate a new test case.
@@
 
-%\section{Grey-box Evolutionary Fuzzing}
-
-%TODO
+%\section{Grey-box Evolutionary Fuzzing} todo
 
@@
 
-%\section{TODO Difficulties and Limitations}
-
-%TODO Path explosion. Code coverage. Complex file formats which mean you create shallow errors over and over again.
-
-%TODO Limitations - one-way functions like bitwise shifts and checksums, cryptographic hashes. encryption.
-
 %TODO add code examples
@@
 
-\section{Intel PIN}
+\section{Intel Pin}
+
+% TODO check if mention Pin compiles from x86 to x86 adding pintool
 
@@
 
+%TODO this tech helps with complex file formats which mean you create shallow errors over and over again.
+
 \section{Automated Dynamic Slice Backsolving}
@@
 
-Stubble architecture, describe
+TODO Stubble architecture, describe
 why intel pin and not dynamo rio, valgrind, etc.
+
+Stubble consists of a pintool which implements DTA, and a Python driver which keeps track of test cases, input and output recorded during execution, and employs dynamic slice backsolving to drive mutation using taint analyses provided by the DTA pintool.
+Pintools are arbitrary C++ which Pin compiles and inserts into a given binary during instrumentation.
+The driver accepts a valid x86 binary and a seed test case.
+From the seed test case, the driver runs the pintool on the binary with the seed test case as input.
+While the binary runs, the pintool notes when taint in introduced or removed from memory or from registers.
+If a memory location or a register is tainted, then any operations which move this data elsewhere or use this data in an operation spread taint to the appropriate areas.
+Moving untainted data into a previously tainted location removes taint from the system.
+For instance, if the eax register is tainted, then adding eax and ebx and storing the result in ebx will taint the ebx register.
+However, should an operation move the value of ebx to eax, then eax will no longer be tainted.
+
+In addition, whenever stubble encounters an instruction that modifies the EFLAGS register, such as the cmp instruction, it is checked to see whether either of the operands is tainted.
+When this is the case, user input has some level of control over the EFLAGS register, so the appropriate flag in the register is marked tainted.
+When a conditional jump instruction is reached, the corresponding flag of which is tainted, stubble begins to backsolve with the goal of providing a test case to explore the other side of the branch.
+After an execution it publishes input, output, taint, and mutation data to the driver, which reasons about possible user input locations and values one byte at a time.
+This means when branch decisions are determined by comparisons at the byte level, the fuzzer can guarantee a new path is taken, provided it can accurately backsolve information about the transformations performed on the byte.
+
+%The fuzzer currently records implicit and explicit taint flows between memory and registers.
+When the EFLAGS register is modified, it is checked whether a comparison instruction with tainted operands was the modifier, and if so this is also recorded.
+
+%We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
+The program concretely executes the binary once with the initial test case, recording taint propagation during execution.
+Stdin, stdout, and stderr are recorded for each run, for later analysis.
+After the initial run, the program automatically starts solving each byte by backsolving to try and find new paths.
 
@@
 
+We assume ASLR is disabled for the binary to be fuzzed.
+This allows the program to easily track and compare execution paths.
+We have implemented the technique for the x86-32 architecture, because Intel Pin works on a select few architectures, of which x86 is the most prevalent.
+Since x86 is quite widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
+64-bit, ARM vs.
+x86 vs.
+PowerPC etc.), this should be no issue.
+Compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
+
+Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing.
+Currently, stubble records input, output, taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
+Stubble also keeps track of the mutations which have already been explored.
+Users can grep for interesting conditions like segfaults or unexpected output, then cross reference the test number with the observed taint flow, input file, and particular mutation tested.
+
 \section{Implementation}
@@
 Pintool, python specifics. Binarys, RE
-
-\section{Limitations}
+how i implemented DTA
+
+\section{Challenges}
+
+% undertainting examples, general DTA issues and how we solved.
+
+%TODO Limitations - one-way functions like bitwise shifts and checksums, cryptographic hashes. encryption.
 
@@
 
-TODO explain how brute force fuzzers or regular oracles would solve, add their expected number of attempts to graph.
 (TODO time smaller oracle attacks)
@@
 
-%We have implemented a proof of concept fuzzer which uses dynamic taint analysis to record the operations performed on user input, then reverses these operations to solve for new paths to explore.
-The fuzzer currently records implicit and explicit taint flows between memory and registers.
-When the EFLAGS register is modified, it is checked whether a comparison instruction with tainted operands was the modifier, and if so this is also recorded.
-After an execution it publishes input, output, taint, and mutation data to a driver program, which reasons about possible user input locations and values one byte at a time.
-This means when branch decisions are determined by comparisons at the byte level, the fuzzer can guarantee a new path is taken, provided it can accurately backsolve information about the transformations performed on the byte.
-
 %\section{Assumptions and Scoping}
 
-%We assume ASLR is disabled for the binary to be fuzzed.
-This allows the program to easily track and compare execution paths.
-We have implemented the technique for the x86-32 architecture, because x86 is widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
-64-bit, ARM vs.
-x86 vs.
-PowerPC etc.), since compilers try to adhere to the C standard and vulnerabilities like buffer overflows exist at a C source code level.
-We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
-The program concretely executes the binary once with the initial test case, recording taint propagation during execution.
-Stdin, stdout, and stderr are recorded for each run, for later analysis.
-After the initial run, the program automatically starts solving each byte by backsolving to try and find new paths.
-
-%TODO in above make sure can catch stderr segfaults, segfaults go to shell's stderr, also a signal
+%TODO in above make sure can catch stderr segfaults, segfaults go to shell's stderr, also a signal, test this
 
@@
 
-\section{Testing Harness}
-
-Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing.
-Currently, stubble records input, output, taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
-Stubble also keeps track of the mutations which have already been explored.
-A driver program keeps track of the observed taint which has already been explored, and selects a new byte to mutate.
-Users can grep for interesting conditions like segfaults or unexpected output, then cross reference the test number with the observed taint flow, input file, particular mutation tested.
-
 %Professional fuzzing products, like Peach Fuzzer
@@
 %Currently have results for crackmes, give idea of our fuzzer vs. %peach fuzz, and where i plan to go.
+
+\chapter{Conclusions}
+
+\section{Applications}
+
+TODO ways this technique could be used.
+TODO talk about why parallelization is good.
+
+\section{Future Work}
 

### 2014-03-22 docs/paper/fsuthesis/thesis-template/paper.tex
paper work and idea for strcpy

@@
 \degreeyear{2014}
-\defensedate{XXXXXXX}
+\defensedate{April 19, 2014}
 
@@
 \committeeperson{Zhi Wang}{Professor Directing Thesis}
-%\committeeperson{Beauxeau D'Claune}{Committee Member}
-%\committeeperson{Arlip Zarseeld}{Committee Member}
+%\committeeperson{Xiuwen Liu}{Committee Member}
+%\committeeperson{Robert van Engelen}{Committee Member}
 
@@
 SFS
-% Dr. Wang
-% Bret Whissel
+%Zhi Wang
+%Bret Whissel
 % Salwan
@@
 
-Finding software bugs is a difficult but lucrative endeavour.
-Fuzzing is one technique for finding bugs, particularly exploitable vulnerabilities, employed by both software companies and nation-state actors.
+Finding software bugs is a difficult but lucrative endeavour, and fuzzing is one technique often employed for finding bugs, particularly exploitable vulnerabilities.
 However, when no source code is available, fuzzing complex programs effectively can prove difficult, and as techniques become more sophisticated they require more resources and time.
-We present a technique, automated dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to reason about not only the location of user input bytes which contribute to interesting program behavior like branching, but also the exact byte value necessary to trigger a desire branch condition.
-We have implemented this technique in a fuzzer, which is able to reason about large and complex user input and reliably drive program execution down new code paths to explore new portions of compiled code.
-
-%TODO add RE protocol to abstract and intro once implemented
+We present a technique, automated dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to improve fuzzers' code coverage, without resorting to heavyweight techniques like symbolic execution.
+We demonstrate this technique with a proof of concept fuzzer which explores paths in a binary to effectively reveal a secret, performing an oracle attack without an oracle.
+Our approach requires no source code, no manual instrumentation, and no symbolic execution, and, as our results show, can reliably discover and explore new execution paths in a timely fashion.
+We believe dynamic slice backsolving represents a potentially strong complementary technique for modern fuzzers to implement.
 
@@
 Symbolic execution improves code coverage, helping to guide fuzzers into deeper, more interesting parts of a program.
-DTA and symbolic execution, however, are computationally expensive, which leaves room for refinement of techniques by using the technique more wisely or modifying it.
+Symbolic execution, however, is computationally expensive, with naive implementations running in time exponential to the number of branches [C], which leaves room for refinement by using the technique more wisely or modifying it.
 Our technique uses DTA to hopefully achieve greater code coverage than random testing, without having to convert code to an intermediate representation or outsource constraints to a solver like symbolic execution.
@@
 
-\section{Contribution}
-
 Because of these downsides, much research tries to attain more reasonable performance by using symbolic execution less or more wisely [J].
@@
 Our implementation of this technique requires no source code, no modification to a binary, no conversion to an IR, and no SMT solvers.
+
+\section{Contribution}
 
@@
 When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
-Stubble is able to reason about large amounts of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is the length of the secret.
-Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
-We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
+
+To test stubble's ability to dynamically discover new branches and generate test cases which will drive future runs down these new branches, we have designed several binaries which receive user input in the form of a file.
+These binaries open and read the file, comparing a subset of the file contents against a secret.
+If the file contains the secret, then a win condition is printed, otherwise a lose condition is printed.
+For the proof of concept, this win condition could be thought of as a segfault, or other interesting condition that suggests an exploitable condition exists.
+We show that stubble is able to discover all paths in the binary, particularly the interesting paths involving the win condition, without any prior knowledge of the secret.
+Stubble works similarly to an oracle attack, able to discover one character within the secret per run, and preserve work across runs to crack the secret in O(n) tests, where n is the secret length in characters.
+In contrast, random byte fuzzers, which exhaustively test all user input bytes which their model declares valid, run indefinitely and have no guarantee of discovering the win condition.
+We have also parallelized stubble at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
+We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing, and that stubble provides a valuable proof of concept for future research into smart fuzzers.
 
@@
 
-\section{Challenges}
+\section{Challenges and Limitations}
 
@@
 
-%TODO Limitations - one-way functions like bitwise shifts and checksums, cryptographic hashes. encryption.
+As a proof of concept, stubble lacks the featurefulness of a complete fuzzer. In particular, understanding more diverse types of user input, such as command line arguments, would prove valuable.
+
+Note that dynamic slice backsolving requires transformations on tainted values to be easily reversible.
+Because of various cryptographic properties, encryption and hashing algorithms are not possible to backsolve.
+In fact, any lossy or not one-to-one operations prove difficult.
+As an example, the UDP checksum algorithm [AP] calculates the checksum of a packet by iterating over a pseudo-header, summing over each octets 16-bit 1's complement.
+Because of the repeating summing, an overflow is possible, and any overflow bits are added in later on.
+This means two non-identical packet headers could result in the same checksum, and so although we can backsolve to the original packet, we cannot make reasonable mutations which will result in the checksum we desire.
 
@@
 \section{Future Work}
+
+% New types of user input like command line arguments. Can get at argv by passing it directly to driver?
 
@@
 	\item [AO] http://www.forbes.com/sites/andygreenberg/2012/03/23/shopping-for-zero-days-an-price-list-for-hackers-secret-software-exploits/
+	\item [AP] Braden, R., Borman, D., and C. Partridge, "Computing the Internet checksum", RFC 1071, September 1988.
 

### 2014-03-22 MyPinToolStrcpy/clean.sh

@@ -1,0 +1,7 @@
+#!/bin/bash -x
+rm -f input/input.* output/output.* taint/taint.* mutations/mutation.*
+rm -f results.out file.out taint.out
+rm -f buffer.out.*
+cp fileLose.txt inputFile.txt
+echo > taint/explored.0
+

### 2014-03-22 MyPinToolStrcpy/driver.py

@@ -1,0 +1,133 @@
+# Driver to decide how to mutate
+
+import os, shutil
+import subprocess
+from operator import itemgetter
+
+
+def test(inputFile, taintFile, seed = ('0', '0', '0') ):
+
+    # First time, don't mutate
+    if seed != ('0', '0', '0'):
+        mutate(inputFile, seed)
+    else:
+        print('Initial run')
+    
+    # command for subprocess, pintool
+    cmd =   [   
+        '../pin/pin', 
+        '-t', 'obj-ia32/MyPinTool.so', 
+        #'--', '../vulnerable_programs/trivial/a.out', inputFile
+        #'--', './a.out', inputFile
+        #'--', './simpleCrackme', inputFile
+        #'--', './simpleCrackme2', inputFile
+        '--', './simpleCrackme50', inputFile
+        #'--', './strcpy', inputFile
+        #'--', 'ls'
+    ]
+
+    # Which test are we running? 
+    testNumber = getTestNumber('./taint/')
+    print 'Running test #' + str(testNumber), 'based on mutation seed', seed, '...' 
+
+    # One iteration of pintool, generates new (input.txt, taint.out) pair
+    outputFile = open('./file.out', 'w')
+    p1 = subprocess.Popen(cmd, stdout=outputFile)
+    p1.wait()
+
+    # Find which taint are new
+    # input -> input/ and mutated
+    # taint -> taint/
+    explored        =   open('./taint/explored.0', 'r').read().split()
+    exploredFile    =   open('./taint/explored.0', 'a')
+    taint           =   open(taintFile, 'r').read().split()
+
+    newTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in taint}
+    exploredTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in explored}
+
+    # Set difference
+    newTaint = {x: newTaintDict[x] for x in newTaintDict if x not in exploredTaintDict.keys()} 
+
+    # Copy taint and append latest taint to explored
+    recordResults(inputFile, outputFile, newTaint, seed, testNumber) 
+    exploredFile.write(':'.join(seed) + "\n")
+
+    # file in format pos:op:arg1:arg2
+    toExplore = [(r, newTaint[r][0], newTaint[r][1]) for r in newTaint]
+
+    toExplore = sorted(toExplore, key=itemgetter(0))
+    return toExplore
+
+# End test
+
+# TODO will need to handle non-character cases for seed[1]
+def mutate(inputFile, seed):
[…]

### 2014-03-22 MyPinToolStrcpy/examples/example3.cpp

@@ -1,0 +1,294 @@
+//
+//  Jonathan Salwan - Copyright (C) 2013-08
+// 
+//  http://shell-storm.org
+//  http://twitter.com/JonathanSalwan
+//
+//  Note: Example 3 - http://shell-storm.org/blog/Taint-analysis-with-Pin/
+//        Spread the taint in memory/registers and follow your data.
+//
+
+#include "pin.H"
+#include <asm/unistd.h>
+#include <fstream>
+#include <iostream>
+#include <list>
+
+std::list<UINT64> addressTainted;
+std::list<REG> regsTainted;
+
+INT32 Usage()
+{
+    cerr << "Ex 3" << endl;
+    return -1;
+}
+
+bool checkAlreadyRegTainted(REG reg)
+{
+  list<REG>::iterator i;
+
+  for(i = regsTainted.begin(); i != regsTainted.end(); i++){
+    if (*i == reg){
+      return true;
+    }
+  }
+  return false;
+}
+
+VOID removeMemTainted(UINT64 addr)
+{
+  addressTainted.remove(addr);
+  std::cout << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
+}
+
+VOID addMemTainted(UINT64 addr)
+{
+  addressTainted.push_back(addr);
+  std::cout << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
+}
+
+bool taintReg(REG reg)
+{
+  if (checkAlreadyRegTainted(reg) == true){
+    std::cout << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
+    return false;
+  }
+
+  switch(reg){
+
+    case REG_EAX:  regsTainted.push_front(REG_EAX); 
+    case REG_AX:   regsTainted.push_front(REG_AX); 
+    case REG_AH:   regsTainted.push_front(REG_AH); 
+    case REG_AL:   regsTainted.push_front(REG_AL); 
+         break;
+
+    case REG_EBX:  regsTainted.push_front(REG_EBX);
+    case REG_BX:   regsTainted.push_front(REG_BX);
+    case REG_BH:   regsTainted.push_front(REG_BH);
+    case REG_BL:   regsTainted.push_front(REG_BL);
+         break;
+
+    case REG_ECX:  regsTainted.push_front(REG_ECX);
[…]

### 2014-03-22 MyPinToolStrcpy/examples/taint_example_3.h

@@ -1,0 +1,256 @@
+unordered_map<ADDRINT, BOOL> AddressTaintMap;
+unordered_map<ADDRINT, BOOL> RegisterTaintMap;
+std::ofstream TaintFile;
+
+bool checkAlreadyRegTainted(REG reg)
+{
+    if (RegisterTaintMap.count(reg) > 0) {
+      return true;
+    }
+  return false;
+}
+
+VOID removeMemTainted(UINT32 addr)
+{
+    AddressTaintMap.erase(addr);
+  TaintFile << std::hex << "\t\t\t" << addr << " is now freed" << std::endl;
+}
+
+VOID addMemTainted(UINT32 addr)
+{
+    AddressTaintMap[addr] = false;
+  TaintFile << std::hex << "\t\t\t" << addr << " is now tainted" << std::endl;
+}
+
+bool taintReg(REG reg)
+{
+  if (checkAlreadyRegTainted(reg) == true){
+    TaintFile << "\t\t\t" << REG_StringShort(reg) << " is already tainted" << std::endl;
+    return false;
+  }
+
+  switch(reg){
+
+    case REG_EAX:  RegisterTaintMap.insert(REG_EAX); 
+    case REG_AX:   RegisterTaintMap.insert(REG_AX); 
+    case REG_AH:   RegisterTaintMap.insert(REG_AH); 
+    case REG_AL:   RegisterTaintMap.insert(REG_AL); 
+         break;
+
+    case REG_EBX:  RegisterTaintMap.insert(REG_EBX);
+    case REG_BX:   RegisterTaintMap.insert(REG_BX);
+    case REG_BH:   RegisterTaintMap.insert(REG_BH);
+    case REG_BL:   RegisterTaintMap.insert(REG_BL);
+         break;
+
+    case REG_ECX:  RegisterTaintMap.insert(REG_ECX);
+    case REG_CX:   RegisterTaintMap.insert(REG_CX);
+    case REG_CH:   RegisterTaintMap.insert(REG_CH);
+    case REG_CL:   RegisterTaintMap.insert(REG_CL);
+         break;
+
+    case REG_EDX:  RegisterTaintMap.insert(REG_EDX); 
+    case REG_DX:   RegisterTaintMap.insert(REG_DX); 
+    case REG_DH:   RegisterTaintMap.insert(REG_DH); 
+    case REG_DL:   RegisterTaintMap.insert(REG_DL); 
+         break;
+
[…]

### 2014-03-22 MyPinTool/driver.py
working on stubble framework to release for DTA

@@ -4,11 +4,12 @@ import os, shutil
 import subprocess
 from operator import itemgetter
 
+seed_value = ('0', '0', '0')
 
-def test(inputFile, taintFile, seed = ('0', '0', '0') ):
+def test(inputFile, taintFile, seed = seed_value):
 
     # First time, don't mutate
-    if seed != ('0', '0', '0'):
+    if seed != seed_value:
         mutate(inputFile, seed)
     else:
         print('Initial run')
@@ -92,7 +93,7 @@ def recordResults(inputFile, outputFile, taintSet, mutation, n):
     shutil.copy(outputFile.name, './output/output.' + str(n) )
 
     # Record mutation n (TODO and it's metadata or tree structure)
-    if mutation != ('0', '0', '0'):
+    if mutation != seed_value:
         open('./mutations/mutation.' + str(n), 'w').write(':'.join(mutation))
     
 

### 2014-03-22 MyPinToolStrcpy/MyPinTool.cpp

@@ -47,7 +47,7 @@ bool IN_MAIN = false;
 /* ===================================================================== */
 /* User Libraries */
 /* ===================================================================== */
-#include "FollowExecution.h"
+//#include "FollowExecution.h"
 //#include "buffer_linux.h"
 //#include "DTA.h"
 //#include "FindUseAfterFree.h"
@@ -57,26 +57,43 @@ bool IN_MAIN = false;
 /* Instrumentation routines                                              */
 /* ===================================================================== */
 
-// Instrument main function, this starts the other instrumentation objects.
-/*
-VOID WatchMain(IMG img, VOID *v)
+// Instrument strcpy
+
+CHAR_PTR (*fptrstrcpy)(CHAR_PTR __dest, const CHAR_PTR __src);
+
+CHAR_PTR  mystrcpy(CHAR_PTR __dest, const CHAR_PTR __src) 
 {
-    // TODO might this work better?
-    for (IMG img = APP_ImgHead(); IMG_Valid(img); img = IMG_Next(img)) {
-        if (IMG_IsMainExecutable(img)) {
-            IMG_AddInstrumentFunction(LogMain, 0);
-        }
-    }
+    OutFile << CurrentTime() << "mystrcpy called " << endl;
+    OutFile.flush();
+    CHAR_PTR  res = fptrstrcpy(__dest, __src);
 
+    return res;
 }
-*/
 
+// Image load callback - inserts the probes.
+void ImgLoad(IMG img, VOID_PTR v) {
+    // Called every time a new image is loaded
+    if ((IMG_Name(img).find("libc.so") != string::npos)
+            || (IMG_Name(img).find("LIBC.SO") != string::npos)
+            || (IMG_Name(img).find("LIBC.so") != string::npos)) 
+    {
+
+        RTN rtnstrcpy = RTN_FindByName(img, "strcpy");
+        if (RTN_Valid(rtnstrcpy) && RTN_IsSafeForProbedReplacement(rtnstrcpy))
+        {
+            OutFile << CurrentTime() << "Inserting probe for strcpy at " << RTN_Address(rtnstrcpy) << endl;
+            OutFile.flush();
+            AFUNPTR fptr = (RTN_ReplaceProbed(rtnstrcpy, AFUNPTR(mystrcpy)));
+            fptrstrcpy = (CHAR_PTR  (*)(CHAR_PTR , const CHAR_PTR ))fptr;
+        }
+
+    }
 
[…]

### 2014-03-22 Stubble/MyPinTool.cpp

@@ -1,0 +1,97 @@
+/*BEGIN_LEGAL 
+Intel Open Source License 
+
+Copyright (c) 2002-2013 Intel Corporation. All rights reserved.
+ 
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are
+met:
+
+Redistributions of source code must retain the above copyright notice,
+this list of conditions and the following disclaimer.  Redistributions
+in binary form must reproduce the above copyright notice, this list of
+conditions and the following disclaimer in the documentation and/or
+other materials provided with the distribution.  Neither the name of
+the Intel Corporation nor the names of its contributors may be used to
+endorse or promote products derived from this software without
+specific prior written permission.
+ 
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE INTEL OR
+ITS CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+END_LEGAL */
+
+#include "pin.H"
+#include <asm/unistd.h>
+#include <fstream>
+#include <iostream>
+#include <list>
+#include <string>
+#include <unordered_map>
+using namespace std;
+
+/* ===================================================================== */
+/* Global Variables */
+/* ===================================================================== */
+
+
+/* ===================================================================== */
+/* User Libraries */
[…]

### 2014-03-22 Stubble/Stubble.h

@@ -1,0 +1,118 @@
+// Stubble.h
+// http://en.wikibooks.org/wiki/X86_Assembly/Control_Flow and the book in general is very helpful
+
+#include <sstream>
+#include <algorithm>
+#include <iterator>
+#include <vector>
+#include <unordered_map>
+#include <list>
+#include <unordered_map>
+
+int insCount = 0;
+list<UINT32> addressTainted;
+list<REG> regsTainted;
+
+UINT32 EFLAGS;
+//INS last_instruction;
+//BOOL taintedCmp = false;
+
+// File for recording taint propagation
+ofstream CondBranchFile;
+ofstream FlagsFile;
+
+// CATEGORIES and ICLASSes to consider
+//XED_CATEGORY_CMOV all cond. move instructions
+
+/* ===================================================================== */
+/* Check instructions that modify EFLAGS                                 */
+/* ===================================================================== */
+// NOTE: this catches the initial change from EFLAGS is 0 to a valid EFLAGS, is it always 514?
+VOID ModifiesEflags(ADDRINT ins, INT32 branchTaken, string insDis, CONTEXT* context) {
+
+    UINT32 tmp_flags = PIN_GetContextReg(context, REG_EFLAGS);
+
+    if (EFLAGS != tmp_flags) {
+        FlagsFile << insDis << ":\t" << PIN_GetContextReg(context, REG_EFLAGS) << endl;
+
+        EFLAGS = tmp_flags;
+    }
+}
+
+/* ===================================================================== */
+/* Check conditional branch instructions                                 */
+/* ===================================================================== */
+VOID ConditionalBranch(ADDRINT ins, INT32 branchTaken, string insDis) {
+
+    CondBranchFile << insDis << endl;
+}
+
+/*
+    // TODO PREDICATE_ZERO to get ZF == 0 or cases for all jumps and backsolve
+    //if (INS_Opcode(ins) == XED_ICLASS_JNZ) {
+        
+    //}
+    if (INS_OperandCount(ins) > 1 && INS_MemoryOperandIsRead(ins, 0) && INS_OperandIsReg(ins, 0)) {
+        INS_InsertCall(
+    else if ( (INS_OperandCount(ins) > 1 && INS_MemoryOperandIsWritten(ins, 0) ) ) {
[…]

### 2014-03-22 Stubble/driver.py

@@ -1,0 +1,134 @@
+# Driver to decide how to mutate
+
+import os, shutil
+import subprocess
+from operator import itemgetter
+
+seed_value = ('0', '0', '0')
+
+def test(inputFile, taintFile, seed = seed_value):
+
+    # First time, don't mutate
+    if seed != seed_value:
+        mutate(inputFile, seed)
+    else:
+        print('Initial run')
+    
+    # command for subprocess, pintool
+    cmd =   [   
+        '../pin/pin', 
+        '-t', 'obj-ia32/MyPinTool.so', 
+        #'--', '../vulnerable_programs/trivial/a.out', inputFile
+        #'--', './a.out', inputFile
+        #'--', './simpleCrackme', inputFile
+        #'--', './simpleCrackme2', inputFile
+        '--', './simpleCrackme50', inputFile
+        #'--', './strcpy', inputFile
+        #'--', 'ls'
+    ]
+
+    # Which test are we running? 
+    testNumber = getTestNumber('./taint/')
+    print 'Running test #' + str(testNumber), 'based on mutation seed', seed, '...' 
+
+    # One iteration of pintool, generates new (input.txt, taint.out) pair
+    outputFile = open('./file.out', 'w')
+    p1 = subprocess.Popen(cmd, stdout=outputFile)
+    p1.wait()
+
+    # Find which taint are new
+    # input -> input/ and mutated
+    # taint -> taint/
+    explored        =   open('./taint/explored.0', 'r').read().split()
+    exploredFile    =   open('./taint/explored.0', 'a')
+    taint           =   open(taintFile, 'r').read().split()
+
+    newTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in taint}
+    exploredTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in explored}
+
+    # Set difference
+    newTaint = {x: newTaintDict[x] for x in newTaintDict if x not in exploredTaintDict.keys()} 
+
+    # Copy taint and append latest taint to explored
+    recordResults(inputFile, outputFile, newTaint, seed, testNumber) 
+    exploredFile.write(':'.join(seed) + "\n")
+
+    # file in format pos:op:arg1:arg2
+    toExplore = [(r, newTaint[r][0], newTaint[r][1]) for r in newTaint]
+
+    toExplore = sorted(toExplore, key=itemgetter(0))
+    return toExplore
+
+# End test
+
+# TODO will need to handle non-character cases for seed[1]
[…]

### 2014-03-22 vulnerable_programs/trivial/strcpy.c

@@ -14,8 +14,10 @@ int main (int argc, char *argv[])
     char str1[20];
     int res = read(fd, buf, 20);
 
+    strcpy(str1, buf);
 
     // Vuln. condition
+    /*
     if (buf[10] == 'A') {
         while (read(fd, buf, 50) > 0) {
             strcat(str1, buf);
@@ -27,6 +29,7 @@ int main (int argc, char *argv[])
     else {
         strcpy(str1, "Didn't work");
     }
+    */
 
     printf("%s\n",str1);
     close(fd);

### 2014-03-22 Stubble/Stubble.h
got a good idea for monitoring eflags

@@ -8,6 +8,7 @@
 #include <unordered_map>
 #include <list>
 #include <unordered_map>
+#include <xed-flag-enum.h>
 
 int insCount = 0;
 list<UINT32> addressTainted;
@@ -32,7 +33,8 @@ VOID ModifiesEflags(ADDRINT ins, INT32 branchTaken, string insDis, CONTEXT* cont
 
     UINT32 tmp_flags = PIN_GetContextReg(context, REG_EFLAGS);
 
-    if (EFLAGS != tmp_flags) {
+    //if (EFLAGS != tmp_flags && tmp_flags & XED_FLAG_df) {
+    if (EFLAGS != tmp_flags && tmp_flags & XED_FLAG_of) {
         FlagsFile << insDis << ":\t" << PIN_GetContextReg(context, REG_EFLAGS) << endl;
 
         EFLAGS = tmp_flags;

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
read over hard copy and made some changes

@@
 We believe dynamic slice backsolving represents a potentially strong complementary technique for modern fuzzers to implement.
+In addition, we plan to release and continue development on Stubble's DTA framework, since we not aware of many freely available and active projects.
 
@@
 These fuzzers vary in purpose and sophistication.
-The simplest of fuzzers may have little understanding of the program it intends to fuzz, merely changing random bytes in user input and monitoring for interesting situations which suggest a bug has been found, such as segmentation faults.
+The simplest of fuzzers may have little or no understanding of the program it intends to fuzz, merely changing random bytes in user input and monitoring for interesting situations which hint at bugs, such as segmentation faults.
 A log is produced, which can be analyzed by a programmer at a later date to try and identify the source of the crash.
@@
 In order to fuzz more smartly, researchers employ several techniques, two of which are significant for this paper.
-Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing.
+Dynamic taint analysis, or DTA, provides valuable information for guided fuzzing.
 DTA is a form of dynamic analysis, which marks user input as tainted at some level of granularity, and follows this taint as it propagates through the binary.
-Certain, task-dependent sinks are identified, and if taint flows to one of these sinks, a trace of program execution allows analysis to follow how taint sources are linked to these sinks.
-Symbolic execution first runs a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of solver which decides what values the element should given the recorded conditions.
+Certain, task-dependent sinks are identified, and if taint flows to one of these sinks, a trace of program execution allows analysts to follow how taint sources are linked to these sinks.
+Symbolic execution first runs a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of constraint solver which decides what values the element should given the recorded conditions.
 Symbolic execution improves code coverage, helping to guide fuzzers into deeper, more interesting parts of a program.
-Symbolic execution, however, is computationally expensive, with naive implementations running in time exponential to the number of branches [C], which leaves room for refinement by using the technique more wisely or modifying it.
+Symbolic execution, however, is computationally expensive, with naive implementations running in time exponential to the number of branches [C], and often requires source code availability and modification, which leaves room for refinement.
 Our technique uses DTA to hopefully achieve greater code coverage than random testing, without having to convert code to an intermediate representation or outsource constraints to a solver like symbolic execution.
@@
 	\item Must convert code to an intermediate representation
-	\item Must emulate the IR in a virtual machine
-	\item Outsources constraint solving to heavyweight SMT solvers
+	\item Outsources constraint solving to heavyweight satisfiability solvers
 \end{itemize}
@@
 As the native program executes, we dynamically instrument the binary and record execution slices.
-Memory accesses, loads and stores, and transformations of tainted bytes are recorded, and then used to backsolved to give exact byte values and locations to explore in future runs.
+Memory accesses, loads and stores, and transformations of tainted bytes are recorded, and then used to backsolve to give exact byte values and locations to explore in future runs.
 Our implementation of this technique requires no source code, no modification to a binary, no conversion to an IR, and no SMT solvers.
@@
 Our technique, automated dynamic slice backsolving, uses dynamic taint analysis to watch user input.
-As user input is introduced, each byte is tracked separately and, when the program transforms or manipulates user input, those transformations are recorded.
-When branches which depend upon user input are reached, the recorded transformations, if possible, are reversed, backsolving for a new value of a particular byte in user input which will lead execution down a different path in the binary.
+As user input is introduced, each byte is tracked separately and, when the program transforms, uses, or moves user input, those actions are recorded.
+When branches which depend upon user input are reached, the recorded slice, if possible, are reversed, backsolving for a new value of a particular byte in user input which will lead execution down a different path in the binary.
 After execution finishes, input test cases are mutated to reflect this new information, and a new execution test runs.
@@
 
-We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries.
+We have implemented this technique in a proof of concept fuzzer, Stubble, which operates on x86 programs.
 Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program.
@@
 
-To test stubble's ability to dynamically discover new branches and generate test cases which will drive future runs down these new branches, we have designed several binaries which receive user input in the form of a file.
+To test Stubble's ability to dynamically discover new branches and generate test cases which will drive future runs down these new branches, we have designed several binaries which receive user input in the form of a file.
 These binaries open and read the file, comparing a subset of the file contents against a secret.
@@
 In contrast, random byte fuzzers, which exhaustively test all user input bytes which their model declares valid, run indefinitely and have no guarantee of discovering the win condition.
-We have also parallelized stubble at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
+We also present a key observation for improving path exploration in the x86 architecture, namely the finite number of conditional branch statements and instructions which modify the flags which branch statements use.
+Targetting these instructions specifically pays dividends.
+Lastly, we have also parallelized Stubble at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
 We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing, and that stubble provides a valuable proof of concept for future research into smart fuzzers.
@@
 When user input is detected, it is marked as tainted at the byte level.
-This means that if user input is conceptualized as a stream of bytes $b_0,b_1,...,b_n$, then the first byte is considered separate from the separate byte, and each is individually followed throughout program execution.
+This means that if user input is conceptualized as a stream of bytes $b_0,b_1,...,b_n$, then the first byte is considered separate from the second byte and so on, with each byte individually followed throughout program execution.
 This level of granularity introduces significantly more overhead than binary tainting, which marks bytes as either tainted or not tainted, but provides far greater detail into which bytes of user input affect which parts of a program.
@@
 Once user input is captured and marked tainted, any memory accesses, loads and stores, and transformations of tainted bytes are recorded as they are encountered.
-This creates a slice of moves and alterations to the bytes, which can be followed like a trail of breadcrumbs back to the original position of the byte.
+This creates a slice of operations involving the tainted bytes, which can be followed like a trail of breadcrumbs back to the original position of the byte.
 This continues as the program executes until a conditional branch is reached.
 When a conditional branch instruction is reached, it is either taken or not taken, based upon the value of some comparison.
-If this branch depends upon tainted values, which have descended in one way or another from user input, then there is a strong possibility that the "road not taken" could be explored if only user input looked appropriate.
-In the case where any transformations to user input are reversible, we can backsolve these transformations and, based upon the comparison, modify the byte value so that it leads to the complement of the previous branch condition.
+If the branch condition depends upon tainted values, which have descended in one way or another from user input, then there is a strong possibility that the "road not taken" could be explored if only user input looked appropriate.
+In the case where all transformations to user input are reversible, we can backsolve these transformations and, based upon the comparison, modify the byte value so that it leads to the complement of the previous branch condition.
 Not only this, we can identify which byte $b_0,b_1,...,b_n$ to modify, since we have followed each byte from their introduction.
@@
 Our contribution is the realization of this idea for a subset of cases, and the automation of solving these slices.
-Our hope is that by solving these slices automatically, we can identify not only the exact location but also the exact value of hot bytes.
+Our hope is that by solving these slices automatically, we can identify not only the exact location but also the relevant values of hot bytes.
 
@@
 inc eax						;transform eax
-mul eax, 5					;transform eax
+mul eax, 7					;transform eax
 cmp eax, 42					;cmp and jmp based on tainted reg value
@@
 
-If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, and we would jump to the memory location 0xBADC0DE.
+If we already had a test case where the value read onto the stack, after the transformations, did not equal 42, then the cmp instruction would not set the zero flag, or ZF, and we would jump to the memory location 0xBADC0DE.
 With dynamic taint analysis in place, we see taint introduced with the read syscall, then moved into the eax register (which is subsequently tainted).
@@
 
-FROM INTRO
-We have implemented this technique in a proof of concept fuzzer, stubble, which operates on x86 binaries.
+We have implemented this technique in a proof of concept fuzzer, Stubble, which operates on x86 binaries.
 Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program.
 Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks.
-When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
+When a tainted branch is found, Stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path of that explored in the current execution.
 Stubble is able to reason about large amounts of bytes of user input, for instance by performing oracle attacks on binaries which check user input against large secrets, requiring O(n) test cases to solve the secret with no previous information, where n is the length of the secret.
 Stubble has also been parallized at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
-We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing.
-END FROM INTRO
 
@@
 
-%The fuzzer currently records implicit and explicit taint flows between memory and registers.
-When the EFLAGS register is modified, it is checked whether a comparison instruction with tainted operands was the modifier, and if so this is also recorded.
-
-%We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
-The program concretely executes the binary once with the initial test case, recording taint propagation during execution.
-Stdin, stdout, and stderr are recorded for each run, for later analysis.
-After the initial run, the program automatically starts solving each byte by backsolving to try and find new paths.
+This is made possible by a key observation about the x86 architecture.
+There are a finite number of conditional branch instructions, which branch based upon the value of one or a combination of flags located in the EFLAGS register.
+In particular, the carry, overflow, parity, sign, and zero flags (CF, OF, PF, SF, ZF) are used to determine whether or not to branch.
+For example, the je, or jump if equal, instruction branches when the zero flag is set, while the jg, or jump if greater than, instruction branches when the zero flag is unset and the sign and overflow flags are equal.
+There are also a limited number of instructions which modify these five flags, and some instructions modify these flags unconditionally, but always setting, unsetting, or toggling them.
+Thus, we can monitor these flags in the EFLAGS register, and only must take note of the last tainted instruction that modified these flags, since untainted instructions cannot be controlled by user input and overwritten taint instructions cannot effect the branch instructions.
+This introduces little additional overhead, since we already must monitor each instruction executed to watch for track taint.
 
@@
 This allows the program to easily track and compare execution paths.
-We have implemented the technique for the x86-32 architecture, because Intel Pin works on a select few architectures, of which x86 is the most prevalent.
+We have implemented the technique for the x86-32 architecture, because Intel Pin works on a few select architectures, of which x86 is the most prevalent.
 Since x86 is quite widespread, and vulnerabilities resulting from unsafe C code should persist across binaries, regardless of both the size and flavor of architecture (32 vs.
@@
 
+We also assume the presence of an algorithm which will detect an exploitable condition, provided it is given the proper binary and input to the binary, and an initial test case.
+For detecting real exploits, something like monitoring when tainted values overwrite the EIP register would be valuable.
+For the proof of concept we use a win condition hard coded into the input binary.
+
 Fuzzers require intuitive but powerful test harnesses, so that users can easily control how a binary is fuzzed and understand the results of fuzz testing.
-Currently, stubble records input, output, taint for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
+Currently, stubble records input, output, and taint explored for each test executed, appending an auto-incrementing id to log files and separating results at the directory level.
 Stubble also keeps track of the mutations which have already been explored.
@@
 
-As a proof of concept, stubble lacks the featurefulness of a complete fuzzer. In particular, understanding more diverse types of user input, such as command line arguments, would prove valuable.
+As a proof of concept, stubble lacks the featurefulness of a complete fuzzer.
+In particular, understanding more diverse types of user input, such as command line arguments, would prove valuable.
+Stubble currently only instruments the read syscall.
+When an appropriate input file is opened it marks all bytes read as tainted.
+A more featurefull fuzzer would instrument other system calls which could introduce taint, and would also handle C library functions which are the source of vulnerabilities, like unsafe string copying functions.
 
@@
 
+TODO we assume away shitty loops
+
 \section{Parallelization}
 
-MyPinToolMultiProcess, why process level instead of threads, etc.
+TODO MyPinToolMultiProcess, why process level instead of threads, etc.
+
+We have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
+Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel.
+Results show an expected speedup for an application with decently independent input.
+
+Sequential:
+After several runs, I've seen performance ranging from ~33 seconds to 19 seconds.
+26.12user 7.15system 0:33.42elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+0inputs+1496outputs (0major+1168365minor)pagefaults 0swaps
+
+14.66user 4.67system 0:19.44elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+0inputs+1496outputs (0major+1168305minor)pagefaults 0swaps
+
+Parallel:
+The parallel implementation seems to decrease time by somewhere around half, which makes sense considering the problem is not embarassingly parellel, and Intel Pin may try and use multiple cores during startup.
+30.64user 9.71system 0:10.83elapsed 372\%CPU (0avgtext+0avgdata 12952maxresident)k
+0inputs+816outputs (0major+1368622minor)pagefaults 0swaps
+
+However, we have seen runs as high as ~13 seconds elapsed.
+Since our testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
+We also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
 
@@
 This bears a strong resemblance to the classic oracle attack in cryptography.
-Note, however, that stubble would be unable to reason effectively about cryptographic hashes or encryption because of properties like one-way functions and the avalanche effect.
+Note as mentioned above, that stubble would be unable to reason effectively about cryptographic hashes or encryption because of properties like one-way functions and the avalanche effect.
 
@@
 Stubble performs similarly to an attacker with access to an oracle, although because execution slices are backsolved its time complexity has a smaller constant than $\frac{m}{2}$.
-Expected number of tries is linear with secret length, as with an oracle attack, but stubble requires roughly two tries per byte, instead of having to test for all possible m.
+The expected number of tries is linear with secret length, as with an oracle attack, but stubble requires roughly two tries per byte, instead of having to test for all possible m.
 
@@
 
-\section{Parallelization}
-
-We have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
-Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel.
-Results show an expected speedup for an application with decently independent input.
-
-Sequential:
-After several runs, I've seen performance ranging from ~33 seconds to 19 seconds.
-26.12user 7.15system 0:33.42elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
-0inputs+1496outputs (0major+1168365minor)pagefaults 0swaps
-
-14.66user 4.67system 0:19.44elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
-0inputs+1496outputs (0major+1168305minor)pagefaults 0swaps
-
-Parallel:
-The parallel implementation seems to decrease time by somewhere around half, which makes sense considering the problem is not embarassingly parellel, and Intel Pin may try and use multiple cores during startup.
-30.64user 9.71system 0:10.83elapsed 372\%CPU (0avgtext+0avgdata 12952maxresident)k
-0inputs+816outputs (0major+1368622minor)pagefaults 0swaps
-
-However, we have seen runs as high as ~13 seconds elapsed.
-Since our testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
-We also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
-
-%
-%Currently have results for crackmes, give idea of our fuzzer vs. %peach fuzz, and where i plan to go.
-
 \chapter{Conclusions}
@@
 
+TODO instrument C library routines like strcpy and strcmp.
 % New types of user input like command line arguments. Can get at argv by passing it directly to driver?

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
working through notes i made last few days, adding to paper

@@
 This bears a strong resemblance to the classic oracle attack in cryptography.
+Consider that incorrect guesses drive execution down one of many losing paths.
+If an attacker can discover new paths, decide how to get to them, and continue to drive closer and closer to the goal in a timely fashion, then they are effectively exploring new paths in a similar way to how we want a fuzzer to act.
+Namely, they continuously find and explore new code in the executable, testing over and over for some condition of interest.
 Note as mentioned above, that stubble would be unable to reason effectively about cryptographic hashes or encryption because of properties like one-way functions and the avalanche effect.
+Likewise, checksum, hashing, and encryption aware fuzzing is another, orthogonal topic of interest [T].
 
@@
 
+Some of the work involved in creating and testing Stubble feels spiritually similar to Netzob, a protocol reverse engineering tool which actively and passively infers protcol grammars and state machines [AQ].
+Dynamic slice backsolving could be used to reverse engineer an unknown protcol by driving execution down increasingly newer and deeper paths.
+In order to do this, we must, by definition, more closely approximate valid input with each run, eventually mutating from random bytes to a valid protocol input.
+
 TODO ways this technique could be used.
@@
 
-TODO instrument C library routines like strcpy and strcmp.
-% New types of user input like command line arguments. Can get at argv by passing it directly to driver?
+Significant care has already been invested to keep Stubble easy to understand and maintain.
+Continuing to expand Stubble's functionality and developing it into a mature fuzzer is the long term goal.
+In order for Stubble to be useful to analysts, it must support the Windows operating system, more system calls and C library routines, and more vectors for user input.
+Intel Pin supports Windows, so in theory Stubble is compatible as well.
+In practice, Stubble currently makes assumptions about compilation and operating systems internals which are appropriate for Linux.
+In future development, these would be moved to a Linux branch, and a Windows branch would be forked, with common code re-used between the two.
+Stubble also only instruments the read syscall.
+Its features would need to be greatly expanded to handle both more relevant Linux system calls and their Windows equivalents.
+In addition, some system calls not only return success statuses, but also have side effects, which must be accounted for [C].
+Lastly, the only input vector captured by Stubble currently is a read on a user supplied input file.
+There are many other ways taint could be introduced into a program, such as command line arguments, stdin, and input devices like keyboards and mice.
+Accurately recording alternative sources of user input has proved difficult.
+For example, command line arguments in Linux are pushed onto the stack before the main routine is called.
+If we instrument the main routine, we avoid catching all sorts of noisy reads on files that are unlikely to introduce taint, like system libraries.
+However, this makes argv inaccessible.
+Instrumenting the entire binary, dynamically loaded libraries and all, grabs argv, but introduces lots of noise.
+Better semantic for differentiating between noise and signal will be a necessity, for instance by maintaining a hardcoded list of names and sizes of standard libraries, so that they can be ignored.
+
+TODO Even without reading system resources, there appears to be an issue of overtainting in Stubble's implementation.
 
@@
 
-TODO overtainting, naive implementations had lots of it.
+TODO learned about OS internals
 TODO difficulties with implementation
@@
 	\item [AP] Braden, R., Borman, D., and C. Partridge, "Computing the Internet checksum", RFC 1071, September 1988.
+	\item [AQ] Bossert, Georges, Frédéric Guihéry, and Guillaume Hiet.
+"Netzob: un outil pour la rétro-conception de protocoles de communication." Actes du Symposium sur la sécurité des technologies de l'information et des communications.
+2012.
 

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
various paper deets

@@
 
+TODO
 Pintool, python specifics. Binarys, RE
 how i implemented DTA
+Pin's API
 
@@
 
-TODO Even without reading system resources, there appears to be an issue of overtainting in Stubble's implementation.
+TODO better "vuln disc." conditions like segfaults, taint reaching EIP.
 
@@
 
+TODO RE'd in IDA Pro a lot
 TODO learned about OS internals

### 2014-03-23 Stubble/Stubble.h
figured out how to handle segfaults in python

@@ -29,13 +29,18 @@ ofstream FlagsFile;
 /* Check instructions that modify EFLAGS                                 */
 /* ===================================================================== */
 // NOTE: this catches the initial change from EFLAGS is 0 to a valid EFLAGS, is it always 514?
-VOID ModifiesEflags(ADDRINT ins, INT32 branchTaken, string insDis, CONTEXT* context) {
+VOID ModifiesEflags(ADDRINT ins, string insDis, CONTEXT* context) {
 
     UINT32 tmp_flags = PIN_GetContextReg(context, REG_EFLAGS);
 
     //if (EFLAGS != tmp_flags && tmp_flags & XED_FLAG_df) {
-    if (EFLAGS != tmp_flags && tmp_flags & XED_FLAG_of) {
-        FlagsFile << insDis << ":\t" << PIN_GetContextReg(context, REG_EFLAGS) << endl;
+    if (EFLAGS != tmp_flags) {
+
+        // overflow, sign, zero, carry, and parity flags
+
+        if (tmp_flags & XED_FLAG_of) {
+            FlagsFile << insDis << ":\t" << PIN_GetContextReg(context, REG_EFLAGS) << endl;
+        }
 
         EFLAGS = tmp_flags;
     }
@@ -83,10 +88,7 @@ VOID Instructions(INS ins, VOID *v)
     else if (INS_HasFallThrough(ins) ) {
         INS_InsertCall(ins, IPOINT_AFTER, AFUNPTR(ModifiesEflags),
                        IARG_INST_PTR,
-                       IARG_BRANCH_TAKEN,
                        IARG_PTR, new string(INS_Disassemble(ins)),
-                       //IARG_PTR, new string(INS_Disassemble(last_instruction)),
-                       //IARG_REG_VALUE, REG_EFLAGS,      
                         IARG_CONST_CONTEXT,
                        IARG_END);
     }

### 2014-03-23 Stubble/handle_signals.py

@@ -1,0 +1,15 @@
+from subprocess import Popen, PIPE
+import signal
+
+# Fork and wait for process
+proc = Popen('./a.out', shell=True, stdout=PIPE, stderr=PIPE)
+proc.wait()
+
+# Check return code of process
+returncode = proc.returncode - 128
+
+
+if returncode == signal.SIGSEGV:
+    print 'Segmentation Fault!'
+
+

### 2014-03-23 MyPinTool/driver.py
turns out need to intercept segfaults with pin, python wont catch it

@@ -19,10 +19,10 @@ def test(inputFile, taintFile, seed = seed_value):
         '../pin/pin', 
         '-t', 'obj-ia32/MyPinTool.so', 
         #'--', '../vulnerable_programs/trivial/a.out', inputFile
-        #'--', './a.out', inputFile
+        '--', './a.out', inputFile
         #'--', './simpleCrackme', inputFile
         #'--', './simpleCrackme2', inputFile
-        '--', './simpleCrackme50', inputFile
+        #'--', './simpleCrackme50', inputFile
         #'--', './strcpy', inputFile
         #'--', 'ls'
     ]

### 2014-03-23 Stubble/MyPinTool.cpp

@@ -41,6 +41,7 @@ using namespace std;
 /* ===================================================================== */
 /* Global Variables */
 /* ===================================================================== */
+ofstream SignalFile;
 
 
 /* ===================================================================== */
@@ -50,9 +51,25 @@ using namespace std;
 
 /* ===================================================================== */
 
+
+//typedef BOOL(* LEVEL_PINCLIENT::INTERCEPT_SIGNAL_CALLBACK)(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, const EXCEPTION_INFO *pExceptInfo, VOID *v)
+    
+
+BOOL intercept_signal(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, const EXCEPTION_INFO *pExceptInfo, VOID *v)
+{
+    SignalFile << "[INTERCEPTED]\t" << sig << endl;
+    //SignalFile << EXCEPTION_INFO << endl;
+//print to 'signal.out', move signal.out to signal.#
+    return sig;
+}
+
+
 VOID Fini(INT32 code, VOID *v)
 {
+
     FiniStubble();
+    SignalFile.close();
+
 }
 
 /* ===================================================================== */
@@ -80,10 +97,14 @@ int main(int argc, char *argv[])
         return Usage();
     }
 
-    // Init functions for modules
+    // Init functions for modules and open recording files
     InitStubble();
+    SignalFile.open("signal.out");
 
     PIN_AddFiniFunction(Fini, 0);
+    
+    // Intercept segfault, signal 11
+    PIN_InterceptSignal(11, intercept_signal, 0);
 
     // Never returns
     PIN_StartProgram();

### 2014-03-23 Stubble/clean.sh

@@ -1,7 +1,7 @@
 #!/bin/bash -x
-rm -f input/input.* output/output.* taint/taint.* mutations/mutation.*
-rm -f results.out file.out taint.out
-rm -f buffer.out.*
-cp fileLose.txt inputFile.txt
-echo > taint/explored.0
+#rm -f input/input.* output/output.* taint/taint.* mutations/mutation.*
+#rm -f results.out file.out taint.out
+#rm -f buffer.out.*
+#cp fileLose.txt inputFile.txt
+#echo > taint/explored.0
 

### 2014-03-23 MyPinTool/driver.py
finished testing

@@ -19,8 +19,8 @@ def test(inputFile, taintFile, seed = seed_value):
         '../pin/pin', 
         '-t', 'obj-ia32/MyPinTool.so', 
         #'--', '../vulnerable_programs/trivial/a.out', inputFile
-        '--', './a.out', inputFile
-        #'--', './simpleCrackme', inputFile
+        #'--', './a.out', inputFile
+        '--', './simpleCrackme', inputFile
         #'--', './simpleCrackme2', inputFile
         #'--', './simpleCrackme50', inputFile
         #'--', './strcpy', inputFile

### 2014-03-23 Stubble/MyPinTool.cpp

@@ -51,15 +51,12 @@ ofstream SignalFile;
 
 /* ===================================================================== */
 
-
-//typedef BOOL(* LEVEL_PINCLIENT::INTERCEPT_SIGNAL_CALLBACK)(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, const EXCEPTION_INFO *pExceptInfo, VOID *v)
-    
-
 BOOL intercept_signal(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, const EXCEPTION_INFO *pExceptInfo, VOID *v)
 {
     SignalFile << "[INTERCEPTED]\t" << sig << endl;
-    //SignalFile << EXCEPTION_INFO << endl;
-//print to 'signal.out', move signal.out to signal.#
+//print to 'signal.out', move signal.out to results/signals/signal.#
+    SignalFile << PIN_ExceptionToString(pExceptInfo) << endl;
+
     return sig;
 }
 

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
finished testing and graphs

@@
 \begin{acknowledgments}
-SFS
-%Zhi Wang
+%Zhi Wang, for mentoringship, research, paper writing, sounding board
+
+SFS, for the generous funding, mentoring, networking opportunities which have given me the opportunity to study computer science.
+Specifically my co-principal investigators, Mike Burmester and Xiuwen Liu.
+
 %Bret Whissel
-% Salwan
+Jonathan Salwan, for his pintool code examples.
+
 \end{acknowledgments}
@@
 Stubble dynamically instruments binaries, and automatically generates test files which exercise new paths in the input program.
-Program input, output, and interesting conditions like segfaults are recorded during execution, and taint propagation is recorded from user input sources to branch sinks.
+Program input, output, and interesting conditions like segmentation fault signals are recorded during execution, and taint propagation is recorded from user input sources to branch sinks.
 When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
@@
 
-Stubble consists of a pintool which implements DTA, and a Python driver which keeps track of test cases, input and output recorded during execution, and employs dynamic slice backsolving to drive mutation using taint analyses provided by the DTA pintool.
+Stubble consists of a pintool which implements DTA, and a Python driver which keeps track of test cases, input and output and segfaults recorded during execution, and employs dynamic slice backsolving to drive mutation using taint analyses provided by the DTA pintool.
 Pintools are arbitrary C++ which Pin compiles and inserts into a given binary during instrumentation.
@@
 
-    \node [block, left of=Pintool, node distance=4cm] (input) {input/};    
-    \node [block, below of=Pintool, below of=input, node distance=2cm] (output) {output/};
-    \node [block, right of=output, node distance=4cm] (explored) {explored/};
+    %\node [block, left of=Pintool, node distance=4cm] (input) {input/};    
+    %\node [block, below of=Pintool, below of=input, node distance=2cm] (output) {output/};
+    %\node [block, right of=output, node distance=4cm] (explored) {explored/};
+	\node [block, left of=Pintool, node distance=4cm] (results) {results};
 
@@
     \path [line] (driver) -- (Pintool);
-    \path [line] (Pintool) -- (input);
-    \path [line] (Pintool) -- (output);
-    \path [line] (Pintool) -- (explored);
+    %\path [line] (Pintool) -- (input);
+    %\path [line] (Pintool) -- (output);
+    %\path [line] (Pintool) -- (explored);
+	\path [line] (Pintool) -- (results);    
     \path [line] (Pintool) -- (decide);
@@
     \path [line,dashed] (test case) -- (driver);
-    \path [line, dashed] (explored) -- (decide);
+    %\path [line, dashed] (explored) -- (decide);
 
@@
 
+While finding and executing new code paths is valuable, a fuzzer without a vulnerability condition to monitor for cannot convey meaningful information to an analyst.
+There are many  ways to detect the presence of a possibly exploitable bug, such as watching for tainted data reaching the instruction pointer, or watching program output for strings that suggest error conditions.
+Since program output is saved after each run, this is one possible way to detect vulnerabilities with Stubble, however, we specifically wanted to catch segmentation faults, since these are often raised when data corrupts pointers or overflows buffers or stack frames.
+Stubble monitors for segfaults using the Pin API.
+A signal-intercepting callback function for signal number 11, segmentation fault, is registered before execution is handed off to the fuzzed program.
+When a segfault occurs, information about the exception is made recorded and published in the signals/ directory.
+
 \section{Challenges and Limitations}
@@
 
-(TODO time smaller oracle attacks)
 TODO attacks which transform input first to show ability to backsolve
@@
     		(1,17)
-    		(4,20)
-    		(7,26)
+    		(5,26)
     		(10,28)
@@
     xtick={0,10,20,30,40,50},
-    ytick={0,20,30,40,50,60,80,100,120,140,160,180,200},
+    ytick={0,20,40,60,80,100,120,140,160,180,200},
     ymajorgrids=true,
@@
     coordinates {
-    		(1,0) % TODO time these first couple
-    		(4,0)
-    		(7,0)
-    		(10,0)
-    		(15,0)
-    		(20, 0)
+    		(1,19)
+    		(5,30)
+    		(10,31)
+    		(15,45)
+    		(20, 53)
     		(25, 101) 
@@
     };
+
+% TODO find a way to label these
+
 \end{axis}
@@
 \begin{biosketch}
-Clark Wood is a Scholarship for Service recipient studying computer science at Florida State University. His research and interests focus on information security.
+Clark Wood is a Scholarship for Service recipient studying computer science at Florida State University.
+His research interests include reverse engineering, cryptography, networking and their intersection.
 \end{biosketch}

### 2014-03-23 docs/paper/fsuthesis/thesis-template/paper.tex
no big changes, getting some chocolate before i finish impl, parallel sections and proofread background

@@
 It takes a set of all constraints and tries negating each constraint independently to generate a new test case.
-SAGE then symbolically re-executes the constraint set using TruScan [TODO CITE] [Q].
+SAGE then symbolically re-executes the constraint set using a trace analysis engine [Q].
 Similarly, s2e uses QEMU for instruction set emulation, and then appears to be a strong trend in white-box fuzzing.
-TODO ADV/DIS?
 
@@
 
-%TODO Peach Fuzzer does both, overview with pictures?
-
 %\section{TODO Local vs. Network}
@@
 
-%TODO add code examples
-%http://en.wikipedia.org/wiki/User_Datagram_Protocol#IPv4_Pseudo_Header
-%IDEA write c program to checksum UDP packets and say whether they pass or not, have fuzzer "correct" packets to pass arbitrary, user decided checksum.
-%update: probably will not work without noticeable modification, but could maybe notice the situation and reverse engineer the algorithm, then print it out or start making a lookup table?
+%TODO add code examples?
 
@@
 While finding bugs of any sort enhances software by providing developers the opportunity to fix problems with their programs, finding bugs that lead to exploitable conditions are of special interest.
-A bug is exploitable if it allows adveraries to undermine confidentiality, integrity, or availability [CITE] via avenues such as information disclosure, denial of service, or remote execution of code.
+A bug is exploitable if it allows adveraries to undermine confidentiality, integrity, or availability via avenues such as information disclosure, denial of service, or remote execution of code.
 Because these bugs stand alone as a separate, particularly worrying class, efforts have been made to automate the process of proving whether an identified bug is also a vulnerability which can be exploited.
@@
 
-TODO Mayhem techniques
-
 AEG required source code, where Mayhem needs access only a binary to execute.
@@
 
-TODO similar to Automatic patch-based exploit generation is possible: Techniques and
+%TODO similar to Automatic patch-based exploit generation is possible: Techniques and
 implications, but mine doesn't require a patch?
-
-%\section{TODO Argos: 0-Day Emulator}
 
@@
 \section{Intel Pin}
-
-% TODO check if mention Pin compiles from x86 to x86 adding pintool
 
@@
 
-\subsection{TODO Conversion to an Intermediate Representation}
-
-Used in javascript fuzzer [AD]
-Used in [C].
-Mitigates dealing with side effects, done by PANDA.
-%http://www.cc.gatech.edu/~brendan/tzb_author.pdf
-%http://iris.lib.neu.edu/cgi/viewcontent.cgi?article=1097&context=elec_comp_theses
-
 \chapter{Contributions}
@@
 Our hope is that by solving these slices automatically, we can identify not only the exact location but also the relevant values of hot bytes.
-
-we ignore ....loops, more TODO
 
@@
 
-TODO Stubble architecture, describe
-why intel pin and not dynamo rio, valgrind, etc.
+TODO why intel pin and not dynamo rio, valgrind, etc.
 
@@
 The constant overhead is probably introduced from overtaint, which itself likely comes from dynamically linked libraries which are opened and read, and thereby mistakenly introduced as tainted input.
-
-TODO attacks which transform input first to show ability to backsolve
 
@@
     };     
-
-% TODO find a way to label these
-
 \end{axis}
@@
 
-%\chapter{Old Contributions}
-
-%\section{Assumptions and Scoping}
-
-%TODO in above make sure can catch stderr segfaults, segfaults go to shell's stderr, also a signal, test this
-
+% TODO add these back in?
 %Current selective symbolic execution engines still appear to introduce significant overhead, between 6 and 78X overhead more than QEMU for S2E.
@@
 These can be dealt with using reasonable heuristics, fuzzers tend to simply count loops and terminate after a set threshold is reached, and could be the subject of future research.
-
-% TODO We then plan to test against S2E and Peach Fuzzer [Z].
 

### 2014-03-24 docs/paper/fsuthesis/thesis-template/paper.tex
added some to implementation

@@
 %Bret Whissel
+
 Jonathan Salwan, for his pintool code examples.
@@
 Targetting these instructions specifically pays dividends.
-Lastly, we have also parallelized Stubble at the process level, allowing for an arbitrary number of independent bytes to be reasoned about concurrently.
 We believe automated dynamic slice backsolving is a reasonable complementary technique to dynamic taint analysis and symbolic execution for binary fuzzing, and that stubble provides a valuable proof of concept for future research into smart fuzzers.
@@
 
-INSERT COOL FIGURE
+TODO INSERT COOL FIGURE of custom data structure
 
@@
 TODO
-Pintool, python specifics. Binarys, RE
+python specifics. Binarys, RE
 how i implemented DTA
 Pin's API
+
+We implemented Stubble using Intel Pin.
+Pin instruments binaries by compiling a user-defined pintool and inserting the instrumentation code into the binary, converting directly from the target architecture to the same architecture, ex.
+from x86 to x86.
+The Pin API is very flexible, allowing for instrumentation at a binary-wide to an instruction-by-instruction level, and there exists an active community of developers.
+In particular, we base our work off of [N].
+Because Stubble must reason about every taint propagation, we instrument at the instruction level, which introduces the most overhead.
+In addition to instrumenting each instruction, we also instrument the read system call.
+Taint is introduced when user input is read into memory.
+This section of memory, the contiguous memory addresses from read's buf parameter to buf + count, is marked tainted.
+
+There are two places we consider taint to propagate to and from, namely registers and memory locations.
+We also must record operations that transform tainted data, so that Stubble can backsolve the transformations later.
+We record this data in data structures derived from the vector, list, tuple and unordered\_map data structures from the C++ STL.
+The registers are represented as an enumerated array of tuples of (int, string).
+Registers start with tuples of (-1, ""), signifying that they are untainted.
+When registers become tainted, we insert values of (byteLocation, filename).
+Registers are altered as taint is overwritten or removed from the system, and since they only contain one value at a time, we mark the register as tainted by the specific byte in user input, using its location to refer to it.
+Memory is conceived of as an unordered\_map of ints to (int, string) tuples.
+This is similar to the registers, except the key is the memory location.
+Since there are a small set of registers it makes sense to design an array which contains all of them, but many diverse memory locations may become tainted throughout execution, so we instead use an unordered\_map.
+Memory is marked tainted or untainted similarly to registers.
+Lastly, we must record operations performed on tainted data.
+This is accomplished by representing user input as an array of lists.
+Each list entry is a string, marking one operation performed on the data.
+Stubble cross references each operation with the register and memory data structures to see which byte of user input should be updated with a transaction.
+After execution, a file of transactions for each byte of user input is printed, and the Python driver parses the operations recorded to backsolve new data values for each byte.
 
@@
 
-\section{Parallelization}
-
-TODO MyPinToolMultiProcess, why process level instead of threads, etc.
-
-We have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
+%\section{Parallelization}
+
+%Because Stubble works at the process level, allowing one run to finish before generating a test file for the next, concurrency seems implementable. However, because
+
+%We have implemented a parallel version of the pintool, mp.c, to fork and exec a user-specified number of processes.
 Because a tainted branch may only be reachable based upon previous branches taken, and also because of complex conditions involving loops, the problem is not embarassingly parallel.
@@
 
-Sequential:
-After several runs, I've seen performance ranging from ~33 seconds to 19 seconds.
-26.12user 7.15system 0:33.42elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
-0inputs+1496outputs (0major+1168365minor)pagefaults 0swaps
-
-14.66user 4.67system 0:19.44elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
-0inputs+1496outputs (0major+1168305minor)pagefaults 0swaps
-
-Parallel:
-The parallel implementation seems to decrease time by somewhere around half, which makes sense considering the problem is not embarassingly parellel, and Intel Pin may try and use multiple cores during startup.
-30.64user 9.71system 0:10.83elapsed 372\%CPU (0avgtext+0avgdata 12952maxresident)k
-0inputs+816outputs (0major+1368622minor)pagefaults 0swaps
-
-However, we have seen runs as high as ~13 seconds elapsed.
+%Sequential:
+%After several runs, I've seen performance ranging from ~33 seconds to 19 seconds.
+%26.12user 7.15system 0:33.42elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+%0inputs+1496outputs (0major+1168365minor)pagefaults 0swaps
+
+%14.66user 4.67system 0:19.44elapsed 99\%CPU (0avgtext+0avgdata 12964maxresident)k
+%0inputs+1496outputs (0major+1168305minor)pagefaults 0swaps
+
+%Parallel:
+%The parallel implementation seems to decrease time by somewhere around half, which makes sense considering the problem is not embarassingly parellel, and Intel Pin may try and use multiple cores during startup.
+%30.64user 9.71system 0:10.83elapsed 372\%CPU (0avgtext+0avgdata 12952maxresident)k
+%0inputs+816outputs (0major+1368622minor)pagefaults 0swaps
+
+%However, we have seen runs as high as ~13 seconds elapsed.
 Since our testing environment has 4GB ram and 4 virtual cores, 4 processes seems to give me the best speedup.
@@
 TODO ways this technique could be used.
-TODO talk about why parallelization is good.
 

### 2014-03-24 docs/paper/fsuthesis/thesis-template/paper.tex
added cool figure for dynamic slice backsolving

@@
 \usetikzlibrary{shapes,arrows}
+
+% Source: http://www.texample.net/tikz/examples/simple-flow-chart/
+
+% Define block styles
+\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
+    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
+\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
+    text width=5em, text centered, rounded corners, minimum height=4em]
+\tikzstyle{line} = [draw, -latex']
+\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
+    minimum height=2em]
 
@@
 
-TODO INSERT COOL FIGURE of custom data structure
+% TODO label this
+\begin{tikzpicture}[node distance = 2cm, auto]
+    % Place input bytes
+    \node [block] (b0) {$b_0$};
+    \node [block, right of=b0, node distance=2.2cm] (b1) {$b_1$};
+    \node [block, right of=b1, node distance=2.2cm] (b2) {$b_2$};
+    \node [block, right of=b2, node distance=2.2cm] (bs) {...};
+    \node [block, right of=bs, node distance=2.2cm] (bn) {$b_n$};
+
+	% Place transformation, flag, and branch nodes 
+    \node [cloud, below of=b1] (t10) {$t_0$};
+    \node [cloud, below of=t10, left of=t10] (t11) {$t_1$};
+    \node [cloud, below of=t11, right of=t11] (flag) {flag};
+    \node [cloud, below of=flag] (branch) {branch};
+    \node [cloud, below of=bn] (flag1) {flag};
+    \node [cloud, below of=flag1] (branch1) {branch};
+
+    % Draw edges
+    \path [line] (b1) -- (t10);
+    \path [line] (t10) -- (t11);
+    \path [line] (t11) -- (flag);
+    \path [line] (flag) -- (branch);
+    \path [line] (bn) -- (flag1);
+    \path [line] (flag1) -- (branch1);
+    %\path [line, dashed] (explored) -- (decide);
+
+\end{tikzpicture}
 
@@
 % Source: http://www.texample.net/tikz/examples/simple-flow-chart/
-
-% Define block styles
-\tikzstyle{decision} = [diamond, draw, fill=blue!20, 
-    text width=4.5em, text badly centered, node distance=3cm, inner sep=0pt]
-\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
-    text width=5em, text centered, rounded corners, minimum height=4em]
-\tikzstyle{line} = [draw, -latex']
-\tikzstyle{cloud} = [draw, ellipse,fill=red!20, node distance=3cm,
-    minimum height=2em]
 
@@
 
-TODO
-python specifics. Binarys, RE
-how i implemented DTA
-Pin's API
+% TODO Binarys, RE?
+% TODO Pin's API more details?
 
@@
 Registers are altered as taint is overwritten or removed from the system, and since they only contain one value at a time, we mark the register as tainted by the specific byte in user input, using its location to refer to it.
+The EFLAGS register is a special case, since certain operations set specific flags, it is possible for one operation to taint the carry flag and for another to taint the overflow flag.
+Thus, we treat each of the important bits of EFLAGS as separate entries, with their own tuple devoted to them.
+
 Memory is conceived of as an unordered\_map of ints to (int, string) tuples.
@@
 
+To test Stubble's ability to perform an oracle attack, we prepared C binaries which checked user input against a secret.
+After compiling with the Tiny C Compiler, which performs minimal optimization and doesn't add security measures like stack cookies, this binary and a default test file are given as input to Stubble.
+
 \section{Challenges and Limitations}
-
-% undertainting examples, general DTA issues and how we solved.
 
@@
 
-TODO we assume away shitty loops
-
+% TODO we assume away shitty loops
+%There are allowable situations in programs which are outside the scope of this program.
+For instance, programs can loop forever [X].
+These can be dealt with using reasonable heuristics, fuzzers tend to simply count loops and terminate after a set threshold is reached, and could be the subject of future research.
+
+% TODO undertainting examples, general DTA issues and how we solved.?
+
+% Probably leave this out, parallelization didn't work out well b/c of input dependence
 %\section{Parallelization}
-
-%Because Stubble works at the process level, allowing one run to finish before generating a test file for the next, concurrency seems implementable. However, because
 
@@
 
-%We are leveraging Intel PIN to perform dynamic binary instrumentation.
-We are testing dummy programs with many paths that are easy to backsolve, similar to the example above.
-A C program which uses sequential switch statements to check user input against a secret, when compiled with tcc, which performs very little optimization, is such an example binary.
-
-%There are allowable situations in programs which are outside the scope of this program.
-For instance, programs can loop forever [X].
-These can be dealt with using reasonable heuristics, fuzzers tend to simply count loops and terminate after a set threshold is reached, and could be the subject of future research.
-
 %\section{Implementation}
-
-%We implement dynamic taint analysis for files as input sources.
-We are basing our implementation of DTA on Jonathan Salwan\'s work [N].
-Currently we instrument the read syscall, watching for all reads executed, then tag user input at the byte level and follow it as it moves throughout the binary.
-We instrument binaries at the assembly instruction level using Intel Pin, which dynamically disassembles each instruction.
-Each instruction is handled differently based upon the following criteria:
 
@@
 Various precautions, such as removing taint for an instruction like "xor eax, eax", must be taken.
-Lossy operations, like shifts, must be handled carefully to be backsolve-able, and checksums and cryptographic operations are not supported.
-
-%As a demonstration we have run our fuzzer, Stubble, against various binaries which open a file and check specific bytes in a file for specific character values.
-If all of these checks pass, then the program outputs a "win" string, otherwise it outputs a "lose" string.
-This can be thought of conceptually as an oracle attack, and is similar to reverse engineering "crackme" exercises.
-Given no knowledge of the secret key, and only able to query an oracle, a successful attack must discover the secret within a reasonable number of guess [CITE?].
-
-%After compiling with the Tiny C Compiler, which performs minimal optimization and doesn't add security measures, this binary and a default test file are given as input to Stubble, which will begin to dynamically generate run cases which will explore new paths within the binary.
-These test cases are fed back into the system, which continues to backsolve to find new ways to explore at branches, until there are no tainted bytes left for exploration.
-
-%Professional fuzzing products, like Peach Fuzzer
-
-%\section{Methodology}
-
-%As of this writing we are moving towards fuzzing Linux utilities.
-Results for toy binaries are promising, with "crackme" type programs which ask for a secret being solved in approximately 2*n runs, where n is the length of the secret.
-There is, however, still some overtainting which must be accounted for.
-%\section{Evaluation}
 
@@
 
-\section{Lessons Learned}
-
-TODO RE'd in IDA Pro a lot
-TODO learned about OS internals
-TODO difficulties with implementation
+% TODO not sure if to put this section in?
+%\section{Experience and Lessons Learned}
+
+%TODO RE'd in IDA Pro a lot
+%TODO learned about OS internals
+%TODO difficulties with implementation
 

### 2014-03-24 docs/paper/fsuthesis/thesis-template/paper.tex
done with paper for the day

@@
 
-%TODO add code examples?
-
 \section{Taint-based Fuzzing}
@@
 
-\section{TODO Mayhem, AEG, Exploitable Bugs}
-
-%TODO AEG [I]?
+\section{Mayhem, Exploitable Bugs}
 
@@
 
-AEG required source code, where Mayhem needs access only a binary to execute.
+AEG [I], a previous work into automatically generating exploits given an exploitable condition, required source code, where Mayhem needs access only a binary to execute.
 Mayhem is, however, limited to a subset of all system calls for the operating system it executes on.
@@
 
-%TODO similar to Automatic patch-based exploit generation is possible: Techniques and
-implications, but mine doesn't require a patch?
+%TODO similar to Automatic patch-based exploit generation is possible: Techniques and implications, but mine doesn't require a patch?
 
@@
 Dynamic Taint Analysis, or DTA, provides valuable information for guided fuzzing.
-Symbolic execution improves code coverage by first running a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of SMT solver [CITE] to solve for what value the element should have under certain conditions.
+Symbolic execution improves code coverage by first running a program concretely to gather constraints on a particular element, then executes the program symbolically, giving these constraints over to some kind of SMT solver to solve for what value the element should have under certain conditions.
 Concolic execution, which has spawned out of the desire to use symbolic execution more wisely due to performance constraints, aims for reasonable runtimes while maintaining good code coverage.
@@
 Both might be read in as input to a program, but the former is much more likely to contain malicious data like shellcode trying to exploit a vulnerability.
-Fuzzers have continued to drill down into finer and finer levels of granularity, from assigning everything with a generic binary value of tainted/not tainted to byte and even bit-level marking of which part of user input affected which variable.
-[CITE] [C] Note that this also expands taint's data type from a bit to something larger, and each tainted object requires this tag.
+Fuzzers have continued to drill down into finer and finer levels of granularity, from assigning everything with a generic binary value of tainted/not tainted to byte-level marking of user input [C].
+Note that this also expands taint's data type from a "tainted-not tainted" bit to a something type, and each tainted object requires this tag.
 
@@
 
-TODO TODO TODO [C] considers concolic execution to be when we first execute concretely and THEN execute the same thing symbolically.
+% TODO TODO TODO [C] considers concolic execution to be when we first execute concretely and THEN execute the same thing symbolically.
 Mixed execution is when we execute once with both concrete and symbolic input--make sure other works stand by this distinction.
 
-TODO talk about how this is called many different things, and is a rather amorphous term.
+% TODO talk about how this is called many different things, and is a rather amorphous term.
 
@@
 
-TODO why intel pin and not dynamo rio, valgrind, etc.
+% TODO why intel pin and not dynamo rio, valgrind, etc.
 
@@
     \node [block, below of=driver, node distance=4cm] (Pintool) {Pintool};
-
-    %\node [block, left of=Pintool, node distance=4cm] (input) {input/};    
-    %\node [block, below of=Pintool, below of=input, node distance=2cm] (output) {output/};
-    %\node [block, right of=output, node distance=4cm] (explored) {explored/};
 	\node [block, left of=Pintool, node distance=4cm] (results) {results};
@@
     \path [line] (driver) -- (Pintool);
-    %\path [line] (Pintool) -- (input);
-    %\path [line] (Pintool) -- (output);
-    %\path [line] (Pintool) -- (explored);
 	\path [line] (Pintool) -- (results);    
@@
     \path [line,dashed] (test case) -- (driver);
-    %\path [line, dashed] (explored) -- (decide);
 
@@
 
-% TODO Binarys, RE?
 % TODO Pin's API more details?
@@
 After compiling with the Tiny C Compiler, which performs minimal optimization and doesn't add security measures like stack cookies, this binary and a default test file are given as input to Stubble.
+Secrets ranged in size from 1 to 50 characters.
+We started with secret of one character, embedded in an arbitrary position somewhere within the several hundred byte input file.
+To decide how to implement dynamic slice backsolving at the assembly level, we began by statically disassembling our binaries with IDA Pro [AH].
+The ability to see control flow and instructions at a block level was invaluable during testing and development.
+After succeeding with smaller inputs we gradually increased the size of the secret.
 
@@
 We also tested with 2, 8, and 16 processes but didn't see a comparable speedup.
-
-\section{Testing}
 
@@
 
-Some of the work involved in creating and testing Stubble feels spiritually similar to Netzob, a protocol reverse engineering tool which actively and passively infers protcol grammars and state machines [AQ].
+% TODO more ways DSB and stubble could be used
+
+Dynamic Slice Backsolving would be useful when source code is not accessible, or when a user doesn't wish to instrument source code to symbolically execute a program.
+Other taint trackers and fuzzers could implement this technique, regardless of whether or not they require source code, to improve path exploration and help create useful mutations.
+
+Stubble could prove useful when analysts have access to a binary, but not its source code.
+Running Stubble on such a binary would produce tests which will execute different paths within the binary.
+These tests could be used as part of a test suite, to ensure that as many paths as possible are exercised during testing.
+
+Some of Stubble's functionality feels spiritually similar to Netzob, a protocol reverse engineering tool which actively and passively infers protcol grammars and state machines [AQ].
 Dynamic slice backsolving could be used to reverse engineer an unknown protcol by driving execution down increasingly newer and deeper paths.
-In order to do this, we must, by definition, more closely approximate valid input with each run, eventually mutating from random bytes to a valid protocol input.
-
-TODO ways this technique could be used.
+By doing this, we must, by definition, more and more closely approximate valid input with each run, eventually mutating from random bytes to a valid protocol input.
+As an example, if an unknown protocol begins messages with an arbitrary string of bytes "ABC", an initial run would fail but notice that, had byte zero been "A", then a new branch could be explored.
+The second run would ensure that byte zero was "A", then similarly notice that had byte two been "B", yet a new branch would have been explored, and so on.
 
@@
 
-TODO better "vuln disc." conditions like segfaults, taint reaching EIP.
+There also remains research to be done regarding parallel taint tracking.
+We parallelized stubble at the process level, which resulted in speed improvements commensurate with the number of processes used.
+However, because of data dependencies, our naive implementation would not always discover and backsolve more complicated paths.
+We suspect solving this would require up-front analysis of data dependencies between bytes of user input before each fork off.
+
+%Stubble would also benefit from better algorithms for discovering vulnerable conditions.
+Monitoring for segfaults and track taint to the instruction pointer, are good indicators, but we could also watch for memory accesses out of declared array boundaries and instrument unsafe C functions to monitor, for example, when
+%heap overflows, etc...
 

### 2014-03-24 MyPinToolMultiProcess/mp.c
working out Stubble arch

@@ -37,7 +37,7 @@ int main(int argc, char* argv[])
             args[1] = "-t";
             args[2] = "obj-ia32/MyPinTool.so"; 
             args[3] = "--";
-            args[4] = "./simpleCrackme";
+            args[4] = "./simpleCrackme10";
             args[5] = argv[2 + i];      // input file, generated by python driver
             args[6] = NULL;
 

### 2014-03-24 Stubble/MyPinTool.cpp

@@ -41,16 +41,18 @@ using namespace std;
 /* ===================================================================== */
 /* Global Variables */
 /* ===================================================================== */
-ofstream SignalFile;
+//ofstream SignalFile;
 
 
 /* ===================================================================== */
 /* User Libraries */
 /* ===================================================================== */
-#include "Stubble.h"
+#include "libs/Stubble.h"
+#include "libs/intercept_signals.h"
 
 /* ===================================================================== */
 
+/*
 BOOL intercept_signal(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, const EXCEPTION_INFO *pExceptInfo, VOID *v)
 {
     SignalFile << "[INTERCEPTED]\t" << sig << endl;
@@ -59,13 +61,14 @@ BOOL intercept_signal(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, c
 
     return sig;
 }
+*/
 
 
 VOID Fini(INT32 code, VOID *v)
 {
 
-    FiniStubble();
-    SignalFile.close();
+    fini_stubble();
+    fini_intercept_signals();
 
 }
 
@@ -95,13 +98,14 @@ int main(int argc, char *argv[])
     }
 
     // Init functions for modules and open recording files
-    InitStubble();
-    SignalFile.open("signal.out");
+    init_stubble();
+    init_intercept_signals();
+    //SignalFile.open("signal.out");
 
     PIN_AddFiniFunction(Fini, 0);
     
     // Intercept segfault, signal 11
-    PIN_InterceptSignal(11, intercept_signal, 0);
+    //PIN_InterceptSignal(11, intercept_signal, 0);
 
     // Never returns
     PIN_StartProgram();

### 2014-03-24 Stubble/build.sh

@@ -1,0 +1,6 @@
+#!/bin/bash -x
+
+touch MyPinTool.cpp
+make PIN_ROOT=../pin/ CXX="g++ -std=c++0x"
+../pin/pin -t obj-ia32/MyPinTool.so -- ./a.out
+

### 2014-03-24 Stubble/clean.sh

@@ -4,4 +4,5 @@
 #rm -f buffer.out.*
 #cp fileLose.txt inputFile.txt
 #echo > taint/explored.0
+rm -f ./results/currentrun/*
 

### 2014-03-24 Stubble/libs/Stubble.h

@@ -1,0 +1,127 @@
+#ifndef __STUBBLE_H__ 
+#define __STUBBLE_H__ 
+
+// Stubble.h
+// http://en.wikibooks.org/wiki/X86_Assembly/Control_Flow and the book in general is very helpful
+
+#include <sstream>
+#include <string>
+#include <algorithm>
+#include <iterator>
+#include <vector>
+#include <unordered_map>
+#include <list>
+#include <unordered_map>
+#include <xed-flag-enum.h>
+
+int insCount = 0;
+list<UINT32> addressTainted;
+list<REG> regsTainted;
+
+string results_dir = "./results/currentrun/";
+
+UINT32 EFLAGS;
+//INS last_instruction;
+//BOOL taintedCmp = false;
+
+// File for recording taint propagation
+ofstream CondBranchFile;
+ofstream FlagsFile;
+
+// CATEGORIES and ICLASSes to consider
+//XED_CATEGORY_CMOV all cond. move instructions
+
+/* ===================================================================== */
+/* Check instructions that modify EFLAGS                                 */
+/* ===================================================================== */
+// NOTE: this catches the initial change from EFLAGS is 0 to a valid EFLAGS, is it always 514?
+VOID ModifiesEflags(ADDRINT ins, string insDis, CONTEXT* context) {
+
+    UINT32 tmp_flags = PIN_GetContextReg(context, REG_EFLAGS);
+
+    //if (EFLAGS != tmp_flags && tmp_flags & XED_FLAG_df) {
+    if (EFLAGS != tmp_flags) {
+
+        // overflow, sign, zero, carry, and parity flags
+
+        if (tmp_flags & XED_FLAG_of) {
+            FlagsFile << insDis << ":\t" << PIN_GetContextReg(context, REG_EFLAGS) << endl;
+        }
+
+        EFLAGS = tmp_flags;
+    }
+}
+
+/* ===================================================================== */
+/* Check conditional branch instructions                                 */
+/* ===================================================================== */
+VOID ConditionalBranch(ADDRINT ins, INT32 branchTaken, string insDis) {
+
+    CondBranchFile << insDis << endl;
+}
+
+/*
[…]

### 2014-03-24 Stubble/libs/intercept_signals.h

@@ -1,0 +1,86 @@
+/*BEGIN_LEGAL 
+Intel Open Source License 
+
+Copyright (c) 2002-2013 Intel Corporation. All rights reserved.
+ 
+Redistribution and use in source and binary forms, with or without
+modification, are permitted provided that the following conditions are
+met:
+
+Redistributions of source code must retain the above copyright notice,
+this list of conditions and the following disclaimer.  Redistributions
+in binary form must reproduce the above copyright notice, this list of
+conditions and the following disclaimer in the documentation and/or
+other materials provided with the distribution.  Neither the name of
+the Intel Corporation nor the names of its contributors may be used to
+endorse or promote products derived from this software without
+specific prior written permission.
+ 
+THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+``AS IS'' AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE INTEL OR
+ITS CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+(INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+END_LEGAL */
+
+
+#ifndef __INTERCEPT_SIGNALS_H__ 
+#define __INTERCEPT_SIGNALS_H__ 
+
+#include "pin.H"
+#include <asm/unistd.h>
+#include <fstream>
+#include <iostream>
+#include <list>
+#include <string>
+#include <unordered_map>
+
+/* ===================================================================== */
+/* Global Variables */
[…]

### 2014-03-24 Stubble/Stubble.h
catching writes to registers

@@ -1,122 +1,0 @@
-// Stubble.h
-// http://en.wikibooks.org/wiki/X86_Assembly/Control_Flow and the book in general is very helpful
-
-#include <sstream>
-#include <algorithm>
-#include <iterator>
-#include <vector>
-#include <unordered_map>
-#include <list>
-#include <unordered_map>
-#include <xed-flag-enum.h>
-
-int insCount = 0;
-list<UINT32> addressTainted;
-list<REG> regsTainted;
-
-UINT32 EFLAGS;
-//INS last_instruction;
-//BOOL taintedCmp = false;
-
-// File for recording taint propagation
-ofstream CondBranchFile;
-ofstream FlagsFile;
-
-// CATEGORIES and ICLASSes to consider
-//XED_CATEGORY_CMOV all cond. move instructions
-
-/* ===================================================================== */
-/* Check instructions that modify EFLAGS                                 */
-/* ===================================================================== */
-// NOTE: this catches the initial change from EFLAGS is 0 to a valid EFLAGS, is it always 514?
-VOID ModifiesEflags(ADDRINT ins, string insDis, CONTEXT* context) {
-
-    UINT32 tmp_flags = PIN_GetContextReg(context, REG_EFLAGS);
-
-    //if (EFLAGS != tmp_flags && tmp_flags & XED_FLAG_df) {
-    if (EFLAGS != tmp_flags) {
-
-        // overflow, sign, zero, carry, and parity flags
-
-        if (tmp_flags & XED_FLAG_of) {
-            FlagsFile << insDis << ":\t" << PIN_GetContextReg(context, REG_EFLAGS) << endl;
-        }
-
-        EFLAGS = tmp_flags;
-    }
-}
-
-/* ===================================================================== */
-/* Check conditional branch instructions                                 */
-/* ===================================================================== */
-VOID ConditionalBranch(ADDRINT ins, INT32 branchTaken, string insDis) {
-
-    CondBranchFile << insDis << endl;
-}
-
-/*
-    // TODO PREDICATE_ZERO to get ZF == 0 or cases for all jumps and backsolve
-    //if (INS_Opcode(ins) == XED_ICLASS_JNZ) {
-        
-    //}
[…]

### 2014-03-24 Stubble/build.sh

@@ -2,5 +2,4 @@
 
 touch MyPinTool.cpp
 make PIN_ROOT=../pin/ CXX="g++ -std=c++0x"
-../pin/pin -t obj-ia32/MyPinTool.so -- ./a.out
 

### 2014-03-24 Stubble/clean.sh

@@ -4,5 +4,5 @@
 #rm -f buffer.out.*
 #cp fileLose.txt inputFile.txt
 #echo > taint/explored.0
-rm -f ./results/currentrun/*
+rm -f ./results/currentrun/*.out
 

### 2014-03-24 Stubble/handle_signals.py

@@ -1,17 +1,0 @@
-from subprocess import Popen, PIPE
-import signal
-
-# doesn't work, use Pin
-# Fork and wait for process
-#proc = Popen('./a.out', shell=True, stdout=PIPE, stderr=PIPE)
-proc = Popen(['../pin/pin', '-t', 'obj-ia32/MyPinTool.so', '--', './a.out'], shell=True, stdout=PIPE, stderr=PIPE)
-proc.wait()
-
-# Check return code of process
-returncode = proc.returncode - 128
-
-
-if returncode == signal.SIGSEGV:
-    print 'Segmentation Fault!'
-
-

### 2014-03-24 Stubble/libs/Stubble.h

@@ -18,44 +18,114 @@ int insCount = 0;
 list<UINT32> addressTainted;
 list<REG> regsTainted;
 
+/* Globals for Stubble */
 string results_dir = "./results/currentrun/";
 
-UINT32 EFLAGS;
-//INS last_instruction;
-//BOOL taintedCmp = false;
+// Array of registers to check for tainted writes
+REG registers[] = { REG_EDI, 
+                    REG_ESI, 
+                    REG_EBP, 
+                    REG_ESP, 
+                    REG_EDX, 
+                    REG_ECX, 
+                    REG_EBX, 
+                    REG_EAX,  
+                    REG_EFLAGS,
+                    REG_EIP,
+                    REG_AL, 
+                    REG_AH, 
+                    REG_AX, 
+                    REG_CL, 
+                    REG_CH, 
+                    REG_CX, 
+                    REG_DL, 
+                    REG_DH, 
+                    REG_DX, 
+                    REG_BL, 
+                    REG_BH, 
+                    REG_BX, 
+                    REG_BP, 
+                    REG_SI, 
+                    REG_DI, 
+                    REG_SP 
+                   };
 
 // File for recording taint propagation
 ofstream CondBranchFile;
-ofstream FlagsFile;
+ofstream TaintRegsFile;
+
+//INS last_instruction;
+//BOOL taintedCmp = false;
+
 
 // CATEGORIES and ICLASSes to consider
 //XED_CATEGORY_CMOV all cond. move instructions
 
-/* ===================================================================== */
-/* Check instructions that modify EFLAGS                                 */
-/* ===================================================================== */
-// NOTE: this catches the initial change from EFLAGS is 0 to a valid EFLAGS, is it always 514?
-VOID ModifiesEflags(ADDRINT ins, string insDis, CONTEXT* context) {
+/* Check each instruction to see if it modifies EFLAGS. 
+ * TODO Only catches if flag value changes. Ex, missed ZF=1->ZF=1 but now tainted.
+ */
+/* 
+VOID CheckEflags(ADDRINT ins, string insDis, CONTEXT* context) {
+
 
     UINT32 tmp_flags = PIN_GetContextReg(context, REG_EFLAGS);
 
[…]

### 2014-03-24 Stubble/libs/intercept_signals.h

@@ -54,12 +54,13 @@ ofstream SignalFile;
 
 /* ===================================================================== */
 
+
+// TODO print to 'signals.out', move signals.out to results/signals/signals.#
 BOOL intercept_signals(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, const EXCEPTION_INFO *pExceptInfo, VOID *v)
 {
-    SignalFile << "[INTERCEPTED]\t" << sig << endl;
-//print to 'signal.out', move signal.out to results/signals/signal.#
-    SignalFile << PIN_ExceptionToString(pExceptInfo) << endl;
 
+    SignalFile << "[INTERCEPTED]\t" << sig << endl;
+    SignalFile << PIN_ExceptionToString(pExceptInfo) << endl;
     return sig;
 }
 
@@ -67,10 +68,40 @@ BOOL intercept_signals(THREADID tid, INT32 sig, CONTEXT *ctxt, BOOL hasHandler, 
 VOID init_intercept_signals()
 {
 
-    SignalFile.open(results_dir + "signal.out");
+    SignalFile.open(results_dir + "signals.out");
 
-    // Intercept segfault, signal 11
-    PIN_InterceptSignal(11, intercept_signals, 0);
+    // Two signals we can't intercept, sigkill and sigstop
+    PIN_InterceptSignal(1, intercept_signals, 0);
+    PIN_InterceptSignal(2, intercept_signals, 0);
+    PIN_InterceptSignal(3, intercept_signals, 0);
+    PIN_InterceptSignal(4, intercept_signals, 0);
+    PIN_InterceptSignal(5, intercept_signals, 0);
+    PIN_InterceptSignal(6, intercept_signals, 0);
+    PIN_InterceptSignal(7, intercept_signals, 0);
+    PIN_InterceptSignal(8, intercept_signals, 0);
+    //PIN_InterceptSignal(9, intercept_signals, 0); // sigkill, can't handle
+    PIN_InterceptSignal(10, intercept_signals, 0);
+    PIN_InterceptSignal(11, intercept_signals, 0); // segfault
+    PIN_InterceptSignal(12, intercept_signals, 0);
+    PIN_InterceptSignal(13, intercept_signals, 0);
+    PIN_InterceptSignal(14, intercept_signals, 0);
+    PIN_InterceptSignal(15, intercept_signals, 0);
[…]

### 2014-03-24 Stubble/run.sh

@@ -1,0 +1,4 @@
+#!/bin/bash -x
+
+../pin/pin -t obj-ia32/MyPinTool.so -- ./a.out
+

### 2014-03-24 docs/paper/fsuthesis/thesis-template/paper.tex
help from bret with latex

@@
 \usepackage{pgfplots}
-%\usepackage{filecontents}
-%\usepackage{pgfplotstable}
-
-%\usepackage[latin1]{inputenc}
+
 \usetikzlibrary{shapes,arrows}
@@
   breakatwhitespace=true,
-  tabsize=3
+  tabsize=3,
+  xleftmargin=2em,
+  xrightmargin=2em,
+  numbersep=8pt
 }
@@
   sensitive=false,
+  basicstyle={\small\ttfamily},
   numbers=left,
@@
   morestring=[b]',
-  morestring=[b]"
+  morestring=[b]",
+  xleftmargin=2em,
+  xrightmargin=2em,
+  numbersep=8pt
 }
@@
 \manuscripttype{Thesis}              % [Thesis, Dissertation, Treatise]
-\degree{Masters of Science}                 
+\degree{Master of Science}                 
 \semester{Spring}                            % [Spring, Summer, Fall]
@@
 However, when no source code is available, fuzzing complex programs effectively can prove difficult, and as techniques become more sophisticated they require more resources and time.
-We present a technique, automated dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to improve fuzzers' code coverage, without resorting to heavyweight techniques like symbolic execution.
-We demonstrate this technique with a proof of concept fuzzer which explores paths in a binary to effectively reveal a secret, performing an oracle attack without an oracle.
+We present a technique, automated dynamic slice backsolving, which, to the best of our knowledge, represents a novel way to improve a black box fuzzer's code coverage, without resorting to heavyweight techniques like symbolic execution.
+We demonstrate this technique with a proof of concept fuzzer, Stubble, which implements our technique to explore paths in a binary and efficiently reveal a secret, performing an oracle attack without an oracle.
 Our approach requires no source code, no manual instrumentation, and no symbolic execution, and, as our results show, can reliably discover and explore new execution paths in a timely fashion.
-We believe dynamic slice backsolving represents a potentially strong complementary technique for modern fuzzers to implement.
-In addition, we plan to release and continue development on Stubble's DTA framework, since we not aware of many freely available and active projects.
+We believe dynamic slice backsolving presents a potentially strong complementary technique for modern fuzzers to implement.
 
@@
 After execution finishes, input test cases are mutated to reflect this new information, and a new execution test runs.
+This is made possible by a key observation regarding the x86 architecture, namely, that a small number of conditional branch instructions are influenced solely by a few flags in the EFLAGS register.
+By watching closely how taint propagates to these flags, we are able to deduce how to mutate user input.
 
@@
 Thus, for a subset of programs, we can determine not only the exact location of user input which determines a branch condition, but also generate precise values for both branch and non-branch cases.
+This is similar to symbolic execution, but without fussing with manual program instrumentation or conversion to an intermediate representation, as with KLEE [V].
 
@@
 Program input, output, and interesting conditions like segmentation fault signals are recorded during execution, and taint propagation is recorded from user input sources to branch sinks.
-When a tainted branch is found, stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
+When a tainted branch is found, Stubble automically backsolves the execution slice and generates a new test case which will drive the program down the opposite path explored in the current execution.
+Considering the distinct lack of black box dynamic taint analyzers, we plan to release Stubble as open source software.
 
@@
 
-%\chapter{Old-Abstract}
-
-% Dynamic taint analysis is difficult because taint can propagate directly via assignment, or indirectly via affecting control flows which affect assignment [D], which make proper implementation tricky.
-The path explosion problem arises from the nature of assembly languages.
-Jump instructions, which may make up a decent percentage of machine instructions in programs, each multiply the total number of existing paths in a binary by two.
-Considering the size of binaries, this quickly leads to an un-tenably large set of possible paths to explore via conventional techniques like symbolic execution.
-And even if it is possible to explore all paths in a binary, analysts still need sample input which can trigger the vulnerable condition, perhaps proving that the binary is exploitable along the way.
-Such automated exploit generation is the subject of much research [H, I].
-
-%This works similarly to a constraint solver, but constraint solving appears to be a traditional bottleneck, requiring generating symbolic input, usually in a different language like LLVM intermediate representation [V] and passing execution to the constraint solver.
-
-%We propose to avoid using a constraint solver entirely, and instead backsolve completely in memory.
-This is easier to implement than many of the clever optimizations used by S2E and could result in speedup over symbolic execution.
-
-%Because there are a finite number of conditional jumps, all of which depend on different flags or combinations of flags in the EFLAGS register, and a finite number of instructions that modify the EFLAGS register in x86, we can create cases for all possible ways jumps are decided.
-We only want to prove this is possible however, so we only implement a subset and instead comment on how to implement the other comparisons.
-
 \chapter{Background and Related Work}
@@
 
+\begin{figure}
 \begin{lstlisting}[style=jsstyle]
@@
 \end{lstlisting}
+\caption{TODO}
+\end{figure}
 
@@
 
+\begin{figure}
 \begin{lstlisting}[style=cstyle]
@@
 
+\begin{figure}
 % TODO label this
@@
 \end{tikzpicture}
+\caption{TODO label}
+\end{figure}
 
@@
 Consider the following example in Intel x86 assembly:
-
+\begin{figure}
 % x86 example
@@
 \end{lstlisting}
+\end{figure}
 
@@
 % Source: http://www.texample.net/tikz/examples/simple-flow-chart/
-
+\begin{figure}
 \begin{tikzpicture}[node distance = 2cm, auto]
@@
 
-\chapter{References}
-
-\begin{itemize}
-	\item [A] Bekrar, Sofia, et al. "A taint based approach for smart fuzzing." Software Testing, Verification and Validation (ICST), 2012 IEEE Fifth International Conference on. IEEE, 2012.
-	\item [B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with Evolutionary Fuzzing", BlackHat and Defcon 2007.
-	\item [C] Schwartz, E.J., Avgerinos, T., Brumley, D.
+% TODO when done, convert to bibtex
+\begin{references}
+	[A] Bekrar, Sofia, et al. "A taint based approach for smart fuzzing." Software Testing, Verification and Validation (ICST), 2012 IEEE Fifth International Conference on. IEEE, 2012.
+
+	[B] DeMott, J., Enbody, R., and Punch, W. "Revolutionizing the Field of Grey-box Attack Surface Testing with Evolutionary Fuzzing", BlackHat and Defcon 2007.
+
+	[C] Schwartz, E.J., Avgerinos, T., Brumley, D.
 "All You Ever Wanted to Know About Dynamic Taint Analysis and Forward Symbolic Execution (but might have been afraid to ask)." 2010 IEEE Symposium on Security and Privacy.
-	\item [D] Clause, J. Li, W., Orso, A. "Dytan: a generic dynamic taint analysis framework". 2007 Int'l symposium on Software testing and analysis. ACM, 2007.
-	\item [E] Ajit, Beng Heng Ng Earlence Fernandes, Aluri Atul Prakash, and David Rodriguez Velazquez Zijiang Yang. "Beyond Instruction Level Taint Propagation." (2013).
-	\item [F] Yamaguchi, Fabian, Felix Lindner, and Konrad Rieck.
+
+	[D] Clause, J. Li, W., Orso, A. "Dytan: a generic dynamic taint analysis framework". 2007 Int'l symposium on Software testing and analysis. ACM, 2007.
+
+	[E] Ajit, Beng Heng Ng Earlence Fernandes, Aluri Atul Prakash, and David Rodriguez Velazquez Zijiang Yang. "Beyond Instruction Level Taint Propagation." (2013).
+
+	[F] Yamaguchi, Fabian, Felix Lindner, and Konrad Rieck.
 "Vulnerability extrapolation: assisted discovery of vulnerabilities using machine learning." Proceedings of the 5th USENIX conference on Offensive technologies.
 USENIX Association, 2011.
-	\item [G] Bao, Tao, et al.
-"Strict control dependence and its effect on dynamic information flow analyses." Proceedings of the 19th international symposium on Software testing and analysis.
-ACM, 2010.
-	\item [H] Cha, Sang Kil, et al. "Unleashing mayhem on binary code." Security and Privacy (SP), 2012 IEEE Symposium on. IEEE, 2012.
-	\item [I] Avgerinos, Thanassis, et al. "AEG: Automatic Exploit Generation." NDSS. Vol. 11. 2011.
-	\item [J] Chipounov, Vitaly, Volodymyr Kuznetsov, and George Candea.
-"S2E: A platform for in-vivo multi-path analysis of software systems." ACM SIGARCH Computer Architecture News 39.1 (2011): 265-278.
-	\item [K] Bellard, Fabrice. "QEMU, a Fast and Portable Dynamic Translator." USENIX Annual Technical Conference, FREENIX Track. 2005.
-	\item [L] Guillon, Christophe. "Program Instrumentation with QEMU." 1st International QEMU Users’ Forum. 2011.
-	\item [M] Luk, Chi-Keung, et al. "Pin: building customized program analysis tools with dynamic instrumentation." Acm Sigplan Notices. Vol. 40. No. 6. ACM, 2005.
-	\item [N] Salwan, Jonathan. Shell-storm.org http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/
-	\item [O] King, James C. "Symbolic execution and program testing." Communications of the ACM 19.7 (1976): 385-394.
-	\item [P] De Moura, Leonardo, and Nikolaj Bjørner. "Z3: An efficient SMT solver." Tools and Algorithms for the Construction and Analysis of Systems. Springer Berlin Heidelberg, 2008. 337-340.
-	\item [Q] Godefroid, Patrice, Michael Y. Levin, and David Molnar. "Sage: Whitebox fuzzing for security testing." Queue 10.1 (2012): 20.
-	\item [R] Ma, Kin-Keung, et al. "Directed symbolic execution." Static Analysis. Springer Berlin Heidelberg, 2011. 95-111.
-	\item [S] Boyer, Robert S., Bernard Elspas, and Karl N. Levitt. "SELECT—a formal system for testing and debugging programs by symbolic execution." ACM SigPlan Notices. Vol. 10. No. 6. ACM, 1975.
-	\item [T] Wang, Tielei, et al. "Checksum-aware fuzzing combined with dynamic taint analysis and symbolic execution." ACM Transactions on Information and System Security (TISSEC) 14.2 (2011): 15.
-	\item [U] Cadar, Cristian, and Koushik Sen. "Symbolic execution for software testing: three decades later." Communications of the ACM 56.2 (2013): 82-90.
-	\item [V] Cadar, Cristian, Daniel Dunbar, and Dawson R. Engler. "KLEE: Unassisted and Automatic Generation of High-Coverage Tests for Complex Systems Programs." OSDI. Vol. 8. 2008.
-	\item [W] McCamant, Stephen, et al. Transformation-aware symbolic execution for system test generation. Tech. Rep. UCB/EECS-2013-125, University of California, Berkeley (Jun 2013), 2013.
-	\item [X] Majumdar, Rupak, and Koushik Sen. "Hybrid concolic testing." Software Engineering, 2007. ICSE 2007. 29th International Conference on. IEEE, 2007.
-	\item [Y] Sen, Koushik, Darko Marinov, and Gul Agha. CUTE: a concolic unit testing engine for C. Vol. 30. No. 5. ACM, 2005.
-	\item [Z] Eddington, Michael. "Peach fuzzing platform." Peach Fuzzer (2011).
-	\item [AA] Zhang, Xiangyu, Rajiv Gupta, and Youtao Zhang. "Precise dynamic slicing algorithms." Software Engineering, 2003. Proceedings. 25th International Conference on. IEEE, 2003.
-	\item [AB] Wang, Tielei, et al. "TaintScope: A checksum-aware directed fuzzing tool for automatic software vulnerability detection." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
-	\item [AC] Sen, Koushik. "Concolic testing." Proceedings of the twenty-second IEEE/ACM international conference on Automated software engineering. ACM, 2007.
-	\item [AD] Saxena, Prateek, et al. "A symbolic execution framework for javascript." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
-	\item [AE] Mozilla Developer Network. https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global\_Objects/eval
-	\item [AF] The WebKit Open Source Project. http://www.webkit.org/
-	\item [AG] Portokalidis, Georgios, Asia Slowinska, and Herbert Bos.
+
+	[G] Bao, Tao, et al. "Strict control dependence and its effect on dynamic information flow analyses." Proceedings of the 19th international symposium on Software testing and analysis. ACM, 2010.
+
+	[H] Cha, Sang Kil, et al. "Unleashing mayhem on binary code." Security and Privacy (SP), 2012 IEEE Symposium on. IEEE, 2012.
+
+	[I] Avgerinos, Thanassis, et al. "AEG: Automatic Exploit Generation." NDSS. Vol. 11. 2011.
+
+	[J] Chipounov, Vitaly, Volodymyr Kuznetsov, and George Candea. "S2E: A platform for in-vivo multi-path analysis of software systems." ACM SIGARCH Computer Architecture News 39.1 (2011): 265-278.
+
+	[K] Bellard, Fabrice. "QEMU, a Fast and Portable Dynamic Translator." USENIX Annual Technical Conference, FREENIX Track. 2005.
+
+	[L] Guillon, Christophe. "Program Instrumentation with QEMU." 1st International QEMU Users’ Forum. 2011.
+
+	[M] Luk, Chi-Keung, et al. "Pin: building customized program analysis tools with dynamic instrumentation." Acm Sigplan Notices. Vol. 40. No. 6. ACM, 2005.
+
+	[N] Salwan, Jonathan. Shell-storm.org http://shell-storm.org/blog/Taint-analysis-and-pattern-matching-with-Pin/
+
+	[O] King, James C. "Symbolic execution and program testing." Communications of the ACM 19.7 (1976): 385-394.
+
+	[P] De Moura, Leonardo, and Nikolaj Bjørner. "Z3: An efficient SMT solver." Tools and Algorithms for the Construction and Analysis of Systems. Springer Berlin Heidelberg, 2008. 337-340.
+
+	[Q] Godefroid, Patrice, Michael Y. Levin, and David Molnar. "Sage: Whitebox fuzzing for security testing." Queue 10.1 (2012): 20.
+
+	[R] Ma, Kin-Keung, et al. "Directed symbolic execution." Static Analysis. Springer Berlin Heidelberg, 2011. 95-111.
+
+	[S] Boyer, Robert S., Bernard Elspas, and Karl N. Levitt. "SELECT—a formal system for testing and debugging programs by symbolic execution." ACM SigPlan Notices. Vol. 10. No. 6. ACM, 1975.
+
+	[T] Wang, Tielei, et al. "Checksum-aware fuzzing combined with dynamic taint analysis and symbolic execution." ACM Transactions on Information and System Security (TISSEC) 14.2 (2011): 15.
+
+	[U] Cadar, Cristian, and Koushik Sen. "Symbolic execution for software testing: three decades later." Communications of the ACM 56.2 (2013): 82-90.
+
+	[V] Cadar, Cristian, Daniel Dunbar, and Dawson R. Engler. "KLEE: Unassisted and Automatic Generation of High-Coverage Tests for Complex Systems Programs." OSDI. Vol. 8. 2008.
+
+	[W] McCamant, Stephen, et al. Transformation-aware symbolic execution for system test generation. Tech. Rep. UCB/EECS-2013-125, University of California, Berkeley (Jun 2013), 2013.
+
+	[X] Majumdar, Rupak, and Koushik Sen. "Hybrid concolic testing." Software Engineering, 2007. ICSE 2007. 29th International Conference on. IEEE, 2007.
+
+	[Y] Sen, Koushik, Darko Marinov, and Gul Agha. CUTE: a concolic unit testing engine for C. Vol. 30. No. 5. ACM, 2005.
+
+	[Z] Eddington, Michael. "Peach fuzzing platform." Peach Fuzzer (2011).
+
+	[AA] Zhang, Xiangyu, Rajiv Gupta, and Youtao Zhang. "Precise dynamic slicing algorithms." Software Engineering, 2003. Proceedings. 25th International Conference on. IEEE, 2003.
+
+	[AB] Wang, Tielei, et al. "TaintScope: A checksum-aware directed fuzzing tool for automatic software vulnerability detection." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
+
+	[AC] Sen, Koushik. "Concolic testing." Proceedings of the twenty-second IEEE/ACM international conference on Automated software engineering. ACM, 2007.
+
+	[AD] Saxena, Prateek, et al. "A symbolic execution framework for javascript." Security and Privacy (SP), 2010 IEEE Symposium on. IEEE, 2010.
+
+	[AE] Mozilla Developer Network. https://developer.mozilla.org/en-US/docs/Web/JavaScript/Reference/Global\_Objects/eval
+
+	[AF] The WebKit Open Source Project. http://www.webkit.org/
+
+	[AG] Portokalidis, Georgios, Asia Slowinska, and Herbert Bos.
 "Argos: an emulator for fingerprinting zero-day attacks for advertised honeypots with automatic signature generation." ACM SIGOPS Operating Systems Review.
@@
 ACM, 2006.
-	\item [AH] Rescue, Data. "IDA Pro Disassembler." 2006-10-20). http://www. datarescue. com/idabase.
-	\item [AI] Garg, Sanjam, et al.
+
+	[AH] Rescue, Data. "IDA Pro Disassembler." 2006-10-20). http://www. datarescue. com/idabase.
+
+	[AI] Garg, Sanjam, et al.
 "Candidate indistinguishability obfuscation and functional encryption for all circuits." Foundations of Computer Science (FOCS), 2013 IEEE 54th Annual Symposium on.
 IEEE, 2013.
-	\item [AJ] Oehlert, Peter. "Violating assumptions with fuzzing." Security \& Privacy, IEEE 3.2 (2005): 58-62.
-	\item [AK] Gilmore, John, and Sten Shebs. "GDB internals—a guide to the internals of the GNU debugger." Found in the doc directory of gdb distribution version 5.1 (2000).
-	\item [AL] Bruening, Derek, and Qin Zhao. "DynamoRIO."	
-	\item [AM] http://googleonlinesecurity.blogspot.com/2011/08/fuzzing-at-scale.html
-	\item [AN] http://www.pwn2own.com/, http://www.pwn2own.com/2014/03/pwn2own-2014-lineup/
-	\item [AO] http://www.forbes.com/sites/andygreenberg/2012/03/23/shopping-for-zero-days-an-price-list-for-hackers-secret-software-exploits/
-	\item [AP] Braden, R., Borman, D., and C. Partridge, "Computing the Internet checksum", RFC 1071, September 1988.
-	\item [AQ] Bossert, Georges, Frédéric Guihéry, and Guillaume Hiet.
+
+	[AJ] Oehlert, Peter. "Violating assumptions with fuzzing." Security \& Privacy, IEEE 3.2 (2005): 58-62.
+
+	[AK] Gilmore, John, and Sten Shebs. "GDB internals—a guide to the internals of the GNU debugger." Found in the doc directory of gdb distribution version 5.1 (2000).
+
+	[AL] Bruening, Derek, and Qin Zhao. "DynamoRIO."
+
+	[AM] http://googleonlinesecurity.blogspot.com/2011/08/fuzzing-at-scale.html
+
+	[AN] http://www.pwn2own.com/, http://www.pwn2own.com/2014/03/pwn2own-2014-lineup/
+
+	[AO] http://www.forbes.com/sites/andygreenberg/2012/03/23/shopping-for-zero-days-an-price-list-for-hackers-secret-software-exploits/
+
+	[AP] Braden, R., Borman, D., and C. Partridge, "Computing the Internet checksum", RFC 1071, September 1988.
+
+	[AQ] Bossert, Georges, Frédéric Guihéry, and Guillaume Hiet.
 "Netzob: un outil pour la rétro-conception de protocoles de communication." Actes du Symposium sur la sécurité des technologies de l'information et des communications.
@@
 
-\end{itemize}
+\end{references}
 

### 2014-03-24 Stubble/driver.py
thinking through DTA

@@ -1,134 +1,0 @@
-# Driver to decide how to mutate
-
-import os, shutil
-import subprocess
-from operator import itemgetter
-
-seed_value = ('0', '0', '0')
-
-def test(inputFile, taintFile, seed = seed_value):
-
-    # First time, don't mutate
-    if seed != seed_value:
-        mutate(inputFile, seed)
-    else:
-        print('Initial run')
-    
-    # command for subprocess, pintool
-    cmd =   [   
-        '../pin/pin', 
-        '-t', 'obj-ia32/MyPinTool.so', 
-        #'--', '../vulnerable_programs/trivial/a.out', inputFile
-        #'--', './a.out', inputFile
-        #'--', './simpleCrackme', inputFile
-        #'--', './simpleCrackme2', inputFile
-        '--', './simpleCrackme50', inputFile
-        #'--', './strcpy', inputFile
-        #'--', 'ls'
-    ]
-
-    # Which test are we running? 
-    testNumber = getTestNumber('./taint/')
-    print 'Running test #' + str(testNumber), 'based on mutation seed', seed, '...' 
-
-    # One iteration of pintool, generates new (input.txt, taint.out) pair
-    outputFile = open('./file.out', 'w')
-    p1 = subprocess.Popen(cmd, stdout=outputFile)
-    p1.wait()
-
-    # Find which taint are new
-    # input -> input/ and mutated
-    # taint -> taint/
-    explored        =   open('./taint/explored.0', 'r').read().split()
-    exploredFile    =   open('./taint/explored.0', 'a')
-    taint           =   open(taintFile, 'r').read().split()
-
-    newTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in taint}
-    exploredTaintDict = {i.split(':')[0]: i.split(':')[1:] for i in explored}
-
-    # Set difference
-    newTaint = {x: newTaintDict[x] for x in newTaintDict if x not in exploredTaintDict.keys()} 
-
-    # Copy taint and append latest taint to explored
-    recordResults(inputFile, outputFile, newTaint, seed, testNumber) 
-    exploredFile.write(':'.join(seed) + "\n")
-
-    # file in format pos:op:arg1:arg2
-    toExplore = [(r, newTaint[r][0], newTaint[r][1]) for r in newTaint]
-
-    toExplore = sorted(toExplore, key=itemgetter(0))
-    return toExplore
-
-# End test
-
-# TODO will need to handle non-character cases for seed[1]
[…]

### 2014-03-24 Stubble/libs/Stubble.h

@@ -4,25 +4,31 @@
 // Stubble.h
 // http://en.wikibooks.org/wiki/X86_Assembly/Control_Flow and the book in general is very helpful
 
+#include <iomanip>
 #include <sstream>
 #include <string>
 #include <algorithm>
-#include <iterator>
+#include <tuple>
+#include <unordered_map>
 #include <vector>
-#include <unordered_map>
-#include <list>
-#include <unordered_map>
-#include <xed-flag-enum.h>
-
-int insCount = 0;
-list<UINT32> addressTainted;
-list<REG> regsTainted;
+//#include <xed-flag-enum.h>
 
 /* Globals for Stubble */
 string results_dir = "./results/currentrun/";
+int UNTAINTED = -1;
+
+// Tainted Registers and Memory
+typedef unordered_map<string, tuple<UINT32, string> > taint_ds;
+taint_ds tainted_registers;
+// TODO make registers an enumerated array of tuple(byteLocation, fileName), if untainted byteLocation = -1
+taint_ds tainted_memory;
+
+
 
 // Array of registers to check for tainted writes
-REG registers[] = { REG_EDI, 
+REG registers[] = { 
+                    REG_EFLAGS,
+                    REG_EDI, 
                     REG_ESI, 
                     REG_EBP, 
                     REG_ESP, 
@@ -30,7 +36,6 @@ REG registers[] = { REG_EDI,
                     REG_ECX, 
                     REG_EBX, 
                     REG_EAX,  
-                    REG_EFLAGS,
                     REG_EIP,
                     REG_AL, 
                     REG_AH, 
@@ -53,6 +58,7 @@ REG registers[] = { REG_EDI,
 // File for recording taint propagation
 ofstream CondBranchFile;
 ofstream TaintRegsFile;
+ofstream EflagsFile;
 
 //INS last_instruction;
 //BOOL taintedCmp = false;
@@ -61,45 +67,11 @@ ofstream TaintRegsFile;
 // CATEGORIES and ICLASSes to consider
 //XED_CATEGORY_CMOV all cond. move instructions
 
-/* Check each instruction to see if it modifies EFLAGS. 
- * TODO Only catches if flag value changes. Ex, missed ZF=1->ZF=1 but now tainted.
- */
-/* 
-VOID CheckEflags(ADDRINT ins, string insDis, CONTEXT* context) {
-
-
[…]

### 2014-03-25 Stubble/libs/Stubble.h
starting to look like a cluster. need to code when less tired

@@ -4,6 +4,8 @@
 // Stubble.h
 // http://en.wikibooks.org/wiki/X86_Assembly/Control_Flow and the book in general is very helpful
 
+#include "syscalls.h"
+#include "intercept_signals.h"
 #include <iomanip>
 #include <sstream>
 #include <string>
@@ -17,11 +19,9 @@
 string results_dir = "./results/currentrun/";
 int UNTAINTED = -1;
 
-// Tainted Registers and Memory
-typedef unordered_map<string, tuple<UINT32, string> > taint_ds;
-taint_ds tainted_registers;
+// Tainted Registers
 // TODO make registers an enumerated array of tuple(byteLocation, fileName), if untainted byteLocation = -1
-taint_ds tainted_memory;
+unordered_map<string, tuple<UINT32, string> > tainted_registers;
 
 
 
@@ -60,10 +60,6 @@ ofstream CondBranchFile;
 ofstream TaintRegsFile;
 ofstream EflagsFile;
 
-//INS last_instruction;
-//BOOL taintedCmp = false;
-
-
 // CATEGORIES and ICLASSes to consider
 //XED_CATEGORY_CMOV all cond. move instructions
 
@@ -86,6 +82,11 @@ ofstream EflagsFile;
         */
 //Calls taintReg(reg) VOID ReadMem(UINT32 insAddr, std::string insDis, UINT32 opCount, REG reg_r, UINT32 memOp, UINT32 sp)
 
+// Handles taint tracking for EFLAGS register's carry/overflow/parity/sign/zero flags
+VOID taint_eflags()
+{
+
+}
 
 // When tainted data is written to a register
 //      1) Record in TaintRegsFile
